---
title: "Out-of-Sample Reweighting to the 69-Student Pool: Composition and Productivity"
subtitle: "Real student demographics; fixed-behavior (composition) channel; 8B house style"
date: "`r format(Sys.time(), '%d %b %Y')`"
output:
  pdf_document: { number_sections: true, latex_engine: pdflatex }
geometry: margin=0.8in
header-includes: \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```

We take the measured non-blind demographic biases and apply them to the true 69-student pool (real demographics, real productivity), simulating blind vs non-blind selection at each hiring cutoff K. Behavior is held fixed (composition channel); this documents how blinding reshapes *who* is hired and whether that moves *productivity*.

# Compositional changes: who gets hired

```{r comp, fig.width=9.5, fig.height=8.5, out.width="100%", fig.align="center"}
print(figComp)
```

Blinding removes the non-blind premia/penalties, so it mechanically reshuffles the demographic composition of hires (e.g., groups that were penalized when identified gain; groups that were given a premium lose). This mirrors the in-sample composition result, now on the real applicant pool.

# Treatment effect on productivity

```{r prod, fig.width=9, fig.height=4.2, out.width="100%", fig.align="center"}
print(figProd)
```

Despite the compositional reshuffle, the effect on the true productivity of the hired cohort is null across the entire hiring margin, in both stages. The composition channel moves *who* is hired without moving *how productive* they are --- because the biases are modest and demographic identity carries little productivity information beyond the visible signals.

# Caveats

Calibration, not estimation: behavior held fixed (statistical-discrimination channel deferred); s(X) extrapolated from 18 profiles; bands are simulation-based (evaluator-clustered); the 69 pool is Berkeley-CS (79\% Asian, with rare Hispanic-female / White-female cells, so those group panels are noisy).
