---
title: "7_Descriptive"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}  
  - \usepackage{float}  
  - \usepackage{placeins}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r fix_unicode_error, include=FALSE}

## Fix Unicode Errors

  #### Clean characters: Remove ALL non-ASCII characters (including U+0080, U+0099, etc.)
  firm_dt_cleaned <- lapply(firm_dt, function(x) {
    if (is.character(x)) {
      # iconv with sub="" removes any character that doesn't fit in standard ASCII
      return(iconv(x, "UTF-8", "ASCII", sub = ""))
    }
    return(x)
  })

  #### Restore data.table status so := works in your next chunk
  setDT(firm_dt_cleaned)

  #### Replace the original object
  firm_dt <- firm_dt_cleaned
  
rm(firm_dt_cleaned)

```



<!-- +++++ ++++++ ++++++ Part 1: Counts +++++ ++++++ ++++++ -->


# Counts

```{r counts, echo=FALSE}

##### ##### Counts by Role and Treatment ##### #####

table_counts <- addmargins(xtabs(~ role + treat, data = firm_dt), 2)

kable(table_counts, format = "latex", booktabs = TRUE,
      caption = "Counts by Role and Treatment") %>%
  kable_styling(latex_options = "HOLD_position")

rm(table_counts)


##### ##### Counts by Versions ##### #####

table_counts_ver <- xtabs(~ role + resume_ver, data = firm_dt)

kable(
  table_counts_ver,
  format = "latex",
  booktabs = TRUE,
  caption = "Counts by Versions") %>%
  kable_styling(latex_options = "HOLD_position")

rm(table_counts_ver)


##### ##### BH: Matched Pairs ##### #####

table_counts_arms <- addmargins(xtabs(~ arm + resume_ver_eng, data = matching_crosswalk),2)

kable(
  table_counts_arms[, c(9)],
  format = "latex",
  booktabs = TRUE,
  col.names = "Number of Pairs",
  caption = "Counts by Matched Pairs") %>%
  kable_styling(latex_options = "HOLD_position")

rm(table_counts_arms)

```

\newpage
## Distribution and Response Rate (Completed / Emailed)

```{r distribution, echo = FALSE}

# Total Email Count (Excluding Bounced)
paste("Number of Emails Addresses Survey was Distributed to (not counting bounced emails):", uniqueN(qualtrics_distribution_dt[!`Status` %in% c("Email Hard Bounce", "Email Soft Bounce", "Email Failed"), `Email Address`]))

# Response Rate (Finished)
status_priority <- c("Survey Finished" = 1, "Survey Partially Finished" = 2, "Survey Started" = 3,
                      "Survey Reopened" = 4, "Session Expired" = 5, "Email Blocked" = 6,
                      "Email Opened" = 7, "Email Sent" = 8)

paste("Response Rate (%): ", round(uniqueN(qualtrics_distribution_dt[!`Status` %in% c("Email Hard Bounce", "Email Soft Bounce", "Email Failed")][, priority := status_priority[`Status`]][order(priority)][!duplicated(`Email Address`)] [, priority := NULL][`Status` == "Survey Finished", `Email Address`]) / uniqueN(qualtrics_distribution_dt[!`Status` %in% c("Email Hard Bounce", "Email Soft Bounce", "Email Failed"), `Email Address`]) * 100, 2))

rm(status_priority)

```



\newpage
<!-- +++++ ++++++ ++++++ Part 2: Demographics +++++ ++++++ ++++++ -->

# Participant Demographics

## Summary Table

```{r demo_table, echo = FALSE, results = 'asis'}

## Set global option to prevent tinytable/siunitx issues
options("modelsummary_format_numeric_latex" = "plain")
options(modelsummary_factory_latex = "kableExtra")

## Variables that needs to be converted from proportion to percentage
pct_cols <- c("resp_female", "resp_male", "resp_nonbinaryother",
              "resp_white", "resp_asian", "resp_hispanic", "resp_black", "resp_raceother",
              "resp_educ_uniabove",
              "resp_income_100ormore",
              "ucb_yes",
              "firm_size_small", "firm_size_mid", "firm_size_large",
              "ats_yes", "bh_race", "bh_gender",
              "currentlyhiring_yes",
              "IRR_ever")

## Generate Descriptive Table
modelsummary::datasummary(
  (`Age` = resp_age) +
    (`Gender: Female (%)` = resp_female) +
    (`Gender: Male (%)` = resp_male) +
    (`Gender: Non-binary / Other (%)` = resp_nonbinaryother) +
    (`Race: White (%)` = resp_white) +
    (`Race: Asian (%)` = resp_asian) +
    (`Race: Hispanic (%)` = resp_hispanic) +
    (`Race: Black (%)` = resp_black) +
    (`Race: Other (%)` = resp_raceother) +
    (`Edu: Have college degree (%)` = resp_educ_uniabove) +
    (`Exp: No. Years at Current Firm` = s2_firm_howlong_in_years) +
    (`Exp: No. Years Recruiting`= s4_recruiting_in_years) +
    (`Exp: Interacted with UCB CS Student (%)` = ucb_yes) +
    (`Firm Size: Less than 100 (%)` = firm_size_small) +
    (`Firm Size: 100 ~ 999 (%)` = firm_size_mid) +
    (`Firm Size: More than 1000 (%)` = firm_size_large) +
    (`Firm Hiring Policy: Uses ATS (%)` = ats_yes) +
    (`Firm Hiring Policy: Blinds Race (%)` = bh_race)  +
    (`Firm Hiring Policy: Blinds Gender (%)` = bh_gender) +
    (`IRR: Firm Currently Hiring (%)` = currentlyhiring_yes) +
    (`IRR: Wants to be Matched to UCB CS Candidate (%)` = IRR_ever) ~
     mean * role,
  data = copy(firm_dt)[, (pct_cols) := lapply(.SD, function(x) x * 100), .SDcols = pct_cols],
  title = "Participant Demographics",
  fmt = 1,
  output = "kableExtra") %>%
  kable_styling(latex_options = c("scale_down", "HOLD_position")) %>%
  # Use pack_rows to create your Panels A and B
  pack_rows("Panel A: Individual Characteristics", 1, 13) %>%
  pack_rows("Panel B: Firm Characteristics", 14, 21)

rm(pct_cols)
```

\newpage
## Primary Industry

```{r demo_firm_industry, echo = FALSE, results = 'asis'}

##### ##### Prep: Industry ##### #####

industry_dict <- c(
  "1" = "Accounting",
  "2" = "Advertising",
  "3" = "Agriculture/Fishing",
  "4" = "Architecture",
  "5" = "Automotive",
  "6" = "Aviation",
  "7" = "Banking/Financial",
  "8" = "Bio-Tech",
  "9" = "Brokerage",
  "10" = "Carpentry/Electrical installations",
  "11" = "Chemicals/Plastics/Rubber",
  "12" = "Communications/Information",
  "13" = "Computer Hardware",
  "14" = "Computer Reseller (software/hardware)",
  "15" = "Computer Software",
  "16" = "Construction",
  "17" = "Consulting",
  "18" = "Consumer Electronics",
  "19" = "Consumer Packaged Goods",
  "20" = "Education",
  "21" = "Energy/Utilities/Oil and Gas",
  "22" = "Engineering",
  "23" = "Environmental Services",
  "24" = "Fashion/Apparel",
  "25" = "Food/Beverage",
  "26" = "Government/Public Sector",
  "27" = "Healthcare",
  "28" = "Hospitality/Tourism",
  "29" = "Human Resources",
  "30" = "Information Technology/IT",
  "31" = "Insurance",
  "32" = "Internet",
  "33" = "Legal/Law",
  "34" = "Manufacturing",
  "35" = "Marketing",
  "36" = "Market Research",
  "37" = "Media/Entertainment",
  "38" = "Military",
  "39" = "Non Profit/Social services",
  "40" = "Personal Services",
  "41" = "Pharmaceuticals",
  "42" = "Printing/Publishing",
  "43" = "Public Relations",
  "44" = "Real Estate/Property",
  "45" = "Retail/Wholesale trade",
  "46" = "Sales",
  "47" = "Security",
  "48" = "Shipping/Distribution",
  "49" = "Telecommunications",
  "50" = "Transportation",
  "96" = "Other (write-in)"
)

## Industries (HR Only)
table_hr <- firm_dt[role == "HR", .N, by = .(s2_firm_industry)][order(-N)]
table_hr[, Industry := industry_dict[as.character(s2_firm_industry)]]
table_hr <- table_hr[order(Industry == "Other (write-in)", -N), .(Industry, N)]

## Industries (Engineer Only)
table_eng <- firm_dt[role == "Eng", .N, by = .(s2_firm_industry)][order(-N)]
table_eng[, Industry := industry_dict[as.character(s2_firm_industry)]]
table_eng <- table_eng[order(Industry == "Other (write-in)", -N), .(Industry, N)]

# 1. Create a row index to facilitate a side-by-side merge
table_hr[, row_id := .I]
table_eng[, row_id := .I]

# 2. Outer join the two tables on the row index to align them perfectly
combined_industry <- merge(table_hr, table_eng, by = "row_id", all = TRUE, suffixes = c("_hr", "_eng"))

# 3. Clean up: Remove the ID and replace NA values with empty strings/blank space
combined_industry[, row_id := NULL]
combined_industry[is.na(Industry_hr), Industry_hr := ""]
combined_industry[is.na(Industry_eng), Industry_eng := ""]

# 4. Produce a single table with four columns
combined_industry %>%
  kbl(format = "latex", 
      booktabs = TRUE, 
      align = "lrlr", 
      col.names = c("HR Professionals", "N", "Software Engineers", "N"),
      caption = "Industry Distribution (Self-Reported)") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"))

rm(industry_dict, table_hr, table_eng, combined_industry)

```

\newpage
## Coding Lanugages (Python and Java)
Note: Of 18 candidates presented, 16 tested in Python, an 2 tested in Java

```{r demo_coding_language, echo = FALSE, results = 'asis'}

temp_dt <- firm_dt[role == "Eng", .(resp_java, resp_python)]
invisible(temp_dt[, eng_versed := fifelse(resp_python == 1 & resp_java == 1, "Both",
                                          fifelse(resp_python == 1 & resp_java == 0, "Python Only",
                                                  fifelse(resp_python == 0 & resp_java == 1, "Java Only",
                                                          fifelse(resp_python == 0 & resp_java == 0, "Neither", NA_character_))))])

temp_dt[, eng_versed := factor(eng_versed, levels = c("Both", "Python Only", "Java Only", "Neither"))]

temp_dt <- temp_dt %>%
  count(eng_versed) %>%
  arrange(eng_versed) %>%
  mutate(
    proportion = n / sum(n),
    percent_label = paste0(eng_versed, "\n", scales::percent(proportion))
  )


ggplot(temp_dt, aes(x = fct_rev(eng_versed), y = proportion, fill = eng_versed)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = scales::percent(proportion)), hjust = -0.1, size = 4) +
  coord_flip() +
  scale_y_continuous(labels = scales::percent, expand = expansion(mult = c(0, 0.15))) +
  theme_minimal() +
  labs(x = NULL, y = NULL, title = "Proportion of Engineers Qualified to Evaluate in Python & Java")

rm(temp_dt)

```

\newpage
## Position Hiring For

```{r positions_hiring, echo = FALSE, fig.width = 10, fig.height = 6}

# Job Labels
job_labels <- c(
  "1" = "AI Engineer", 
  "2" = "Back-End Developer", 
  "3" = "Blockchain Developer",
  "4" = "Computer Hardware Engineer", 
  "5" = "Cloud Engineer", 
  "6" = "Front-End Developer",
  "7" = "Full-Stack Developer", 
  "8" = "Information Security Analyst",
  "9" = "Machine Learning Engineer", 
  "10" = "Mobile App Developer",
  "11" = "Network Engineer",
  "12" = "Project Manager", 
  "13" = "Software Developer/Engineer",
  "14" = "System Architect",
  "15" = "Web Designer",
  "16" = "UX Designer",
  "17" = "Video Game Developer"
)

# Function to create job summary and plot
plot_jobs_by_role <- function(dt, role_name) {
  job_cols <- paste0("job_", 1:17)
  job_summary <- data.table(
    job_name = job_labels[as.character(1:17)],
    count = dt[role == role_name, sapply(.SD, sum, na.rm = TRUE), .SDcols = job_cols]
  )
  job_summary[, job_name := factor(job_name, levels = rev(job_labels))]
  
  ggplot(job_summary, aes(x = job_name, y = count)) +
    geom_col(fill = "steelblue") +
    geom_text(aes(label = count), hjust = -0.1, size = 3.5) +
    coord_flip() +
    scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
    theme_minimal() +
    labs(x = NULL, y = "Count", title = paste0("(",role_name, ") Hiring"))
}

p_hr <- plot_jobs_by_role(firm_dt, "HR")
p_eng <- plot_jobs_by_role(firm_dt, "Eng")

combined_plot <- p_hr + p_eng
print(combined_plot)

rm(job_labels, plot_jobs_by_role, p_hr, p_eng, combined_plot)  
```



\newpage
## Residence Location

```{r location, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', out.width='100%'}

## HR and Engineer Residence Locations

  #### Extract 5 Digit Zip Code
  df_zip <- firm_dt %>%
    mutate(zip5 = str_extract(as.character(s6_address_5), "\\d{5}")) %>%
    filter(!is.na(zip5)) %>%
    distinct(zip5)
  
  #### Lookup to States
  zip_crosswalk <- zipcodeR::reverse_zipcode(df_zip$zip5) %>%
    select(zip5 = zipcode, state_name = state) %>%
    # Get FIPS codes by joining with a standard state lookup
    left_join(
      tigris::states(cb = TRUE) %>% st_drop_geometry() %>% select(state_fips = STATEFP, state_name = STUSPS),
      by = "state_name"
    )
  
  #### Merge in State FIPs code to firm_dt
  firm_dt <- firm_dt %>%
    mutate(zip5 = str_extract(as.character(s6_address_5), "\\d{5}")) %>%
    left_join(zip_crosswalk %>% select(zip5, state_fips), by = "zip5") %>%
    as.data.table()

  #### Aggregate counts by state and role
  hr_state_counts <- firm_dt[role == "HR" & !is.na(state_fips), count := .N, by = state_fips][role == "HR" & !is.na(state_fips), .(state_fips, count)]
  eng_state_counts <- firm_dt[role == "Eng" & !is.na(state_fips), count := .N, by = state_fips][role == "Eng" & !is.na(state_fips), .(state_fips, count)]
  missing_hr  <- firm_dt[role == "HR" & is.na(state_fips), .N]
  missing_eng <- firm_dt[role == "Eng" & is.na(state_fips), .N]
  
  #### Get state geometries (contiguous US)
  hr_states_sf <- tigris::states(cb = TRUE, year = 2023, class = "sf") %>%
    filter(!(STATEFP %in% c("02","15","72","60","66","69","78"))) %>%
    left_join(hr_state_counts, by = c("STATEFP" = "state_fips")) %>%
    mutate(count = replace_na(count, 0))

  eng_states_sf <- tigris::states(cb = TRUE, year = 2023, class = "sf") %>%
    filter(!(STATEFP %in% c("02","15","72","60","66","69","78"))) %>%
    left_join(eng_state_counts, by = c("STATEFP" = "state_fips")) %>%
    mutate(count = replace_na(count, 0))
  
  #### Output Choropleth Map
  hr_state_choropleth <- ggplot(hr_states_sf) +
    geom_sf(aes(fill = count), color = "white", size = 0.2) +
    scale_fill_viridis_c(
      option = "plasma", 
      name = "N",
      na.value = "grey95",
      guide = guide_colorbar(barwidth = 0.5, barheight = 3, title.position = "top")
    ) +
    coord_sf(expand = FALSE) +
    labs(
      title = "HR",
      caption = paste0("Total N = ", sum(unique(hr_states_sf)$count), " (Missing Zip = ", missing_hr, ")")
    ) +
    theme_minimal() +
    theme(
      legend.position = "right",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank()
    )
  
  eng_state_choropleth <- ggplot(eng_states_sf) +
    geom_sf(aes(fill = count), color = "white", size = 0.2) +
    scale_fill_viridis_c(
      option = "plasma", 
      name = "N",
      na.value = "grey95",
      guide = guide_colorbar(barwidth = 0.5, barheight = 3, title.position = "top")
    ) +
    coord_sf(expand = FALSE) +
    labs(
      title = "Engineers",
      caption = paste0("Total N = ", sum(unique(eng_states_sf)$count), " (Missing Zip = ", missing_eng, ")")
    ) +
    theme_minimal() +
    theme(
      legend.position = "right",
      plot.title = element_text(hjust = 0.5, face = "bold"),
      plot.subtitle = element_text(hjust = 0.5),
      axis.text = element_blank(),
      axis.ticks = element_blank(),
      panel.grid = element_blank()
    )

(hr_state_choropleth | eng_state_choropleth) + plot_annotation(title = "Respondent Residence Locations", 
                             theme = theme(plot.title = element_text(hjust = 0.5, size = 16, face = "bold")))

rm(df_zip,zip_crosswalk, hr_state_counts, eng_state_counts, hr_states_sf, eng_states_sf, missing_hr, missing_eng, 
   hr_state_choropleth, eng_state_choropleth)

```



<!-- +++++ ++++++ ++++++ Part 3: Balance Check +++++ ++++++ ++++++ -->
\newpage

# Balance Check

## Balance across Treatment (Nonblind vs Blind)

```{r Treatment Balance Check Table Function, echo = FALSE}

# ---------- Balance-table function using kable ----------
make_balance_table <- function(dt, covars, dict, title = NULL) {

  beta      <- numeric(length(covars))
  se_beta   <- numeric(length(covars))
  p_beta    <- numeric(length(covars))
  ctrl_mean <- numeric(length(covars))
  Ns        <- integer(length(covars))

  names(beta) <- names(se_beta) <- names(p_beta) <-
    names(ctrl_mean) <- names(Ns) <- covars

  for (v in covars) {
    # regression: covariate on treat_blind
    m <- suppressMessages(
      suppressWarnings(
         feols(as.formula(paste0(v, " ~ treat_blind")), data = dt, se = "hetero")
       )
     )

    beta[v]    <- coef(m)[["treat_blind"]]
    se_beta[v] <- se(m)[["treat_blind"]]
    p_beta[v]  <- pvalue(m)[["treat_blind"]]

    idx <- !is.na(dt[[v]]) & !is.na(dt$treat_blind)
    ctrl_mean[v] <- mean(dt[idx & dt$treat_blind == 0, get(v)], na.rm = TRUE)
    Ns[v]        <- sum(idx)
  }

  # significance stars
  stars <- ifelse(p_beta < 0.01, "***",
           ifelse(p_beta < 0.05, "**",
           ifelse(p_beta < 0.10, "*", "")))

  beta_fmt <- sprintf("%.3f%s", beta, stars)
  se_fmt   <- paste0("(", sprintf("%.3f", se_beta), ")")
  cm_fmt   <- sprintf("%.3f", ctrl_mean)
  N_fmt    <- as.character(Ns)

  # column labels from dict, in the order of covars
  col_names <- unname(dict[covars])
  # fallback: if some labels missing in dict, use variable names
  col_names[is.na(col_names)] <- covars[is.na(col_names)]

  # build 4-row table
  tab <- rbind(
    "Difference (Blind - Nonblind)" = beta_fmt,
    "SE"                                      = se_fmt,
    "Non-Blind Group Mean"                        = cm_fmt,
    "N"                                       = N_fmt
  )

  colnames(tab) <- col_names   # visible column headers

  # base kable object
  tbl <- kable(
    tab,
    format   = "latex",
    booktabs = TRUE,
    caption  = title,
    escape   = TRUE
  )

  # add HOLD_position so the table doesn't float
  tbl <- kable_styling(
    tbl,
    latex_options = "HOLD_position"
  )

  tbl
}

# ---------- Formatting Function ----------

fix_tabular <- function(x, new_spec) {
  # x: kable / knitr_kable object
  # new_spec: the full column spec you want, e.g. "@{}l c|cc|ccc@{}"

  x <- paste(as.character(x), collapse = "\n")

  # Replace whatever is inside { } after \begin{tabular}[t]
  x <- sub(
    "\\\\begin\\{tabular\\}\\[t\\]\\{[^}]*\\}",
    paste0("\\\\begin{tabular}[t]{", new_spec, "}"),
    x
  )

  x
}

```


```{r Balance Table Print, echo = FALSE, results = 'asis'}

# ---------- Choose and Label Covariates ----------

## Respondent Demographics
covars_resp_demo <- c("resp_age", 
                      "resp_female",
                      "resp_male",
                      "resp_white",
                      "resp_hispanic",
                      "resp_asian"
                      )

dict_resp_demo = c(
  "treat_blind"               = "Difference (Blind - Control)",
  "resp_age"                  = "Age",
  "resp_female"               = "Female",
  "resp_male"                 = "Male",
  "resp_white"                = "White",
  "resp_hispanic"             = "Hispanic",
  "resp_asian"                = "Asian"
  )

covars_resp_demo2 <- c("resp_income_50", 
                      "resp_income_100",
                      "resp_income_150",
                      "resp_income_200",
                      "resp_income_500ormore",
                      "resp_educ_uniabove"
                      )

dict_resp_demo2 = c(
  "treat_blind"               = "Difference (Blind - Control)",
  "resp_income_50"            = "< 50K",
  "resp_income_100"           = "50-100K",
  "resp_income_150"           = "100-150K",
  "resp_income_200"           = "150-200K",
  "resp_income_500ormore"     = "200K+",
  "resp_educ_uniabove"        = "University degree or more"
  )

## Firm Demographics
covars_firm_demo <- c(
  "firm_size_small", 
  "firm_size_mid", 
  "firm_size_large",
  "s2_firm_gendercomp_1",
  "s2_firm_gendercomp_2",
  "s2_firm_racecomp_1", 
  "s2_firm_racecomp_3", 
  "s2_firm_racecomp_4"
)

dict_firm_demo = c(
  "treat_blind"               = "Difference (Blind - Control)",
  "firm_size_small"           = "Size_Small",
  "firm_size_mid"             = "Size_Mid",
  "firm_size_large"           = "Size_Large",
  "s2_firm_gendercomp_1"      = "Male %",
  "s2_firm_gendercomp_2"      = "Female %",
  "s2_firm_racecomp_1"        = "White %",
  "s2_firm_racecomp_3"        = "Hispanic %",
  "s2_firm_racecomp_4"        = "Asian %"
)

## Firm's DEI Policies
covars_dei <- c(
  "bh_yes",
  "dei_policy_1", 
  "dei_policy_2", 
  "dei_policy_3", 
  "dei_policy_4", 
  "dei_policy_5", 
  "dei_policy_6"
)
  
dict_dei = c(
  "treat_blind"               = "Difference (Blind - Control)",
  "bh_yes"                 = "Conducts BH",
  "dei_policy_1"              = "Non Discrimination Policy",
  "dei_policy_2"              = "Diveristy Policy",
  "dei_policy_3"              = "DEI Training",
  "dei_policy_4"              = "DEI Position",
  "dei_policy_5"              = "Tranparent Policy",
  "dei_policy_6"              = "Affinity Groups"
)

# covars_dei2 <- c(
#   "dei_group_1", 
#   "dei_group_2", 
#   "dei_group_3", 
#   "dei_group_4", 
#   "dei_group_5", 
#   "dei_group_6"
# )
#   
# dict_dei2 = c(
#   "treat_blind"              = "Difference (Blind - Control)",
#   "dei_group_1"              = "White",
#   "dei_group_2"              = "Black",
#   "dei_group_3"              = "Hispanic",
#   "dei_group_4"              = "Asian",
#   "dei_group_5"              = "Male",
#   "dei_group_6"              = "Female"
# )

# ---------- Print 1: HR (ALL)----------

cat("\\textbf{Within HR (Treatment Balance) - All}")

# Table 1
res_hr_demo <- make_balance_table(firm_dt[role == "HR"],  covars_resp_demo, dict_resp_demo, "HR: Respondent Demographics")
res_hr_demo <- fix_tabular(res_hr_demo, "l|c|cc|ccc@{}")
cat(res_hr_demo)
rm(res_hr_demo)

# Table 2
res_hr_demo2 <- make_balance_table(firm_dt[role == "HR"],  covars_resp_demo2, dict_resp_demo2, "HR: Respondent Demographics 2")
res_hr_demo2 <- fix_tabular(res_hr_demo2, "l|ccccc|cc@{}")
cat(res_hr_demo2)
rm(res_hr_demo2)

# Table 3
res_hr_firm <- make_balance_table(firm_dt[role == "HR"],  covars_firm_demo, dict_firm_demo, "HR: Firm Characteristics")
res_hr_firm <- fix_tabular(res_hr_firm, "l|ccc|cc|ccc@{}")
cat(res_hr_firm)
rm(res_hr_firm)

# Table 4
res_hr_dei <- make_balance_table(firm_dt[role == "HR"],  covars_dei,       dict_dei,       "HR: Firm's DEI Policies")
res_hr_dei <- fix_tabular(res_hr_dei, "l|c|cccccc@{}")
cat(res_hr_dei)
rm(res_hr_dei)

# ---------- Print 2: Eng (All)----------

cat("\\newpage\n")
cat("\\vspace{1em}\n\\textbf{Within Engineer (Treatment Balance) - All}")

# Table 1
res_eng_demo <- make_balance_table(firm_dt[role == "Eng"], covars_resp_demo, dict_resp_demo, "Engineers: Respondent Demographics")
res_eng_demo <- fix_tabular(res_eng_demo, "l|c|cc|ccc@{}")
cat(res_eng_demo)

# Table 2
res_eng_demo2 <- make_balance_table(firm_dt[role == "Eng"], covars_resp_demo2, dict_resp_demo2, "Engineers: Respondent Demographics 2")
res_eng_demo2 <- fix_tabular(res_eng_demo2, "l|ccccc|cc@{}")
cat(res_eng_demo2)

# Table 3
res_eng_firm <- make_balance_table(firm_dt[role == "Eng"], covars_firm_demo, dict_firm_demo, "Engineers: Firm Characteristics")
res_eng_firm <- fix_tabular(res_eng_firm, "l|ccc|cc|ccc@{}")
cat(res_eng_firm)

# Table 4
res_eng_dei <- make_balance_table(firm_dt[role == "Eng"], covars_dei,       dict_dei,       "Engineers: Firm's DEI Policies")
res_eng_dei <- fix_tabular(res_eng_dei, "l|c|cccccc@{}")
cat(res_eng_dei)

```

\newpage
## Balance across Versions

```{r Versions Balance Check Table Function, echo = FALSE}

# ---------- Version-balance table: means by resume_ver + joint p-value ----------

make_version_balance_table <- function(dt, covars, dict,
                                       title = NULL,
                                       hline_after = NULL) {
  # dt    : data.table subset (e.g., treat == "blind")
  # covars: vector of variable names to check
  # dict  : named vector mapping var name -> pretty label for row names
  # title : LaTeX caption
  # hline_after: character vector of row labels AFTER which to draw \midrule
  
  # ensure resume_ver is present and not missing
  dt <- dt[!is.na(resume_ver)]
  
  # ---- sample sizes by resume_ver ----
  Ns_dt <- dt[, .N, by = resume_ver]
  data.table::setorder(Ns_dt, resume_ver)
  
  # ---- means by version ----
  means_dt <- dt[, lapply(.SD, mean, na.rm = TRUE),
                 by = resume_ver, .SDcols = covars]
  data.table::setorder(means_dt, resume_ver)
  
  # align Ns with means_dt
  Ns <- Ns_dt$N[match(means_dt$resume_ver, Ns_dt$resume_ver)]
  
  means_mat <- t(as.matrix(means_dt[, ..covars]))   # rows: covars, cols: versions
  colnames(means_mat) <- paste0(means_dt$resume_ver, " (N = ", Ns, ")")
  
  # ---- joint F-test p-values ----
  p_joint <- numeric(length(covars))
  names(p_joint) <- covars
  
  for (v in covars) {
    f <- as.formula(paste0(v, " ~ factor(resume_ver)"))
    m <- lm(f, data = dt)
    a <- anova(m)
    p_joint[v] <- a["factor(resume_ver)", "Pr(>F)"]
  }
  
  # ---- pretty labels ----
  row_labels <- unname(dict[covars])
  row_labels[is.na(row_labels)] <- covars[is.na(row_labels)]
  rownames(means_mat) <- row_labels
  
  means_chr <- apply(means_mat, c(1, 2), function(x) sprintf("%.3f", x))
  
  # significance stars for p-values
  stars <- ifelse(p_joint < 0.01, "***",
           ifelse(p_joint < 0.05, "**",
           ifelse(p_joint < 0.10, "*", "")))
  p_chr <- sprintf("%.3f%s", p_joint, stars)
  
  tab <- cbind(means_chr, "p-value (joint test)" = p_chr)
  
  # ---- build kable ----
  tbl <- knitr::kable(
    tab,
    format   = "latex",
    booktabs = TRUE,
    caption  = title,
    escape   = TRUE
  )
  
  # add horizontal lines after specific row labels, if requested
  if (!is.null(hline_after)) {
    rn  <- rownames(tab)
    idx <- match(hline_after, rn)
    idx <- idx[!is.na(idx)]
    if (length(idx) > 0) {
      for (i in idx) {
        tbl <- kableExtra::row_spec(tbl, i, extra_latex_after = "\\midrule")
      }
    }
  }
  
  tbl <- kableExtra::kable_styling(
    tbl,
    latex_options = "HOLD_position"
  )
  
  tbl
}

```

```{r Print Version Balance, echo = FALSE, results = 'asis'}

# ---------- Print 5: HR Non-Blind (All)----------

cat("\\textbf{Version Balance within Nonblinded HR (All)}")

# Blind: Respondent Demographics
make_version_balance_table(
  firm_dt[role == "HR" & treat == "nonblind"],
  c(covars_resp_demo,covars_resp_demo2),
  c(dict_resp_demo,dict_resp_demo2),
  title = "HR Nonblind: Respondent Demographics",
  hline_after  = c("Age", "Male", "Asian", "200K+")
)

# Blind: Firm Characteristics
make_version_balance_table(
  firm_dt[role == "HR" & treat == "nonblind"],
  covars_firm_demo ,
  dict_firm_demo,
  title = "HR Nonblind: Firm Characteristics",
  hline_after = c("Size_Large", "Female %")
)

# Blind: Firm' Demographics's DEI Policies
make_version_balance_table(
  firm_dt[role == "HR" & treat == "nonblind"],
  covars_dei,
  dict_dei,
  title = "HR Nonblind: Firm' Demographics's DEI Policies",
  hline_after = c("Conducts BH")
)


# ---------- Print 6: Engineer Non-Blind (All)----------

cat("\\newpage\n")
cat("\\textbf{Version Balance within Nonblinded Engineers (All)}")

# Blind: Respondent Demographics
make_version_balance_table(
  firm_dt[role == "Eng" & treat == "nonblind"],
  c(covars_resp_demo,covars_resp_demo2),
  c(dict_resp_demo,dict_resp_demo2),
  title = "Eng Nonblind: Respondent Demographics",
  hline_after  = c("Age", "Male", "Asian", "200K+")
)

# Blind: Firm Characteristics
make_version_balance_table(
  firm_dt[role == "Eng" & treat == "nonblind"],
  covars_firm_demo ,
  dict_firm_demo,
  title = "Eng Nonblind: Firm Characteristics",
  hline_after = c("Size_Large", "Female %")
)

# Blind: Firm' Demographics's DEI Policies
make_version_balance_table(
  firm_dt[role == "Eng" & treat == "nonblind"],
  covars_dei,
  dict_dei,
  title = "Eng Nonblind: Firm' Demographics's DEI Policies",
  hline_after = c("Conducts BH")
)


```

```{r,echo = FALSE}
## Clean Up
rm(covars_dei, covars_firm_demo, covars_resp_demo, covars_resp_demo2,
   dict_dei, dict_firm_demo, dict_resp_demo, dict_resp_demo2,
   res_eng_dei, res_eng_demo, res_eng_demo2,res_eng_firm,
   make_version_balance_table, make_balance_table)
```


\newpage
<!-- +++++ ++++++ ++++++ Part 4: Behavioral Exploration +++++ ++++++ ++++++ -->

# [Explorations] 

## Proportion of Candidates Passed to Next Stage

```{r advance_selfreport, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.align = 'center'}

temp <- firm_dt[!is.na(s4_application_num) & !is.na(s4_interview_num) & s4_application_num != 0, s4_advance_rate := s4_interview_num / s4_application_num * 100]

mean_stats <- temp[, .(mean_val = mean(s4_advance_rate, na.rm = TRUE)), by = role]

ggplot(temp[!is.na(s4_advance_rate)], aes(x = s4_advance_rate)) +
  geom_histogram(
    binwidth=5
  ) +
  facet_wrap(~ role) + 
  geom_vline(data = mean_stats, aes(xintercept = mean_val),
            color="blue", linetype="dashed", size=1) + 
  geom_text(data = mean_stats, 
            aes(x = mean_val + 2,  y = 20, 
                label = paste0("Mean: ", round(mean_val, 1))), 
            color = "blue", 
            hjust = 0) + 
  labs(y = "Counts", x = "Self-Reported Advance Rate (%)")

rm(temp, mean_stats)

```


\clearpage
## (HR) Number Candidates Passed to Next Stage

```{r advance_experiment, echo = FALSE, results = 'asis', fig.align = 'center'}

temp <- unique(firm_long_dt[role == "HR", counts_advanced := sum(sc_advance), by = .(responseid)][role == "HR", .(role, responseid, counts_advanced)])

mean_stats <- temp[, .(mean_val = mean(counts_advanced, na.rm = TRUE))]

ggplot(temp, 
       aes(x = counts_advanced)) + 
  geom_histogram(
    binwidth = 1
  ) + 
  geom_vline(data = mean_stats, aes(xintercept = mean_val), 
             color = "blue", linetype = "dashed", size = 1) + 
  geom_text(data = mean_stats,
            aes(x = mean_val + 2, y = 20,
                label = paste0("Mean: ", round(mean_val, 1))),
            color = "blue", 
            hjust = 0) + 
  labs(y = "Counts of HR", x = "Number of Candidates Advanced among 18")

rm(temp, mean_stats)

```

\clearpage
## (HR) Correlation between Self Reported Advance Rate and Experimental Advance Rate

```{r corr_advance, echo = FALSE, results = 'asis', fig.align = 'center'}

temp1 <- firm_dt[!is.na(s4_application_num) & !is.na(s4_interview_num) & s4_application_num != 0, s4_advance_rate := s4_interview_num / s4_application_num * 100][!is.na(s4_advance_rate), .(responseid, s4_advance_rate)]

temp2 <- unique(firm_long_dt[role == "HR", counts_advanced := sum(sc_advance), by = .(responseid)][role == "HR", .(responseid, counts_advanced)])

temp3 <- merge(temp1, temp2, by = "responseid")

cor_val <- cor(temp3$s4_advance_rate, temp3$counts_advanced)

ggplot(temp3, aes(x = counts_advanced, y = s4_advance_rate)) +
  geom_jitter(alpha = 0.5, width = 0.5, height = 0.2) + 
  geom_smooth(method = "lm", color = "blue", fill = "lightblue") +
  labs(
    title = paste0("Self-Reported vs. Actual Advance Rates (Corr: ", round(cor_val, 2), ")"),
    x = "Actual Resumes Passed (Count 0-18)",
    y = "Self-Reported Advance Rate (%)"
  ) +
  theme_minimal()  

rm(temp1, temp2, temp3, cor_val)

```

\clearpage  
## Correlation between IRR (want to receive resumes) and median time spent on resumes

```{r IRR_time, echo = FALSE, results = 'asis', fig.align = 'center'}

temp <- unique(firm_long_dt[, timeonpage_median := median(timeonpage), by = .(responseid)][, .(responseid, role, IRR_ever, timeonpage_median)])

ggplot(temp, aes(x = factor(IRR_ever), y = timeonpage_median, fill = factor(IRR_ever))) +
  
  # Add boxplots to show the median and distribution
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +
  
  # Optional: Add jittered points to show the raw data behind the boxes
  geom_jitter(width = 0.2, alpha = 0.3) +
  
  # Split: HR on Left, Engineer on Right
  facet_wrap(~ role) + 
  
  # Labels and Formatting
  labs(
    title = "Correlation: IRR Status vs. Respondent's Median Time on Page",
    x = "IRR Ever (0 = No, 1 = Yes)",
    y = "Median Time on Page (Seconds)",
    fill = "IRR Status"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

rm(temp)
```

\newpage
## Relationship between Time Spent on Evaluation by Treatment

```{r blinding_time, echo = FALSE, results = 'asis', fig.align = 'center'}

temp <- unique(firm_long_dt[, timeonpage_median := median(timeonpage), by = .(responseid)][, .(responseid, role, treat, timeonpage_median)])

ggplot(temp, aes(x = factor(treat), y = timeonpage_median, fill = factor(treat))) +
  
  # Add boxplots to show the median and distribution
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +
  
  # Optional: Add jittered points to show the raw data behind the boxes
  geom_jitter(width = 0.2, alpha = 0.3) +
  
  # Split: HR on Left, Engineer on Right
  facet_wrap(~ role) + 
  
  # Labels and Formatting
  labs(
    title = "Correlation: Treatment vs. Respondent's Median Time on Page",
    x = "Treatment",
    y = "Median Time on Page (Seconds)",
    fill = "Blind Treatment"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

rm(temp)

```


\newpage
## (Causal) Relationship between Time Spent On and Off the Evaluation by Treatment

```{r blinding_time_causal, echo = FALSE, results = 'asis'}

# --- Time On Page ---
model_timeon_hr  <- feols(timeonpage ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race, firm_long_dt[role == "HR"], vcov = ~ responseid)
model_timeon_eng <- feols(timeonpage ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race + resp_python + resp_java, firm_long_dt[role == "Eng"], vcov = ~ responseid)

tbl_on <- modelsummary(list("HR" = model_timeon_hr, "Engineers" = model_timeon_eng),
                       stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
                       output = "latex",
                       float = FALSE,
                       coef_map = c("treatblind" = "Blind Treatment"),
                       gof_omit = "R2 Within|AIC|BIC|RMSE")

# --- Time Off Page ---
model_timeoff_hr  <- feols(timeoffpage ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race, firm_long_dt[role == "HR"], vcov = ~ responseid)
model_timeoff_eng <- feols(timeoffpage ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race + resp_python + resp_java, firm_long_dt[role == "Eng"], vcov = ~ responseid)

tbl_off <- modelsummary(list("HR" = model_timeoff_hr, "Engineers" = model_timeoff_eng),
                        stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
                        output = "latex",
                        float = FALSE,
                        coef_map = c("treatblind" = "Blind Treatment"),
                        gof_omit = "R2 Within|AIC|BIC|RMSE")

# --- Render side-by-side via LaTeX minipages ---
# modelsummary wraps its tabular in \begin{table}...\end{table} even with
# float = FALSE. That outer floating environment is what fails inside a
# minipage with "Not in outer par mode". Strip it so we have a bare tabular,
# then add titles manually as bold text above each minipage.
strip_table_env <- function(x) {
  s <- paste(as.character(x), collapse = "\n")
  s <- gsub("\\\\begin\\{table\\}[^\n]*\n?", "", s)
  s <- gsub("\\\\end\\{table\\}\\s*", "", s)
  s
}

cat("\\noindent\\begin{tabular}{@{}c@{\\hspace{1em}}c@{}}\n")
cat("\\begin{minipage}[t]{0.48\\linewidth}\\centering\n")
cat("\\textbf{Effect of Treatment on Time Spent On Page (Fixed Effects)}\\par\\smallskip\n")
cat(strip_table_env(tbl_on))
cat("\n\\end{minipage} &\n")
cat("\\begin{minipage}[t]{0.48\\linewidth}\\centering\n")
cat("\\textbf{Effect of Treatment on Time Spent Off Page (Fixed Effects)}\\par\\smallskip\n")
cat(strip_table_env(tbl_off))
cat("\n\\end{minipage}\n")
cat("\\end{tabular}\n")

rm(strip_table_env)

rm(model_timeon_hr, model_timeon_eng,
   model_timeoff_hr, model_timeoff_eng,
   tbl_on, tbl_off)

```


\newpage
## (Eng Only) Relationship between Open Resume / Codes by Treatment

```{r blinding_open_resume, echo = FALSE, results = 'asis', fig.align='center', out.width='45%', fig.pos="H"}

temp <- unique(firm_long_dt[role == "Eng"][, .(responseid, treat, prop_open_resume, prop_open_code)])
  
ggplot(temp, aes(x = factor(treat), y = prop_open_resume, fill = factor(treat))) +
  
  # Add boxplots to show the median and distribution
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +
  
  # Optional: Add jittered points to show the raw data behind the boxes
  geom_jitter(width = 0.2, alpha = 0.3) +
  
  # Labels and Formatting
  labs(
    title = "Correlation: Treatment vs. Resume Open Rates",
    x = "Treatment",
    y = "Proportion of Resume Opened",
    fill = "Blind Treatment"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggplot(temp, aes(x = factor(treat), y = prop_open_code, fill = factor(treat))) +

  # Add boxplots to show the median and distribution
  geom_boxplot(alpha = 0.6, outlier.shape = NA) +

  # Optional: Add jittered points to show the raw data behind the boxes
  geom_jitter(width = 0.2, alpha = 0.3) +

  # Labels and Formatting
  labs(
    title = "Correlation: Treatment vs. Code Open Rates",
    x = "Treatment",
    y = "Proportion of Resume Opened",
    fill = "Blind Treatment"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

rm(temp)

```


\newpage
## (Causal) Relationship between Open Resume / Codes by Treatment

```{r blinding_open_resume_causal, echo = FALSE, results = 'asis', fig.align='center', out.width='45%'}

model_open_res  <- feols(open_resume ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race + resp_python + resp_java, firm_long_dt[role == "Eng"], vcov = ~ responseid)
model_open_code1 <- feols(open_code1 ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race + resp_python + resp_java, firm_long_dt[role == "Eng"], vcov = ~ responseid)
model_open_code2 <- feols(open_code2 ~ treat + resp_age | r_do + resume_index + resp_gender + resp_race + resp_python + resp_java, firm_long_dt[role == "Eng"], vcov = ~ responseid)

modelsummary(list("P(Open Res)" = model_open_res, "P(Open Code 1)" = model_open_code1, "P(Open Code 2)" = model_open_code2),
             stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
             title = "Effect of Treatment on Rate of Opening Res / Codes",
             output = "kableExtra",
             coef_map = c("treatblind" = "Blind Treatment"),
             gof_omit = "R2 Within|AIC|BIC|RMSE") %>%
  kable_styling(latex_options = "HOLD_position")

rm(model_open_res, model_open_code1, model_open_code2)

```



\newpage
## Relationship between Blinding & IRR (want to receive resumes)

```{r blinding_irr, echo = FALSE, results = 'asis'}
firm_dt[, .(Proportion = round(mean(IRR_ever, na.rm = TRUE), 2), N = .N), by = .(role, treat)][order(role, treat)] |>
  knitr::kable(format = "latex", booktabs = TRUE)
```


## Relationship between Blinding & Looking at Outside Resources

```{r blinding_outsidesearch, echo = FALSE, results = 'asis'}
firm_dt[, .(Proportion = round(mean(s3_outside_res, na.rm = TRUE),2), N = .N), by = .(role, treat)][order(role, treat)] |>
  knitr::kable(format = "latex", booktabs = TRUE)
```



\newpage
<!-- +++++ ++++++ ++++++ Part 5: Thoughts on Blind Hiring +++++ ++++++ ++++++ -->
# Section 5: Thoughts on Blind Hirings (Collected for Last 2 weeks)

## s5_insights_bh_chg (Blinded Group Only)

(Optional but encouraged) While evaluating candidates without names (or other information that could signal demographic background, such as home address or languages), how—if at all—did this affect the way you evaluated the candidates? What went through your mind?

(Please describe your thought process in your own words. There is no right or wrong answer.)

```{r s5_insights_bh_chg, echo = FALSE, results='asis'}
responses <- firm_dt[!is.na(s5_insights_bh_chg) & nchar(s5_insights_bh_chg) > 0 & 
                       role == "HR", s5_insights_bh_chg]
cat("\n\n\\vspace{12pt}\n")
cat("\\noindent \\textbf{HR Responses} \n\n")
cat(paste0(seq_along(responses), ". ", responses, collapse = "\n\n"))
rm(responses)

responses <- firm_dt[!is.na(s5_insights_bh_chg) & nchar(s5_insights_bh_chg) > 0 & 
                       role == "Eng", s5_insights_bh_chg]
cat("\n\n\\vspace{12pt}\n")
cat("\\noindent \\textbf{Engineer Responses} \n\n")
cat(paste0(seq_along(responses), ". ", responses, collapse = "\n\n"))
rm(responses)
```

\newpage
## s5_guess_gender and s5_guess_race

Thinking back on the candidates you evaluated, what do you believe was the approximate gender composition of the 18 candidates? Of race composition?

```{r s5_guess_gender, echo = FALSE, results='asis'}

# 1. Define variables and labels
guess_vars <- c("s5_guess_gender_1", "s5_guess_gender_2", "s5_guess_gender_3",
                "s5_guess_race_1", "s5_guess_race_2", "s5_guess_race_3", "s5_guess_race_4", "s5_guess_race_5")
labels <- c("Male", "Female", "Gender (Other)",
            "White", "Asian", "Hispanic", "Black", "Race (Other)")

# 2. Function to calculate stats with N in labels
get_role_stats <- function(target_role) {
  subset_dt <- firm_dt[role == target_role & resume_ver != "v7"]
  
  # Calculate N for each treatment arm
  n_blind    <- nrow(subset_dt[treat == "blind" & !is.na(s5_guess_gender_1)])
  n_nonblind <- nrow(subset_dt[treat == "nonblind" & !is.na(s5_guess_gender_1)])
  
  suppressWarnings({
    role_results <- lapply(guess_vars, function(var) {
      m_blind    <- mean(subset_dt[treat == "blind"][[var]], na.rm = TRUE)
      m_nonblind <- mean(subset_dt[treat == "nonblind"][[var]], na.rm = TRUE)
      
      test <- t.test(as.formula(paste0(var, " ~ treat")), data = subset_dt)
      diff <- m_blind - m_nonblind
      pval <- test$p.value
      stars <- ifelse(pval < 0.01, "***", ifelse(pval < 0.05, "**", ifelse(pval < 0.1, "*", "")))
      
      return(c(
        blind = sprintf("%.3f", m_blind),
        nonblind = sprintf("%.3f", m_nonblind),
        diff = sprintf("%.3f", diff),
        pval = sprintf("%.3f%s", pval, stars)
      ))
    })
  })
  
  res <- t(do.call(rbind, role_results))
  
  # Update row names to include N
  rownames(res) <- c(
    paste0("Blind (N = ", n_blind, ")"),
    paste0("Non-blind (N = ", n_nonblind, ")"),
    "Difference (B - NB)",
    "P-value"
  )
  return(res)
}

# 3. Execute calculations
hr_stats  <- get_role_stats("HR")
eng_stats <- get_role_stats("Eng")

# 4. Assemble the final matrix
tab_matrix <- rbind(
  "Panel A: HR Professionals" = rep("", 8),
  hr_stats,
  " "                         = rep("", 8), # Spacer row
  "Panel B: Software Engineers" = rep("", 8),
  eng_stats
)

colnames(tab_matrix) <- labels

# 5. Generate Table
tbl <- kable(
  tab_matrix,
  format   = "latex",
  booktabs = TRUE,
  caption  = "Candidate Identity Guesses: Treatment Comparison with Sample Sizes",
  escape   = TRUE,
  align    = "lcccccccc"
) %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(c(1, 7), bold = TRUE) %>% 
  row_spec(c(5, 11), italic = TRUE, color = "gray")

# 6. Apply custom vertical lines
tbl_fixed <- fix_tabular(tbl, "l|ccc|ccccc")

cat(tbl_fixed)

rm(guess_vars, labels, get_role_stats,
   hr_stats, eng_stats, tab_matrix, tbl, tbl_fixed)

```


\newpage
<!-- +++++ ++++++ ++++++ Part 6: Qualitative Responses +++++ ++++++ ++++++ -->
# Qualtitative Responses

## s6_insight_hr

(Optional) Can you share any ways in which you felt engineers, who usually conduct technical interviews, pursued or not pursued DEI objectives in the hiring process and what impact it had on the firm, overall?

```{r s6_insight_hr, eval= TRUE, echo = FALSE, results='asis'}

responses <- firm_dt[!is.na(s6_insight_hr) & nchar(s6_insight_hr) > 5, s6_insight_hr]
cat(paste0(seq_along(responses), ". ", responses, collapse = "\n\n"))
rm(responses)
```


\newpage
## s5_insight_engineer

(Optional) Can you share any ways in which you felt HR influenced or encouraged DEI objectives in the hiring process and what impact it had on the firm, overall?

```{r s5_insight_engineer, eval= TRUE, echo = FALSE, results='asis'}
responses <- firm_dt[!is.na(s5_insight_engineer) & nchar(s5_insight_engineer) > 5, s5_insight_engineer]
cat(paste0(seq_along(responses), ". ", responses, collapse = "\n\n"))
rm(responses)
```

\newpage
## s5_insights_industry

(Optional) Do you have any additional thoughts on hiring trends or DEI initiatives? Feel free to share whatever you believe would be helpful for researchers.

```{r s5_insights_industry, eval= TRUE, echo = FALSE, results='asis'}
responses <- firm_dt[!is.na(s5_insights_industry) & nchar(s5_insights_industry) > 5, s5_insights_industry]
cat(paste0(seq_along(responses), ". ", responses, collapse = "\n\n"))
rm(responses)
```

\newpage
## s6_feedback

(Optional) Do you have any suggestions for improving this survey?

```{r s6_feedback, eval= TRUE, echo = FALSE, results='asis'}
responses <- firm_dt[!is.na(s6_feedback) & nchar(s6_feedback) > 5, s6_feedback]
cat(paste0(seq_along(responses), ". ", responses, collapse = "\n\n"))
rm(responses)
```


<!-- \newpage -->
<!-- <!-- +++++ ++++++ ++++++ Part 7: Additional Quality Check +++++ ++++++ ++++++ --> -->
<!-- # Additional Quality Check -->

<!-- ## Engineers: Correlation between Test Cases and Overall Score / Coding Score -->
<!-- ```{r eng_correlation_with_test_cases, eval= FALSE, echo = FALSE, fig.align='center', out.width='100%'} -->

<!-- # Compute within-respondent correlations -->
<!-- resp_cors <- firm_long_dt[role == "Eng", .( -->
<!--   cor_overall = cor(test_case, sc_overall_z, use = "complete.obs"), -->
<!--   cor_coding = cor(test_case, sc_coding_z, use = "complete.obs") -->
<!-- ), by = .(role, responseid, treat)] -->

<!-- # Negative Correlations? -->
<!-- # resp_cors[cor_overall < 0] -->
<!-- # resp_cors[cor_coding < 0] -->

<!-- # Graph Distributions of Correlations -->
<!-- p1_blind <- ggplot(resp_cors[treat == "blind"], aes(x = cor_overall)) + -->
<!--   geom_histogram(bins = 30, fill = "steelblue", color = "white") + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed", color = "red") + -->
<!--   theme_minimal() + -->
<!--   labs(x = "Correlation", y = "Count", title = "(Blind) Test Case vs Overall") -->

<!-- p2_blind <- ggplot(resp_cors[treat == "blind"], aes(x = cor_coding)) + -->
<!--   geom_histogram(bins = 30, fill = "steelblue", color = "white") + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed", color = "red") + -->
<!--   theme_minimal() + -->
<!--   labs(x = "Correlation", y = "Count", title = "(Blind) Test Case vs Coding") -->

<!-- grid.arrange(p1_blind, p2_blind, ncol = 2) -->

<!-- p1_nonblind <- ggplot(resp_cors[treat == "nonblind"], aes(x = cor_overall)) + -->
<!--   geom_histogram(bins = 30, fill = "steelblue", color = "white") + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed", color = "red") + -->
<!--   theme_minimal() + -->
<!--   labs(x = "Correlation", y = "Count", title = "(NonBlind) Test Case vs Overall") -->

<!-- p2_nonblind <- ggplot(resp_cors[treat == "nonblind"], aes(x = cor_coding)) + -->
<!--   geom_histogram(bins = 30, fill = "steelblue", color = "white") + -->
<!--   geom_vline(xintercept = 0, linetype = "dashed", color = "red") + -->
<!--   theme_minimal() + -->
<!--   labs(x = "Correlation", y = "Count", title = "(NonBlind) Test Case vs Coding") -->

<!-- grid.arrange(p1_nonblind, p2_nonblind, ncol = 2) -->

<!-- rm(resp_cors, p1_blind, p2_blind, p1_nonblind, p2_nonblind) -->

<!-- ``` -->

<!-- ## Engineers: Time Spent On Page -->

<!-- ```{r Taskmaster_Eng_Graph, eval= FALSE, echo = FALSE, fig.width = 16, fig.height = 20, results = "asis", message = FALSE, warning = FALSE} -->

<!-- # Subset for marking special resume_indices -->
<!-- special_resumes <- c(1, 5, 8, 11, 14) -->
<!-- mark_dt <- taskmaster_long_dt[role == "Eng" & resume_index %in% special_resumes] -->

<!-- eng_ids   <- unique(taskmaster_long_dt[role == "Eng", responseid]) -->
<!-- n_panels  <- length(eng_ids) -->
<!-- per_page  <- 5 * 6 -->
<!-- n_pages   <- ceiling(n_panels / per_page) -->

<!-- for (i in seq_len(n_pages)) { -->
<!--   p <- ggplot( -->
<!--     taskmaster_long_dt[role == "Eng"], -->
<!--     aes(x = r_do, group = responseid) -->
<!--   ) + -->
<!--     ## (ii) Vertical lines at special resume_indices -->
<!--     geom_vline( -->
<!--       data = mark_dt, -->
<!--       aes(xintercept = r_do), -->
<!--       color = "gold", alpha = 0.4, linewidth = 3 -->
<!--     ) + -->
<!--     ## (i) Blue line connects clipped values -->
<!--     geom_line(aes(y = timeonpage_clipped), -->
<!--               color = "steelblue", linewidth = 0.7) + -->
<!--     geom_point(aes(y = timeonpage_clipped), -->
<!--                color = "steelblue", size = 1.2) + -->
<!--     ## TimeOn outliers above upper threshold (dark blue dots) -->
<!--     geom_point( -->
<!--       data = taskmaster_long_dt[role == "Eng" & out_On == TRUE], -->
<!--       aes(x = r_do, y = timeonpage_clipped), -->
<!--       color = "darkblue", size = 2.2 -->
<!--     ) + -->
<!--     ## TimeOn flags below lower threshold (red dots) -->
<!--     geom_point( -->
<!--       data = taskmaster_long_dt[role == "Eng" & timeon_flag == TRUE], -->
<!--       aes(x = r_do, y = timeonpage), -->
<!--       color = "red", size = 2.2 -->
<!--     ) + -->
<!--     ## TimeOff: dashed line + points -->
<!--     geom_line(aes(y = timeoffpage_clipped), -->
<!--               color = "grey60", linewidth = 0.7, linetype = "dashed") + -->
<!--     geom_point(aes(y = timeoffpage_clipped), -->
<!--                color = "grey60", size = 1.0) + -->
<!--     ## TimeOff outliers (black dots) -->
<!--     geom_point( -->
<!--       data = taskmaster_long_dt[role == "Eng" & out_Off == TRUE], -->
<!--       aes(x = r_do, y = timeoffpage_clipped), -->
<!--       color = "black", size = 2.0 -->
<!--     ) + -->
<!--     scale_x_continuous(breaks = seq(1, 18, by = 2), limits = c(1, 18)) + -->
<!--     scale_y_continuous(limits = c(0, 100), breaks = seq(0, 100, 25)) + -->
<!--     facet_wrap_paginate( -->
<!--       ~ responseid, -->
<!--       ncol = 5, nrow = 6, page = i, scales = "free" -->
<!--     ) + -->
<!--     labs( -->
<!--       title = sprintf("(Taskmaster) Engineer: Time Spent On / Off Resume — Page %d of %d", i, n_pages), -->
<!--       x = "Resume Page (1–18) in order shown", -->
<!--       y = "Time On/Off Page (seconds)" -->
<!--     ) + -->
<!--     theme_minimal(base_size = 10) + -->
<!--     theme( -->
<!--       plot.subtitle = ggtext::element_markdown(size = 9), -->
<!--       strip.text    = element_text(size = 7), -->
<!--       axis.text.x   = element_text(size = 7), -->
<!--       axis.text.y   = element_text(size = 7) -->
<!--     ) -->
<!--   print(p) -->
<!--   if (i < n_pages) cat("\\newpage\n") -->
<!-- } -->

<!-- rm(special_resumes, mark_dt, eng_ids, n_panels, per_page, n_pages) -->

<!-- ``` -->




