---
title: "8A_Report_Preferences"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{xcolor}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- ##### ##### ##### ##### ##### Demographic Preferences ##### ##### ##### ##### ##### -->

# Preferences (All Dimensions)

\textcolor{blue}{\textbf{Takeaway}}: On average, HR shows little demographic preference, while Engineers display a stronger preference for non-White groups over White Males.


```{r stage_pref_alldimensions, echo = FALSE, results = 'asis'}

## Run All Regressions
suppressMessages(suppressWarnings({
  #### HR Models
  reg_hr_cod <- feols(sc_coding_z ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "HR"], vcov = ~ responseid)
  reg_hr_fit <- feols(sc_fit_z    ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "HR"], vcov = ~ responseid)
  reg_hr_sta <- feols(sc_stay_z   ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "HR"], vcov = ~ responseid)
  reg_hr_ovr <- feols(sc_overall_z~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "HR"], vcov = ~ responseid)
  reg_hr_adv <- feols(sc_advance  ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "HR"], vcov = ~ responseid)

  #### Engineer Models
  reg_eng_cod <- feols(sc_coding_z ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "Eng"], vcov = ~ responseid)
  reg_eng_fit <- feols(sc_fit_z    ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "Eng"], vcov = ~ responseid)
  reg_eng_sta <- feols(sc_stay_z   ~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "Eng"], vcov = ~ responseid)
  reg_eng_ovr <- feols(sc_overall_z~ i(race_gender) | resume_index + responseid + r_do, firm_long_dt[treat == "nonblind" & role == "Eng"], vcov = ~ responseid)
}))

## Setup Labels
rg_labels <- c("White Female", "Asian Male", "Asian Female", "Hispanic Male", "Hispanic Female")
rg_raw <- grep("^race_gender", names(coef(reg_hr_cod)), value = TRUE)

dict_dims <- c(
  setNames(rg_labels, rg_raw),
  "resume_index" = "Resume (Content) FE",
  "responseid"   = "Respondent FE",
  "r_do"         = "Display Position FE"
)

## Generate Side-by-Side Table (9 columns)
tbl <- fixest::etable(
  list(
    # HR Panel (5 cols)
    "Coding" = reg_hr_cod, "Fit" = reg_hr_fit, "Stay" = reg_hr_sta, "Overall" = reg_hr_ovr, "Advance" = reg_hr_adv,
    # Eng Panel (4 cols)
    "Coding " = reg_eng_cod, "Fit " = reg_eng_fit, "Stay " = reg_eng_sta, "Overall " = reg_eng_ovr
  ),
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  keep = "%^race_gender",
  drop = "%^(Intercept)$",
  dict = dict_dims,
  fitstat = c("n", "r2"),
  digits = 3,
  se.below = TRUE,
  notes = c("Standard errors clustered by respondent.", "Significance levels: * p<0.1, ** p<0.05, *** p<0.01")
)

## Final Layout Modifications 

  #### Header spanning: HR occupies cols 2-6 (5 cols), Eng occupies cols 7-10 (4 cols)
  tbl <- sub(
    "\\\\toprule",
    paste0("\\\\toprule & \\\\multicolumn{5}{c}{Panel A: HR (Non-blind, N = ", nobs(reg_hr_cod)/18, ")} & \\\\multicolumn{4}{c}{Panel B: Engineer (Non-blind, N = ", nobs(reg_eng_cod)/18, ")} \\\\\\\\ \\\\cmidrule(lr){2-6} \\\\cmidrule(lr){7-10}"),
    tbl
  )
  
  #### Clean up formatting
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering", tbl)

## Print
cat(tbl)

rm(reg_hr_cod, reg_hr_fit, reg_hr_sta, reg_hr_ovr, reg_hr_adv, 
   reg_eng_cod, reg_eng_fit, reg_eng_sta, reg_eng_ovr,
   rg_labels, rg_raw, dict_dims, tbl)
```

```{r stage_pref_overall, echo = FALSE, eval = FALSE, results = 'asis'}

## Regression: Overall Scores

    #### HR
    reg_pref_ovr_hr <- feols(sc_overall_z ~ i(race_gender),
                             data = firm_long_dt[treat == "nonblind" & role == "HR"],
                             vcov = ~ responseid)

    reg_pref_ovr_hr_1 <- feols(sc_overall_z ~ i(race_gender) | resume_index,
                               data = firm_long_dt[treat == "nonblind" & role == "HR"],
                               vcov = ~ responseid)

    reg_pref_ovr_hr_2 <- feols(sc_overall_z ~ i(race_gender) | resume_index + responseid,
                               data = firm_long_dt[treat == "nonblind" & role == "HR"],
                               vcov = ~ responseid)

    reg_pref_ovr_hr_3 <- feols(sc_overall_z ~ i(race_gender) | resume_index + responseid + r_do,
                               data = firm_long_dt[treat == "nonblind" & role == "HR"],
                               vcov = ~ responseid)

    #### Engineer
    reg_pref_ovr_eng <- feols(sc_overall_z ~ i(race_gender),
                              data = firm_long_dt[treat == "nonblind" & role == "Eng"],
                              vcov = ~ responseid)

    reg_pref_ovr_eng_1 <- feols(sc_overall_z ~ i(race_gender) | resume_index,
                                data = firm_long_dt[treat == "nonblind" & role == "Eng"],
                                vcov = ~ responseid)

    reg_pref_ovr_eng_2 <- feols(sc_overall_z ~ i(race_gender) | resume_index + responseid,
                                data = firm_long_dt[treat == "nonblind" & role == "Eng"],
                                vcov = ~ responseid)

    reg_pref_ovr_eng_3 <- feols(sc_overall_z ~ i(race_gender) | resume_index + responseid + r_do,
                                data = firm_long_dt[treat == "nonblind" & role == "Eng"],
                                vcov = ~ responseid)
    
    
## Set-up Table

  #### Build dictionary from actual coefficient names
  rg_raw <- grep("^race_gender", names(coef(reg_pref_ovr_hr)), value = TRUE)
  
  rg_labels <- c("White Female",
                 "Asian Male",
                 "Asian Female",
                 "Hispanic Male",
                 "Hispanic Female")
  
  dict_rg <- setNames(rg_labels, rg_raw)
  
  dict_all <- c(
    dict_rg,
    "sc_overall_z" = "Overall Rating",
    "resume_index" = "Resume (Content) FE",
    "responseid"   = "Respondent FE",
    "r_do"         = "Display Position FE"
  )
  
  panelA <- paste0("Panel A: HR (Non-blind, N = ",
                   nrow(firm_dt[role == "HR" & treat == "nonblind"]), ")")
  panelB <- paste0("Panel B: Eng (Non-blind, N = ",
                   nrow(firm_dt[role == "Eng" & treat == "nonblind"]), ")")
  

  tbl <- fixest::etable(
    list(
      "HR Base"        = reg_pref_ovr_hr,
      "+ Res FE"       = reg_pref_ovr_hr_1,
      "+ Resp FE"      = reg_pref_ovr_hr_2,
      "+ DO FE"        = reg_pref_ovr_hr_3,
      "Eng Base"       = reg_pref_ovr_eng,
      "+ Res FE"       = reg_pref_ovr_eng_1,
      "+ Resp FE"      = reg_pref_ovr_eng_2,
      "+ DO FE"        = reg_pref_ovr_eng_3
    ),
    tex       = TRUE,
    style.tex = style.tex("aer"),
    keep      = "%^race_gender",
    drop      = "%^(Intercept)$",
    dict      = dict_all,
    fitstat = c("n", "r2", "ar2"),
    digits    = 3,
    se.below  = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.10),
    notes = c("Standard errors clustered by respondent.", 
              "Significance levels: * p<0.1, ** p<0.05, *** p<0.01")
  )

## Column 9: Calculate Difference (HR vs Eng) P Values (Two-Sample Z-Test)
    
  #### Extract Coefficients and SEs from the full models
  b_hr  <- coef(reg_pref_ovr_hr_3)[rg_raw]
  se_hr <- se(reg_pref_ovr_hr_3)[rg_raw]
  
  b_eng  <- coef(reg_pref_ovr_eng_3)[rg_raw]
  se_eng <- se(reg_pref_ovr_eng_3)[rg_raw]
  
  #### Calculate Z-score and P-value
  z_scores <- (b_hr - b_eng) / sqrt(se_hr^2 + se_eng^2)
  p_vals   <- 2 * (1 - pnorm(abs(z_scores)))
  
  #### Helper to assign stars based on p-values
  get_stars <- function(p) {
    if (p <= 0.01) return("***")
    if (p <= 0.05) return("**")
    if (p <= 0.10) return("*")
    return("")
  }
  
  #### Format p-values with stars for the table (3 decimals)
  p_vals_fmt <- sprintf("%.3f", p_vals)
  stars <- sapply(p_vals, get_stars)
  p_vals_with_stars <- paste0(p_vals_fmt, stars)
  names(p_vals_with_stars) <- rg_raw 
    
  #### Helper to assign stars based on p-values
  get_stars <- function(p) {
    if (p <= 0.01) return("***")
    if (p <= 0.05) return("**")
    if (p <= 0.10) return("*")
    return("")
  } 
  
  #### Latex Formatting
  
    ###### Fix Alignment: Change {lcccccccc} (9 cols) to {lcccc|cccc|c} (10 cols)
    tbl <- sub("\\{lcccccccc\\}", "{lcccc|cccc|c}", tbl)

    ###### Fix Header: Add the "p-val" column header
    tbl <- sub(
      "\\(8\\) \\\\\\\\", 
      "(8) & \\\\makecell{p-value on\\\\\\\\diff (4)-(8)} \\\\\\\\", 
      tbl
    )

    ###### Inject P-value Data Rows
    # Loop through the exact variable names found in the model
    for(var in rg_raw) {
      lbl <- dict_all[var]     # e.g., "White Female"
      pval <- p_vals_with_stars[var]  # e.g., "0.844"
      
      # Find row starting with Label, append "& pval \\"
      # We use fixed=TRUE for the pattern to be safe, but need regex for the replacement
      pattern <- paste0("(", lbl, ".*?)\\\\\\\\")
      replacement <- paste0("\\1 & ", pval, " \\\\\\\\")
      
      tbl <- sub(pattern, replacement, tbl)
    }

## Final Layout Modifications 
    
  #### Fix Empty Rows (Standard Errors)
  tbl <- gsub("(\\s+\\(.*?)\\\\\\\\", "\\1 & \\\\\\\\", tbl)
  
  #### Fix Bottom Rows (Stats)
  bottom_labels <- c("Observations", "R$^2$", "Adjusted R$^2$", 
                     "Resume .* FE", "Respondent .* FE", "Display .* FE")
  for(lab in bottom_labels) {
    tbl <- gsub(paste0("^(", lab, ".*?)\\\\\\\\"), "\\1 & \\\\\\\\", tbl)
  }
  
  #### Fix Top Header Spanning
  tbl <- sub(
    "\\\\multicolumn\\{8\\}\\{c\\}\\{Overall Rating\\}", 
    paste0(
      "\\\\multicolumn{9}{c}{Outcome: Overall Score (Z)} \\\\\\\\ \\\\cmidrule(lr){2-10} & ",
      "\\\\multicolumn{4}{c}{", panelA, "} & ",
      "\\\\multicolumn{4}{c}{", panelB, "} &" 
    ),
    tbl
  )

  #### Center of Page
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering", tbl)

## Print
cat(tbl)  
  

## Clean Up
rm(panelA, panelB, tbl, rg_raw, rg_labels, dict_rg, dict_all,
   b_eng, b_hr, se_hr, se_eng, pval, p_vals, p_vals_fmt, p_vals_with_stars, stars, replacement, var, z_scores,
   bottom_labels, lab, lbl, pattern, 
   reg_pref_ovr_hr, reg_pref_ovr_hr_1, reg_pref_ovr_hr_2, reg_pref_ovr_hr_3, 
   reg_pref_ovr_eng, reg_pref_ovr_eng_1, reg_pref_ovr_eng_2, reg_pref_ovr_eng_3)

```


\newpage
# Heterogeneity in Preferences (By Respondent Demographics)

\textcolor{blue}{\textbf{Takeaway}}: HR does not display preference based on demographic concordance. Engineers assign a slight premium (0.56--0.86\% of a SD) to non-concordant groups, driven primarily by White Male Engineers --- the majority group among Engineers --- whose positive preference favors non-White demographic groups.

\textcolor{blue}{\textbf{Takeaway (2)}}: In the U.S. IT setting, the traditional concordance bias (homophily) and animus (discrimination against minorities) story can be rejected. 


<!-- ## Functions for Concordance and Heterogeneity  -->
```{r pref_heterogeneity_functions, eval = TRUE, include = FALSE, echo = FALSE}

## Function for Linear Combination Test - Race Only
total_effects_lincom_race <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  candidate_demographics <- c("White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")
  res_list <- list()

  for(cand in candidate_demographics) {
    main_term <- paste0("race_gender::", cand)
    
    if(resp_group == "White") {
      est <- coefs[main_term]
      var_sum <- vcov_mat[main_term, main_term]
    } else {
      # The interaction terms are structured as: resp_var:race_gender::candidate
      if(resp_group == "Asian") {
        int_term <- paste0("resp_asian:race_gender::", cand)
      } else if(resp_group == "Hispanic") {
        int_term <- paste0("resp_hispanic:race_gender::", cand)
      } else if(resp_group == "Black") {
        int_term <- paste0("resp_black:race_gender::", cand)
      }
      
      if(!int_term %in% names(coefs)) {
        res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      est <- coefs[main_term] + coefs[int_term]
      v_main <- vcov_mat[main_term, main_term]
      v_int  <- vcov_mat[int_term, int_term]
      cov_mi <- vcov_mat[main_term, int_term]
      var_sum <- v_main + v_int + 2 * cov_mi
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function for Individually Plotting Total Effects - Race Only
plot_heterogeneity_race <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role) {
  
  respondent_groups <- c("White", "Asian", "Hispanic", "Black")
  
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_race(model, g), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Respondent = g, Candidate = "White_Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))
  
  plot_data <- plot_data[Respondent != "Other"]
  
  # Set factor order for Respondent FIRST
  plot_data[, Respondent := factor(Respondent, levels = c("White", "Asian", "Hispanic", "Black"))]
  
  # Add N counts to respondent labels
  if(!is.null(resp_counts)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    resp_counts_subset <- resp_counts[, .(resp_race, N = get(N_col))]
    plot_data <- plot_data[resp_counts_subset, on = c(Respondent = "resp_race")]
    plot_data[, Respondent_Label := paste0(Respondent, " (N=", N, ")")]
    
    # Set factor order for Respondent_Label explicitly
    respondent_label_order <- c(
      paste0("White (N=", resp_counts_subset[resp_race == "White", N], ")"),
      paste0("Asian (N=", resp_counts_subset[resp_race == "Asian", N], ")"),
      paste0("Hispanic (N=", resp_counts_subset[resp_race == "Hispanic", N], ")"),
      paste0("Black (N=", resp_counts_subset[resp_race == "Black", N], ")")
    )
    plot_data[, Respondent_Label := factor(Respondent_Label, levels = respondent_label_order)]
  } else {
    plot_data[, Respondent_Label := Respondent]
  }
  
  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", "Asian_Male" = "AM", "Asian_Female" = "AF", "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "AF", "AM", "WF", "WM"))]
  
  # Extract race from candidate (White, Asian, Hispanic)
  plot_data[, Candidate_Race := fcase(
    Candidate %in% c("White_Male", "White_Female"), "White",
    Candidate %in% c("Asian_Male", "Asian_Female"), "Asian",
    Candidate %in% c("Hispanic_Male", "Hispanic_Female"), "Hispanic",
    default = "Other"
  )]
  
  # Create match status based on race concordance
  plot_data[, Match_Status := ifelse(as.character(Respondent) == Candidate_Race, "Concordant Race", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Race"))]
  
  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Respondent_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Race" = "#D55E00")) +
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")
  
  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

## Function for Linear Combination Test - Race Only (Collapsing on / Ignoring Gender)
total_effects_lincom_race_collapsedongender <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  candidate_races <- c("White", "Asian", "Hispanic")
  res_list <- list()

  for(cand_race in candidate_races) {
    main_term <- paste0("race::", cand_race)
    
    if(resp_group == "White") {
      if(main_term %in% names(coefs)) {
        est <- coefs[main_term]
        var_sum <- vcov_mat[main_term, main_term]
      } else {
        est <- NA
        var_sum <- NA
      }
    } else {
      # The interaction terms are structured as: resp_var:race::candidate_race
      if(resp_group == "Asian") {
        int_term <- paste0("resp_asian:race::", cand_race)
      } else if(resp_group == "Hispanic") {
        int_term <- paste0("resp_hispanic:race::", cand_race)
      } else if(resp_group == "Black") {
        int_term <- paste0("resp_black:race::", cand_race)
      }
      
      if(!int_term %in% names(coefs)) {
        res_list[[cand_race]] <- data.table(Respondent = resp_group, Candidate_Race = cand_race, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      
      if(main_term %in% names(coefs)) {
        est <- coefs[main_term] + coefs[int_term]
        v_main <- vcov_mat[main_term, main_term]
        v_int  <- vcov_mat[int_term, int_term]
        cov_mi <- vcov_mat[main_term, int_term]
        var_sum <- v_main + v_int + 2 * cov_mi
      } else {
        est <- coefs[int_term]
        var_sum <- vcov_mat[int_term, int_term]
      }
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand_race]] <- data.table(Respondent = resp_group, Candidate_Race = cand_race, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function for Plotting - Race Only (Collapsing on / Ignoring Gender)
plot_heterogeneity_race_collapsedongender <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role) {
  
  respondent_groups <- c("White", "Asian", "Hispanic", "Black")
  
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_race_collapsedongender(model, g), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Respondent = g, Candidate_Race = "White", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))
  
  plot_data <- plot_data[Respondent != "Other"]
  
  # Set factor order for Respondent FIRST
  plot_data[, Respondent := factor(Respondent, levels = c("White", "Asian", "Hispanic", "Black"))]
  
  # Add N counts to respondent labels
  if(!is.null(resp_counts)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    resp_counts_subset <- resp_counts[, .(resp_race, N = get(N_col))]
    plot_data <- plot_data[resp_counts_subset, on = c(Respondent = "resp_race")]
    plot_data[, Respondent_Label := paste0(Respondent, " (N=", N, ")")]
    
    # Set factor order for Respondent_Label explicitly
    respondent_label_order <- c(
      paste0("White (N=", resp_counts_subset[resp_race == "White", N], ")"),
      paste0("Asian (N=", resp_counts_subset[resp_race == "Asian", N], ")"),
      paste0("Hispanic (N=", resp_counts_subset[resp_race == "Hispanic", N], ")"),
      paste0("Black (N=", resp_counts_subset[resp_race == "Black", N], ")")
    )
    plot_data[, Respondent_Label := factor(Respondent_Label, levels = respondent_label_order)]
  } else {
    plot_data[, Respondent_Label := Respondent]
  }
  
  plot_data[, Candidate_Race := factor(Candidate_Race, levels = c("Hispanic", "Asian", "White"))]
  
  # Create match status based on race concordance
  plot_data[, Match_Status := ifelse(as.character(Respondent) == as.character(Candidate_Race), "Concordant Race", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Race"))]
  
  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Race)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Respondent_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Race" = "#D55E00")) +
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")
  
  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

## Function for Linear Combination Test - Gender Only
total_effects_lincom_gender <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  candidate_demographics <- c("White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")
  res_list <- list()

  for(cand in candidate_demographics) {
    main_term <- paste0("race_gender::", cand)
    
    if(resp_group == "Male") {
      est <- coefs[main_term]
      var_sum <- vcov_mat[main_term, main_term]
    } else {
      # For gender heterogeneity: resp_male interaction
      int_term <- paste0("race_gender::", cand, ":resp_male")
      
      if(!int_term %in% names(coefs)) {
        res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      # For Female respondents, we need main - interaction (since resp_male=0 for females)
      est <- coefs[main_term] + coefs[int_term]
      v_main <- vcov_mat[main_term, main_term]
      v_int  <- vcov_mat[int_term, int_term]
      cov_mi <- vcov_mat[main_term, int_term]
      var_sum <- v_main + v_int + 2 * cov_mi
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function for Individually Plotting Total Effects - Gender Only
plot_heterogeneity_gender <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role) {
  
  respondent_groups <- c("Male", "Female")
  
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_gender(model, g), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Respondent = g, Candidate = "White_Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))

  # Set factor order for Respondent FIRST
  plot_data[, Respondent := factor(Respondent, levels = c("Male", "Female"))]
  
  # Add N counts to respondent labels
  if(!is.null(resp_counts)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    resp_counts_subset <- resp_counts[, .(resp_gender, N = get(N_col))]
    plot_data <- plot_data[resp_counts_subset, on = c(Respondent = "resp_gender")]
    plot_data[, Respondent_Label := paste0(Respondent, " (N=", N, ")")]
    
    # Set factor order for Respondent_Label explicitly
    respondent_label_order <- c(
      paste0("Male (N=", resp_counts_subset[resp_gender == "Male", N], ")"),
      paste0("Female (N=", resp_counts_subset[resp_gender == "Female", N], ")")
    )
    plot_data[, Respondent_Label := factor(Respondent_Label, levels = respondent_label_order)]
  } else {
    plot_data[, Respondent_Label := Respondent]
  }

  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", "Asian_Male" = "AM", "Asian_Female" = "AF", "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "AF", "AM", "WF", "WM"))]
  
  # Extract gender from candidate
  plot_data[, Candidate_Gender := fcase(
    Candidate %in% c("White_Male", "Asian_Male", "Hispanic_Male"), "Male",
    Candidate %in% c("White_Female", "Asian_Female", "Hispanic_Female"), "Female",
    default = "Other"
  )]
  
  # Create match status based on gender concordance
  plot_data[, Match_Status := ifelse(as.character(Respondent) == Candidate_Gender, "Concordant Gender", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Gender"))]

  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Respondent_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Gender" = "#D55E00")) +
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")

  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

## Function for Linear Combination Test - Gender Only (Collapsing on / Ignoring Race)
total_effects_lincom_gender_collapsedonrace <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  candidate_genders <- c("Male", "Female")
  res_list <- list()

  for(cand_gender in candidate_genders) {
    main_term <- paste0("gender::", cand_gender)
    
    if(resp_group == "Male") {
      if(main_term %in% names(coefs)) {
        est <- coefs[main_term]
        var_sum <- vcov_mat[main_term, main_term]
      } else {
        est <- NA
        var_sum <- NA
      }
    } else {
      # For Female respondents: resp_male interaction
      int_term <- paste0("gender::", cand_gender, ":resp_male")
      
      if(!int_term %in% names(coefs)) {
        res_list[[cand_gender]] <- data.table(Respondent = resp_group, Candidate_Gender = cand_gender, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      
      if(main_term %in% names(coefs)) {
        est <- coefs[main_term] + coefs[int_term]
        v_main <- vcov_mat[main_term, main_term]
        v_int  <- vcov_mat[int_term, int_term]
        cov_mi <- vcov_mat[main_term, int_term]
        var_sum <- v_main + v_int + 2 * cov_mi
      } else {
        est <- coefs[int_term]
        var_sum <- vcov_mat[int_term, int_term]
      }
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand_gender]] <- data.table(Respondent = resp_group, Candidate_Gender = cand_gender, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function for Plotting - Gender Only (Collapsing on / Ignoring Race)
plot_heterogeneity_gender_collapsedonrace <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role) {
  
  respondent_groups <- c("Male", "Female")
  
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_gender_collapsedonrace(model, g), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Respondent = g, Candidate_Gender = "Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))
  
  # Set factor order for Respondent FIRST
  plot_data[, Respondent := factor(Respondent, levels = c("Male", "Female"))]
  
  # Add N counts to respondent labels
  if(!is.null(resp_counts)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    resp_counts_subset <- resp_counts[, .(resp_gender, N = get(N_col))]
    plot_data <- plot_data[resp_counts_subset, on = c(Respondent = "resp_gender")]
    plot_data[, Respondent_Label := paste0(Respondent, " (N=", N, ")")]
    
    # Set factor order for Respondent_Label explicitly
    respondent_label_order <- c(
      paste0("Male (N=", resp_counts_subset[resp_gender == "Male", N], ")"),
      paste0("Female (N=", resp_counts_subset[resp_gender == "Female", N], ")")
    )
    plot_data[, Respondent_Label := factor(Respondent_Label, levels = respondent_label_order)]
  } else {
    plot_data[, Respondent_Label := Respondent]
  }
  
  plot_data[, Candidate_Gender := factor(Candidate_Gender, levels = c("Female", "Male"))]
  
  # Create match status based on gender concordance
  plot_data[, Match_Status := ifelse(as.character(Respondent) == as.character(Candidate_Gender), "Concordant Gender", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Gender"))]
  
  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Gender)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Respondent_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Gender" = "#D55E00")) +
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")
  
  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

## Function for Linear Combination Test - Race and Gender Together
total_effects_lincom_racegender <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  candidate_demographics <- c("White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")
  res_list <- list()

  for(cand in candidate_demographics) {
    main_term <- paste0("race_gender::", cand)
    if(resp_group == "White_Male") {
      est <- coefs[main_term]
      var_sum <- vcov_mat[main_term, main_term]
    } else {
      int_term <- paste0("resp_race_gender::", resp_group, ":race_gender::", cand)
      if(!int_term %in% names(coefs)) {
        res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      est <- coefs[main_term] + coefs[int_term]
      v_main <- vcov_mat[main_term, main_term]
      v_int  <- vcov_mat[int_term, int_term]
      cov_mi <- vcov_mat[main_term, int_term]
      var_sum <- v_main + v_int + 2 * cov_mi
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function for Individually Plotting Total Effects - Race and Gender Together
plot_heterogeneity_racegender <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role = NULL) {
  
  respondent_groups <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")
  
  # Generate Data
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_racegender(model, g), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Respondent = g, Candidate = "White_Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))

  # Abbreviations Map
  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", "Asian_Male" = "AM", "Asian_Female" = "AF", "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  
  # Process Panel Headers (Respondent Labels)
  if(!is.null(resp_counts) && !is.null(role)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    counts_sub <- resp_counts[, .(resp_race_gender, N = get(N_col))]
    
    # FIX: Use merge(all.x=TRUE) to strictly keep only the 6 plotting groups
    # This drops any NA/Other rows that might be in counts_sub
    plot_data <- merge(plot_data, counts_sub, by.x = "Respondent", by.y = "resp_race_gender", all.x = TRUE)
    plot_data[is.na(N), N := 0] # Fill NAs with 0 if missing
    
    # Create Label with N (e.g., "WM (N=32)")
    plot_data[, Panel_Label := paste0(abbrevs[as.character(Respondent)], " (N=", N, ")")]
    
    # Create factor order matching standard demographic order
    ordered_levels <- character(0)
    for(g in respondent_groups) {
       n_val <- unique(plot_data[Respondent == g, N])
       if(length(n_val) > 0) {
         ordered_levels <- c(ordered_levels, paste0(abbrevs[g], " (N=", n_val, ")"))
       }
    }
    plot_data[, Panel_Label := factor(Panel_Label, levels = ordered_levels)]
    
  } else {
    # Fallback if no counts provided
    plot_data[, Panel_Label := abbrevs[as.character(Respondent)]]
    plot_data[, Panel_Label := factor(Panel_Label, levels = c("WM", "WF", "AM", "AF", "HM", "HF"))]
  }

  # Process Y-Axis (Candidate Labels)
  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "AF", "AM", "WF", "WM"))]
  
  # Match Status
  plot_data[, Match_Status := ifelse(as.character(Respondent) == as.character(Candidate), "Concordant Demographic", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Demographic"))]

  # Plot
  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Panel_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Demographic" = "#D55E00")) + 
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")

  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

## Function for Linear Combination Test - Detailed Race & Gender
total_effects_lincom_detailed_race_gender <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  candidate_demographics <- c("White_Female", 
                              "Chinese_Male", "Chinese_Female", 
                              "Indian_Male", "Indian_Female", 
                              "Hispanic_Male", "Hispanic_Female")
  res_list <- list()

  for(cand in candidate_demographics) {
    main_term <- paste0("race_gender_detailed::", cand)
    if(resp_group == "White_Male") {
      if(main_term %in% names(coefs)) {
        est <- coefs[main_term]
        var_sum <- vcov_mat[main_term, main_term]
      } else {
        est <- NA; var_sum <- NA
      }
    } else {
      int_term <- paste0("resp_race_gender_detailed::", resp_group, ":race_gender_detailed::", cand)
      if(!int_term %in% names(coefs)) {
        res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      if(main_term %in% names(coefs)) {
        est <- coefs[main_term] + coefs[int_term]
        v_main <- vcov_mat[main_term, main_term]
        v_int  <- vcov_mat[int_term, int_term]
        cov_mi <- vcov_mat[main_term, int_term]
        var_sum <- v_main + v_int + 2 * cov_mi
      } else {
        est <- coefs[int_term]
        var_sum <- vcov_mat[int_term, int_term]
      }
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function for Linear Combination Test - Recentered to Concordant Group
total_effects_lincom_detailed_race_gender_recentered <- function(model, resp_group) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  
  candidate_demographics <- c("White_Male", "White_Female", 
                              "Chinese_Male", "Chinese_Female", 
                              "Indian_Male", "Indian_Female", 
                              "Hispanic_Male", "Hispanic_Female")
  
  # Build linear combination vector for each candidate
  build_lc <- function(cand) {
    lc <- rep(0, length(coefs))
    names(lc) <- names(coefs)
    
    if (cand != "White_Male") {
      main_term <- paste0("race_gender_detailed::", cand)
      if (main_term %in% names(coefs)) lc[main_term] <- 1
    }
    if (resp_group != "White_Male" && cand != "White_Male") {
      int_term <- paste0("resp_race_gender_detailed::", resp_group, ":race_gender_detailed::", cand)
      if (int_term %in% names(coefs)) lc[int_term] <- 1
    }
    return(lc)
  }
  
  # Get all LC vectors
  lc_list <- lapply(setNames(candidate_demographics, candidate_demographics), build_lc)
  
  # Concordant group LC (reference point)
  concordant_lc <- lc_list[[resp_group]]
  
  # Compute recentered estimates
  res_list <- list()
  for (cand in candidate_demographics) {
    if (cand == resp_group) {
      # Concordant: by definition 0
      res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, 
                                     Estimate = 0, SE = 0, Pval = 1, Label = "")
      next
    }
    
    diff_lc <- lc_list[[cand]] - concordant_lc
    est <- as.numeric(diff_lc %*% coefs)
    var_est <- as.numeric(t(diff_lc) %*% vcov_mat %*% diff_lc)
    
    if (is.na(var_est) || var_est <= 1e-14) { se <- NA } else { se <- sqrt(var_est) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score)))
      sig_label <- ""
      if (pval < 0.01) { sig_label <- "***" } 
      else if (pval < 0.05) { sig_label <- "**" } 
      else if (pval < 0.10) { sig_label <- "*" }
    }
    
    res_list[[cand]] <- data.table(Respondent = resp_group, Candidate = cand, 
                                   Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  
  return(rbindlist(res_list))
}

## Function for Plotting - Detailed Race & Gender WITH N COUNTS
plot_heterogeneity_detailed_race_gender <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role = NULL) {
  
  respondent_groups <- c("White_Male", "White_Female", 
                         "Chinese_Male", "Chinese_Female",
                         "Indian_Male", "Indian_Female",
                         "Hispanic_Male", "Hispanic_Female")
  
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_detailed_race_gender(model, g), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Respondent = g, Candidate = "White_Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))

  # Abbreviations Map
  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", 
               "Chinese_Male" = "ChM", "Chinese_Female" = "ChF",
               "Indian_Male" = "InM", "Indian_Female" = "InF",
               "Korean_Male" = "KoM", "Korean_Female" = "KoF",
               "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  
  # Process Panel Headers with N counts
  if(!is.null(resp_counts) && !is.null(role)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    counts_sub <- resp_counts[, .(resp_race_gender_detailed, N = get(N_col))]
    
    # Safe Merge
    plot_data <- merge(plot_data, counts_sub, by.x = "Respondent", by.y = "resp_race_gender_detailed", all.x = TRUE)
    plot_data[is.na(N), N := 0]
    
    # Create Label
    plot_data[, Panel_Label := paste0(abbrevs[as.character(Respondent)], " (N=", N, ")")]
    
    # Set Ordered Levels based on respondent_groups order
    ordered_levels <- character(0)
    for(g in respondent_groups) {
       n_val <- unique(plot_data[Respondent == g, N])
       if(length(n_val) > 0) {
         ordered_levels <- c(ordered_levels, paste0(abbrevs[g], " (N=", n_val, ")"))
       }
    }
    plot_data[, Panel_Label := factor(Panel_Label, levels = ordered_levels)]
    
  } else {
    plot_data[, Panel_Label := abbrevs[as.character(Respondent)]]
    plot_data[, Panel_Label := factor(Panel_Label, levels = c("WM", "WF", "ChM", "ChF", "InM", "InF", "KoM", "KoF", "HM", "HF"))]
  }

  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "InF", "InM", "ChF", "ChM", "WF", "WM"))]
  
  plot_data[, Match_Status := ifelse(as.character(Respondent) == as.character(Candidate), "Concordant Demographic", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Demographic"))]

  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Panel_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Demographic" = "#D55E00")) + 
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(breaks = c(-1, 0, 1)) + coord_cartesian(xlim = c(-1.4, 1.4), clip = "off")

  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

## Function for Plotting - Detailed Race & Gender WITH N COUNTS - Recentered to Concordant Group
plot_heterogeneity_detailed_race_gender_recentered <- function(model, plot_title, x_label, show_y_text = TRUE, resp_counts = NULL, role = NULL) {
  
  respondent_groups <- c("White_Male", "White_Female", 
                         "Chinese_Male", "Chinese_Female",
                         "Indian_Male", "Indian_Female",
                         "Hispanic_Male", "Hispanic_Female")
  
  plot_data <- rbindlist(lapply(respondent_groups, function(g) {
    dt <- tryCatch(total_effects_lincom_detailed_race_gender_recentered(model, g), error = function(e) return(NULL))
    return(dt)
  }))

  # Abbreviations Map
  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", 
               "Chinese_Male" = "ChM", "Chinese_Female" = "ChF",
               "Indian_Male" = "InM", "Indian_Female" = "InF",
               "Korean_Male" = "KoM", "Korean_Female" = "KoF",
               "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  
  # Process Panel Headers with N counts
  if(!is.null(resp_counts) && !is.null(role)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    counts_sub <- resp_counts[, .(resp_race_gender_detailed, N = get(N_col))]
    
    # Safe Merge
    plot_data <- merge(plot_data, counts_sub, by.x = "Respondent", by.y = "resp_race_gender_detailed", all.x = TRUE)
    plot_data[is.na(N), N := 0]
    
    # Create Label
    plot_data[, Panel_Label := paste0(abbrevs[as.character(Respondent)], " (N=", N, ")")]
    
    # Set Ordered Levels based on respondent_groups order
    ordered_levels <- character(0)
    for(g in respondent_groups) {
       n_val <- unique(plot_data[Respondent == g, N])
       if(length(n_val) > 0) {
         ordered_levels <- c(ordered_levels, paste0(abbrevs[g], " (N=", n_val, ")"))
       }
    }
    plot_data[, Panel_Label := factor(Panel_Label, levels = ordered_levels)]
    
  } else {
    plot_data[, Panel_Label := abbrevs[as.character(Respondent)]]
    plot_data[, Panel_Label := factor(Panel_Label, levels = c("WM", "WF", "ChM", "ChF", "InM", "InF", "KoM", "KoF", "HM", "HF"))]
  }

  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "InF", "InM", "ChF", "ChM", "WF", "WM"))]
  
  plot_data[, Match_Status := ifelse(as.character(Respondent) == as.character(Candidate), "Concordant Demographic", "Nonconcordant")]
  plot_data[, Match_Status := factor(Match_Status, levels = c("Nonconcordant", "Concordant Demographic"))]

  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Match_Status), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Match_Status), 
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Panel_Label) +
    scale_color_manual(values = c("Nonconcordant" = "black", "Concordant Demographic" = "#D55E00")) + 
    labs(title = plot_title, x = x_label, y = NULL, color = "") + 
    theme_bw(base_size = 10) +
    theme(
      legend.position = "bottom", legend.margin = margin(t = -5, b=0, unit="pt"),
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(breaks = c(-1, 0, 1)) + coord_cartesian(xlim = c(-1.4, 1.4), clip = "off")

  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

##### ##### ##### Functions for Calculating and Plotting Preferences by DEI ##### ##### #####

## Function: Calculate Total Effects for DEI Groups (0 vs 1)
total_effects_lincom_dei <- function(model, group_val, dei_var_name) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  coef_names <- names(coefs)
  
  candidate_demographics <- c("White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")
  res_list <- list()

  for(cand in candidate_demographics) {
    
    # --- A. Find Main Effect ---
    # Based on your output: "race_gender::White_Female"
    term_main <- paste0("race_gender::", cand)
    
    # Check if it exists
    if (!(term_main %in% coef_names)) {
      term_main <- NULL
    }
    
    # --- B. Find Interaction Effect ---
    # Based on your output: "race_gender::Candidate:factor(resp_pro_dei_race)::1"
    term_int <- paste0("race_gender::", cand, ":factor(", dei_var_name, ")::1")
    
    # Check if it exists
    if (!(term_int %in% coef_names)) {
      term_int <- NULL
    }

    # --- C. Calculate Estimate & Variance ---
    est <- NA
    var_sum <- NA
    
    if(group_val == 0) {
      # Group 0 (Neutral/Anti-DEI): Main Effect Only
      if(!is.null(term_main)) {
        est <- coefs[term_main]
        var_sum <- vcov_mat[term_main, term_main]
      }
    } else {
      # Group 1 (Pro-DEI): Main + Interaction
      if(!is.null(term_main) && !is.null(term_int)) {
        est <- coefs[term_main] + coefs[term_int]
        v1 <- vcov_mat[term_main, term_main]
        v2 <- vcov_mat[term_int, term_int]
        cov <- vcov_mat[term_main, term_int]
        var_sum <- v1 + v2 + 2 * cov
      } 
      # Fallback: If interaction dropped due to collinearity, use Main
      else if (!is.null(term_main)) {
        est <- coefs[term_main]
        var_sum <- vcov_mat[term_main, term_main]
      }
    }
    
    # --- D. Statistics ---
    if (is.na(var_sum) || var_sum <= 1e-14) { 
        se <- NA; pval <- NA; sig_label <- "" 
    } else { 
        se <- sqrt(var_sum)
        z_score <- est / se
        pval <- 2 * (1 - pnorm(abs(z_score))) 
        sig_label <- fcase(pval < 0.01, "***", pval < 0.05, "**", pval < 0.1, "*", default = "")
    }
    
    res_list[[cand]] <- data.table(Group = group_val, Candidate = cand, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function: Plot DEI Heterogeneity
plot_heterogeneity_dei <- function(model, plot_title, dei_var_col, resp_counts, role) {
  
  # Generate Estimates
  plot_data <- rbindlist(lapply(c(0, 1), function(g) {
    dt <- tryCatch(total_effects_lincom_dei(model, g, dei_var_col), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(Group = g, Candidate = "White_Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))
  
  if(nrow(plot_data) == 0) return(ggplot() + theme_void() + labs(title = "No Data Found"))

  # Get Counts (Robust)
  N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
  
  # Ensure clean matching for counts
  n_0 <- tryCatch(resp_counts[as.character(get(dei_var_col)) == "0", get(N_col)], error = function(e) 0)
  if(length(n_0) == 0) n_0 <- 0
  n_1 <- tryCatch(resp_counts[as.character(get(dei_var_col)) == "1", get(N_col)], error = function(e) 0)
  if(length(n_1) == 0) n_1 <- 0
  
  # Create Labels
  plot_data[, Panel_Label := fcase(
    Group == 0, paste0("Neutral/Anti-DEI\n(N=", n_0, ")"),
    Group == 1, paste0("Pro-DEI\n(N=", n_1, ")")
  )]
  plot_data[, Panel_Label := factor(Panel_Label, levels = c(paste0("Pro-DEI\n(N=", n_1, ")"), paste0("Neutral/Anti-DEI\n(N=", n_0, ")")))]

  # Formatting
  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", "Asian_Male" = "AM", "Asian_Female" = "AF", "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "AF", "AM", "WF", "WM"))]
  plot_data[, Color_Group := ifelse(Group == 1, "Pro", "Neutral")]

  # Plot
  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE, color = Color_Group), 
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label, color = Color_Group), vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE, show.legend = FALSE) +
    facet_grid(~ Panel_Label) +
    scale_color_manual(values = c("Neutral" = "black", "Pro" = "#D55E00")) +
    labs(title = plot_title, x = "Discrimination (Z)", y = NULL) + 
    theme_bw(base_size = 10) +
    theme(
      strip.text = element_text(face = "bold", size = 9), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm")
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")

  return(p)
}

##### ##### ##### Functions for Calculating and Plotting Preferences by Firm Size ##### ##### #####

## Function: Calculate Total Effects for Firm Size Groups
total_effects_lincom_firmsize <- function(model, firm_size) {
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  
  candidate_demographics <- c("White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")
  res_list <- list()

  for(cand in candidate_demographics) {
    main_term <- paste0("race_gender::", cand)
    
    if(firm_size == "small") {
      # Small firms: Main effect only
      est <- coefs[main_term]
      var_sum <- vcov_mat[main_term, main_term]
      
    } else if(firm_size == "mid") {
      # Mid firms: Main + mid interaction
      int_term <- paste0("race_gender::", cand, ":firm_size_mid")
      
      if(!int_term %in% names(coefs)) {
        res_list[[cand]] <- data.table(FirmSize = firm_size, Candidate = cand, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      
      est <- coefs[main_term] + coefs[int_term]
      v_main <- vcov_mat[main_term, main_term]
      v_int  <- vcov_mat[int_term, int_term]
      cov_mi <- vcov_mat[main_term, int_term]
      var_sum <- v_main + v_int + 2 * cov_mi
      
    } else if(firm_size == "large") {
      # Large firms: Main + large interaction
      int_term <- paste0("race_gender::", cand, ":firm_size_large")
      
      if(!int_term %in% names(coefs)) {
        res_list[[cand]] <- data.table(FirmSize = firm_size, Candidate = cand, Estimate = NA, SE = NA, Pval = NA, Label = "")
        next
      }
      
      est <- coefs[main_term] + coefs[int_term]
      v_main <- vcov_mat[main_term, main_term]
      v_int  <- vcov_mat[int_term, int_term]
      cov_mi <- vcov_mat[main_term, int_term]
      var_sum <- v_main + v_int + 2 * cov_mi
    }
    
    if (is.na(var_sum) || var_sum <= 1e-14) { se <- NA } else { se <- sqrt(var_sum) }
    if (is.na(se)) { pval <- NA; sig_label <- "" } else {
      z_score <- est / se
      pval <- 2 * (1 - pnorm(abs(z_score))) 
      sig_label <- ""
      if(pval < 0.01) {sig_label <- "***"} else if(pval < 0.05) {sig_label <- "**"} else if(pval < 0.10) {sig_label <- "*"}
    }
    res_list[[cand]] <- data.table(FirmSize = firm_size, Candidate = cand, Estimate = est, SE = se, Pval = pval, Label = sig_label)
  }
  return(rbindlist(res_list))
}

## Function: Plot Firm Size Heterogeneity
plot_heterogeneity_firmsize <- function(model, plot_title, x_label, show_y_text = TRUE, firm_counts = NULL, role) {
  
  firm_sizes <- c("small", "mid", "large")
  
  plot_data <- rbindlist(lapply(firm_sizes, function(fs) {
    dt <- tryCatch(total_effects_lincom_firmsize(model, fs), error = function(e) return(NULL))
    if(!is.null(dt)) {
      ref_row <- data.table(FirmSize = fs, Candidate = "White_Male", Estimate = 0, SE = 0, Pval = 1, Label = "")
      dt <- rbind(dt, ref_row)
    }
    return(dt)  
  }))
  
  # Set factor order for FirmSize FIRST
  plot_data[, FirmSize := factor(FirmSize, levels = c("small", "mid", "large"))]
  
  # Add N counts to firm size labels
  if(!is.null(firm_counts)) {
    N_col <- ifelse(role == "HR", "N_HR", "N_Eng")
    firm_counts_subset <- firm_counts[, .(firm_size, N = get(N_col))]
    plot_data <- plot_data[firm_counts_subset, on = c(FirmSize = "firm_size")]
    plot_data[, FirmSize_Label := paste0(toupper(substring(FirmSize, 1, 1)), substring(FirmSize, 2), " (N=", N, ")")]
    
    # Set factor order for FirmSize_Label explicitly
    firmsize_label_order <- c(
      paste0("Small (N=", firm_counts_subset[firm_size == "small", N], ")"),
      paste0("Mid (N=", firm_counts_subset[firm_size == "mid", N], ")"),
      paste0("Large (N=", firm_counts_subset[firm_size == "large", N], ")")
    )
    plot_data[, FirmSize_Label := factor(FirmSize_Label, levels = firmsize_label_order)]
  } else {
    plot_data[, FirmSize_Label := paste0(toupper(substring(FirmSize, 1, 1)), substring(FirmSize, 2))]
    plot_data[, FirmSize_Label := factor(FirmSize_Label, levels = c("Small", "Mid", "Large"))]
  }
  
  abbrevs <- c("White_Male" = "WM", "White_Female" = "WF", "Asian_Male" = "AM", "Asian_Female" = "AF", "Hispanic_Male" = "HM", "Hispanic_Female" = "HF")
  plot_data[, Candidate_Abbr := abbrevs[as.character(Candidate)]]
  plot_data[, Candidate_Abbr := factor(Candidate_Abbr, levels = c("HF", "HM", "AF", "AM", "WF", "WM"))]
  
  p <- ggplot(plot_data, aes(x = Estimate, y = Candidate_Abbr)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Estimate - 1.96*SE, xmax = Estimate + 1.96*SE), 
                    color = "black",
                    size = 0.4, position = position_dodge(width = 0.5), na.rm = TRUE) +
    geom_text(aes(label = Label), 
              color = "black",
              vjust = -0.6, fontface = "bold", size = 3, na.rm = TRUE) +
    facet_grid(~ FirmSize_Label) +
    labs(title = plot_title, x = x_label, y = NULL) + 
    theme_bw(base_size = 10) +
    theme(
      strip.text = element_text(face = "bold", size = 8), 
      axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 7),
      panel.spacing = unit(0.1, "cm"), plot.margin = margin(5, 5, 5, 5)
    ) +
    scale_x_continuous(n.breaks = 3) + coord_cartesian(xlim = c(-1.25, 1.25), clip = "off")
  
  if(show_y_text == FALSE) {
    p <- p + theme(axis.text.y = element_blank(), axis.ticks.y = element_blank())
  }
  return(p)
}

##### ##### ##### Functions for Plotting Side-by-Side ##### ##### #####

## Function for Plotting HR and Engineer Graphs Side-by-Side on One Dimension
hetero_side_by_side_plots <- function(p_hr, p_eng, title_text) {
  #### Combine Graphs
  legend <- get_legend(p_hr + theme(legend.box.margin = margin(0, 0, 0, 12)))
  prow <- plot_grid(
    p_hr + theme(legend.position="none"),
    p_eng + theme(legend.position="none"),
    align = 'vh', 
    labels = NULL, 
    hjust = -1, 
    nrow = 1, 
    rel_widths = c(1, 0.95)
  )
  
  #### Add y-axis label
  y_label <- ggdraw() + 
    draw_label("Applicant Demographic", size = 10, fontface = "bold", angle = 90)
  
  #### Combine y-axis label with plots
  prow_with_ylabel <- plot_grid(
    y_label,
    prow,
    ncol = 2,
    rel_widths = c(0.02, 1)
  )
  
  #### Output Plots Side-by-Side
  combined_plot <- plot_grid(prow_with_ylabel, legend, ncol = 1, rel_heights = c(1, .1))
  
  ###### Title
  title <- ggdraw() + 
    draw_label(title_text, fontface = "bold", size = 14, hjust = 0.5)
  
  ###### Caption
  caption <- ggdraw() + 
    draw_label("*** p < 0.01, ** p < 0.05, * p < 0.10", 
    fontface = "plain", size = 9, hjust = 0.5)
  
  ##### Add Title and Caption
  final_plot <- plot_grid(
    title,
    combined_plot,
    caption,
    ncol = 1,
    rel_heights = c(0.05, 1, 0.05)
  )
  
  return(final_plot)
}

## Function for Plotting HR and Engineer Graphs Side-by-Side on Concordance
plot_simple_concordance <- function(model_hr, model_eng = NULL, title) {
  
  # Helper to extract data from a model
  get_data <- function(m, role_label) {
    if(is.null(m)) return(NULL) # Safety check
    
    ests <- broom::tidy(m, conf.int = TRUE)
    term_name <- grep("concordance", ests$term, value=TRUE)
    row <- ests[ests$term == term_name, ]
    
    data.table(
      Role = role_label,
      Estimate = row$estimate,
      Conf.Low = row$conf.low,
      Conf.High = row$conf.high,
      Pval = row$p.value
    )
  }
  
  # 1. Get HR Data
  dt_hr <- get_data(model_hr, "HR Managers")
  
  # 2. Get Eng Data (Only if model provided)
  if (!is.null(model_eng)) {
    dt_eng <- get_data(model_eng, "Engineers")
    dt <- rbind(dt_hr, dt_eng)
  } else {
    dt <- dt_hr
  }
  
  # Add Significance Labels
  dt[, Label := fcase(
    Pval < 0.01, "***",
    Pval < 0.05, "**",
    Pval < 0.10, "*",
    default = ""
  )]
  
  # Plot
  ggplot(dt, aes(x = Estimate, y = Role)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_pointrange(aes(xmin = Conf.Low, xmax = Conf.High), 
                    color = "#D55E00", size = 0.8) +
    geom_text(aes(label = Label), vjust = -0.5, fontface = "bold", size = 4) +
    labs(title = title, x = "Preference for Own Group", y = "") +
    theme_bw(base_size = 11) +
    scale_x_continuous(limits = c(-0.5, 0.5))
}

```

## By Concordant Race (using detailed Asian categorization)

```{r concordant_race, echo = FALSE, results = 'asis'}
models_hr_concordance_race  <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_race_detailed | resume_index + responseid + r_do,
          data = firm_long_dt[treat=="nonblind" & role=="HR" & resp_race %in% c("White", "Asian", "Hispanic")], vcov=~responseid)
))
names(models_hr_concordance_race) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

models_eng_concordance_race <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_race_detailed | resume_index + responseid + r_do, 
          data = firm_long_dt[treat=="nonblind" & role=="Eng" & resp_race %in% c("White", "Asian", "Hispanic")], vcov=~responseid)
))
names(models_eng_concordance_race) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

chk <- "\\checkmark"

tbl <- etable(
  c(models_hr_concordance_race, models_eng_concordance_race),
  tex = TRUE, style.tex = style.tex("aer"),
  keep = "%concordance",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  dict = c("concordance_race_detailed" = "Concordant Race"),
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  extralines = list(
    "Resume (Content) FE" = rep(chk, 9),
    "Respondent FE" = rep(chk, 9),
    "Display Position FE" = rep(chk, 9)
  ),
  title = "Effect of Racial Concordance on Scores",
  notes = "Standard errors clustered by respondent."
)

# Inject spanning headers
n_hr <- uniqueN(firm_long_dt[treat == "nonblind" & role == "HR", responseid])
n_eng <- uniqueN(firm_long_dt[treat == "nonblind" & role == "Eng", responseid])

tbl <- sub(
    "\\\\toprule",
    paste0("\\\\toprule & \\\\multicolumn{5}{c}{\\\\textbf{Panel A: HR (Non-blind, N = ", n_hr, ")}} & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer (Non-blind, N = ", n_eng, ")}} \\\\\\\\ \\\\cmidrule(lr){2-6} \\\\cmidrule(lr){7-10}"),
    tbl
)

# Remove auto-generated dep var row
tbl <- gsub("\\s*&\\s*\\\\multicolumn\\{9\\}\\{c\\}\\{.*?\\}\\\\\\\\", "", tbl)

tbl_final <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)

cat(tbl_final)

rm(models_hr_concordance_race, models_eng_concordance_race,
   chk, n_hr, n_eng, tbl, tbl_final)
```


## By Concordant Gender (includes Male / Female respondents only)

```{r concordant_gender, echo = FALSE, results = 'asis'}

models_hr_concordance_gender  <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_gender | resume_index + responseid + r_do, 
        data = firm_long_dt[treat=="nonblind" & role=="HR" & resp_gender %in% c("Male", "Female")], vcov=~responseid)
  ))
names(models_hr_concordance_gender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")


models_eng_concordance_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_gender | resume_index + responseid + r_do,
        data = firm_long_dt[treat=="nonblind" & role=="Eng" & resp_gender %in% c("Male", "Female")], vcov=~responseid)
))
names(models_eng_concordance_gender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

chk <- "\\checkmark"

tbl <- etable(
  c(models_hr_concordance_gender, models_eng_concordance_gender),
  tex = TRUE, style.tex = style.tex("aer"),
  keep = "%concordance",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  dict = c("concordance_gender" = "Concordant Gender"),
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  extralines = list(
    "Resume (Content) FE" = rep(chk, 9),
    "Respondent FE" = rep(chk, 9),
    "Display Position FE" = rep(chk, 9)
  ),
  title = "Effect of Racial Concordance on Scores",
  notes = "Standard errors clustered by respondent."
)

# Inject spanning headers
n_hr <- uniqueN(firm_long_dt[treat == "nonblind" & role == "HR", responseid])
n_eng <- uniqueN(firm_long_dt[treat == "nonblind" & role == "Eng", responseid])

tbl <- sub(
    "\\\\toprule",
    paste0("\\\\toprule & \\\\multicolumn{5}{c}{\\\\textbf{Panel A: HR (Non-blind, N = ", n_hr, ")}} & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer (Non-blind, N = ", n_eng, ")}} \\\\\\\\ \\\\cmidrule(lr){2-6} \\\\cmidrule(lr){7-10}"),
    tbl
)

# Remove auto-generated dep var row
tbl <- gsub("\\s*&\\s*\\\\multicolumn\\{9\\}\\{c\\}\\{.*?\\}\\\\\\\\", "", tbl)

tbl_final <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)

cat(tbl_final)

rm(models_hr_concordance_gender, models_eng_concordance_gender,
   chk, n_hr, n_eng, tbl, tbl_final)

```

<!-- ### By Concordant Race and Gender -->

```{r concordant_racegender, echo = FALSE, eval = FALSE, results = 'asis'}

models_hr_concordance_racegender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_race_gender | resume_index + responseid + r_do_bythree, 
        data = firm_long_dt[treat=="nonblind" & role=="HR" & resp_race_gender %in% c("White_Male", "White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")], vcov=~responseid)
))
names(models_hr_concordance_racegender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

models_eng_concordance_racegender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_race_gender | resume_index + responseid + r_do_bythree, 
        data = firm_long_dt[treat=="nonblind" & role=="Eng" & resp_race_gender %in% c("White_Male", "White_Female", "Asian_Male", "Asian_Female", "Hispanic_Male", "Hispanic_Female")], vcov=~responseid)
))
names(models_eng_concordance_racegender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

chk <- "\\checkmark"

tbl <- etable(
  c(models_hr_concordance_racegender, models_eng_concordance_racegender),
  tex = TRUE, style.tex = style.tex("aer"),
  keep = "%concordance",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  dict = c("concordance_race" = "Concordant Race"),
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  extralines = list(
    "Resume (Content) FE" = rep(chk, 9),
    "Respondent FE" = rep(chk, 9),
    "Display Position FE" = rep(chk, 9)
  ),
  title = "Effect of Racial Concordance on Scores",
  notes = "Standard errors clustered by respondent."
)

# Inject spanning headers
n_hr <- uniqueN(firm_long_dt[treat == "nonblind" & role == "HR", responseid])
n_eng <- uniqueN(firm_long_dt[treat == "nonblind" & role == "Eng", responseid])

tbl <- sub(
    "\\\\toprule",
    paste0("\\\\toprule & \\\\multicolumn{5}{c}{\\\\textbf{Panel A: HR (Non-blind, N = ", n_hr, ")}} & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer (Non-blind, N = ", n_eng, ")}} \\\\\\\\ \\\\cmidrule(lr){2-6} \\\\cmidrule(lr){7-10}"),
    tbl
)

# Remove auto-generated dep var row
tbl <- gsub("\\s*&\\s*\\\\multicolumn\\{9\\}\\{c\\}\\{.*?\\}\\\\\\\\", "", tbl)

tbl_final <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)

cat(tbl_final)

rm(models_hr_concordance_racegender, models_eng_concordance_racegender,
   chk, n_hr, n_eng, tbl, tbl_final)

```

## By Concordant Race and Gender (using detailed Asian categorization)

```{r concordant_racegender_detailed, echo = FALSE, results = 'asis'}

models_hr_concordance_detailed <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_race_gender_detailed | resume_index + responseid + r_do_bythree, 
        data = firm_long_dt[treat=="nonblind" & role=="HR" & resp_race_gender_detailed %in% c("White_Male", "White_Female", "Hispanic_Male", "Hispanic_Female", "Chinese_Male", "Chinese_Female", "Indian_Male", "Indian_Female")], vcov=~responseid)
))
names(models_hr_concordance_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

models_eng_concordance_detailed <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_race_gender_detailed | resume_index + responseid + r_do_bythree, 
        data = firm_long_dt[treat=="nonblind" & role=="Eng" & resp_race_gender_detailed %in% c("White_Male", "White_Female", "Hispanic_Male", "Hispanic_Female", "Chinese_Male", "Chinese_Female", "Indian_Male", "Indian_Female")], vcov=~responseid)
))
names(models_eng_concordance_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

chk <- "\\checkmark"

tbl <- etable(
  c(models_hr_concordance_detailed, models_eng_concordance_detailed),
  tex = TRUE, style.tex = style.tex("aer"),
  keep = "%concordance",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  dict = c("concordance_race_gender_detailed" = "Concordant Race Gender"),
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  extralines = list(
    "Resume (Content) FE" = rep(chk, 9),
    "Respondent FE" = rep(chk, 9),
    "Display Position FE" = rep(chk, 9)
  ),
  title = "Effect of Racial Concordance on Scores",
  notes = "Standard errors clustered by respondent."
)

# Inject spanning headers
n_hr <- uniqueN(firm_long_dt[treat == "nonblind" & role == "HR", responseid])
n_eng <- uniqueN(firm_long_dt[treat == "nonblind" & role == "Eng", responseid])

tbl <- sub(
    "\\\\toprule",
    paste0("\\\\toprule & \\\\multicolumn{5}{c}{\\\\textbf{Panel A: HR (Non-blind, N = ", n_hr, ")}} & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer (Non-blind, N = ", n_eng, ")}} \\\\\\\\ \\\\cmidrule(lr){2-6} \\\\cmidrule(lr){7-10}"),
    tbl
)

# Remove auto-generated dep var row
tbl <- gsub("\\s*&\\s*\\\\multicolumn\\{9\\}\\{c\\}\\{.*?\\}\\\\\\\\", "", tbl)

tbl_final <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)

cat(tbl_final)

rm(models_hr_concordance_detailed, models_eng_concordance_detailed,
   chk, n_hr, n_eng, tbl, tbl_final)

```


### Who drives Engineers' Bias Against Concordant Race Gender Groups

\vspace{0.25cm}
Below graph centers the concordant group.

```{r stage_pref_heterogeneity_detailed_ovr_only, eval = TRUE, echo = FALSE, out.width="100%", fig.width=14, fig.height=5, fig.align='center', results='asis'}

# --- 1. Regressions ---

models_hr_hetero_detailed <- suppressMessages(suppressWarnings(
    feols(
    c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
      i(race_gender_detailed, ref = "White_Male") + 
      i(resp_race_gender_detailed, race_gender_detailed, ref = "White_Male") 
    | resume_index + responseid + r_do_bythree,
    data = firm_long_dt[treat == "nonblind" & role == "HR" & resp_race_gender_detailed %in% c("White_Male", "White_Female", "Hispanic_Male", "Hispanic_Female", "Chinese_Male", "Chinese_Female", "Indian_Male", "Indian_Female")],
    vcov = ~ responseid
  )
))
names(models_hr_hetero_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

models_eng_hetero_detailed <- suppressMessages(suppressWarnings(
    feols(
    c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ 
      i(race_gender_detailed, ref = "White_Male") + 
      i(resp_race_gender_detailed, race_gender_detailed, ref = "White_Male") 
    | resume_index + responseid + r_do_bythree,
    data = firm_long_dt[treat == "nonblind" & role == "Eng" & resp_race_gender_detailed %in% c("White_Male", "White_Female", "Hispanic_Male", "Hispanic_Female", "Chinese_Male", "Chinese_Female", "Indian_Male", "Indian_Female")],
    vcov = ~ responseid
  )
))
names(models_eng_hetero_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

# --- 2. Calculate Counts for Labels ---

resp_counts_hetero_detailed <- firm_long_dt[treat == "nonblind" & resp_race_gender_detailed %in% c("White_Male", "White_Female", "Hispanic_Male", "Hispanic_Female", "Chinese_Male", "Chinese_Female", "Indian_Male", "Indian_Female") & race_gender_detailed %in% c("White_Male", "White_Female", "Hispanic_Male", "Hispanic_Female", "Chinese_Male", "Chinese_Female", "Indian_Male", "Indian_Female"), .(
  N_HR = uniqueN(responseid[role == "HR"]),
  N_Eng = uniqueN(responseid[role == "Eng"])
), by = .(resp_race_gender_detailed)]

# --- 3. Generate Plots ---
  
#### Overall
p_ovr_hr_det <- plot_heterogeneity_detailed_race_gender_recentered(models_hr_hetero_detailed$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
p_ovr_eng_det <- plot_heterogeneity_detailed_race_gender_recentered(models_eng_hetero_detailed$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

#### Coding
p_coding_hr_det <- plot_heterogeneity_detailed_race_gender_recentered(models_hr_hetero_detailed$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
p_coding_eng_det <- plot_heterogeneity_detailed_race_gender_recentered(models_eng_hetero_detailed$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

#### Fit
p_fit_hr_det <- plot_heterogeneity_detailed_race_gender_recentered(models_hr_hetero_detailed$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
p_fit_eng_det <- plot_heterogeneity_detailed_race_gender_recentered(models_eng_hetero_detailed$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

#### Stay
p_stay_hr_det <- plot_heterogeneity_detailed_race_gender_recentered(models_hr_hetero_detailed$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
p_stay_eng_det <- plot_heterogeneity_detailed_race_gender_recentered(models_eng_hetero_detailed$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

#### Advance
p_advance_hr_det <- plot_heterogeneity_detailed_race_gender_recentered(models_hr_hetero_detailed$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")  
p_empty <- ggplot() + annotate("text", x = 0, y = 0, label = "Engineers: Not Measured", size = 5, color = "gray50") + theme_void()

# --- 4. Print ---
suppressWarnings({
  
  # Overall
  p_full_interaction <- hetero_side_by_side_plots(p_ovr_hr_det, p_ovr_eng_det, "Overall (Z)")
  print(cowplot::plot_grid(p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # # Coding
  # p_full_interaction <- hetero_side_by_side_plots(p_coding_hr_det, p_coding_eng_det, "Coding (Z)")
  # print(cowplot::plot_grid(p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  # cat("\\newpage\n")
  # 
  # # Fit
  # p_full_interaction <- hetero_side_by_side_plots(p_fit_hr_det, p_fit_eng_det, "Fit (Z)")
  # print(cowplot::plot_grid(p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  # cat("\\newpage\n")
  # 
  # # Stay
  # p_full_interaction <- hetero_side_by_side_plots(p_stay_hr_det, p_stay_eng_det, "Stay (Z)")
  # print(cowplot::plot_grid(p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  # cat("\\newpage\n")
  # 
  # # Advance
  # p_full_interaction <- hetero_side_by_side_plots(p_advance_hr_det, p_empty, "Advance (0/1, LPM)")
  # print(cowplot::plot_grid(p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
})

Plot_Pref_Hetero_ConcodanceDetailed <- p_full_interaction

rm(models_hr_hetero_detailed, models_eng_hetero_detailed,
   resp_counts_hetero_detailed,
   p_ovr_hr_det, p_ovr_eng_det,
   p_coding_hr_det, p_coding_eng_det,
   p_fit_hr_det, p_fit_eng_det,
   p_stay_hr_det, p_stay_eng_det,
   p_advance_hr_det,
   p_full_interaction
)

```


\clearpage
# Heterogeneity in Preferences (By Respondent DEI / Diversity Preferencs)

\textcolor{blue}{\textbf{Takeaway}}: No individual DEI / diversity preference measure --- stated, revealed, or firm-level --- explains variation in demographic discrimination.

## (2-way Interaction Models) By Individual DEI / Diversity Variables

```{r dei_final_overall, eval = TRUE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr_nb  <- firm_long_dt[treat == "nonblind" & role == "HR"]
dt_eng_nb <- firm_long_dt[treat == "nonblind" & role == "Eng"]

proxies <- c(
  "pro_dei_race_z",
  "pro_dei_gender_z",
  "pro_diverse_z",
  "div_priority_z",
  "firm_attention_race_z",
  "firm_attention_gender_z"
)
col_labels <- c("Race DEI", "Gender DEI", "Diverse Wkpl", "Div Goal", "Firm Race Attn", "Firm Gender Attn")

fit_one <- function(d, pr) {
  feols(
    as.formula(sprintf(
      "sc_overall_z ~ i(race_gender, ref='White_Male') + i(race_gender, %s, ref='White_Male') | responseid + resume_index + r_do",
      pr)),
    data = d, vcov = ~ responseid
  )
}

models_hr  <- lapply(proxies, function(p) fit_one(dt_hr_nb,  p))
models_eng <- lapply(proxies, function(p) fit_one(dt_eng_nb, p))
all_models <- c(models_hr, models_eng)

groups <- c("White_Female"    = "White Female",
            "Asian_Male"      = "Asian Male",
            "Asian_Female"    = "Asian Female",
            "Hispanic_Male"   = "Hispanic Male",
            "Hispanic_Female" = "Hispanic Female")

# Collapse interaction coefficient names (one per proxy) into a single
# display label so each demographic's interaction row is shared across
# columns. NB: fixest names interactions from i(race_gender, proxy, ref=...)
# as "race_gender::<level>:<proxy>" (factor first, continuous after).
dict_main  <- setNames(unname(groups), paste0("race_gender::", names(groups)))
dict_inter <- unlist(lapply(proxies, function(p) {
  setNames(paste0(unname(groups), " $\\times$ Pro DEI/Diversity (Z)"),
           paste0("race_gender::", names(groups), ":", p))
}))
dict_all <- c(dict_main, dict_inter)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%race_gender",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume FE"     = rep(chk, 12),
    "Respondent FE" = rep(chk, 12),
    "Position FE"   = rep(chk, 12)
  )
)

# Inject header block above \toprule: Takeaway (italic) + Outcome Var
# (bold), then Panel A / Panel B labels, then short column names.
proxy_hdr <- paste(col_labels, collapse = " & ")

tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{13}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z)}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-7} \\\\cmidrule(lr){8-13}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)

tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
# Shrink font + tighten column padding + compress row height, all in a
# group scope so the changes don't leak out of the table.
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)


cat(tbl)

rm(dt_hr_nb, dt_eng_nb, proxies, col_labels, fit_one, models_hr, models_eng, all_models,
   groups, dict_main, dict_inter, dict_all, chk, tbl, proxy_hdr)
```

\scriptsize Standard errors clustered by respondent. Sample: non-blind arm. \normalsize

```{r dei_final_urm, eval = TRUE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr_nb  <- firm_long_dt[treat == "nonblind" & role == "HR"]
dt_eng_nb <- firm_long_dt[treat == "nonblind" & role == "Eng"]

zstd <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

## Combined indices: row-mean of two z-scored measures, re-standardized within sample.
dt_hr_nb [, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)), .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_eng_nb[, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)), .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_hr_nb [, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)), .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]
dt_eng_nb[, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)), .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]

proxies    <- c("pro_dei_view_z", "pro_diverse_z", "div_priority_z", "firm_attention_z")
col_labels <- c("DEI Views (R \\\\& G)", "Diverse Wkpl", "Div Goal", "Firm DEI Attn (R \\\\& G)")

fit_urm <- function(d, pr) {
  feols(
    as.formula(sprintf(
      "sc_overall_z ~ urm_tech + urm_tech:%s | responseid + resume_index + r_do",
      pr)),
    data = d, vcov = ~ responseid
  )
}

models_hr  <- lapply(proxies, function(p) fit_urm(dt_hr_nb,  p))
models_eng <- lapply(proxies, function(p) fit_urm(dt_eng_nb, p))
all_models <- c(models_hr, models_eng)

## Collapse interaction coef names into a single shared row.
dict_all <- c(
  "urm_tech" = "URM (WF, AF, HM, HF)",
  setNames(
    rep("URM $\\times$ Pro DEI/Diversity (Z)", length(proxies)),
    paste0("urm_tech:", proxies)
  )
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume FE"     = rep(chk, 8),
    "Respondent FE" = rep(chk, 8),
    "Position FE"   = rep(chk, 8)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{9}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z)}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-5} \\\\cmidrule(lr){6-9}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)

tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr_nb, dt_eng_nb, zstd, proxies, col_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, proxy_hdr)
```

\newpage
## (2-way Interaction Models) By Whether the Firm Targets the Same Applicant Demographic

\textcolor{blue}{\textbf{Takeaway}}: When a firm states it targets a demographic, its individual evaluators rate applicants of that group \textit{lower}, not higher --- more strongly among engineers than among HR. This mirrors the substitution pattern documented in Section \ref{sec:triple}: where institutional DEI effort is high, individual evaluators appear to ease off from the institutional push.

```{r dei_final_targets, eval = TRUE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr_nb  <- firm_long_dt[treat == "nonblind" & role == "HR"]
dt_eng_nb <- firm_long_dt[treat == "nonblind" & role == "Eng"]

## Prepare applicant-match indicators and combined firm-target dummies
prep <- function(d) {
  d[, appl_male     := as.integer(gender == "Male")]
  d[, appl_female   := as.integer(gender == "Female")]
  d[, appl_asian    := as.integer(race == "Asian")]
  d[, appl_hispanic := as.integer(race == "Hispanic")]
  d[, firm_targets_fh  := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
  d[, firm_targets_fhb := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L | firm_targets_black == 1L)]
  invisible(d)
}
prep(dt_hr_nb); prep(dt_eng_nb)

chk <- "\\checkmark"

## ---------- TOP: Single regression per role, four match interactions jointly ----------
fit_match_joint <- function(d) {
  feols(
    sc_overall_z ~ i(race_gender, ref = "White_Male")
                 + appl_male     : firm_targets_male
                 + appl_female   : firm_targets_female
                 + appl_asian    : firm_targets_asian
                 + appl_hispanic : firm_targets_hispanic
                 | responseid + resume_index + r_do,
    data = d, vcov = ~ responseid
  )
}

m_hr_t  <- fit_match_joint(dt_hr_nb)
m_eng_t <- fit_match_joint(dt_eng_nb)

dict_t <- c(
  "race_gender::White_Female"          = "White Female",
  "race_gender::Asian_Male"            = "Asian Male",
  "race_gender::Asian_Female"          = "Asian Female",
  "race_gender::Hispanic_Male"         = "Hispanic Male",
  "race_gender::Hispanic_Female"       = "Hispanic Female",
  "appl_male:firm_targets_male"        = "Applicant Male $\\times$ Firm Targets Male",
  "appl_female:firm_targets_female"    = "Applicant Female $\\times$ Firm Targets Female",
  "appl_asian:firm_targets_asian"      = "Applicant Asian $\\times$ Firm Targets Asian",
  "appl_hispanic:firm_targets_hispanic"= "Applicant Hispanic $\\times$ Firm Targets Hispanic"
)

tbl_t <- etable(
  list("HR" = m_hr_t, "Engineer" = m_eng_t),
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = c("%race_gender", "%appl_"),
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_t,
  extralines = list(
    "Resume FE"     = rep(chk, 2),
    "Respondent FE" = rep(chk, 2),
    "Position FE"   = rep(chk, 2)
  )
)

tbl_t <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{3}{c}{\\\\textbf{Firm Targets $\\\\times$ Same Applicant Demographic (s5\\\\_policy\\\\_diversity)}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\textbf{Panel A: HR} & \\\\textbf{Panel B: Engineer} \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_t
)
tbl_t <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_t)
tbl_t <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
  tbl_t
)
tbl_t <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_t)

cat(tbl_t)

## ---------- BOTTOM: URM-Tech x Combined firm-target dummy ----------
fit_urm_t <- function(d, target_var) {
  feols(
    as.formula(sprintf(
      "sc_overall_z ~ urm_tech + urm_tech:%s | responseid + resume_index + r_do",
      target_var)),
    data = d, vcov = ~ responseid
  )
}

targets      <- c("firm_targets_fh", "firm_targets_fhb")
col_labels_b <- c("Targets F or H", "Targets F, H, or B")

models_hr_b  <- lapply(targets, function(t) fit_urm_t(dt_hr_nb,  t))
models_eng_b <- lapply(targets, function(t) fit_urm_t(dt_eng_nb, t))
all_models_b <- c(models_hr_b, models_eng_b)

dict_b <- c(
  "urm_tech" = "URM (WF, AF, HM, HF)",
  setNames(rep("URM $\\times$ Firm Targets URM", length(targets)), paste0("urm_tech:", targets))
)

tbl_b <- etable(
  all_models_b,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = "%urm_tech",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_b,
  extralines = list(
    "Resume FE"     = rep(chk, 4),
    "Respondent FE" = rep(chk, 4),
    "Position FE"   = rep(chk, 4)
  )
)

proxy_hdr_b <- paste(col_labels_b, collapse = " & ")
tbl_b <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{5}{c}{\\\\textbf{URM-Tech Binary Cut $\\\\times$ Combined Firm-Target Dummy}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-3} \\\\cmidrule(lr){4-5}",
    " & ", proxy_hdr_b, " & ", proxy_hdr_b, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_b
)
tbl_b <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_b)
tbl_b <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl_b
)
tbl_b <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_b)

cat(tbl_b)

rm(dt_hr_nb, dt_eng_nb, prep, fit_match_joint, m_hr_t, m_eng_t, dict_t, tbl_t,
   fit_urm_t, targets, col_labels_b, models_hr_b, models_eng_b, all_models_b,
   dict_b, tbl_b, proxy_hdr_b, chk)
```

\scriptsize F = Female, H = Hispanic, B = Black. "Targets F or H" $\Rightarrow$ `firm_targets_female = 1` OR `firm_targets_hispanic = 1`; "Targets F, H, or B" additionally includes `firm_targets_black = 1` (robustness check; note that Black applicants are not in the study). URM $=$ \{WF, AF, HM, HF\}. \normalsize



\newpage
## (Triple Interaction Models) By Respondent's Priority for DEI $\times$ Firm Attention on DEI
\label{sec:triple}

\textcolor{blue}{\textbf{Takeaway}}: The negative triple interactions for HR (with both race-DEI and gender-DEI firm-attention proxies) support the **substitution** hypothesis, not backlash.

\textcolor{blue}{\textbf{Hypothesis}}: **Substitution vs. Backlash Effect.**

- **Substitution**: When a firm already prioritizes DEI, individuals who *also* personally prioritize DEI reduce (rather than amplify) the URM premium --- they treat the firm's push as sufficient and ease off. *Expect a negative sign on the triple interaction term.*

- **Backlash**: When a firm prioritizes DEI, individuals who do *not* personally prioritize DEI react by rating URM applicants lower. *Expect a positive sign on the triple interaction term.*

```{r dei_final_triple, eval = TRUE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr_nb  <- firm_long_dt[treat == "nonblind" & role == "HR"]
dt_eng_nb <- firm_long_dt[treat == "nonblind" & role == "Eng"]

chk <- "\\checkmark"

fit_triple_urm <- function(d, proxy_b) {
  feols(
    as.formula(sprintf(
      "sc_overall_z ~ urm_tech * div_priority_z * %s | responseid + resume_index + r_do",
      proxy_b)),
    data = d, vcov = ~ responseid
  )
}

m_hr_r  <- fit_triple_urm(dt_hr_nb,  "firm_attention_race_z")
m_eng_r <- fit_triple_urm(dt_eng_nb, "firm_attention_race_z")
m_hr_g  <- fit_triple_urm(dt_hr_nb,  "firm_attention_gender_z")
m_eng_g <- fit_triple_urm(dt_eng_nb, "firm_attention_gender_z")

# Effective respondent counts per model (respondents with non-missing proxy)
n_used <- c(
  dt_hr_nb[!is.na(firm_attention_race_z),    uniqueN(responseid)],
  dt_eng_nb[!is.na(firm_attention_race_z),   uniqueN(responseid)],
  dt_hr_nb[!is.na(firm_attention_gender_z),  uniqueN(responseid)],
  dt_eng_nb[!is.na(firm_attention_gender_z), uniqueN(responseid)]
)
n_full <- c(
  dt_hr_nb[,  uniqueN(responseid)],
  dt_eng_nb[, uniqueN(responseid)],
  dt_hr_nb[,  uniqueN(responseid)],
  dt_eng_nb[, uniqueN(responseid)]
)
n_drop <- n_full - n_used

models_trp <- list("HR (Race)" = m_hr_r, "Eng (Race)" = m_eng_r,
                   "HR (Gender)" = m_hr_g, "Eng (Gender)" = m_eng_g)

dict_trp <- c(
  "urm_tech" = "URM (WF, AF, HM, HF)",
  "urm_tech:div_priority_z" = "URM $\\times$ Respondent Prioritizes Diversity",
  "urm_tech:firm_attention_race_z" = "URM $\\times$ Firm DEI Attn",
  "urm_tech:firm_attention_gender_z" = "URM $\\times$ Firm DEI Attn",
  "urm_tech:div_priority_z:firm_attention_race_z"   = "URM $\\times$ Respondent Prioritizes Diversity $\\times$ Firm DEI Attn",
  "urm_tech:div_priority_z:firm_attention_gender_z" = "URM $\\times$ Respondent Prioritizes Diversity $\\times$ Firm DEI Attn"
)

tbl_trp <- etable(
  models_trp,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = "%urm_tech",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_trp,
  extralines = list(
    "Resume FE"          = rep(chk, 4),
    "Respondent FE"      = rep(chk, 4),
    "Position FE"        = rep(chk, 4),
    "Respondents (used)" = as.character(n_used),
    "Dropped (NA proxy)" = as.character(n_drop)
  )
)

tbl_trp <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{5}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z). URM-Tech Binary Cut.}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Race-DEI Attn}}",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Gender-DEI Attn}} \\\\\\\\",
    " \\\\cmidrule(lr){2-3} \\\\cmidrule(lr){4-5}",
    " & HR & Eng & HR & Eng \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_trp
)
tbl_trp <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_trp)
tbl_trp <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
  tbl_trp
)
tbl_trp <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_trp)

cat(tbl_trp)

rm(dt_hr_nb, dt_eng_nb, chk, fit_triple_urm, m_hr_r, m_eng_r, m_hr_g, m_eng_g,
   models_trp, dict_trp, tbl_trp, n_used, n_full, n_drop)
```

\scriptsize `div_priority_z` = z-score of (8 $-$ `s4_goals_5`), the revealed priority of "Diversity and Representation" in the respondent's ranking of seven hiring goals. `firm_attention_race_z` / `firm_attention_gender_z` = z-scores of `s5_view_dei_race_f` / `s5_view_dei_gender_f`, the respondent's perception of their firm's current DEI attention level. Standard errors clustered by respondent. Sample: non-blind arm; respondents with a missing firm-DEI-attention response are dropped by \texttt{feols} (see the ``Respondents (used)'' and ``Dropped (NA proxy)'' rows). \normalsize

\vspace{0.5em}

> *Note on interpretation*: On the full non-blind Engineer sample (all 74 respondents), a two-way model `sc_overall_z ~ urm_tech | responseid + resume_index + r_do_bythree` reports a statistically significant $\hat\beta_{\text{URM}} = +0.060$ ($p = .041$). It attenuates to statistically insignificant $\hat\beta \approx +0.040$ in the triple-model subsample for two reasons: (a) $\approx 18\%$ of Engineers are dropped due to answering ``Do Not Know'' in the question that elicits how much firm pays attentions to DEI, and (b) these dropped respondents happen to rate URM applicants more favorably than respondents who did characterize their firm's DEI posture.


-->
\clearpage
## Non-linear Demographic Biases for Low vs High Quality Candidates (GPA & Coding Score)

```{r nonlinear_preferences, echo = FALSE, include = FALSE}

# ==============================================================================
# HELPER FUNCTIONS
# ==============================================================================
extract_split_data <- function(model_split, role_label, tier_labels) {
  plot_list <- list()
  for (i in seq_along(model_split)) {
    df <- as.data.frame(coeftable(model_split[[i]]))
    df$Term <- rownames(df)
    df$Tier <- tier_labels[i]
    plot_list[[i]] <- df
  }
  plot_df <- do.call(rbind, plot_list)
  plot_df$Term <- gsub("race_gender::", "", plot_df$Term)
  plot_df$Term <- gsub("_", " ", plot_df$Term)
  plot_df$Term <- factor(plot_df$Term, levels = unique(plot_df$Term))
  plot_df$stars <- ifelse(plot_df$`Pr(>|t|)` < 0.01, "***",
                   ifelse(plot_df$`Pr(>|t|)` < 0.05, "**",
                   ifelse(plot_df$`Pr(>|t|)` < 0.1, "*", "")))
  plot_df$Role <- role_label
  plot_df$Tier <- factor(plot_df$Tier, levels = tier_labels)
  return(plot_df)
}

make_split_plot <- function(plot_df, title_label, color_vals, shape_vals, show_y = TRUE) {
  p <- ggplot(plot_df, aes(x = Term, y = Estimate, color = Tier, shape = Tier)) +
    geom_hline(yintercept = 0, color = "black", linewidth = 0.5) +
    geom_pointrange(aes(ymin = Estimate - 1.96 * `Std. Error`,
                        ymax = Estimate + 1.96 * `Std. Error`),
                    position = position_dodge(width = 0.6), size = 0.4) +
    geom_text(aes(label = stars, y = Estimate + 1.96 * `Std. Error` + 0.02),
              position = position_dodge(width = 0.6), size = 3.5, vjust = 0, 
              color = "black", show.legend = FALSE) +
    scale_color_manual(values = color_vals) +
    scale_shape_manual(values = shape_vals) +
    scale_y_continuous(expand = expansion(mult = c(0.1, 0.15))) +
    coord_cartesian(ylim = c(-0.65, 0.65)) +
    labs(title = title_label,
         x = "Applicant Demographic (vs. White Male)",
         y = "Predicted Premium (Overall Z-Score)",
         color = "Tier:", shape = "Tier:") +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
          axis.text.y = element_text(size = 8),
          axis.title = element_text(size = 9),
          legend.position = "top",
          legend.title = element_text(face = "bold", size = 8),
          legend.text = element_text(size = 8),
          plot.title = element_text(face = "bold", size = 9),
          plot.margin = margin(5, 10, 5, 5, "pt"))
  if (!show_y) p <- p + theme(axis.title.y = element_blank())
  return(p)
}
```


#### HR

```{r nonlinear_pref_HR, eval = TRUE, echo = FALSE, fig.width=9, fig.height=6, fig.align='center'}

# ==============================================================================
# (GPA) High / Mid / Low - Six Demographics
# ==============================================================================
hr_gpa_split <- feols(sc_overall_z ~ i(race_gender, ref="White_Male") | 
                      resume_index + responseid + r_do, 
                      split = ~gpa_tier3, cluster = ~responseid,
                      data = firm_long_dt[treat == "nonblind" & role == "HR" & s3_outside_res == 0])

gpa_tier3s <- c("Low GPA", "Mid GPA", "Top GPA")
gpa_colors <- c("Low GPA" = "black", "Mid GPA" = "steelblue", "Top GPA" = "indianred1")
gpa_shapes <- c("Low GPA" = 16, "Mid GPA" = 15, "Top GPA" = 17)

hr_gpa_df <- extract_split_data(hr_gpa_split, "HR", gpa_tier3s)

# gpa_tier2s <- c("Non_Elite_GPA", "Elite_GPA")
# gpa_colors <- c("Non_Elite_GPA" = "black", "Elite_GPA" = "steelblue")
# gpa_shapes <- c("Non_Elite_GPA" = 16, "Elite_GPA" = 15)
# 
# hr_gpa_df <- extract_split_data(hr_gpa_split, "HR", gpa_tier2s)

p_hr_gpa <- make_split_plot(hr_gpa_df, "HR: Premium by GPA Tier", gpa_colors, gpa_shapes, show_y = TRUE)

# ==============================================================================
# (GPA) High / Mid / Low - URM
# ==============================================================================

hr_urm_gpa_split <- feols(sc_overall_z ~ urm_tech | 
                          resume_index + responseid + r_do, 
                          split = ~gpa_tier3, cluster = ~responseid,
                          data = firm_long_dt[treat == "nonblind" & role == "HR" & s3_outside_res == 0])

hr_urm_gpa_df   <- extract_split_data(hr_urm_gpa_split,  "HR",       gpa_tier3s)

p_hr_urm_gpa   <- make_split_plot(hr_urm_gpa_df,  "HR: URM Premium by GPA Tier",   gpa_colors,  gpa_shapes,  show_y = TRUE)

# ==============================================================================
# Coding Ability (Top vs Bottom Coding Score or Test Cases) - Six Demographics
# ==============================================================================
hr_test_split <- feols(sc_overall_z ~ i(race_gender, ref="White_Male") | 
                       resume_index + responseid + r_do, 
                       split = ~top_half_coder, cluster = ~responseid,
                       data = firm_long_dt[treat == "nonblind" & role == "HR" & s3_outside_res == 0])

test_tiers <- c("Bottom 50% Coders", "Top 50% Coders")
test_colors <- c("Bottom 50% Coders" = "black", "Top 50% Coders" = "indianred1")
test_shapes <- c("Bottom 50% Coders" = 16, "Top 50% Coders" = 17)

hr_test_df <- extract_split_data(hr_test_split, "HR", test_tiers)

p_hr_test <- make_split_plot(hr_test_df, "HR: Premium by Coding Ability", test_colors, test_shapes, show_y = TRUE)

# ==============================================================================
# Coding Ability (Top vs Bottom Coding Score or Test Cases) - URM
# ==============================================================================

hr_urm_test_split <- feols(sc_overall_z ~ urm_tech | 
                           resume_index + responseid + r_do, 
                           split = ~top_half_coder, cluster = ~responseid,
                           data = firm_long_dt[treat == "nonblind" & role == "HR" & s3_outside_res == 0])

hr_urm_test_df  <- extract_split_data(hr_urm_test_split,  "HR",       test_tiers)

p_hr_urm_test  <- make_split_plot(hr_urm_test_df,  "HR: URM Premium by Coding Ability",  test_colors, test_shapes, show_y = TRUE)


# ==============================================================================
# Output
# ==============================================================================
(p_hr_gpa + p_hr_test + plot_layout(guides = "collect")) /
(p_hr_urm_gpa + p_hr_urm_test + plot_layout(guides = "collect")) +
  plot_layout(guides = "collect") &
  theme(legend.position = "top")

```

\newpage
#### Engineer

```{r nonlinear_pref_Eng, eval = TRUE, echo = FALSE, fig.width=9, fig.height=6, fig.align='center'}

# ==============================================================================
# (GPA) High / Mid / Low - Six Demographics
# ==============================================================================
eng_gpa_split <- feols(sc_overall_z ~ i(race_gender, ref="White_Male") | 
                       resume_index + responseid + r_do, 
                       split = ~gpa_tier3, cluster = ~responseid,
                       data = firm_long_dt[treat == "nonblind" & role == "Eng" & s3_outside_res == 0])

gpa_tier3s <- c("Low GPA", "Mid GPA", "Top GPA")
gpa_colors <- c("Low GPA" = "black", "Mid GPA" = "steelblue", "Top GPA" = "indianred1")
gpa_shapes <- c("Low GPA" = 16, "Mid GPA" = 15, "Top GPA" = 17)

eng_gpa_df <- extract_split_data(eng_gpa_split, "Engineer", gpa_tier3s)

# gpa_tier2s <- c("Non_Elite_GPA", "Elite_GPA")
# gpa_colors <- c("Non_Elite_GPA" = "black", "Elite_GPA" = "steelblue")
# gpa_shapes <- c("Non_Elite_GPA" = 16, "Elite_GPA" = 15)
# 
# eng_gpa_df <- extract_split_data(eng_gpa_split, "Engineer", gpa_tier2s)

p_eng_gpa <- make_split_plot(eng_gpa_df, "Engineer: Premium by GPA Tier", gpa_colors, gpa_shapes, show_y = FALSE)

# ==============================================================================
# (GPA) High / Mid / Low - URM
# ==============================================================================

eng_urm_gpa_split <- feols(sc_overall_z ~ urm_tech | 
                           resume_index + responseid + r_do, 
                           split = ~gpa_tier3, cluster = ~responseid,
                           data = firm_long_dt[treat == "nonblind" & role == "Eng" & s3_outside_res == 0])

eng_urm_gpa_df  <- extract_split_data(eng_urm_gpa_split, "Engineer", gpa_tier3s)

p_eng_urm_gpa  <- make_split_plot(eng_urm_gpa_df, "Engineer: URM Premium by GPA Tier",  gpa_colors,  gpa_shapes,  show_y = FALSE)

# ==============================================================================
# Coding Ability (Top vs Bottom Coding Score or Test Cases) - Six Demographics
# ==============================================================================
eng_test_split <- feols(sc_overall_z ~ i(race_gender, ref="White_Male") | 
                        resume_index + responseid + r_do, 
                        split = ~top_half_coder, cluster = ~responseid,
                        data = firm_long_dt[treat == "nonblind" & role == "Eng" & s3_outside_res == 0])

test_tiers <- c("Bottom 50% Coders", "Top 50% Coders")
test_colors <- c("Bottom 50% Coders" = "black", "Top 50% Coders" = "indianred1")
test_shapes <- c("Bottom 50% Coders" = 16, "Top 50% Coders" = 17)

eng_test_df <- extract_split_data(eng_test_split, "Engineer", test_tiers)

p_eng_test <- make_split_plot(eng_test_df, "Engineer: Premium by Coding Ability", test_colors, test_shapes, show_y = FALSE)

# ==============================================================================
# Coding Ability (Top vs Bottom Coding Score or Test Cases) - URM
# ==============================================================================
eng_urm_test_split <- feols(sc_overall_z ~ urm_tech | 
                            resume_index + responseid + r_do, 
                            split = ~top_half_coder, cluster = ~responseid,
                            data = firm_long_dt[treat == "nonblind" & role == "Eng" & s3_outside_res == 0])

eng_urm_test_df <- extract_split_data(eng_urm_test_split, "Engineer", test_tiers)

p_eng_urm_test <- make_split_plot(eng_urm_test_df, "Engineer: URM Premium by Coding Ability", test_colors, test_shapes, show_y = FALSE)


# ==============================================================================
# Output
# ==============================================================================
(p_eng_gpa + p_eng_test + plot_layout(guides = "collect")) /
(p_eng_urm_gpa + p_eng_urm_test + plot_layout(guides = "collect")) +
  plot_layout(guides = "collect") &
  theme(legend.position = "top")


```

\newpage
###### (Eng) Signal from GPA vs Coding Test

```{r Horserace, echo = FALSE, eval = TRUE, results='asis'}

eng_horse_race <- feols(sc_overall_z ~ urm_tech + urm_tech:test_case_z + urm_tech:gpa_z | 
                        resume_index + responseid + r_do, 
                        cluster = ~responseid,
                        data = firm_long_dt[treat == "nonblind" & role == "Eng" & s3_outside_res == 0])

tbl <- etable(
  eng_horse_race,
  tex = TRUE, style.tex = style.tex("aer"),
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  dict = c("urm_tech"    = "URM",
           "test_case_z" = "Coding Score (Z)",
           "gpa_z"       = "GPA (Z)"),
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  title = "Signal from GPA vs. Coding Test: Engineer (Non-blind)",
  notes = "Standard errors clustered by respondent. Sample restricted to non-blind condition, Engineer role."
)

# Inject FE rows manually before \bottomrule
tbl <- sub(
  "\\\\bottomrule",
  "Resume FE & $\\\\checkmark$ \\\\\\\\\nRespondent FE & $\\\\checkmark$ \\\\\\\\\nPosition FE & $\\\\checkmark$ \\\\\\\\\n\\\\bottomrule",
  tbl
)

tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)

cat(tbl)

rm(eng_horse_race, tbl)

```


\clearpage
## Heterogeneity by Firm Size
```{r stage_pref_heterogeneity_by_firmsize, eval = TRUE, echo = FALSE, out.width="100%", fig.width=14, fig.height=4.5, fig.align='center', results='asis'}

## Regressions: Heterogeneity by Firm Size
## Note: Small firms are the reference group (omitted)
## Only includes respondents with valid firm size responses (s2_firm_size != 96)

  #### HR
  models_hr_hetero_firmsize <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(race_gender, ref = "White_Male") + 
        i(race_gender, firm_size_mid, ref = "White_Male") +
        i(race_gender, firm_size_large, ref = "White_Male")
      | resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "HR" & s2_firm_size != 96],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_firmsize) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")
  
  #### Engineer
  models_eng_hetero_firmsize <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ 
        i(race_gender, ref = "White_Male") + 
        i(race_gender, firm_size_mid, ref = "White_Male") +
        i(race_gender, firm_size_large, ref = "White_Male")
      | resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "Eng" & s2_firm_size != 96],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_firmsize) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

## Calculate respondent counts for labeling
resp_counts_hetero_firmsize <- firm_long_dt[treat == "nonblind" & s2_firm_size != 96, .(
  N_HR = uniqueN(responseid[role == "HR"]),
  N_Eng = uniqueN(responseid[role == "Eng"])
), by = .(
  firm_size = fcase(
    firm_size_small == 1, "small",
    firm_size_mid == 1, "mid",
    firm_size_large == 1, "large"
  )
)]

## Create plots for each outcome
  #### Overall
  p_ovr_hr_firmsize <- plot_heterogeneity_firmsize(models_hr_hetero_firmsize$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_firmsize, "HR")
  p_ovr_eng_firmsize <- plot_heterogeneity_firmsize(models_eng_hetero_firmsize$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_firmsize, "Eng")
  
  #### Coding
  p_coding_hr_firmsize <- plot_heterogeneity_firmsize(models_hr_hetero_firmsize$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_firmsize, "HR")
  p_coding_eng_firmsize <- plot_heterogeneity_firmsize(models_eng_hetero_firmsize$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_firmsize, "Eng")
  
  #### Fit
  p_fit_hr_firmsize <- plot_heterogeneity_firmsize(models_hr_hetero_firmsize$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_firmsize, "HR")
  p_fit_eng_firmsize <- plot_heterogeneity_firmsize(models_eng_hetero_firmsize$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_firmsize, "Eng")
  
  #### Stay
  p_stay_hr_firmsize <- plot_heterogeneity_firmsize(models_hr_hetero_firmsize$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_firmsize, "HR")
  p_stay_eng_firmsize <- plot_heterogeneity_firmsize(models_eng_hetero_firmsize$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_firmsize, "Eng")
  
  #### Advance (HR only)
  p_advance_hr_firmsize <- plot_heterogeneity_firmsize(models_hr_hetero_firmsize$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_firmsize, "HR")

## Print plots
suppressWarnings({
  print(hetero_side_by_side_plots(p_ovr_hr_firmsize, p_ovr_eng_firmsize, "Overall (Z) by Firm Size"))
  print(hetero_side_by_side_plots(p_coding_hr_firmsize, p_coding_eng_firmsize, "Coding (Z) by Firm Size"))
  print(hetero_side_by_side_plots(p_fit_hr_firmsize, p_fit_eng_firmsize, "Fit (Z) by Firm Size"))
  print(hetero_side_by_side_plots(p_stay_hr_firmsize, p_stay_eng_firmsize, "Stay (Z) by Firm Size"))
  print(hetero_side_by_side_plots(p_advance_hr_firmsize, p_empty, "Advance (0/1, LPM) by Firm Size"))
})

## Clean up
rm(models_hr_hetero_firmsize, models_eng_hetero_firmsize,
   resp_counts_hetero_firmsize,
   p_ovr_hr_firmsize, p_ovr_eng_firmsize,
   p_coding_hr_firmsize, p_coding_eng_firmsize,
   p_fit_hr_firmsize, p_fit_eng_firmsize,
   p_stay_hr_firmsize, p_stay_eng_firmsize,
   p_advance_hr_firmsize
)
```


```{r, include = FALSE, eval = FALSE, echo = TRUE}

rm(p_empty,
   total_effects_lincom_gender, total_effects_lincom_gender_collapsedonrace,
   total_effects_lincom_race, total_effects_lincom_race_collapsedongender,
   total_effects_lincom_racegender, total_effects_lincom_detailed_race_gender,
   total_effects_lincom_firmsize, 
   total_effects_lincom_dei,
   plot_heterogeneity_gender, plot_heterogeneity_gender_collapsedonrace,
   plot_heterogeneity_race, plot_heterogeneity_race_collapsedongender,
   plot_heterogeneity_racegender, plot_heterogeneity_race_collapsedongender,
   plot_heterogeneity_detailed_race_gender,
   plot_heterogeneity_firmsize,
   plot_heterogeneity_dei,
   plot_simple_concordance,
   hetero_side_by_side_plots
)

```

































<!-- ##### ##### ##### ##### ##### ARCHIVED: Heterogeneity in Preferences ##### ##### ##### ##### ##### -->


<!-- ## By Race -->
<!-- Note: Concordance graphs drop responses by demographic groups not represented in the resume's hypothetical names. (i.e. Drops responses by Blacks) -->

```{r stage_pref_heterogeneity_by_race, eval = FALSE, echo = FALSE, out.width="100%", fig.width=14, fig.height=10, fig.align='center', results='asis'}

## Regressions: Heterogeneity by Respondent Race

  #### HR
  models_hr_hetero_race <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(race_gender, ref = "White_Male") * resp_asian + 
        i(race_gender, ref = "White_Male") * resp_hispanic + 
        i(race_gender, ref = "White_Male") * resp_black + 
        i(race_gender, ref = "White_Male") * resp_raceother | 
        resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "HR"],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_race) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")
  
  models_hr_hetero_race_collapsedongender <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(race, ref = "White") * resp_asian + 
        i(race, ref = "White") * resp_hispanic + 
        i(race, ref = "White") * resp_black + 
        i(race, ref = "White") * resp_raceother | 
        resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "HR"],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_race_collapsedongender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")
  
  models_hr_concordance_race  <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_race | resume_index + responseid + r_do,
          data = firm_long_dt[treat=="nonblind" & role=="HR"], vcov=~responseid)
    ))
  names(models_hr_concordance_race) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")
  
  #### Engineer
  models_eng_hetero_race <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
        i(race_gender, ref = "White_Male") * resp_asian + 
        i(race_gender, ref = "White_Male") * resp_hispanic + 
        i(race_gender, ref = "White_Male") * resp_black + 
        i(race_gender, ref = "White_Male") * resp_raceother | 
        resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "Eng"],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_race) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")
  
  models_eng_hetero_race_collapsedongender <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
        i(race, ref = "White") * resp_asian + 
        i(race, ref = "White") * resp_hispanic + 
        i(race, ref = "White") * resp_black + 
        i(race, ref = "White") * resp_raceother | 
        resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "Eng"],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_race_collapsedongender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

  models_eng_concordance_race <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_race | resume_index + responseid + r_do, 
          data = firm_long_dt[treat=="nonblind" & role=="Eng"], vcov=~responseid)
    ))
  names(models_eng_concordance_race) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")
  
## Calculate respondent counts for labeling
resp_counts_hetero_race <- firm_long_dt[treat == "nonblind", .(
  N_HR = uniqueN(responseid[role == "HR"]),
  N_Eng = uniqueN(responseid[role == "Eng"])
), by = .(
  resp_race = fcase(
    resp_white == 1, "White",
    resp_asian == 1, "Asian", 
    resp_hispanic == 1, "Hispanic",
    resp_black == 1, "Black",
    default = "Other"
  )
)][resp_race != "Other"]


## Create plots for each outcome
  #### Overall
  p_ovr_hr_race <- plot_heterogeneity_race(models_hr_hetero_race$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_ovr_eng_race <- plot_heterogeneity_race(models_eng_hetero_race$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_ovr_hr_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_hr_hetero_race_collapsedongender$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_ovr_eng_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_eng_hetero_race_collapsedongender$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_ovr_race_concordance <- plot_simple_concordance(models_hr_concordance_race$sc_overall_z, models_eng_concordance_race$sc_overall_z, "Overall (Z) - Collapsed on Concordance (Race) - Includes only Wh/As/Hp Respondents")
  
  #### Coding
  p_coding_hr_race <- plot_heterogeneity_race(models_hr_hetero_race$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_coding_eng_race <- plot_heterogeneity_race(models_eng_hetero_race$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_coding_hr_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_hr_hetero_race_collapsedongender$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_coding_eng_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_eng_hetero_race_collapsedongender$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_coding_race_concordance <- plot_simple_concordance(models_hr_concordance_race$sc_coding_z, models_eng_concordance_race$sc_coding_z, "Coding (Z) - Collapsed on Concordance (Race) - Includes only Wh/As/Hp Respondents")

  #### Fit
  p_fit_hr_race <- plot_heterogeneity_race(models_hr_hetero_race$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_fit_eng_race <- plot_heterogeneity_race(models_eng_hetero_race$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_fit_hr_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_hr_hetero_race_collapsedongender$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_fit_eng_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_eng_hetero_race_collapsedongender$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_fit_race_concordance <- plot_simple_concordance(models_hr_concordance_race$sc_fit_z, models_eng_concordance_race$sc_fit_z, "Fit (Z) - Collapsed on Concordance (Race) - Includes only Wh/As/Hp Respondents")

  #### Stay
  p_stay_hr_race <- plot_heterogeneity_race(models_hr_hetero_race$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_stay_eng_race <- plot_heterogeneity_race(models_eng_hetero_race$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_stay_hr_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_hr_hetero_race_collapsedongender$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_stay_eng_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_eng_hetero_race_collapsedongender$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_race, "Eng")
  p_stay_race_concordance <- plot_simple_concordance(models_hr_concordance_race$sc_stay_z, models_eng_concordance_race$sc_stay_z, "Stay (Z) - Collapsed on Concordance (Race) - Includes only Wh/As/Hp Respondents")

  #### Advance
  p_advance_hr_race <- plot_heterogeneity_race(models_hr_hetero_race$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_advance_hr_race_collapsedongender <- plot_heterogeneity_race_collapsedongender(models_hr_hetero_race_collapsedongender$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_race, "HR")
  p_advance_race_concordance <- plot_simple_concordance(models_hr_concordance_race$sc_advance, NULL, title = "Advance (LPM) - Concordance (Race) - Includes only Wh/As/Hp Respondents"
)
  p_empty <- ggplot() + annotate("text", x = 0, y = 0, label = "Engineers: Not Measured", size = 5, color = "gray50") + theme_void()
  
suppressWarnings({
  
  # --- 1. Overall ---
  # Create Layouts
  p_conc_ovr_centered <- cowplot::plot_grid(NULL, p_ovr_race_concordance, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_mid_ovr <- hetero_side_by_side_plots(p_ovr_hr_race_collapsedongender, p_ovr_eng_race_collapsedongender, "Overall (Z) - Collapsed on Gender")
  p_bot_ovr <- hetero_side_by_side_plots(p_ovr_hr_race, p_ovr_eng_race, "Overall (Z)")

  # Stack and Print
  print(cowplot::plot_grid(p_conc_ovr_centered, p_mid_ovr, p_bot_ovr, ncol=1, rel_heights=c(0.4, 1, 1)))
  cat("\\newpage\n")

  # --- 2. Coding ---
  p_conc_cod_centered <- cowplot::plot_grid(NULL, p_coding_race_concordance, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_mid_cod <- hetero_side_by_side_plots(p_coding_hr_race_collapsedongender, p_coding_eng_race_collapsedongender, "Coding (Z) - Collapsed on Gender")
  p_bot_cod <- hetero_side_by_side_plots(p_coding_hr_race, p_coding_eng_race, "Coding (Z)")

  print(cowplot::plot_grid(p_conc_cod_centered, p_mid_cod, p_bot_cod, ncol=1, rel_heights=c(0.4, 1, 1)))
  cat("\\newpage\n")

  # --- 3. Fit ---
  p_conc_fit_centered <- cowplot::plot_grid(NULL, p_fit_race_concordance, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_mid_fit <- hetero_side_by_side_plots(p_fit_hr_race_collapsedongender, p_fit_eng_race_collapsedongender, "Fit (Z) - Collapsed on Gender")
  p_bot_fit <- hetero_side_by_side_plots(p_fit_hr_race, p_fit_eng_race, "Fit (Z)")

  print(cowplot::plot_grid(p_conc_fit_centered, p_mid_fit, p_bot_fit, ncol=1, rel_heights=c(0.4, 1, 1)))
  cat("\\newpage\n")

  # --- 4. Stay ---
  p_conc_stay_centered <- cowplot::plot_grid(NULL, p_stay_race_concordance, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_mid_stay <- hetero_side_by_side_plots(p_stay_hr_race_collapsedongender, p_stay_eng_race_collapsedongender, "Stay (Z) - Collapsed on Gender")
  p_bot_stay <- hetero_side_by_side_plots(p_stay_hr_race, p_stay_eng_race, "Stay (Z)")

  print(cowplot::plot_grid(p_conc_stay_centered, p_mid_stay, p_bot_stay, ncol=1, rel_heights=c(0.4, 1, 1)))
  cat("\\newpage\n")

  # --- 5. Advance ---
  p_conc_adv_centered <- cowplot::plot_grid(NULL, p_advance_race_concordance, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_mid_adv <- hetero_side_by_side_plots(p_advance_hr_race_collapsedongender, p_empty, "Advance (0/1, LPM) - Collapsed on Gender")
  p_bot_adv <- hetero_side_by_side_plots(p_advance_hr_race, p_empty, "Advance (0/1, LPM)")

  print(cowplot::plot_grid(p_conc_adv_centered, p_mid_adv, p_bot_adv, ncol=1, rel_heights=c(0.4, 1, 1)))
})

# rm(models_hr_hetero_race, models_hr_hetero_race_collapsedongender, models_hr_concordance_race,
#    models_eng_hetero_race, models_eng_hetero_race_collapsedongender, models_eng_concordance_race, 
#    resp_counts_hetero_race, p_ovr_hr_race, p_ovr_eng_race, p_ovr_hr_race_collapsedongender, p_ovr_eng_race_collapsedongender, p_ovr_race_concordance,
#    p_coding_hr_race, p_coding_eng_race, p_coding_hr_race_collapsedongender, p_coding_eng_race_collapsedongender, p_coding_race_concordance,
#    p_fit_hr_race, p_fit_eng_race, p_fit_hr_race_collapsedongender, p_fit_eng_race_collapsedongender, p_fit_race_concordance,
#    p_stay_hr_race, p_stay_eng_race, p_stay_hr_race_collapsedongender, p_stay_eng_race_collapsedongender, p_stay_race_concordance,
#    p_advance_hr_race, p_advance_hr_race_collapsedongender, p_advance_race_concordance, 
#    p_mid_ovr, p_bot_ovr, p_conc_ovr_centered,
#    p_mid_cod, p_bot_cod, p_conc_cod_centered, 
#    p_mid_fit, p_bot_fit, p_conc_fit_centered,
#    p_mid_stay, p_bot_stay, p_conc_stay_centered,
#    p_mid_adv, p_bot_adv, p_conc_adv_centered)

```

<!-- \clearpage -->
<!-- ## By Gender -->
<!-- Note: Concordance graphs drop responses by demographic groups not represented in the resume's hypothetical names. (i.e. Drops responses by Nonbinary) -->

```{r stage_pref_heterogeneity_by_gender, eval = FALSE, echo = FALSE, out.width="100%", fig.width=14, fig.height=4.5, fig.align='center', results='asis'}

## Regressions: Heterogeneity by Respondent Gender
  
  #### HR
  models_hr_concordance_gender  <- suppressMessages(suppressWarnings(
    feols(sc_overall_z ~ concordance_race | resume_index + responseid + r_do, 
          data = firm_long_dt[treat=="nonblind" & role=="HR"], vcov=~responseid)
    ))
  models_eng_concordance_gender <- suppressMessages(suppressWarnings(
    feols(sc_overall_z ~ concordance_race | resume_index + responseid + r_do,
          data = firm_long_dt[treat=="nonblind" & role=="Eng"], vcov=~responseid)
  ))

  models_hr_hetero_gender <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(race_gender, ref = "White_Male") + 
        i(race_gender, resp_male, ref = "White_Male") 
      | resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "HR"],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_gender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")
  
  models_hr_hetero_gender_collapsedonrace <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(gender, ref = "Male") + 
        i(gender, resp_male, ref = "Male") 
      | resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "HR"],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_gender_collapsedonrace) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")
  
  #### Engineer
  models_eng_hetero_gender <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ 
        i(race_gender, ref = "White_Male") + 
        i(race_gender, resp_male, ref = "White_Male") 
      | resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "Eng"],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_gender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")
  
  models_eng_hetero_gender_collapsedonrace <- suppressMessages(suppressWarnings(
    feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ 
        i(gender, ref = "Male") + 
        i(gender, resp_male, ref = "Male") 
      | resume_index + responseid + r_do,
      data = firm_long_dt[treat == "nonblind" & role == "Eng"],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_gender_collapsedonrace) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

## Calculate respondent counts for labeling
resp_counts_hetero_gender <- firm_long_dt[treat == "nonblind", .(
  N_HR = uniqueN(responseid[role == "HR"]),
  N_Eng = uniqueN(responseid[role == "Eng"])
), by = .(
  resp_gender = ifelse(resp_male == 1, "Male", "Female")
)]

## Create plots for each outcome
  #### Overall
  p_ovr_hr_gender <- plot_heterogeneity_gender(models_hr_hetero_gender$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_ovr_eng_gender <- plot_heterogeneity_gender(models_eng_hetero_gender$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  p_ovr_hr_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_hr_hetero_gender_collapsedonrace$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_ovr_eng_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_eng_hetero_gender_collapsedonrace$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  
  #### Coding
  p_coding_hr_gender <- plot_heterogeneity_gender(models_hr_hetero_gender$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_coding_eng_gender <- plot_heterogeneity_gender(models_eng_hetero_gender$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  p_coding_hr_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_hr_hetero_gender_collapsedonrace$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_coding_eng_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_eng_hetero_gender_collapsedonrace$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  
  #### Fit
  p_fit_hr_gender <- plot_heterogeneity_gender(models_hr_hetero_gender$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_fit_eng_gender <- plot_heterogeneity_gender(models_eng_hetero_gender$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  p_fit_hr_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_hr_hetero_gender_collapsedonrace$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_fit_eng_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_eng_hetero_gender_collapsedonrace$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  
  #### Stay
  p_stay_hr_gender <- plot_heterogeneity_gender(models_hr_hetero_gender$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_stay_eng_gender <- plot_heterogeneity_gender(models_eng_hetero_gender$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  p_stay_hr_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_hr_hetero_gender_collapsedonrace$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_stay_eng_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_eng_hetero_gender_collapsedonrace$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_gender, "Eng")
  
  #### Advance
  p_advance_hr_gender <- plot_heterogeneity_gender(models_hr_hetero_gender$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")
  p_advance_hr_gender_collapsedonrace <- plot_heterogeneity_gender_collapsedonrace(models_hr_hetero_gender_collapsedonrace$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_gender, "HR")

## Print plots
suppressWarnings({
  print(hetero_side_by_side_plots(p_ovr_hr_gender_collapsedonrace, p_ovr_eng_gender_collapsedonrace, "Overall (Z) - Collapsed on Race / Concordance - Includes only M/F respondents"))
  print(hetero_side_by_side_plots(p_ovr_hr_gender, p_ovr_eng_gender, "Overall (Z)"))
  
  print(hetero_side_by_side_plots(p_coding_hr_gender_collapsedonrace, p_coding_eng_gender_collapsedonrace, "Coding (Z) - Collapsed on Race / Concordance - Includes only M/F respondents"))
  print(hetero_side_by_side_plots(p_coding_hr_gender, p_coding_eng_gender, "Coding (Z)"))
  
  print(hetero_side_by_side_plots(p_fit_hr_gender_collapsedonrace, p_fit_eng_gender_collapsedonrace, "Fit (Z) - Collapsed on Race / Concordance - Includes only M/F respondents"))
  print(hetero_side_by_side_plots(p_fit_hr_gender, p_fit_eng_gender, "Fit (Z)"))
  
  print(hetero_side_by_side_plots(p_stay_hr_gender_collapsedonrace, p_stay_eng_gender_collapsedonrace, "Stay (Z) - Collapsed on Race / Concordance - Includes only M/F respondents"))
  print(hetero_side_by_side_plots(p_stay_hr_gender, p_stay_eng_gender, "Stay (Z)"))
  
  print(hetero_side_by_side_plots(p_advance_hr_gender_collapsedonrace, p_empty, "Advance (0/1, LPM) - Collapsed on Race / Concordance - Includes only M/F respondents"))
  print(hetero_side_by_side_plots(p_advance_hr_gender, p_empty, "Advance (0/1, LPM)"))
})


rm(models_hr_concordance_gender, models_eng_concordance_gender, 
   models_hr_hetero_gender, models_hr_hetero_gender_collapsedonrace, 
   models_eng_hetero_gender, models_eng_hetero_gender_collapsedonrace, 
   resp_counts_hetero_gender,
   p_ovr_hr_gender, p_ovr_eng_gender, p_ovr_hr_gender_collapsedonrace, p_ovr_eng_gender_collapsedonrace, 
   p_coding_hr_gender, p_coding_eng_gender, p_coding_hr_gender_collapsedonrace, p_coding_eng_gender_collapsedonrace, 
   p_fit_hr_gender, p_fit_eng_gender, p_fit_hr_gender_collapsedonrace, p_fit_eng_gender_collapsedonrace, 
   p_stay_hr_gender, p_stay_eng_gender, p_stay_hr_gender_collapsedonrace, p_stay_eng_gender_collapsedonrace, 
   p_advance_hr_gender, p_advance_hr_gender_collapsedonrace
)
```

<!-- \clearpage -->
<!-- ## By Race_Gender -->
<!-- Note: Concordance graphs drop responses by demographic groups not represented in the resume's hypothetical names. (i.e. Drops responses by Blacks, Nonbinary) -->

```{r stage_pref_heterogeneity_racegender, eval = FALSE, echo = FALSE, out.width="100%", fig.width=14, fig.height=10, fig.align='center', results='asis'}

# --- 1. Regressions ---

  # A. Concordance Models (Top: Binary Match vs. No Match)
  models_hr_concordance_racegender <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_race_gender | resume_index + responseid + r_do_bythree, 
          data = firm_long_dt[treat=="nonblind" & role=="HR"], vcov=~responseid)
  ))
  names(models_hr_concordance_racegender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

  models_eng_concordance_racegender <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_race_gender | resume_index + responseid + r_do_bythree, 
          data = firm_long_dt[treat=="nonblind" & role=="Eng"], vcov=~responseid)
  ))
  names(models_eng_concordance_racegender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

  # B. Full Interaction Models (Bottom: Original Detailed Breakdown)
  models_hr_hetero_racegender <- suppressMessages(suppressWarnings(
      feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(race_gender, ref = "White_Male") + 
        i(resp_race_gender, race_gender, ref = "White_Male") 
      | resume_index + responseid + r_do_bythree,
      data = firm_long_dt[treat == "nonblind" & role == "HR"],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_racegender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

  models_eng_hetero_racegender <- suppressMessages(suppressWarnings(
      feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ 
        i(race_gender, ref = "White_Male") + 
        i(resp_race_gender, race_gender, ref = "White_Male") 
      | resume_index + responseid + r_do_bythree,
      data = firm_long_dt[treat == "nonblind" & role == "Eng" & resp_race_gender != "Other"],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_racegender) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

# --- 2. Calculate Counts for Labels (FIXED: Filter out NAs) ---
  resp_counts_hetero_racegender <- firm_long_dt[treat == "nonblind" & !is.na(resp_race_gender) & resp_race_gender != "Other", .(
    N_HR = uniqueN(responseid[role == "HR"]),
    N_Eng = uniqueN(responseid[role == "Eng"])
  ), by = .(resp_race_gender)]

# --- 3. Generate Plots ---
  
  #### Overall
  p_ovr_conc <- plot_simple_concordance(models_hr_concordance_racegender$sc_overall_z, models_eng_concordance_racegender$sc_overall_z, "Overall (Z) - Concordance Premium (Race & Gender)")
  p_ovr_hr <- plot_heterogeneity_racegender(models_hr_hetero_racegender$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_racegender, "HR")
  p_ovr_eng <- plot_heterogeneity_racegender(models_eng_hetero_racegender$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_racegender, "Eng")

  #### Coding
  p_cod_conc <- plot_simple_concordance(models_hr_concordance_racegender$sc_coding_z, models_eng_concordance_racegender$sc_coding_z, "Coding (Z) - Concordance Premium (Race & Gender)")
  p_cod_hr <- plot_heterogeneity_racegender(models_hr_hetero_racegender$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_racegender, "HR")
  p_cod_eng <- plot_heterogeneity_racegender(models_eng_hetero_racegender$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_racegender, "Eng")

  #### Fit
  p_fit_conc <- plot_simple_concordance(models_hr_concordance_racegender$sc_fit_z, models_eng_concordance_racegender$sc_fit_z, "Fit (Z) - Concordance Premium (Race & Gender)")
  p_fit_hr <- plot_heterogeneity_racegender(models_hr_hetero_racegender$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_racegender, "HR")
  p_fit_eng <- plot_heterogeneity_racegender(models_eng_hetero_racegender$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_racegender, "Eng")

  #### Stay
  p_stay_conc <- plot_simple_concordance(models_hr_concordance_racegender$sc_stay_z, models_eng_concordance_racegender$sc_stay_z, "Stay (Z) - Concordance Premium (Race & Gender)")
  p_stay_hr <- plot_heterogeneity_racegender(models_hr_hetero_racegender$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_racegender, "HR")
  p_stay_eng <- plot_heterogeneity_racegender(models_eng_hetero_racegender$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_racegender, "Eng")

  #### Advance (HR only for Concordance, Empty for Eng)
  p_adv_conc <- plot_simple_concordance(models_hr_concordance_racegender$sc_advance, NULL, title = "Advance (LPM) - Concordance Premium (Race & Gender)")
  p_adv_hr <- plot_heterogeneity_racegender(models_hr_hetero_racegender$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_racegender, "HR")
  p_empty <- ggplot() + annotate("text", x = 0, y = 0, label = "Engineers: Not Measured", size = 5, color = "gray50") + theme_void()

# --- 4. Print (Two Rows Per Page) ---
suppressWarnings({
  
  # Overall
  p_conc_centered <- cowplot::plot_grid(NULL, p_ovr_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_ovr_hr, p_ovr_eng, "Overall (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Coding
  p_conc_centered <- cowplot::plot_grid(NULL, p_cod_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_cod_hr, p_cod_eng, "Coding (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Fit
  p_conc_centered <- cowplot::plot_grid(NULL, p_fit_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_fit_hr, p_fit_eng, "Fit (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Stay
  p_conc_centered <- cowplot::plot_grid(NULL, p_stay_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_stay_hr, p_stay_eng, "Stay (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Advance
  p_conc_centered <- cowplot::plot_grid(NULL, p_adv_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_adv_hr, p_empty, "Advance (0/1)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
})

rm(models_hr_concordance_racegender, models_eng_concordance_racegender, 
   models_hr_hetero_racegender, models_eng_hetero_racegender, 
   resp_counts_hetero_racegender,
   p_ovr_conc, p_ovr_hr, p_ovr_eng, 
   p_cod_conc, p_cod_hr, p_cod_eng, 
   p_fit_conc, p_fit_hr, p_fit_eng, 
   p_stay_conc, p_stay_hr, p_stay_eng, 
   p_adv_conc, p_adv_hr, 
   p_conc_centered, p_full_interaction
)
```

<!-- \clearpage -->
<!-- ## By Race_Gender_Detailed -->
<!-- Note: Concordance graphs drop responses by demographic groups not represented in the resume's hypothetical names. (i.e. Drops responses by Koreans, Japanese, Pakistani) -->

```{r stage_pref_heterogeneity_detailed, eval = FALSE, echo = FALSE, out.width="100%", fig.width=14, fig.height=9.5, fig.align='center', results='asis'}

# --- 1. Regressions ---

  # A. Concordance Models (Top)
  models_hr_concordance_detailed <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ concordance_race_gender_detailed | resume_index + responseid + r_do_bythree, 
          data = firm_long_dt[treat=="nonblind" & role=="HR"], vcov=~responseid)
  ))
  names(models_hr_concordance_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

  models_eng_concordance_detailed <- suppressMessages(suppressWarnings(
    feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ concordance_race_gender_detailed | resume_index + responseid + r_do_bythree, 
          data = firm_long_dt[treat=="nonblind" & role=="Eng"], vcov=~responseid)
  ))
  names(models_eng_concordance_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

  # B. Full Interaction Models (Bottom)
  models_hr_hetero_detailed <- suppressMessages(suppressWarnings(
      feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~ 
        i(race_gender_detailed, ref = "White_Male") + 
        i(resp_race_gender_detailed, race_gender_detailed, ref = "White_Male") 
      | resume_index + responseid + r_do_bythree,
      data = firm_long_dt[treat == "nonblind" & role == "HR"],
      vcov = ~ responseid
    )
  ))
  names(models_hr_hetero_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z", "sc_advance")

  models_eng_hetero_detailed <- suppressMessages(suppressWarnings(
      feols(
      c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~ 
        i(race_gender_detailed, ref = "White_Male") + 
        i(resp_race_gender_detailed, race_gender_detailed, ref = "White_Male") 
      | resume_index + responseid + r_do_bythree,
      data = firm_long_dt[treat == "nonblind" & role == "Eng" & resp_race_gender != "Other"],
      vcov = ~ responseid
    )
  ))
  names(models_eng_hetero_detailed) <- c("sc_coding_z", "sc_fit_z", "sc_stay_z", "sc_overall_z")

# --- 2. Calculate Counts for Labels ---
  resp_counts_hetero_detailed <- firm_long_dt[treat == "nonblind" & !is.na(resp_race_gender_detailed) & resp_race_gender_detailed != "Other", .(
    N_HR = uniqueN(responseid[role == "HR"]),
    N_Eng = uniqueN(responseid[role == "Eng"])
  ), by = .(resp_race_gender_detailed)]

# --- 3. Generate Plots ---
  
  #### Overall
  p_ovr_conc <- plot_simple_concordance(models_hr_concordance_detailed$sc_overall_z, models_eng_concordance_detailed$sc_overall_z, "Overall (Z) - Concordance (Detailed Race/Gender)")
  p_ovr_hr_det <- plot_heterogeneity_detailed_race_gender(models_hr_hetero_detailed$sc_overall_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
  p_ovr_eng_det <- plot_heterogeneity_detailed_race_gender(models_eng_hetero_detailed$sc_overall_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

  #### Coding
  p_cod_conc <- plot_simple_concordance(models_hr_concordance_detailed$sc_coding_z, models_eng_concordance_detailed$sc_coding_z, "Coding (Z) - Concordance (Detailed Race/Gender)")
  p_coding_hr_det <- plot_heterogeneity_detailed_race_gender(models_hr_hetero_detailed$sc_coding_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
  p_coding_eng_det <- plot_heterogeneity_detailed_race_gender(models_eng_hetero_detailed$sc_coding_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

  #### Fit
  p_fit_conc <- plot_simple_concordance(models_hr_concordance_detailed$sc_fit_z, models_eng_concordance_detailed$sc_fit_z, "Fit (Z) - Concordance (Detailed Race/Gender)")
  p_fit_hr_det <- plot_heterogeneity_detailed_race_gender(models_hr_hetero_detailed$sc_fit_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
  p_fit_eng_det <- plot_heterogeneity_detailed_race_gender(models_eng_hetero_detailed$sc_fit_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

  #### Stay
  p_stay_conc <- plot_simple_concordance(models_hr_concordance_detailed$sc_stay_z, models_eng_concordance_detailed$sc_stay_z, "Stay (Z) - Concordance (Detailed Race/Gender)")
  p_stay_hr_det <- plot_heterogeneity_detailed_race_gender(models_hr_hetero_detailed$sc_stay_z, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")
  p_stay_eng_det <- plot_heterogeneity_detailed_race_gender(models_eng_hetero_detailed$sc_stay_z, "Engineers", "Discrimination (Z)", FALSE, resp_counts_hetero_detailed, "Eng")

  #### Advance
  p_adv_conc <- plot_simple_concordance(models_hr_concordance_detailed$sc_advance, NULL, title = "Advance (LPM) - Concordance (Detailed Race/Gender)")
  p_advance_hr_det <- plot_heterogeneity_detailed_race_gender(models_hr_hetero_detailed$sc_advance, "Human Resources", "Discrimination (Z)", TRUE, resp_counts_hetero_detailed, "HR")  
  p_empty <- ggplot() + annotate("text", x = 0, y = 0, label = "Engineers: Not Measured", size = 5, color = "gray50") + theme_void()

# --- 4. Print ---
suppressWarnings({
  
  # Overall
  p_conc_centered <- cowplot::plot_grid(NULL, p_ovr_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_ovr_hr_det, p_ovr_eng_det, "Overall (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Coding
  p_conc_centered <- cowplot::plot_grid(NULL, p_cod_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_coding_hr_det, p_coding_eng_det, "Coding (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Fit
  p_conc_centered <- cowplot::plot_grid(NULL, p_fit_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_fit_hr_det, p_fit_eng_det, "Fit (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Stay
  p_conc_centered <- cowplot::plot_grid(NULL, p_stay_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_stay_hr_det, p_stay_eng_det, "Stay (Z)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
  cat("\\newpage\n")

  # Advance
  p_conc_centered <- cowplot::plot_grid(NULL, p_adv_conc, NULL, ncol=3, rel_widths=c(0.25, 0.5, 0.25))
  p_full_interaction <- hetero_side_by_side_plots(p_advance_hr_det, p_empty, "Advance (0/1, LPM)")
  print(cowplot::plot_grid(p_conc_centered, p_full_interaction, ncol=1, rel_heights=c(0.4, 1.2)))
})


rm(models_hr_concordance_detailed, models_eng_concordance_detailed, 
   models_hr_hetero_detailed, models_eng_hetero_detailed, 
   resp_counts_hetero_detailed, 
   p_ovr_conc, p_ovr_hr_det, p_ovr_eng_det, 
   p_cod_conc, p_coding_hr_det, p_coding_eng_det, 
   p_fit_conc, p_fit_hr_det, p_fit_eng_det, 
   p_stay_conc, p_stay_hr_det, p_stay_eng_det, 
   p_adv_conc, p_advance_hr_det,
   p_conc_centered, p_full_interaction
)
```