---
title: "Stage-by-Stage Impact of Blind Hiring"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{bbm}
  - \usepackage{array}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- +++++ ++++++ ++++++ Part 5-2: Analysis (Stage-by-Stage Impact of Blind Hiring) +++++ ++++++ ++++++ -->


# Summary

\textbf{Core Thesis:}

The traditional justification for blind hiring is built on the assumption of \emph{in-group favoritism} --- the premise that majority gatekeepers harbor implicit biases against underrepresented minorities (URMs) and systematically favor candidates who look like themselves. Blind hiring is theoretically deployed to level the playing field by removing demographic ``noise'' and revealing pure technical ``signal.''

Our experiment demonstrates the \emph{exact opposite} is occurring in modern software engineering hiring.

Because majority gatekeepers organically apply an informal ``out-group premium'' to minority candidates, blinding demographic information fundamentally reshuffles hiring outcomes --- mechanically harming URMs and boosting White Males. Furthermore, this informal bias is highly elastic to formal corporate policy. When firms lack explicit diversity mandates, individual evaluators engage in \emph{compensatory bias}, informally boosting minority scores. Enforcing blind hiring in these environments destroys this potential safety net. Finally, despite claims that demographics are distracting ``noise,'' blinding resumes yielded \emph{no improvement} in the actual technical quality of the selected candidates.

\newpage

# Overall Treatment Effect on Evaluations (Reshuffling)

\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{The Finding:} Blinding demographic information during candidate evaluation \emph{reshuffles} hiring outcomes by disrupting a pre-existing system of \emph{demographic premiums and penalties}.
  \item \textbf{The Winners: White Males.} Evaluated by Engineers, White Male overall scores mechanically rise by \textcolor{blue}{+8.5\%} of a SD under blinding.
  \item \textbf{The Losers: Hispanic candidates.} When stripped of their demographic identity, Hispanic Male scores plunge by \textcolor{blue}{-11.5\%} of a SD (evaluated by HR), and Hispanic Female scores fall by \textcolor{blue}{-6.9\%} of a SD (evaluated by Engineers).
  \item \textbf{The Takeaway:} Blind hiring removes a \emph{baseline penalty} that White Males were experiencing in the non-blind evaluations, while simultaneously stripping Hispanic candidates of an \emph{(diversity) premium}.
  \item \textbf{Caveat:} Hiring is often an \emph{ordinal ranking} problem --- one candidate's gain corresponds to another's lost opportunity --- so the absence of statistical significance on a given row does not mean the corresponding group is unaffected by blinding.
\end{itemize}
\vspace{-0.9em}

```{r blind_hiring_treatment_effects_demo, echo = FALSE, results = 'asis'}
## Treatment Effects of Blind Hiring
## Reference: Blind resumes (baseline)
## Shows effect of revealing each demographic vs. keeping it blind

## HR Models (with sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_hr_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))
names(models_hr_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

## Engineer Models (no sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_eng_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))
names(models_eng_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

## Flip coefficient signs so a positive coefficient = effect of blinding.
flip_coef_signs <- function(model) {
  model$coefficients <- -1 * model$coefficients
  return(model)
}
models_hr_blind  <- lapply(models_hr_blind,  flip_coef_signs)
models_eng_blind <- lapply(models_eng_blind, flip_coef_signs)

## Coefficient map - ONLY show demographic coefficients
coef_map_blind <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female"
)

## Custom gof_map
gof_custom_blind <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

## FE / controls footer rows (displayed inside the table). Respondent FE and
## Respondent Characteristics are placed adjacent to make the contrast visible:
## we do NOT soak up respondent heterogeneity with a fixed effect, but we DO
## include respondent demographic controls as absorbing FEs + age polynomial.
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows_hr <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_hr) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")
## 6 coefs * (est+se) = 12 rows; FE rows sit immediately after.
attr(fe_rows_hr, "position") <- 13:16

fe_rows_eng <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_eng) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")
attr(fe_rows_eng, "position") <- 13:16

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel A: HR}\n\n")

modelsummary(
  models_hr_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_hr,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(16, extra_latex_after = "\\midrule")

cat("\\end{minipage}\n")
cat("\\hfill\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel B: Engineer}\n\n")

modelsummary(
  models_eng_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_eng,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(16, extra_latex_after = "\\midrule")

cat("\\end{minipage}\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{\\textwidth}\\raggedright\\scriptsize\n")
cat("\\textit{Standard errors clustered by respondent.}\\\\\n")
cat("\\textit{Note on Interpreting Coefficients:} The underlying regression uses Blind resumes as the reference category, so raw coefficients capture (nonblind $-$ blind) or the effect of being blinded for each demographic on standardized overall evaluation scores. We then multiply by $-1$ to report (blind $-$ nonblind), aligning the sign convention with the standard ``effect of blinding'' framing. Positive coefficient $\\Rightarrow$ blinding raises the score for that demographic.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

## Clean up
rm(models_hr_blind, models_eng_blind, coef_map_blind, gof_custom_blind, flip_coef_signs,
   chk, nox, fe_rows_hr, fe_rows_eng)
```




\clearpage
# Rejecting In-Group Favoritism (Why White Males Win)
\enlargethispage{2.5in}

\begingroup\small
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}\setlength\itemindent{0pt}
  \item \textbf{The Context:} White Males constitute the overwhelming majority of Software Engineer evaluators in this sample (and the industry at large). \emph{Legacy theories assume this group favors its own.}
  \item \textbf{The Finding:} Our experiment shows that the modern tech industry actually operates on a preference for the \emph{out-group} (or preference for \emph{under-represented groups}). Because White Males make up the majority of the evaluator pool, their behavior drives the aggregate metrics. When you blind resumes, the scores of concordant (race/gender) applicants evaluated by Engineers actually rise by \textcolor{blue}{+6.9\%} of a SD ($p < 0.05$) while the scores of discordant applicants fall by \textcolor{blue}{-0.9\%} of a SD ($p < 0.05$).
  \item \textbf{The Takeaway:} This shows that, under non-blinded evaluations, the majority gatekeepers were \emph{actively penalizing} candidates who looked like themselves and assigning a \emph{premium to evaluation scores of minority candidates}. Enforcing blind hiring doesn't stop discrimination against minorities; it stops the White Male majority from systematically boosting them. This explains why, in our experiment, White Male applicants are the primary beneficiaries of blind hiring: they are ``rescued'' from the baseline penalty imposed by their own demographic engineer peers.
\end{itemize}
\endgroup
\vspace{-1.4em}

## By Concordant Race (matched on detailed Asian Ethnicity)

```{r bh_heterogeneity_concordance_race, echo = FALSE, results = 'asis'}
## Tri-level variable: Blind / Nonblind-Concordant / Nonblind-Nonconcordant
## Use detailed-race concordance: Asian respondents are matched at the
## sub-ethnicity level (Chinese / Indian). Korean / Japanese / other-Asian
## respondents in nonblind are coded as always-discordant in 5_Cleaning.R,
## so they remain in the regression rather than being dropped.
firm_long_dt[, blind_concordance_race := fcase(
  treat == "blind",                                     "Blind",
  treat == "nonblind" & concordance_race_detailed == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_detailed == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race := factor(blind_concordance_race,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

## HR and Engineer regressions — same FE skeleton as Section 1.1
models_hr_bh_conc_race <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_race, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_race) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_race <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_race, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_race) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_race  <- lapply(models_hr_bh_conc_race,  flip_coef_signs)
models_eng_bh_conc_race <- lapply(models_eng_bh_conc_race, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_race, models_eng_bh_conc_race)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")  # trailing space disambiguator

coef_map_conc <- c(
  "blind_concordance_race::Nonblind_Concordant"    = "Concordant Applicant",
  "blind_concordance_race::Nonblind_Nonconcordant" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
## Place FE rows immediately after the 4 coef rows (2 coefs * (est+se)).
attr(fe_rows, "position") <- 5:8

n_hr_wah  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_race), responseid])
n_eng_wah <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_race), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_wah, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_wah, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined at the detailed race level: Asian respondents are matched at the sub-ethnicity level (Chinese / Indian). Respondents whose race is not represented in the applicant pool (e.g., Black, Other; Korean / Japanese / other-Asian whose sub-ethnicity is not Chinese or Indian) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_race, models_eng_bh_conc_race, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_wah, n_eng_wah, panel_a_lbl, panel_b_lbl)
```
\vspace{-0.8em}
## By Concordant Gender

```{r bh_heterogeneity_concordance_gender, echo = FALSE, results = 'asis'}
firm_long_dt[, blind_concordance_gender := fcase(
  treat == "blind",                              "Blind",
  treat == "nonblind" & concordance_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_gender := factor(blind_concordance_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

models_hr_bh_conc_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_gender) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_gender) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_gender  <- lapply(models_hr_bh_conc_gender,  flip_coef_signs)
models_eng_bh_conc_gender <- lapply(models_eng_bh_conc_gender, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_gender, models_eng_bh_conc_gender)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "blind_concordance_gender::Nonblind_Concordant"    = "Concordant Applicant",
  "blind_concordance_gender::Nonblind_Nonconcordant" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

n_hr_mf  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_gender), responseid])
n_eng_mf <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_gender), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_mf, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_mf, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Respondents whose gender is not represented in the applicant pool (e.g., Non-binary, Other) are treated as always-discordant in nonblind, since the applicant names are exclusively Male or Female.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_gender, models_eng_bh_conc_gender, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_mf, n_eng_mf, panel_a_lbl, panel_b_lbl)
```


\clearpage
## By Concordant Race and Gender

```{r bh_heterogeneity_concordance_broad, echo = FALSE, results = 'asis'}
## Weaker-concordance robustness check: race-gender match at the broad level.
## Asian respondents (regardless of detailed sub-group: Chinese, Indian,
## Korean, Japanese, etc.) match Asian applicants. Uses the pre-built
## `concordance_race_gender` (= 1 if race_gender == resp_race_gender at the
## {White, Asian, Hispanic} x {Male, Female} level).
firm_long_dt[, blind_concordance_race_gender := fcase(
  treat == "blind",                                   "Blind",
  treat == "nonblind" & concordance_race_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race_gender := factor(blind_concordance_race_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

models_hr_bh_conc_rg <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_rg) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_rg <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_rg) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_rg  <- lapply(models_hr_bh_conc_rg,  flip_coef_signs)
models_eng_bh_conc_rg <- lapply(models_eng_bh_conc_rg, flip_coef_signs)

all_models <- c(models_hr_bh_conc_rg, models_eng_bh_conc_rg)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "blind_concordance_race_gender::Nonblind_Concordant"    = "Concordant Applicant",
  "blind_concordance_race_gender::Nonblind_Nonconcordant" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

n_hr_wah  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_race_gender), responseid])
n_eng_wah <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_race_gender), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_wah, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_wah, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined as race-gender match at the broad level (Asian respondents are matched at the broad Asian level rather than by detailed sub-ethnicity). Respondents whose race or gender is not represented in the applicant pool (e.g., Black, Other; Non-binary, Other-gender) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_rg, models_eng_bh_conc_rg, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_wah, n_eng_wah, panel_a_lbl, panel_b_lbl)
```


## By Concordant Race and Gender (matched on detailed Asian Ethnicity)

```{r bh_heterogeneity_concordance_detailed, echo = FALSE, results = 'asis'}
## Uses the pre-built `concordance_race_gender_detailed_blind` factor from
## 5_Cleaning.R. Asian respondents whose detailed sub-ethnicity (e.g.,
## Korean, Japanese) is not represented in the applicant pool are coded as
## always-discordant in nonblind, so they are kept in the regression rather
## than dropped.

models_hr_bh_conc_det <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(concordance_race_gender_detailed_blind, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_det) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_det <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(concordance_race_gender_detailed_blind, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_det) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_det  <- lapply(models_hr_bh_conc_det,  flip_coef_signs)
models_eng_bh_conc_det <- lapply(models_eng_bh_conc_det, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_det, models_eng_bh_conc_det)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "concordance_race_gender_detailed_blind::Concordant_Group" = "Concordant Applicant",
  "concordance_race_gender_detailed_blind::Discordant_Group" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

n_hr_det  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(concordance_race_gender_detailed_blind), responseid])
n_eng_det <- uniqueN(firm_long_dt[role == "Eng" & !is.na(concordance_race_gender_detailed_blind), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_det, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_det, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined at the detailed race-gender level: applicants are Chinese, Indian, White, or Hispanic (by gender). Respondents whose detailed race-gender is not represented in the applicant pool (e.g., Korean / Japanese / other-Asian sub-ethnicities; Black, Other-race; Non-binary, Other-gender) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_det, models_eng_bh_conc_det, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_det, n_eng_det, panel_a_lbl, panel_b_lbl)
```


\clearpage
# Institutional Substitution (Firm Policy vs. Individual Bias)

\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{The Puzzle of Individual Ideology (Section 4.1):} If one merely examines the two-way relationship between an evaluator's personal DEI priority and their evaluation scores, the effects appear surprisingly \emph{muted and statistically noisy}. At first glance, one might incorrectly conclude that personal ideology has little impact on how blind hiring reshuffles outcomes.
  \begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item \textbf{Compensatory Bias} (Firms with NO Diversity Mandate, see \textcolor{red}{red lines}): When a firm lacks an explicit objective policy targeting URMs, highly pro-DEI HR professionals engage in \emph{compensatory bias}. They fill the perceived institutional void by informally inflating minority candidates' scores in the baseline.
    \item \textbf{Institutional Crowding-Out} (Firms WITH a Diversity Mandate, see \textcolor{blue}{blue lines}): Conversely, when the firm explicitly mandates URM targeting, this formal policy \emph{crowds out} the evaluator's informal efforts. The pro-DEI HR professional, when combined with institutional DEI targeting policy, \emph{mutes} from assigning premium to under-represented minority's scores.
  \end{itemize}
  \item (Note \emph{Divergence between HR and Engineer Results}, particularly in Triple Interaction.)
\end{itemize}
\vspace{-0.9em}

## By Individual DEI / Diversity Preferences

\begin{itemize}\setlength{\itemsep}{1pt}\setlength{\parskip}{0pt}\setlength{\topsep}{2pt}
  \item \textbf{Index A} --- equal-weight average (1/5 each) of five z-scored items: the four stated DEI views plus the revealed-priority ranking of ``Diversity and Representation'' from the seven-goals question.
  \item \textbf{Index B} --- first principal component of the same five items.
\end{itemize}

```{r bh_dei_overall, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

proxies <- c(
  "pro_dei_race_z",
  "pro_dei_gender_z",
  "pro_diverse_z",
  "div_priority_z",
  "firm_attention_race_z",
  "firm_attention_gender_z"
)
col_labels <- c("Race DEI", "Gender DEI", "Diverse Wkpl", "Div Goal",
                "Firm Race Attn", "Firm Gender Attn")

## LHS is negated so that all coefficients flip at the regression level;
## etable (unlike modelsummary) ignores post-hoc overrides of $coefficients,
## so we flip via I(-sc_overall_z) instead of via a flip_coef_signs wrapper.
fit_one <- function(d, pr) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      pr)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(proxies, function(p) fit_one(dt_hr,  p))
models_eng <- lapply(proxies, function(p) fit_one(dt_eng, p))
all_models <- c(models_hr, models_eng)

groups <- c("White_Male"      = "White Male",
            "White_Female"    = "White Female",
            "Asian_Male"      = "Asian Male",
            "Asian_Female"    = "Asian Female",
            "Hispanic_Male"   = "Hispanic Male",
            "Hispanic_Female" = "Hispanic Female")

dict_main  <- setNames(unname(groups), paste0("race_gender::", names(groups)))
dict_inter <- unlist(lapply(proxies, function(p) {
  setNames(paste0(unname(groups), " $\\times$ Pro DEI/Diversity (Z)"),
           paste0("race_gender::", names(groups), ":", p))
}))
dict_all <- c(dict_main, dict_inter)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%race_gender",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume (Content) FE"      = rep(chk, 12),
    "Display Position FE"      = rep(chk, 12),
    "Respondent Demographic FE" = rep(chk, 12)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")

tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{13}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-7} \\\\cmidrule(lr){8-13}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)

tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, proxies, col_labels, fit_one,
   models_hr, models_eng, all_models, groups, dict_main, dict_inter, dict_all,
   chk, tbl, proxy_hdr)
```

```{r bh_dei_indices_combined, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

## Axis decomposition: Non-Hisp Male (WM+AM) / Non-Hisp Female (WF+AF) / Hispanic
## (HM+HF). Levels ordered Male, Female, Hispanic so coefficient rows print in
## that order.
build_axis <- function(d) {
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d
}
dt_hr  <- build_axis(dt_hr)
dt_eng <- build_axis(dt_eng)

indices    <- c("dei_index_A_z", "dei_index_B_z")
idx_labels <- c("Index A", "Index B")

## ---------- LEFT: per-race-gender ----------
fit_rg <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx)),
    data = d, vcov = ~ responseid
  )))
}
models_rg <- c(lapply(indices, function(p) fit_rg(dt_hr,  p)),
               lapply(indices, function(p) fit_rg(dt_eng, p)))

groups <- c("White_Male"     = "White Male",
            "White_Female"   = "White Female",
            "Asian_Male"     = "Asian Male",
            "Asian_Female"   = "Asian Female",
            "Hispanic_Male"  = "Hispanic Male",
            "Hispanic_Female"= "Hispanic Female")
dict_rg <- c(
  setNames(unname(groups), paste0("race_gender::", names(groups))),
  unlist(lapply(indices, function(p) {
    setNames(paste0(unname(groups), " $\\times$ DEI Index"),
             paste0("race_gender::", names(groups), ":", p))
  })),
  setNames(rep("DEI Index", length(indices)), indices)
)

## ---------- RIGHT: URM cut ----------
fit_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + %s + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx)),
    data = d, vcov = ~ responseid
  )))
}
models_urm <- c(lapply(indices, function(p) fit_urm(dt_hr,  p)),
                lapply(indices, function(p) fit_urm(dt_eng, p)))

dict_urm <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("DEI Index", length(indices)), indices),
  setNames(rep("URM $\\times$ DEI Index",    length(indices)),
           paste0("urm_tech_blind::Nonblind_URM:",    indices)),
  setNames(rep("Non-URM $\\times$ DEI Index", length(indices)),
           paste0("urm_tech_blind::Nonblind_NonURM:", indices))
)

## ---------- RIGHT BOTTOM: URM axis decomposition ----------
fit_axis <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_axis_blind, ref = 'Blind') + %s + i(urm_axis_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx)),
    data = d, vcov = ~ responseid
  )))
}
models_axis <- c(lapply(indices, function(p) fit_axis(dt_hr,  p)),
                 lapply(indices, function(p) fit_axis(dt_eng, p)))

dict_axis <- c(
  "urm_axis_blind::Nonblind_MaleNonHisp"   = "Male (non-hispanic)",
  "urm_axis_blind::Nonblind_FemaleNonHisp" = "Female (non-hispanic)",
  "urm_axis_blind::Nonblind_Hispanic"      = "Hispanic",
  setNames(rep("DEI Index", length(indices)), indices),
  setNames(rep("Male (non-hispanic) $\\times$ DEI Index",   length(indices)),
           paste0("urm_axis_blind::Nonblind_MaleNonHisp:",   indices)),
  setNames(rep("Female (non-hispanic) $\\times$ DEI Index", length(indices)),
           paste0("urm_axis_blind::Nonblind_FemaleNonHisp:", indices)),
  setNames(rep("Hispanic $\\times$ DEI Index",        length(indices)),
           paste0("urm_axis_blind::Nonblind_Hispanic:",      indices))
)

chk <- "\\checkmark"
nox <- "$\\times$"

shared_notes <- c(
  "Standard errors clustered by respondent.",
  "Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group."
)
extralines_4 <- list(
  "Resume (Content) FE"        = rep(chk, 4),
  "Display Position FE"        = rep(chk, 4),
  "Respondent FE"              = rep(nox, 4),
  "Respondent Characteristics" = rep(chk, 4)
)

build_tbl <- function(models, dict, keep_pat, header_text, notes_arg = shared_notes,
                      extralines_arg = extralines_4, fitstat_arg = c("n", "r2", "ar2")) {
  tbl <- etable(
    models, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = keep_pat,
    fitstat = fitstat_arg,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict,
    notes = notes_arg,
    extralines = extralines_arg
  )
  idx_hdr <- paste(idx_labels, collapse = " & ")
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{5}{c}{\\\\textbf{", header_text, "}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\multicolumn{2}{c}{\\\\textbf{Panel A: HR}}",
      " & \\\\multicolumn{2}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
      " \\\\cmidrule(lr){2-3} \\\\cmidrule(lr){4-5}",
      " & ", idx_hdr, " & ", idx_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  ## Resize to a fraction of textwidth (not full) so that a 4-data-column table
  ## doesn't get vertically stretched to fill a 0.49-textwidth minipage.
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{0.72\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.72}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  ## Inject midrules separating coefs / FE rows / fitstat. Then dedupe in case
  ## etable already inserted one between the FE block and the fitstat block.
  tbl <- sub("Resume \\(Content\\) FE",
             "\\\\midrule\nResume (Content) FE", tbl, perl = TRUE)
  tbl <- sub("Observations",
             "\\\\midrule\nObservations", tbl, perl = TRUE)
  tbl <- gsub("(?:\\\\midrule\\s*){2,}", "\\\\midrule\n", tbl, perl = TRUE)
  ## Strip outer table env so the tabular can be placed inside a minipage.
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

tbl_left  <- build_tbl(models_rg,  dict_rg,
                       "%race_gender",
                       "Per Race-Gender",
                       notes_arg = c("The DEI Index level effect is included in each regression.",
                                     shared_notes))
## Right-top (URM cut) and right-bottom (axis): drop FE and fitstat rows from
## both since LEFT (Per Race-Gender) already shows the same FE structure and N.
## A single combined note at the foot of the right column carries this info.
tbl_right <- build_tbl(models_urm, dict_urm,
                       "%urm_tech_blind",
                       "Per URM Cut",
                       notes_arg = NULL,
                       extralines_arg = NULL,
                       fitstat_arg = NA)
tbl_axis  <- build_tbl(models_axis, dict_axis,
                       "%urm_axis_blind",
                       "Per URM Cut --- Axis Decomposition",
                       notes_arg = c("FE structure, controls, N, and DEI Index level effect as in the left-side table.",
                                     "Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group."),
                       extralines_arg = NULL,
                       fitstat_arg = NA)

cat("\\begin{table}[H]\\centering\n")
cat("\\begin{minipage}[t]{0.49\\textwidth}\\centering\n")
cat(tbl_left)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.49\\textwidth}\\centering\n")
cat(tbl_right)
cat("\\par\\vspace{0.2em}\n")
cat(tbl_axis)
cat("\\end{minipage}\n")
cat("\\end{table}\n")

rm(dt_hr, dt_eng, indices, idx_labels, build_axis, fit_rg, fit_urm, fit_axis,
   models_rg, models_urm, models_axis, groups, dict_rg, dict_urm, dict_axis,
   chk, nox, shared_notes, extralines_4, build_tbl,
   tbl_left, tbl_right, tbl_axis)
```


```{r bh_dei_urm, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

zstd <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

## Combined indices: row-mean of two z-scored measures, re-standardized within sample.
dt_hr [, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_eng[, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_hr [, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]
dt_eng[, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]

proxies    <- c("pro_dei_view_z", "pro_diverse_z", "div_priority_z", "firm_attention_z")
col_labels <- c("DEI Views (R \\\\& G)", "Diverse Wkpl", "Div Goal", "Firm DEI Attn (R \\\\& G)")

## Here we build a URM-tech x Blind indicator by hand.
## urm_tech_blind_factor: Blind / Nonblind-URM / Nonblind-NonURM
dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                           "Blind",
  treat == "nonblind" & urm_tech == 1,         "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0,         "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                           "Blind",
  treat == "nonblind" & urm_tech == 1,         "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0,         "Nonblind_NonURM",
  default = NA_character_
)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

## LHS negated so coefficients flip at the regression level (etable does not
## respect post-hoc overrides of $coefficients).
fit_urm <- function(d, pr) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      pr)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(proxies, function(p) fit_urm(dt_hr,  p))
models_eng <- lapply(proxies, function(p) fit_urm(dt_eng, p))
all_models <- c(models_hr, models_eng)

dict_all <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ Pro DEI/Diversity (Z)",    length(proxies)),
           paste0("urm_tech_blind::Nonblind_URM:",    proxies)),
  setNames(rep("Non-URM $\\times$ Pro DEI/Diversity (Z)", length(proxies)),
           paste0("urm_tech_blind::Nonblind_NonURM:", proxies))
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 8),
    "Display Position FE"       = rep(chk, 8),
    "Respondent Demographic FE" = rep(chk, 8)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{9}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-5} \\\\cmidrule(lr){6-9}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, zstd, proxies, col_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, proxy_hdr)
```


```{r bh_dei_indices_urm, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z")
idx_labels <- c("Index A", "Index B")

fit_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(indices, function(p) fit_urm(dt_hr,  p))
models_eng <- lapply(indices, function(p) fit_urm(dt_eng, p))
all_models <- c(models_hr, models_eng)

dict_all <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ DEI Index",    length(indices)),
           paste0("urm_tech_blind::Nonblind_URM:",    indices)),
  setNames(rep("Non-URM $\\times$ DEI Index", length(indices)),
           paste0("urm_tech_blind::Nonblind_NonURM:", indices))
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  notes = "URM-Tech = \\{White Female, Asian Female, Hispanic Male, Hispanic Female\\}. Sample: both blind and nonblind arms. Coefficients flipped via I(-sc\\_overall\\_z) so positive => effect of blinding. Standard errors clustered by respondent.",
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 6),
    "Display Position FE"       = rep(chk, 6),
    "Respondent Demographic FE" = rep(chk, 6)
  )
)

idx_hdr <- paste(idx_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{7}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- URM Cut, Three DEI / Diversity Index Options, signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-4} \\\\cmidrule(lr){5-7}",
    " & ", idx_hdr, " & ", idx_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
## Force equal-width centered data columns (see note in indices_overall chunk).
tbl <- sub("\\{lcccccc\\}",
           "{l*{6}{>{\\\\centering\\\\arraybackslash}p{0.7in}}}",
           tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, indices, idx_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, idx_hdr)
```


## (Triple Interaction Models) By Whether the Firm Targets URM $\times$ Respondent's DEI Priority

```{r bh_dei_targets, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

## URM axis decomposition: Non-Hisp Male / Non-Hisp Female / Hispanic.
build_axis <- function(d) {
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d
}
dt_hr  <- build_axis(dt_hr)
dt_eng <- build_axis(dt_eng)

indices    <- c("dei_index_A_z", "dei_index_B_z")
idx_labels <- c("Index A", "Index B")

chk <- "\\checkmark"
nox <- "$\\times$"

extralines_4 <- list(
  "Resume (Content) FE"        = rep(chk, 2),
  "Display Position FE"        = rep(chk, 2),
  "Respondent FE"              = rep(nox, 2),
  "Respondent Characteristics" = rep(chk, 2)
)

## Per-race-gender triple (TOP panel of each Index minipage).
fit_triple_22_rg <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + firm_targets_fh + I(firm_targets_fh * %s) + i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, firm_targets_fh, ref = 'Blind') + i(race_gender, I(firm_targets_fh * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx, idx, idx)),
    data = d, vcov = ~ responseid
  )))
}

## URM-cut triple (MIDDLE panel of each Index minipage).
fit_triple_22_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + firm_targets_fh + I(firm_targets_fh * %s) + i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, firm_targets_fh, ref = 'Blind') + i(urm_tech_blind, I(firm_targets_fh * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx, idx, idx)),
    data = d, vcov = ~ responseid
  )))
}

## URM-axis triple (BOTTOM panel of each Index minipage).
fit_triple_22_axis <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + firm_targets_fh + I(firm_targets_fh * %s) + i(urm_axis_blind, ref = 'Blind') + i(urm_axis_blind, %s, ref = 'Blind') + i(urm_axis_blind, firm_targets_fh, ref = 'Blind') + i(urm_axis_blind, I(firm_targets_fh * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx, idx, idx)),
    data = d, vcov = ~ responseid
  )))
}

groups_rg <- c("White_Male"     = "White Male",
               "White_Female"   = "White Female",
               "Asian_Male"     = "Asian Male",
               "Asian_Female"   = "Asian Female",
               "Hispanic_Male"  = "Hispanic Male",
               "Hispanic_Female"= "Hispanic Female")

build_22_top <- function(idx, lbl) {
  m_hr  <- fit_triple_22_rg(dt_hr,  idx)
  m_eng <- fit_triple_22_rg(dt_eng, idx)
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_top <- setNames(
    paste0(unname(groups_rg), " $\\times$ Firm Targets URM $\\times$ DEI Index"),
    paste0("race_gender::", names(groups_rg), ":I(firm_targets_fh * ", idx, ")")
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%race_gender::.*:I\\(",
    fitstat = NA,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_top,
    notes = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- Per Race-Gender (triple terms)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.72}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

build_22_bot <- function(idx, lbl) {
  m_hr  <- fit_triple_22_urm(dt_hr,  idx)
  m_eng <- fit_triple_22_urm(dt_eng, idx)
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_trp <- c(
    "urm_tech_blind::Nonblind_URM"                                = "URM",
    "urm_tech_blind::Nonblind_NonURM"                             = "Non-URM",
    setNames("URM $\\times$ DEI Index",            paste0("urm_tech_blind::Nonblind_URM:", idx)),
    setNames("Non-URM $\\times$ DEI Index",        paste0("urm_tech_blind::Nonblind_NonURM:", idx)),
    "urm_tech_blind::Nonblind_URM:firm_targets_fh"    = "URM $\\times$ Firm Targets URM",
    "urm_tech_blind::Nonblind_NonURM:firm_targets_fh" = "Non-URM $\\times$ Firm Targets URM",
    setNames("URM $\\times$ Firm Targets URM $\\times$ DEI Index",
             paste0("urm_tech_blind::Nonblind_URM:I(firm_targets_fh * ", idx, ")")),
    setNames("Non-URM $\\times$ Firm Targets URM $\\times$ DEI Index",
             paste0("urm_tech_blind::Nonblind_NonURM:I(firm_targets_fh * ", idx, ")"))
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_tech_blind",
    fitstat = "n",
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_trp,
    notes = NULL,
    extralines = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- URM Cut (full triple)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.72}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("Resume \\(Content\\) FE",
             "\\\\midrule\nResume (Content) FE", tbl, perl = TRUE)
  tbl <- sub("Observations",
             "\\\\midrule\nObservations", tbl, perl = TRUE)
  tbl <- gsub("(?:\\\\midrule\\s*){2,}", "\\\\midrule\n", tbl, perl = TRUE)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

## Axis-cut triple, full 12 coefficients (levels, x DEI, x FT, triple).
build_22_axis <- function(idx, lbl) {
  m_hr  <- fit_triple_22_axis(dt_hr,  idx)
  m_eng <- fit_triple_22_axis(dt_eng, idx)
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  cells <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
  labs  <- c("Male (NH)", "Female (NH)", "Hispanic")

  dict_axis <- c(
    setNames(labs, paste0("urm_axis_blind::", cells)),
    setNames(paste0(labs, " $\\times$ DEI"),
             paste0("urm_axis_blind::", cells, ":", idx)),
    setNames(paste0(labs, " $\\times$ FT"),
             paste0("urm_axis_blind::", cells, ":firm_targets_fh")),
    setNames(paste0(labs, " $\\times$ FT $\\times$ DEI"),
             paste0("urm_axis_blind::", cells, ":I(firm_targets_fh * ", idx, ")"))
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_axis_blind",
    fitstat = NA,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_axis,
    notes = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- URM Axis (full triple)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  ## No resizebox: render at natural \scriptsize so table is small vertically
  ## (since long row labels would otherwise force enlargement to fill minipage).
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "{\\\\scriptsize\\\\renewcommand{\\\\arraystretch}{0.85}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

## ---------------------------------------------------------------------------
## §2.2 layout: tables (URM-axis triple for Index A) on top, then three-panel
## "scissors" marginal-effects plot for HR (Index A) below.
## Figure must be generated first since cat() output references plot_file_22.
## ---------------------------------------------------------------------------

## "Scissors" marginal-effects plot for HR (Index A), three panels.
## TE_X(DEI, FT) = beta_X + beta_{X x DEI} * DEI + beta_{X x FT} * FT
##                   + beta_{X x FT x DEI} * DEI * FT
## SE via quadratic form v' Sigma v with v = (1, DEI, FT, DEI*FT).
m_hr_axis_A  <- fit_triple_22_axis(dt_hr,  "dei_index_A_z")
m_eng_axis_A <- fit_triple_22_axis(dt_eng, "dei_index_A_z")
cf_hr  <- coef(m_hr_axis_A);  V_hr  <- vcov(m_hr_axis_A)
cf_eng <- coef(m_eng_axis_A); V_eng <- vcov(m_eng_axis_A)

cells_22 <- list(
  "Male (non-hispanic)" = c(
    level  = "urm_axis_blind::Nonblind_MaleNonHisp",
    dei    = "urm_axis_blind::Nonblind_MaleNonHisp:dei_index_A_z",
    ft     = "urm_axis_blind::Nonblind_MaleNonHisp:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_MaleNonHisp:I(firm_targets_fh * dei_index_A_z)"
  ),
  "Female (non-hispanic)" = c(
    level  = "urm_axis_blind::Nonblind_FemaleNonHisp",
    dei    = "urm_axis_blind::Nonblind_FemaleNonHisp:dei_index_A_z",
    ft     = "urm_axis_blind::Nonblind_FemaleNonHisp:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_FemaleNonHisp:I(firm_targets_fh * dei_index_A_z)"
  ),
  "Hispanic" = c(
    level  = "urm_axis_blind::Nonblind_Hispanic",
    dei    = "urm_axis_blind::Nonblind_Hispanic:dei_index_A_z",
    ft     = "urm_axis_blind::Nonblind_Hispanic:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_Hispanic:I(firm_targets_fh * dei_index_A_z)"
  )
)

dei_grid <- seq(-2, 2, length.out = 41)
plot_dt <- as.data.table(expand.grid(role = c("HR", "Eng"),
                                      group = names(cells_22),
                                      DEI = dei_grid, FT = c(0, 1),
                                      stringsAsFactors = FALSE))
plot_dt[, c("est", "se") := {
  ix <- unname(cells_22[[group]])
  v  <- c(1, DEI, FT, DEI * FT)
  cf <- if (role == "HR") cf_hr else cf_eng
  V  <- if (role == "HR") V_hr  else V_eng
  list(sum(cf[ix] * v),
       sqrt(c(v %*% V[ix, ix] %*% v)))
}, by = .(role, group, DEI, FT)]
plot_dt[, ':='(lwr = est - 1.96 * se, upr = est + 1.96 * se)]
plot_dt[, FT_label := factor(FT, levels = c(0, 1),
                              labels = c("Firm does NOT target URM",
                                         "Firm targets URM"))]
plot_dt[, group := factor(group,
                          levels = c("Male (non-hispanic)",
                                     "Female (non-hispanic)",
                                     "Hispanic"))]
plot_dt[, role := factor(role, levels = c("HR", "Eng"))]

y_lim <- range(c(plot_dt$lwr, plot_dt$upr)) * 1.05
panel_letters <- c("Male (non-hispanic)" = "A",
                   "Female (non-hispanic)" = "B",
                   "Hispanic" = "C")

scissors_panel <- function(rl, grp) {
  d <- plot_dt[role == rl & group == grp]
  ggplot(d, aes(x = DEI, y = est, color = FT_label, fill = FT_label, linetype = FT_label)) +
    annotate("rect", xmin = -2, xmax = 2, ymin = 0,         ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
    annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA) +
    geom_line(linewidth = 1) +
    annotate("text", x = 0, y = y_lim[2] * 0.93, label = "Blinding helps",
             hjust = 0.5, vjust = 1, size = 2.4, fontface = "italic", color = "darkgreen") +
    annotate("text", x = 0, y = y_lim[1] * 0.93, label = "Blinding hurts",
             hjust = 0.5, vjust = 0, size = 2.4, fontface = "italic", color = "darkred") +
    scale_color_manual(values = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_fill_manual(values  = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_linetype_manual(values = c("Firm does NOT target URM" = "dashed",
                                     "Firm targets URM"        = "solid")) +
    coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
    labs(title = paste0("Panel ", panel_letters[grp],
                        ifelse(rl == "HR", "1", "2"), ": ",
                        rl, " --- ", grp),
         x = paste0(rl, " Evaluator's DEI Index A (z-score)"),
         y = "Effect of Blinding (Δ Overall Z-Score)",
         color = NULL, fill = NULL, linetype = NULL) +
    theme_bw(base_size = 8) +
    theme(legend.position = "bottom",
          plot.title = element_text(size = 9, face = "bold"),
          axis.title = element_text(size = 8),
          panel.grid.minor = element_blank())
}

scissors <- (scissors_panel("HR",  "Male (non-hispanic)") |
             scissors_panel("HR",  "Female (non-hispanic)") |
             scissors_panel("HR",  "Hispanic")) /
            (scissors_panel("Eng", "Male (non-hispanic)") |
             scissors_panel("Eng", "Female (non-hispanic)") |
             scissors_panel("Eng", "Hispanic")) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_22 <- file.path(fig_dir, "8B_22_scissors.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_22, plot = scissors, width = 11, height = 4.0, device = "pdf")
))

## ---------------------------------------------------------------------------
## Layout output: single Index A axis triple table on top, three-panel figure
## below, both wrapped in one minipage so LaTeX keeps them on the same page.
## ---------------------------------------------------------------------------
axis_A <- build_22_axis(indices[1], idx_labels[1])

cat("\\begin{center}\n")
cat(axis_A)
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize URM-axis triple regression with Index A as the DEI proxy. FE: Resume (Content) $\\checkmark$, Display Position $\\checkmark$, Respondent $\\times$, Respondent Characteristics $\\checkmark$. SE clustered by respondent. \\textit{Firm Targets URM} $=$ \\texttt{firm\\_targets\\_female} OR \\texttt{firm\\_targets\\_hispanic}. Positive coefficient $\\Rightarrow$ blinding raises the score for that group.\\par}\n")
cat("\\end{center}\n")
cat("\\nopagebreak[4]\n")
cat("\\begin{center}\n")
cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_22, "}\n", sep = "")
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize Top row: HR evaluators (Panels A1, B1, C1). Bottom row: Engineer evaluators (Panels A2, B2, C2). Lines: predicted effect of blinding on each group's overall score as a function of the rater's DEI Index A; shaded bands are 95\\% CIs from the linear combination of axis-triple coefficients (SE clustered by respondent).\\par}\n")
cat("\\end{center}\n")


rm(dt_hr, dt_eng, indices, idx_labels, chk, nox, groups_rg,
   extralines_4, build_axis, fit_triple_22_rg, fit_triple_22_urm, fit_triple_22_axis,
   build_22_top, build_22_bot, build_22_axis,
   axis_A,
   m_hr_axis_A, m_eng_axis_A, cf_hr, V_hr, cf_eng, V_eng,
   cells_22, dei_grid, plot_dt, y_lim,
   panel_letters, scissors_panel, scissors, fig_dir, plot_file_22)
```

## (Triple Interaction Models) By Respondent's Priority for DEI $\times$ Firm Attention on DEI

```{r bh_dei_triple, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

chk <- "\\checkmark"

## LHS negated so all coefficients flip at the regression level; etable does
## not respect post-hoc $coefficients overrides.
fit_triple_urm <- function(d, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, div_priority_z, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(div_priority_z * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      proxy_b, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

m_hr_r  <- fit_triple_urm(dt_hr,  "firm_attention_race_z")
m_eng_r <- fit_triple_urm(dt_eng, "firm_attention_race_z")
m_hr_g  <- fit_triple_urm(dt_hr,  "firm_attention_gender_z")
m_eng_g <- fit_triple_urm(dt_eng, "firm_attention_gender_z")

n_used <- c(
  dt_hr [!is.na(firm_attention_race_z),    uniqueN(responseid)],
  dt_eng[!is.na(firm_attention_race_z),   uniqueN(responseid)],
  dt_hr [!is.na(firm_attention_gender_z),  uniqueN(responseid)],
  dt_eng[!is.na(firm_attention_gender_z), uniqueN(responseid)]
)
n_full <- c(
  dt_hr [, uniqueN(responseid)],
  dt_eng[, uniqueN(responseid)],
  dt_hr [, uniqueN(responseid)],
  dt_eng[, uniqueN(responseid)]
)
n_drop <- n_full - n_used

models_trp <- list("HR (Race)" = m_hr_r, "Eng (Race)" = m_eng_r,
                   "HR (Gender)" = m_hr_g, "Eng (Gender)" = m_eng_g)

dict_trp <- c(
  "urm_tech_blind::Nonblind_URM"                                       = "URM",
  "urm_tech_blind::Nonblind_URM:div_priority_z"                        = "URM $\\times$ Respondent Prioritizes Diversity",
  "urm_tech_blind::Nonblind_URM:firm_attention_race_z"                 = "URM $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:firm_attention_gender_z"               = "URM $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:I(div_priority_z * firm_attention_race_z)"   = "URM $\\times$ Resp Prioritizes $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:I(div_priority_z * firm_attention_gender_z)" = "URM $\\times$ Resp Prioritizes $\\times$ Firm DEI Attn"
)

tbl_trp <- etable(
  models_trp,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = "%urm_tech_blind::Nonblind_URM",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_trp,
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 4),
    "Display Position FE"       = rep(chk, 4),
    "Respondent Demographic FE" = rep(chk, 4),
    "Respondents (used)"        = as.character(n_used),
    "Dropped (NA proxy)"        = as.character(n_drop)
  )
)

tbl_trp <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{5}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Race-DEI Attn}}",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Gender-DEI Attn}} \\\\\\\\",
    " \\\\cmidrule(lr){2-3} \\\\cmidrule(lr){4-5}",
    " & HR & Eng & HR & Eng \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_trp
)
tbl_trp <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_trp)
tbl_trp <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
  tbl_trp
)
tbl_trp <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_trp)

cat(tbl_trp)

rm(dt_hr, dt_eng, chk, fit_triple_urm, m_hr_r, m_eng_r, m_hr_g, m_eng_g,
   models_trp, dict_trp, tbl_trp, n_used, n_full, n_drop)
```


```{r bh_dei_indices_triple, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

## URM axis decomposition: Non-Hisp Male / Non-Hisp Female / Hispanic.
build_axis <- function(d) {
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d
}
dt_hr  <- build_axis(dt_hr)
dt_eng <- build_axis(dt_eng)

indices    <- c("dei_index_A_z", "dei_index_B_z")
idx_labels <- c("Index A", "Index B")

chk <- "\\checkmark"
nox <- "$\\times$"

shared_notes <- c(
  "Standard errors clustered by respondent.",
  "\\textit{Note:} Firm DEI Attn proxy is \\texttt{firm\\_dei\\_attention\\_z} (within-cell z-score of the equal-weight average of \\texttt{firm\\_attention\\_race\\_z} and \\texttt{firm\\_attention\\_gender\\_z}).",
  "Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group."
)
extralines_4 <- list(
  "Resume (Content) FE"        = rep(chk, 2),
  "Display Position FE"        = rep(chk, 2),
  "Respondent FE"              = rep(nox, 2),
  "Respondent Characteristics" = rep(chk, 2)
)

## Per-race-gender triple (for the TOP panel of each Index minipage).
fit_triple_rg <- function(d, idx, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + %s + I(%s * %s) + i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, I(%s * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, proxy_b, idx, proxy_b, idx, proxy_b, idx, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

## URM-cut triple (for the MIDDLE panel of each Index minipage).
fit_triple_urm <- function(d, idx, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + %s + I(%s * %s) + i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(%s * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, proxy_b, idx, proxy_b, idx, proxy_b, idx, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

## URM-axis triple (for the BOTTOM panel of each Index minipage).
fit_triple_axis <- function(d, idx, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + %s + I(%s * %s) + i(urm_axis_blind, ref = 'Blind') + i(urm_axis_blind, %s, ref = 'Blind') + i(urm_axis_blind, %s, ref = 'Blind') + i(urm_axis_blind, I(%s * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, proxy_b, idx, proxy_b, idx, proxy_b, idx, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

groups_rg <- c("White_Male"     = "White Male",
               "White_Female"   = "White Female",
               "Asian_Male"     = "Asian Male",
               "Asian_Female"   = "Asian Female",
               "Hispanic_Male"  = "Hispanic Male",
               "Hispanic_Female"= "Hispanic Female")

build_top_tbl <- function(idx, lbl) {
  m_hr  <- fit_triple_rg(dt_hr,  idx, "firm_dei_attention_z")
  m_eng <- fit_triple_rg(dt_eng, idx, "firm_dei_attention_z")
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  ## Dict: only the 6 triple terms get readable labels (one per demographic).
  dict_top <- setNames(
    paste0(unname(groups_rg), " $\\times$ DEI Index $\\times$ Firm DEI Attn"),
    paste0("race_gender::", names(groups_rg), ":I(", idx, " * firm_dei_attention_z)")
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%race_gender::.*:I\\(",
    fitstat = NA,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_top,
    notes = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- Per Race-Gender (triple terms)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.72}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

build_bot_tbl <- function(idx, lbl) {
  m_hr  <- fit_triple_urm(dt_hr,  idx, "firm_dei_attention_z")
  m_eng <- fit_triple_urm(dt_eng, idx, "firm_dei_attention_z")
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_trp <- c(
    "urm_tech_blind::Nonblind_URM"                         = "URM",
    "urm_tech_blind::Nonblind_NonURM"                      = "Non-URM",
    setNames("URM $\\times$ DEI Index",     paste0("urm_tech_blind::Nonblind_URM:", idx)),
    setNames("Non-URM $\\times$ DEI Index", paste0("urm_tech_blind::Nonblind_NonURM:", idx)),
    "urm_tech_blind::Nonblind_URM:firm_dei_attention_z"    = "URM $\\times$ Firm DEI Attn",
    "urm_tech_blind::Nonblind_NonURM:firm_dei_attention_z" = "Non-URM $\\times$ Firm DEI Attn",
    setNames("URM $\\times$ DEI Index $\\times$ Firm DEI Attn",
             paste0("urm_tech_blind::Nonblind_URM:I(", idx, " * firm_dei_attention_z)")),
    setNames("Non-URM $\\times$ DEI Index $\\times$ Firm DEI Attn",
             paste0("urm_tech_blind::Nonblind_NonURM:I(", idx, " * firm_dei_attention_z)"))
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_tech_blind",
    fitstat = "n",
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_trp,
    notes = NULL,
    extralines = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- URM Cut (full triple)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.72}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("Resume \\(Content\\) FE",
             "\\\\midrule\nResume (Content) FE", tbl, perl = TRUE)
  tbl <- sub("Observations",
             "\\\\midrule\nObservations", tbl, perl = TRUE)
  tbl <- gsub("(?:\\\\midrule\\s*){2,}", "\\\\midrule\n", tbl, perl = TRUE)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

## Axis-cut triple, full 12 coefficients (levels, x DEI, x Firm DEI Attn, triple).
## Mirrors build_bot_tbl in coverage; drops FE / fitstat (in middle block).
build_axis_tbl <- function(idx, lbl) {
  m_hr  <- fit_triple_axis(dt_hr,  idx, "firm_dei_attention_z")
  m_eng <- fit_triple_axis(dt_eng, idx, "firm_dei_attention_z")
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  cells <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
  labs  <- c("Male (non-hispanic)", "Female (non-hispanic)", "Hispanic")

  dict_axis <- c(
    setNames(labs, paste0("urm_axis_blind::", cells)),
    setNames(paste0(labs, " $\\times$ DEI Index"),
             paste0("urm_axis_blind::", cells, ":", idx)),
    setNames(paste0(labs, " $\\times$ Firm DEI Attn"),
             paste0("urm_axis_blind::", cells, ":firm_dei_attention_z")),
    setNames(paste0(labs, " $\\times$ DEI $\\times$ Firm DEI Attn"),
             paste0("urm_axis_blind::", cells, ":I(", idx, " * firm_dei_attention_z)"))
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_axis_blind",
    fitstat = NA,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_axis,
    notes = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- URM Axis (full triple)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.72}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

## Each minipage stacks: top (per-RG triple terms only) and axis (URM-axis full
## triple, 12 coefficients). The URM-cut block is dropped because the axis block
## subsumes it: URM = NHF + Hispanic, Non-URM = NHM (Non-Hisp Male).
top_A  <- build_top_tbl (indices[1], idx_labels[1]); axis_A <- build_axis_tbl(indices[1], idx_labels[1])
top_B  <- build_top_tbl (indices[2], idx_labels[2]); axis_B <- build_axis_tbl(indices[2], idx_labels[2])

cat("\\begin{table}[H]\\centering\n")
cat("\\hfill\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_A); cat("\\par\\vspace{0.3em}\n"); cat(axis_A)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_B); cat("\\par\\vspace{0.3em}\n"); cat(axis_B)
cat("\\end{minipage}\\hfill\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{\\textwidth}\\raggedright\\scriptsize\n")
cat("Top panel: per-race-gender triple (only the 6 triple terms shown). Bottom panel: URM-axis triple (full 12 coefficients), where Male (non-hispanic) = WM+AM, Female (non-hispanic) = WF+AF, Hispanic = HM+HF. The URM-cut block is omitted: it is implied by the axis block (URM = Female (non-hispanic) + Hispanic; Non-URM = Male (non-hispanic)). Both blocks share identical specification: Resume (Content) FE $\\checkmark$, Display Position FE $\\checkmark$, Respondent FE $\\times$, Respondent Characteristics $\\checkmark$.\\\\\n")
cat("Standard errors clustered by respondent.\\\\\n")
cat("\\textit{Note:} Firm DEI Attn proxy is \\texttt{firm\\_dei\\_attention\\_z} (within-cell z-score of the equal-weight average of \\texttt{firm\\_attention\\_race\\_z} and \\texttt{firm\\_attention\\_gender\\_z}).\\\\\n")
cat("Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n")

rm(dt_hr, dt_eng, indices, idx_labels, chk, nox, groups_rg,
   shared_notes, extralines_4, build_axis,
   fit_triple_rg, fit_triple_urm, fit_triple_axis,
   build_top_tbl, build_bot_tbl, build_axis_tbl,
   top_A, top_B, axis_A, axis_B)
```


\newpage
# Treatment Effect on Productivity of Hired (The Efficiency Myth)

\vspace{-0.4em}
If blind hiring reshuffles outcomes (Sections 2--4), proponents might argue it is a necessary trade-off for strict meritocracy and better technical hires. Our results show otherwise.
\vspace{-0.4em}

\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{Signal Extraction Remains Flat (S5.1.):} Removing demographic information (or noise) does \emph{not} meaningfully improve their ability to identify top ability candidates.
  \item \textbf{Quality of Hires Does Not Improve (S5.2.):} Blind hiring has a \emph{null} effect on the actual coding quality of the hired cohort.
\end{itemize}
\vspace{-1em}

## Does Blinding Lead to More Accurate Coding Evaluations?

\textcolor{blue}{\textbf{Takeaway}}: Evaluators do extract signal about candidates' actual coding ability --- Engineers much more strongly than HR, consistent with Engineers seeing the code while HR sees only the resume. Blinding, however, does \emph{not} meaningfully change this signal-extraction ability in either role: the $\texttt{true\_coding\_z} \times \texttt{blind}$ interaction is small, negative, and statistically insignificant for both HR and Engineers. If blinding --- which in our experiment amounts to removing random, uninformative demographic noise --- improved signal-extraction ability, we would expect a positive and statistically significant interaction term. In short, blinding \emph{reshuffles} who receives high scores (Section 1.1) but does not change \emph{how well} those scores track actual coding skill.

\textcolor{blue}{\textbf{Specification}}:
\vspace{-0.7em}
$$
\text{Hiring Evaluation Score (Z)} \sim \text{True Coding Ability (Z)} \times \mathbbm{1}[\text{Blind arm}] \mid \text{Respondent FE} + \text{Display Position FE}.
$$
\vspace{-1.4em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item $H_0\!: \beta = 0$ --- the evaluator extracts \emph{no signal} from true coding ability.
    \item $H_0\!: \beta = 1$ --- the evaluator is \emph{perfectly calibrated}: a $1$ SD rise in true ability produces exactly a $1$ SD rise in the rating, with no shrinkage.
\end{itemize}

```{r blind_hiring_signal_extraction, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Pooled z-score of the lab coding score (constant within resume_index)
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]

## Two pooled interacted regressions --- one per role. Since treat is
## between-respondent, responseid FE absorbs the main effect of treat but
## leaves both the main slope on true_coding_z (identified from within-
## respondent variation, by definition the nonblind arm's slope since
## nonblind is the reference) and the interaction slope identifiable.
m_hr  <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))

## Extract arm-specific slopes, SEs, and the four tests (H0: beta = 0 / 1
## for each arm) from a single pooled model. beta_nonblind = main coef;
## beta_blind = main + interaction; SE(beta_blind) via linear-combination
## formula using the full vcov matrix.
extract_stats <- function(m) {
  ct    <- coeftable(m)
  V     <- vcov(m)
  main_name <- "true_coding_z"
  int_name  <- "true_coding_z:treat::blind"

  b_main <- ct[main_name, "Estimate"]
  s_main <- ct[main_name, "Std. Error"]
  b_int  <- ct[int_name,  "Estimate"]
  s_int  <- ct[int_name,  "Std. Error"]
  cov_mi <- V[main_name, int_name]

  b_nb <- b_main
  s_nb <- s_main
  b_b  <- b_main + b_int
  s_b  <- sqrt(s_main^2 + s_int^2 + 2 * cov_mi)

  pval <- function(t) 2 * (1 - pnorm(abs(t)))
  p_nb_0 <- pval(b_nb / s_nb)
  p_nb_1 <- pval((b_nb - 1) / s_nb)
  p_b_0  <- pval(b_b  / s_b)
  p_b_1  <- pval((b_b  - 1) / s_b)
  ## H0: beta_blind = beta_nonblind is the same as H0: beta_interaction = 0,
  ## so we read its p-value directly off the interaction coefficient.
  p_eq   <- ct[int_name, 4]

  fs <- fitstat(m, c("r2", "ar2"), simplify = TRUE)
  list(b_nb = unname(b_nb), s_nb = unname(s_nb),
       b_b  = unname(b_b),  s_b  = unname(s_b),
       p_nb_0 = p_nb_0, p_nb_1 = p_nb_1,
       p_b_0  = p_b_0,  p_b_1  = p_b_1,
       p_eq   = unname(p_eq),
       n = m$nobs, r2 = unname(fs["r2"]), ar2 = unname(fs["ar2"]))
}

s_hr  <- extract_stats(m_hr)
s_eng <- extract_stats(m_eng)

## Formatting helpers.
sig_stars <- function(p) {
  if (is.na(p))        ""
  else if (p < 0.01)   "***"
  else if (p < 0.05)   "**"
  else if (p < 0.10)   "*"
  else                 ""
}
fmt_p <- function(p) {
  if (is.na(p)) return("")
  pstr <- if (p < 0.001) "$<\\!0.001$" else sprintf("%.3f", p)
  paste0("p = ", pstr, sig_stars(p))
}

chk <- "\\checkmark"
nox <- "$\\times$"

cell_col <- function(s) c(
  sprintf("%.3f~(%.3f)", s$b_nb, s$s_nb),
  sprintf("%.3f~(%.3f)", s$b_b,  s$s_b),
  format(s$n,   big.mark = ","),
  sprintf("%.3f", s$r2),
  sprintf("%.3f", s$ar2),
  nox, chk, chk, nox
)

tbl <- data.frame(
  lbl = c("$\\hat\\beta_{\\text{nonblind}}$ (slope, nonblind arm)",
          "$\\hat\\beta_{\\text{blind}}$ (slope, blind arm)",
          "Observations",
          "$R^2$",
          "Adj. $R^2$",
          "Resume (Content) FE",
          "Display Position FE",
          "Respondent FE",
          "Respondent Characteristics"),
  HR  = cell_col(s_hr),
  Eng = cell_col(s_eng),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
names(tbl) <- c(" ", "HR", "Engineer")

## Build the plot and save it to disk so we can include it via
## \includegraphics inside a LaTeX minipage layout.
plot_data <- data.frame(
  role = factor(c("HR", "HR", "Engineer", "Engineer"),
                levels = c("HR", "Engineer")),
  arm  = factor(c("Nonblind", "Blind", "Nonblind", "Blind"),
                levels = c("Nonblind", "Blind")),
  est  = c(s_hr$b_nb,  s_hr$b_b,  s_eng$b_nb, s_eng$b_b),
  se   = c(s_hr$s_nb,  s_hr$s_b,  s_eng$s_nb, s_eng$s_b)
)
plot_data$ci_lo <- plot_data$est - 1.96 * plot_data$se
plot_data$ci_hi <- plot_data$est + 1.96 * plot_data$se

p_signal <- ggplot(plot_data, aes(x = est, y = arm, color = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.2, linewidth = 0.8) +
  geom_point(size = 3) +
  facet_wrap(~ role, ncol = 1, strip.position = "left") +
  scale_x_continuous(limits = c(-0.05, 1.1), breaks = seq(0, 1, 0.2)) +
  scale_color_manual(values = c("Nonblind" = "#d62728", "Blind" = "#1f77b4")) +
  labs(x = expression(hat(beta)*": slope of evaluator rating on true coding ability"),
       y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0, face = "bold"))

## Save plot to disk so we can include it via \includegraphics inside a
## LaTeX minipage (table on left, plot on right).
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file <- file.path(fig_dir, "8B_signal_extraction.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file, plot = p_signal, width = 4.5, height = 2.6, device = "pdf")
))

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[c]{0.50\\textwidth}\n")
cat("\\centering\n")
cat("{\\fontsize{7}{9}\\selectfont\n")

## Plain kable + row_spec (no kable_styling, since kable_styling adds an
## inner \\begin{table} wrapper that LaTeX rejects inside a minipage).
print(
  kable(tbl, format = "latex", booktabs = TRUE, escape = FALSE,
        align = "lcc", row.names = FALSE) %>%
    row_spec(2, extra_latex_after = "\\midrule") %>%
    row_spec(5, extra_latex_after = "\\midrule")
)

cat("}\n")
cat("\\end{minipage}%\n")
cat("\\begin{minipage}[c]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file, "}\n", sep = "")
cat("\\end{minipage}\n")

cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{0.98\\textwidth}\\scriptsize\n")
cat("Cluster-robust standard errors (by respondent) shown in parentheses next to each $\\hat\\beta$. Stars on p-values: * $p<0.10$, ** $p<0.05$, *** $p<0.01$. \\textit{Note:} Both arm-specific slopes come from a single pooled interacted regression per role, \\texttt{sc\\_coding\\_z \\textasciitilde\\ true\\_coding\\_z * i(treat, ref = 'nonblind') | responseid + r\\_do}; $\\hat\\beta_{\\text{nonblind}}$ is read off the main coefficient, and $\\hat\\beta_{\\text{blind}}$ is computed as (main + interaction) with SE derived via the standard linear-combination formula using the estimated variance--covariance matrix. The ``Resume (Content) FE'' row is marked as not included because \\texttt{overall\\_score} is a resume-level property (one lab score per resume), so a resume-content FE would absorb the RHS and leave the main slope unidentified. ``Respondent Characteristics'' is marked as not included because respondent-level variables (age, gender, race, education, income) are all perfectly collinear with the respondent FE and therefore absorbed by it.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

rm(m_hr, m_eng, s_hr, s_eng,
   extract_stats, sig_stars, fmt_p, cell_col,
   chk, nox, tbl, plot_data, p_signal, plot_file, fig_dir)
```

## Does Blind Hiring Select Better Coders?


```{r blind_hiring_coding_quality, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

# ==============================================================================
# HELPER: Dynamic standardization relative to nonblind group at each k
# ==============================================================================
get_avg_coding_score <- function(role_filter, treat_filter, k, 
                                  pass_var_prefix, data) {
  col <- paste0(pass_var_prefix, k)
  d   <- data[role == role_filter & treat == treat_filter & get(col) == 1]
  if (nrow(d) == 0) return(NA_real_)
  mean(d$overall_score, na.rm = TRUE)
}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# ==============================================================================
results_list <- list()

for (k in 1:18) {

  # --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]

  # Dynamic standardization: relative to nonblind mean/sd at this k
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do + q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_hr)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }

  # --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]

  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do + q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_eng)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

# ==============================================================================
# PLOT
# ==============================================================================
ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    title    = "Does Blind Hiring Select Better Coders?",
    subtitle = paste("Effect of blinding on actual coding quality of selected candidates.",
                     "Standardized relative to nonblind group at each k."),
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Positive = blind hiring selects candidates with higher actual coding scores.\nSignificance: * p<0.10, ** p<0.05, *** p<0.01"
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )

rm(results_list, dt_plot, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```

```{r blind_hiring_demographic_selection, eval = FALSE, echo=FALSE, fig.width=12, fig.height=10}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# LHS: hr_passk / eng_topk (0/1 selected)
# RHS: race_gender with "Blind" as reference, then flip signs
# ==============================================================================
results_all <- list()

demo_labels <- c("White_Male", "White_Female", "Asian_Male",
                 "Asian_Female", "Hispanic_Male", "Hispanic_Female")

for (k in 1:18) {

  hr_col  <- paste0("hr_pass", k)
  eng_col <- paste0("eng_top", k)

  # --- HR ---
  tryCatch({
    m_hr <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(hr_col,
        " ~ i(race_gender, ref = 'Blind') |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income")),
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_hr)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})

  # --- Engineer ---
  tryCatch({
    m_eng <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(eng_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income +
          resp_python + resp_java")),
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_eng)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})
}

# ==============================================================================
# ASSEMBLE AND PLOT
# ==============================================================================
dt_plot <- rbindlist(results_all)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, demo  := factor(demo,  levels = c("White Male",    "White Female",
                                             "Asian Male",    "Asian Female",
                                             "Hispanic Male", "Hispanic Female"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]
dt_plot[, star_y := ifelse(estimate >= 0,
                            ci_high + 0.005,
                            ci_low  - 0.005)]

ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.6, size = 0.4, fatten = 3) +
  geom_text(aes(y = star_y, label = sig_stars),
            vjust = ifelse(dt_plot$estimate >= 0, 0, 1),
            size = 3, color = "black", show.legend = FALSE) +
  facet_grid(demo ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = seq(1, 18, by = 3),
                     name   = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.20))) +
  labs(
    title    = "Effect of Blind Hiring on Selection Probability by Demographic Group",
    subtitle = paste("Blinding effect = -(effect of revealing identity vs blind).",
                     "Positive = more likely selected under blinding."),
    y        = "Blinding Effect on Selection Probability",
    color    = "Evaluator Role",
    caption  = "Significance: * p<0.10, ** p<0.05, *** p<0.01. Base group: Blind resumes."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10),
    legend.text        = element_text(size = 9),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    strip.text.y       = element_text(angle = 0),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0),
    panel.spacing      = unit(0.4, "lines")
  )

rm(results_all, dt_plot, demo_labels, dg, k,
   hr_col, eng_col, m_hr, m_eng, ct,
   est, se, p_val, coef_nm)
```



\clearpage
# Heterogeneity in Treatment Effects by Candidate Quality (Appendix)

\textit{The §2 demographic-effect regression run on subsamples by candidate quality. Three cuts: per-cell (6 race-gender groups), URM-tech (URM = WF+AF+HM+HF vs Non-URM = WM+AM), and URM-axis (Male non-Hispanic / Female non-Hispanic / Hispanic). Two splits per cut: GPA tier (Low / Mid / Top) and Coding tier (Bottom / Top half on \texttt{test\_case}). LHS sign-flipped so positive $\Rightarrow$ blinding raises the score.}
\vspace{-0.4em}


```{r appendix_het_by_quality_graphs, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.width = 11, fig.height = 6}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

build_aux <- function(d) {
  d[, urm_tech_blind := fcase(
    treat == "blind",                    "Blind",
    treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
    treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
    default = NA_character_)]
  d[, urm_tech_blind := factor(urm_tech_blind,
    levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d
}
dt_hr  <- build_aux(dt_hr)
dt_eng <- build_aux(dt_eng)

## Helper: extract estimates from a feols split-fit, restricted to the
## demographic factor's coefficient rows. Returns a long data frame with
## Term / Tier / Estimate / SE / stars columns.
extract_split_te <- function(model_split, factor_var, tier_labels) {
  parts <- list()
  for (i in seq_along(model_split)) {
    df <- as.data.frame(coeftable(model_split[[i]]))
    df$Term <- rownames(df)
    df$Tier <- tier_labels[i]
    parts[[i]] <- df
  }
  out <- do.call(rbind, parts)
  out <- out[grepl(paste0("^", factor_var, "::"), out$Term), ]
  out$Term <- gsub(paste0(factor_var, "::"), "", out$Term)
  out$Term <- gsub("Nonblind_", "", out$Term)
  out$Term <- gsub("MaleNonHisp",   "Male (NH)",   out$Term)
  out$Term <- gsub("FemaleNonHisp", "Female (NH)", out$Term)
  out$Term <- gsub("_", " ", out$Term)
  out$Term <- factor(out$Term, levels = unique(out$Term))
  out$stars <- ifelse(out$`Pr(>|t|)` < 0.01, "***",
                ifelse(out$`Pr(>|t|)` < 0.05, "**",
                ifelse(out$`Pr(>|t|)` < 0.10, "*", "")))
  out$Tier <- factor(out$Tier, levels = tier_labels)
  out
}

make_split_plot <- function(plot_df, title_label, color_vals, shape_vals, show_y = TRUE) {
  p <- ggplot(plot_df, aes(x = Term, y = Estimate, color = Tier, shape = Tier)) +
    geom_hline(yintercept = 0, color = "black", linewidth = 0.4) +
    geom_pointrange(aes(ymin = Estimate - 1.96 * `Std. Error`,
                        ymax = Estimate + 1.96 * `Std. Error`),
                    position = position_dodge(width = 0.6), size = 0.3) +
    geom_text(aes(label = stars, y = Estimate + 1.96 * `Std. Error` + 0.015),
              position = position_dodge(width = 0.6), size = 2.6, vjust = 0,
              color = "black", show.legend = FALSE) +
    scale_color_manual(values = color_vals) +
    scale_shape_manual(values = shape_vals) +
    coord_cartesian(ylim = c(-0.5, 0.5)) +
    labs(title = title_label, x = NULL,
         y = "Effect of Blinding (Δ Overall Z)",
         color = "Tier:", shape = "Tier:") +
    theme_bw(base_size = 8) +
    theme(axis.text.x  = element_text(angle = 30, hjust = 1, size = 7),
          axis.title.y = element_text(size = 8),
          legend.position = "top",
          legend.title = element_text(face = "bold", size = 8),
          legend.text  = element_text(size = 7),
          plot.title   = element_text(face = "bold", size = 9),
          plot.margin  = margin(3, 6, 3, 3, "pt"))
  if (!show_y) p <- p + theme(axis.title.y = element_blank())
  p
}

gpa_levels <- c("Low_GPA", "Mid_GPA", "Top_GPA")
gpa_labels <- c("Low GPA", "Mid GPA", "Top GPA")
gpa_colors <- c("Low GPA" = "black", "Mid GPA" = "steelblue", "Top GPA" = "indianred1")
gpa_shapes <- c("Low GPA" = 16, "Mid GPA" = 15, "Top GPA" = 17)

code_levels <- c(0, 1)
code_labels <- c("Bottom 50% Coders", "Top 50% Coders")
code_colors <- c("Bottom 50% Coders" = "black", "Top 50% Coders" = "indianred1")
code_shapes <- c("Bottom 50% Coders" = 16, "Top 50% Coders" = 17)

## Wrapper: fit the §2 demographic-effect regression on a sample with split.
fit_split <- function(d, factor_var, split_var) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(%s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      factor_var)),
    data = d, split = as.formula(paste0("~", split_var)), vcov = ~ responseid)))
}

build_role_panel <- function(d, role_label, show_y_left = TRUE) {
  ## six fits per role
  m_rg_gpa  <- fit_split(d, "race_gender",     "gpa_tier3")
  m_rg_cod  <- fit_split(d, "race_gender",     "top_half_coder")
  m_ut_gpa  <- fit_split(d, "urm_tech_blind",  "gpa_tier3")
  m_ut_cod  <- fit_split(d, "urm_tech_blind",  "top_half_coder")
  m_ax_gpa  <- fit_split(d, "urm_axis_blind",  "gpa_tier3")
  m_ax_cod  <- fit_split(d, "urm_axis_blind",  "top_half_coder")

  df_rg_gpa <- extract_split_te(m_rg_gpa, "race_gender",    gpa_labels)
  df_rg_cod <- extract_split_te(m_rg_cod, "race_gender",    code_labels)
  df_ut_gpa <- extract_split_te(m_ut_gpa, "urm_tech_blind", gpa_labels)
  df_ut_cod <- extract_split_te(m_ut_cod, "urm_tech_blind", code_labels)
  df_ax_gpa <- extract_split_te(m_ax_gpa, "urm_axis_blind", gpa_labels)
  df_ax_cod <- extract_split_te(m_ax_cod, "urm_axis_blind", code_labels)

  p1 <- make_split_plot(df_rg_gpa, paste0(role_label, ": Per-Cell, by GPA"),
                        gpa_colors, gpa_shapes, show_y = show_y_left)
  p2 <- make_split_plot(df_rg_cod, paste0(role_label, ": Per-Cell, by Coding"),
                        code_colors, code_shapes, show_y = FALSE)
  p3 <- make_split_plot(df_ut_gpa, paste0(role_label, ": URM-tech, by GPA"),
                        gpa_colors, gpa_shapes, show_y = show_y_left)
  p4 <- make_split_plot(df_ut_cod, paste0(role_label, ": URM-tech, by Coding"),
                        code_colors, code_shapes, show_y = FALSE)
  p5 <- make_split_plot(df_ax_gpa, paste0(role_label, ": URM-axis, by GPA"),
                        gpa_colors, gpa_shapes, show_y = show_y_left)
  p6 <- make_split_plot(df_ax_cod, paste0(role_label, ": URM-axis, by Coding"),
                        code_colors, code_shapes, show_y = FALSE)

  list(rg_gpa = p1, rg_cod = p2,
       ut_gpa = p3, ut_cod = p4,
       ax_gpa = p5, ax_cod = p6)
}

panels_hr  <- build_role_panel(dt_hr,  "HR",  show_y_left = TRUE)
panels_eng <- build_role_panel(dt_eng, "Eng", show_y_left = TRUE)

## Save HR figure (3 rows × 2 cols).
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_hr  <- file.path(fig_dir, "8B_het_by_quality_HR.pdf")
plot_file_eng <- file.path(fig_dir, "8B_het_by_quality_Eng.pdf")

fig_hr <- (panels_hr$rg_gpa + panels_hr$rg_cod) /
          (panels_hr$ut_gpa + panels_hr$ut_cod) /
          (panels_hr$ax_gpa + panels_hr$ax_cod) +
          plot_layout(guides = "collect") &
          theme(legend.position = "top")

fig_eng <- (panels_eng$rg_gpa + panels_eng$rg_cod) /
           (panels_eng$ut_gpa + panels_eng$ut_cod) /
           (panels_eng$ax_gpa + panels_eng$ax_cod) +
           plot_layout(guides = "collect") &
           theme(legend.position = "top")

suppressMessages(suppressWarnings({
  ggsave(plot_file_hr,  plot = fig_hr,  width = 10, height = 9, device = "pdf")
  ggsave(plot_file_eng, plot = fig_eng, width = 10, height = 9, device = "pdf")
}))

cat("\\noindent\\textbf{HR Evaluators}\\par\\vspace{0.2em}\n")
cat("\\begin{center}\\includegraphics[width=0.85\\textwidth]{", plot_file_hr, "}\\end{center}\n", sep = "")
cat("\\clearpage\n")
cat("\\noindent\\textbf{Engineer Evaluators}\\par\\vspace{0.2em}\n")
cat("\\begin{center}\\includegraphics[width=0.85\\textwidth]{", plot_file_eng, "}\\end{center}\n", sep = "")

rm(dt_hr, dt_eng, build_aux, extract_split_te, make_split_plot, fit_split, build_role_panel,
   gpa_levels, gpa_labels, gpa_colors, gpa_shapes,
   code_levels, code_labels, code_colors, code_shapes,
   panels_hr, panels_eng, fig_hr, fig_eng,
   plot_file_hr, plot_file_eng, fig_dir)
```
