---
title: "Stage-by-Stage Impact of Blind Hiring"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{bbm}
  - \usepackage{array}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- +++++ ++++++ ++++++ Part 5-2: Analysis (Stage-by-Stage Impact of Blind Hiring) +++++ ++++++ ++++++ -->


# Treatment Effect on Evaluations

## On All Dimensions (Z)

\textcolor{blue}{\textbf{Takeaway}}: Blinding demographic information \emph{reshuffles} candidates' relative evaluations across stages.
\vspace{-0.9em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{Findings.} HR: Hispanic Male candidates' Overall scores fall by \textcolor{blue}{11.5\%} of a SD under blinding. Engineers: White Male scores rise by \textcolor{blue}{8.5\%} of a SD, Hispanic Female scores fall by \textcolor{blue}{6.9\%} of a SD.
  \item \textbf{Caveat.} Hiring is often an ordinal ranking problem --- one candidate's gain corresponds to another's lost opportunity --- so the absence of statistical significance on a given row does not mean the corresponding group is unaffected by blinding.
\end{itemize}
\vspace{-0.9em}

```{r blind_hiring_treatment_effects_demo, echo = FALSE, results = 'asis'}
## Treatment Effects of Blind Hiring
## Reference: Blind resumes (baseline)
## Shows effect of revealing each demographic vs. keeping it blind

## HR Models (with sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_hr_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))
names(models_hr_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

## Engineer Models (no sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_eng_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))
names(models_eng_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

## Flip coefficient signs so a positive coefficient = effect of blinding.
flip_coef_signs <- function(model) {
  model$coefficients <- -1 * model$coefficients
  return(model)
}
models_hr_blind  <- lapply(models_hr_blind,  flip_coef_signs)
models_eng_blind <- lapply(models_eng_blind, flip_coef_signs)

## Coefficient map - ONLY show demographic coefficients
coef_map_blind <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female"
)

## Custom gof_map
gof_custom_blind <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

## FE / controls footer rows (displayed inside the table). Respondent FE and
## Respondent Characteristics are placed adjacent to make the contrast visible:
## we do NOT soak up respondent heterogeneity with a fixed effect, but we DO
## include respondent demographic controls as absorbing FEs + age polynomial.
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows_hr <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_hr) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")
## 6 coefs * (est+se) = 12 rows; FE rows sit immediately after.
attr(fe_rows_hr, "position") <- 13:16

fe_rows_eng <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_eng) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")
attr(fe_rows_eng, "position") <- 13:16

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel A: HR}\n\n")

modelsummary(
  models_hr_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_hr,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(16, extra_latex_after = "\\midrule")

cat("\\end{minipage}\n")
cat("\\hfill\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel B: Engineer}\n\n")

modelsummary(
  models_eng_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_eng,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(16, extra_latex_after = "\\midrule")

cat("\\end{minipage}\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{\\textwidth}\\raggedright\\scriptsize\n")
cat("\\textit{Standard errors clustered by respondent.}\\\\\n")
cat("\\textit{Note on Interpreting Coefficients:} The underlying regression uses Blind resumes as the reference category, so raw coefficients capture (nonblind $-$ blind) or the effect of being blinded for each demographic on standardized overall evaluation scores. We then multiply by $-1$ to report (blind $-$ nonblind), aligning the sign convention with the standard ``effect of blinding'' framing. Positive coefficient $\\Rightarrow$ blinding raises the score for that demographic.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

## Clean up
rm(models_hr_blind, models_eng_blind, coef_map_blind, gof_custom_blind, flip_coef_signs,
   chk, nox, fe_rows_hr, fe_rows_eng)
```


\newpage
## Does Blinding Lead to More Accurate Coding Evaluations?

\textcolor{blue}{\textbf{Takeaway}}: Evaluators do extract signal about candidates' actual coding ability --- Engineers much more strongly than HR, consistent with Engineers seeing the code while HR sees only the resume. Blinding, however, does \emph{not} meaningfully change this signal-extraction ability in either role: the $\texttt{true\_coding\_z} \times \texttt{blind}$ interaction is small, negative, and statistically insignificant for both HR and Engineers. If blinding --- which in our experiment amounts to removing random, uninformative demographic noise --- improved signal-extraction ability, we would expect a positive and statistically significant interaction term. In short, blinding \emph{reshuffles} who receives high scores (Section 1.1) but does not change \emph{how well} those scores track actual coding skill.

\textcolor{blue}{\textbf{Specification}}:
\vspace{-0.7em}
$$
\text{Hiring Evaluation Score (Z)} \sim \text{True Coding Ability (Z)} \times \mathbbm{1}[\text{Blind arm}] \mid \text{Respondent FE} + \text{Display Position FE}.
$$
\vspace{-1.4em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item $H_0\!: \beta = 0$ --- the evaluator extracts \emph{no signal} from true coding ability.
    \item $H_0\!: \beta = 1$ --- the evaluator is \emph{perfectly calibrated}: a $1$ SD rise in true ability produces exactly a $1$ SD rise in the rating, with no shrinkage.
\end{itemize}

```{r blind_hiring_signal_extraction, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Pooled z-score of the lab coding score (constant within resume_index)
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]

## Two pooled interacted regressions --- one per role. Since treat is
## between-respondent, responseid FE absorbs the main effect of treat but
## leaves both the main slope on true_coding_z (identified from within-
## respondent variation, by definition the nonblind arm's slope since
## nonblind is the reference) and the interaction slope identifiable.
m_hr  <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))

## Extract arm-specific slopes, SEs, and the four tests (H0: beta = 0 / 1
## for each arm) from a single pooled model. beta_nonblind = main coef;
## beta_blind = main + interaction; SE(beta_blind) via linear-combination
## formula using the full vcov matrix.
extract_stats <- function(m) {
  ct    <- coeftable(m)
  V     <- vcov(m)
  main_name <- "true_coding_z"
  int_name  <- "true_coding_z:treat::blind"

  b_main <- ct[main_name, "Estimate"]
  s_main <- ct[main_name, "Std. Error"]
  b_int  <- ct[int_name,  "Estimate"]
  s_int  <- ct[int_name,  "Std. Error"]
  cov_mi <- V[main_name, int_name]

  b_nb <- b_main
  s_nb <- s_main
  b_b  <- b_main + b_int
  s_b  <- sqrt(s_main^2 + s_int^2 + 2 * cov_mi)

  pval <- function(t) 2 * (1 - pnorm(abs(t)))
  p_nb_0 <- pval(b_nb / s_nb)
  p_nb_1 <- pval((b_nb - 1) / s_nb)
  p_b_0  <- pval(b_b  / s_b)
  p_b_1  <- pval((b_b  - 1) / s_b)
  ## H0: beta_blind = beta_nonblind is the same as H0: beta_interaction = 0,
  ## so we read its p-value directly off the interaction coefficient.
  p_eq   <- ct[int_name, 4]

  fs <- fitstat(m, c("r2", "ar2"), simplify = TRUE)
  list(b_nb = unname(b_nb), s_nb = unname(s_nb),
       b_b  = unname(b_b),  s_b  = unname(s_b),
       p_nb_0 = p_nb_0, p_nb_1 = p_nb_1,
       p_b_0  = p_b_0,  p_b_1  = p_b_1,
       p_eq   = unname(p_eq),
       n = m$nobs, r2 = unname(fs["r2"]), ar2 = unname(fs["ar2"]))
}

s_hr  <- extract_stats(m_hr)
s_eng <- extract_stats(m_eng)

## Formatting helpers.
sig_stars <- function(p) {
  if (is.na(p))        ""
  else if (p < 0.01)   "***"
  else if (p < 0.05)   "**"
  else if (p < 0.10)   "*"
  else                 ""
}
fmt_p <- function(p) {
  if (is.na(p)) return("")
  pstr <- if (p < 0.001) "$<\\!0.001$" else sprintf("%.3f", p)
  paste0("p = ", pstr, sig_stars(p))
}

chk <- "\\checkmark"
nox <- "$\\times$"

cell_col <- function(s) c(
  sprintf("%.3f~(%.3f)", s$b_nb, s$s_nb),
  sprintf("%.3f~(%.3f)", s$b_b,  s$s_b),
  format(s$n,   big.mark = ","),
  sprintf("%.3f", s$r2),
  sprintf("%.3f", s$ar2),
  nox, chk, chk, nox
)

tbl <- data.frame(
  lbl = c("$\\hat\\beta_{\\text{nonblind}}$ (slope, nonblind arm)",
          "$\\hat\\beta_{\\text{blind}}$ (slope, blind arm)",
          "Observations",
          "$R^2$",
          "Adj. $R^2$",
          "Resume (Content) FE",
          "Display Position FE",
          "Respondent FE",
          "Respondent Characteristics"),
  HR  = cell_col(s_hr),
  Eng = cell_col(s_eng),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
names(tbl) <- c(" ", "HR", "Engineer")

## Build the plot and save it to disk so we can include it via
## \includegraphics inside a LaTeX minipage layout.
plot_data <- data.frame(
  role = factor(c("HR", "HR", "Engineer", "Engineer"),
                levels = c("HR", "Engineer")),
  arm  = factor(c("Nonblind", "Blind", "Nonblind", "Blind"),
                levels = c("Nonblind", "Blind")),
  est  = c(s_hr$b_nb,  s_hr$b_b,  s_eng$b_nb, s_eng$b_b),
  se   = c(s_hr$s_nb,  s_hr$s_b,  s_eng$s_nb, s_eng$s_b)
)
plot_data$ci_lo <- plot_data$est - 1.96 * plot_data$se
plot_data$ci_hi <- plot_data$est + 1.96 * plot_data$se

p_signal <- ggplot(plot_data, aes(x = est, y = arm, color = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.2, linewidth = 0.8) +
  geom_point(size = 3) +
  facet_wrap(~ role, ncol = 1, strip.position = "left") +
  scale_x_continuous(limits = c(-0.05, 1.1), breaks = seq(0, 1, 0.2)) +
  scale_color_manual(values = c("Nonblind" = "#d62728", "Blind" = "#1f77b4")) +
  labs(x = expression(hat(beta)*": slope of evaluator rating on true coding ability"),
       y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0, face = "bold"))

## Save plot to disk so we can include it via \includegraphics inside a
## LaTeX minipage (table on left, plot on right).
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file <- file.path(fig_dir, "8B_signal_extraction.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file, plot = p_signal, width = 4.5, height = 2.6, device = "pdf")
))

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[c]{0.50\\textwidth}\n")
cat("\\centering\n")
cat("{\\fontsize{7}{9}\\selectfont\n")

## Plain kable + row_spec (no kable_styling, since kable_styling adds an
## inner \\begin{table} wrapper that LaTeX rejects inside a minipage).
print(
  kable(tbl, format = "latex", booktabs = TRUE, escape = FALSE,
        align = "lcc", row.names = FALSE) %>%
    row_spec(2, extra_latex_after = "\\midrule") %>%
    row_spec(5, extra_latex_after = "\\midrule")
)

cat("}\n")
cat("\\end{minipage}%\n")
cat("\\begin{minipage}[c]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file, "}\n", sep = "")
cat("\\end{minipage}\n")

cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{0.98\\textwidth}\\scriptsize\n")
cat("Cluster-robust standard errors (by respondent) shown in parentheses next to each $\\hat\\beta$. Stars on p-values: * $p<0.10$, ** $p<0.05$, *** $p<0.01$. \\textit{Note:} Both arm-specific slopes come from a single pooled interacted regression per role, \\texttt{sc\\_coding\\_z \\textasciitilde\\ true\\_coding\\_z * i(treat, ref = 'nonblind') | responseid + r\\_do}; $\\hat\\beta_{\\text{nonblind}}$ is read off the main coefficient, and $\\hat\\beta_{\\text{blind}}$ is computed as (main + interaction) with SE derived via the standard linear-combination formula using the estimated variance--covariance matrix. The ``Resume (Content) FE'' row is marked as not included because \\texttt{overall\\_score} is a resume-level property (one lab score per resume), so a resume-content FE would absorb the RHS and leave the main slope unidentified. ``Respondent Characteristics'' is marked as not included because respondent-level variables (age, gender, race, education, income) are all perfectly collinear with the respondent FE and therefore absorbed by it.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

rm(m_hr, m_eng, s_hr, s_eng,
   extract_stats, sig_stars, fmt_p, cell_col,
   chk, nox, tbl, plot_data, p_signal, plot_file, fig_dir)
```


\newpage
## Heterogeneity in Signal Extraction by Candidate Quality

\textcolor{blue}{\textbf{Hypothesis}}: Evaluators may pay more attention to ``appealing'' candidates, so the slope of evaluator rating on true coding ability ($\hat\beta$) might be steeper for top-tier applicants. We split the resume sample by (a) lab coding ability (top half vs bottom half on \texttt{test\_case}) and (b) GPA tier (\texttt{gpa\_tier3}: Low / Mid / Top), then re-run the §1.2 specification within each subsample.

```{r blind_hiring_signal_extraction_heterogeneity, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

## Helper: fit the §1.2 spec on a subsample and extract arm-specific slopes
## with the linear-combination SE for the blind arm.
fit_subsample <- function(d) {
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind") | responseid + r_do,
        data = d, vcov = ~ responseid)
}
extract_slopes <- function(m) {
  ct <- coeftable(m); V <- vcov(m)
  b_main <- ct["true_coding_z", "Estimate"]
  s_main <- ct["true_coding_z", "Std. Error"]
  b_int  <- ct["true_coding_z:treat::blind", "Estimate"]
  s_int  <- ct["true_coding_z:treat::blind", "Std. Error"]
  cov_mi <- V["true_coding_z", "true_coding_z:treat::blind"]
  list(b_nb = unname(b_main), s_nb = unname(s_main),
       b_b  = unname(b_main + b_int),
       s_b  = unname(sqrt(s_main^2 + s_int^2 + 2 * cov_mi)))
}

## --- Coding tier (top half vs bottom half) ---
build_row <- function(role_lbl, tier_lbl, s) {
  data.frame(role = role_lbl, tier = tier_lbl, arm = c("Nonblind", "Blind"),
             est = c(s$b_nb, s$b_b), se = c(s$s_nb, s$s_b))
}
het_coding <- rbind(
  build_row("HR",       "Top half",    extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "HR"  & top_half_coder == 1]))))),
  build_row("HR",       "Bottom half", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "HR"  & top_half_coder == 0]))))),
  build_row("Engineer", "Top half",    extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "Eng" & top_half_coder == 1]))))),
  build_row("Engineer", "Bottom half", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "Eng" & top_half_coder == 0])))))
)
het_coding$ci_lo <- het_coding$est - 1.96 * het_coding$se
het_coding$ci_hi <- het_coding$est + 1.96 * het_coding$se
het_coding$role <- factor(het_coding$role, levels = c("HR", "Engineer"))
het_coding$tier <- factor(het_coding$tier, levels = c("Top half", "Bottom half"))
het_coding$arm  <- factor(het_coding$arm,  levels = c("Nonblind", "Blind"))

p_coding <- ggplot(het_coding, aes(x = est, y = arm, color = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.25, linewidth = 0.7) +
  geom_point(size = 2.5) +
  facet_grid(role ~ tier, switch = "y") +
  scale_x_continuous(limits = c(-0.1, 1.2), breaks = seq(0, 1, 0.5)) +
  scale_color_manual(values = c("Nonblind" = "#d62728", "Blind" = "#1f77b4")) +
  labs(x = expression(hat(beta)*": slope on true coding ability"),
       y = NULL, color = NULL,
       title = "By coding tier (top vs bottom half)") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0, face = "bold"),
        plot.title = element_text(size = 10, hjust = 0.5))

## --- GPA tier (Low / Mid / Top) ---
het_gpa <- rbind(
  build_row("HR",       "Low GPA", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "HR"  & gpa_tier3 == "Low_GPA"]))))),
  build_row("HR",       "Mid GPA", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "HR"  & gpa_tier3 == "Mid_GPA"]))))),
  build_row("HR",       "Top GPA", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "HR"  & gpa_tier3 == "Top_GPA"]))))),
  build_row("Engineer", "Low GPA", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "Eng" & gpa_tier3 == "Low_GPA"]))))),
  build_row("Engineer", "Mid GPA", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "Eng" & gpa_tier3 == "Mid_GPA"]))))),
  build_row("Engineer", "Top GPA", extract_slopes(suppressMessages(suppressWarnings(
    fit_subsample(firm_long_dt[role == "Eng" & gpa_tier3 == "Top_GPA"])))))
)
het_gpa$ci_lo <- het_gpa$est - 1.96 * het_gpa$se
het_gpa$ci_hi <- het_gpa$est + 1.96 * het_gpa$se
het_gpa$role <- factor(het_gpa$role, levels = c("HR", "Engineer"))
het_gpa$tier <- factor(het_gpa$tier, levels = c("Low GPA", "Mid GPA", "Top GPA"))
het_gpa$arm  <- factor(het_gpa$arm,  levels = c("Nonblind", "Blind"))

p_gpa <- ggplot(het_gpa, aes(x = est, y = arm, color = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.25, linewidth = 0.7) +
  geom_point(size = 2.5) +
  facet_grid(role ~ tier, switch = "y") +
  scale_x_continuous(limits = c(-0.1, 1.2), breaks = seq(0, 1, 0.5)) +
  scale_color_manual(values = c("Nonblind" = "#d62728", "Blind" = "#1f77b4")) +
  labs(x = expression(hat(beta)*": slope on true coding ability"),
       y = NULL, color = NULL,
       title = "By GPA tier") +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0, face = "bold"),
        plot.title = element_text(size = 10, hjust = 0.5))

## Save plots
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_coding <- file.path(fig_dir, "8B_signal_extraction_het_coding.pdf")
plot_file_gpa    <- file.path(fig_dir, "8B_signal_extraction_het_gpa.pdf")
suppressMessages(suppressWarnings({
  ggsave(plot_file_coding, plot = p_coding, width = 4.2, height = 3.0, device = "pdf")
  ggsave(plot_file_gpa,    plot = p_gpa,    width = 5.5, height = 3.0, device = "pdf")
}))

cat("\\begin{figure}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[c]{0.42\\textwidth}\n")
cat("\\centering\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file_coding, "}\n", sep = "")
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[c]{0.55\\textwidth}\n")
cat("\\centering\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file_gpa, "}\n", sep = "")
cat("\\end{minipage}\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{0.98\\textwidth}\\scriptsize\n")
cat("Each panel shows the slope $\\hat\\beta$ of the evaluator's rating on true coding ability, fit on the labeled subsample with the same specification as §1.2 (\\texttt{sc\\_coding\\_z \\textasciitilde\\ true\\_coding\\_z * i(treat, ref = 'nonblind') | responseid + r\\_do}). Vertical dashed lines mark $\\hat\\beta = 0$ (no signal) and $\\hat\\beta = 1$ (perfect calibration). Horizontal bars are 95\\% CIs based on cluster-robust standard errors (by respondent).\n")
cat("\\end{minipage}\n")
cat("\\end{figure}\n\n")

rm(fit_subsample, extract_slopes, build_row,
   het_coding, het_gpa, p_coding, p_gpa,
   plot_file_coding, plot_file_gpa, fig_dir)
```


\clearpage
# Treatment Effect: Heterogeneity by DEI / Diversity Preferences



## By Individual DEI / Diversity Preferences

\begin{itemize}\setlength{\itemsep}{1pt}\setlength{\parskip}{0pt}\setlength{\topsep}{2pt}
  \item \textbf{Index A} --- equal-weight average of the four-item stated DEI views.
  \item \textbf{Index B} --- equal-weight composite of Index A and the respondent's revealed-priority ranking of ``Diversity and Representation'' from the seven-goals question.
  \item \textbf{Index C} --- first principal component of the same five items.
\end{itemize}

```{r bh_dei_overall, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

proxies <- c(
  "pro_dei_race_z",
  "pro_dei_gender_z",
  "pro_diverse_z",
  "div_priority_z",
  "firm_attention_race_z",
  "firm_attention_gender_z"
)
col_labels <- c("Race DEI", "Gender DEI", "Diverse Wkpl", "Div Goal",
                "Firm Race Attn", "Firm Gender Attn")

## LHS is negated so that all coefficients flip at the regression level;
## etable (unlike modelsummary) ignores post-hoc overrides of $coefficients,
## so we flip via I(-sc_overall_z) instead of via a flip_coef_signs wrapper.
fit_one <- function(d, pr) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      pr)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(proxies, function(p) fit_one(dt_hr,  p))
models_eng <- lapply(proxies, function(p) fit_one(dt_eng, p))
all_models <- c(models_hr, models_eng)

groups <- c("White_Male"      = "White Male",
            "White_Female"    = "White Female",
            "Asian_Male"      = "Asian Male",
            "Asian_Female"    = "Asian Female",
            "Hispanic_Male"   = "Hispanic Male",
            "Hispanic_Female" = "Hispanic Female")

dict_main  <- setNames(unname(groups), paste0("race_gender::", names(groups)))
dict_inter <- unlist(lapply(proxies, function(p) {
  setNames(paste0(unname(groups), " $\\times$ Pro DEI/Diversity (Z)"),
           paste0("race_gender::", names(groups), ":", p))
}))
dict_all <- c(dict_main, dict_inter)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%race_gender",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume (Content) FE"      = rep(chk, 12),
    "Display Position FE"      = rep(chk, 12),
    "Respondent Demographic FE" = rep(chk, 12)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")

tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{13}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-7} \\\\cmidrule(lr){8-13}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)

tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, proxies, col_labels, fit_one,
   models_hr, models_eng, all_models, groups, dict_main, dict_inter, dict_all,
   chk, tbl, proxy_hdr)
```

```{r bh_dei_indices_combined, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")

## ---------- LEFT: per-race-gender ----------
fit_rg <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx)),
    data = d, vcov = ~ responseid
  )))
}
models_rg <- c(lapply(indices, function(p) fit_rg(dt_hr,  p)),
               lapply(indices, function(p) fit_rg(dt_eng, p)))

groups <- c("White_Male"     = "White Male",
            "White_Female"   = "White Female",
            "Asian_Male"     = "Asian Male",
            "Asian_Female"   = "Asian Female",
            "Hispanic_Male"  = "Hispanic Male",
            "Hispanic_Female"= "Hispanic Female")
dict_rg <- c(
  setNames(unname(groups), paste0("race_gender::", names(groups))),
  unlist(lapply(indices, function(p) {
    setNames(paste0(unname(groups), " $\\times$ DEI Index"),
             paste0("race_gender::", names(groups), ":", p))
  })),
  setNames(rep("DEI Index", length(indices)), indices)
)

## ---------- RIGHT: URM cut ----------
fit_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + %s + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx)),
    data = d, vcov = ~ responseid
  )))
}
models_urm <- c(lapply(indices, function(p) fit_urm(dt_hr,  p)),
                lapply(indices, function(p) fit_urm(dt_eng, p)))

dict_urm <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("DEI Index", length(indices)), indices),
  setNames(rep("URM $\\times$ DEI Index",    length(indices)),
           paste0("urm_tech_blind::Nonblind_URM:",    indices)),
  setNames(rep("Non-URM $\\times$ DEI Index", length(indices)),
           paste0("urm_tech_blind::Nonblind_NonURM:", indices))
)

chk <- "\\checkmark"
nox <- "$\\times$"

shared_notes <- c(
  "Standard errors clustered by respondent.",
  "Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group."
)
extralines_4 <- list(
  "Resume (Content) FE"        = rep(chk, 6),
  "Display Position FE"        = rep(chk, 6),
  "Respondent FE"              = rep(nox, 6),
  "Respondent Characteristics" = rep(chk, 6)
)

build_tbl <- function(models, dict, keep_pat, header_text, notes_arg = shared_notes) {
  tbl <- etable(
    models, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = keep_pat,
    fitstat = c("n", "r2", "ar2"),
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict,
    notes = notes_arg,
    extralines = extralines_4
  )
  idx_hdr <- paste(idx_labels, collapse = " & ")
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{7}{c}{\\\\textbf{", header_text, "}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\multicolumn{3}{c}{\\\\textbf{Panel A: HR}}",
      " & \\\\multicolumn{3}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
      " \\\\cmidrule(lr){2-4} \\\\cmidrule(lr){5-7}",
      " & ", idx_hdr, " & ", idx_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.85}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  ## Inject midrules separating coefs / FE rows / fitstat. Then dedupe in case
  ## etable already inserted one between the FE block and the fitstat block.
  tbl <- sub("Resume \\(Content\\) FE",
             "\\\\midrule\nResume (Content) FE", tbl, perl = TRUE)
  tbl <- sub("Observations",
             "\\\\midrule\nObservations", tbl, perl = TRUE)
  tbl <- gsub("(?:\\\\midrule\\s*){2,}", "\\\\midrule\n", tbl, perl = TRUE)
  ## Strip outer table env so the tabular can be placed inside a minipage.
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

tbl_left  <- build_tbl(models_rg,  dict_rg,
                       c("%race_gender", "%dei_index"),
                       "Per Race-Gender")
tbl_right <- build_tbl(models_urm, dict_urm,
                       "%urm_tech_blind",
                       "Per URM Cut",
                       notes_arg = c("The DEI Index level effect is included in each regression.",
                                     shared_notes))

cat("\\begin{table}[H]\\centering\n")
cat("\\begin{minipage}[t]{0.49\\textwidth}\\centering\n")
cat(tbl_left)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.49\\textwidth}\\centering\n")
cat(tbl_right)
cat("\\end{minipage}\n")
cat("\\end{table}\n")

rm(dt_hr, dt_eng, indices, idx_labels, fit_rg, fit_urm,
   models_rg, models_urm, groups, dict_rg, dict_urm, chk, nox,
   shared_notes, extralines_4, build_tbl, tbl_left, tbl_right)
```


```{r bh_dei_urm, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

zstd <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

## Combined indices: row-mean of two z-scored measures, re-standardized within sample.
dt_hr [, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_eng[, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_hr [, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]
dt_eng[, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]

proxies    <- c("pro_dei_view_z", "pro_diverse_z", "div_priority_z", "firm_attention_z")
col_labels <- c("DEI Views (R \\\\& G)", "Diverse Wkpl", "Div Goal", "Firm DEI Attn (R \\\\& G)")

## Here we build a URM-tech x Blind indicator by hand.
## urm_tech_blind_factor: Blind / Nonblind-URM / Nonblind-NonURM
dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                           "Blind",
  treat == "nonblind" & urm_tech == 1,         "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0,         "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                           "Blind",
  treat == "nonblind" & urm_tech == 1,         "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0,         "Nonblind_NonURM",
  default = NA_character_
)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

## LHS negated so coefficients flip at the regression level (etable does not
## respect post-hoc overrides of $coefficients).
fit_urm <- function(d, pr) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      pr)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(proxies, function(p) fit_urm(dt_hr,  p))
models_eng <- lapply(proxies, function(p) fit_urm(dt_eng, p))
all_models <- c(models_hr, models_eng)

dict_all <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ Pro DEI/Diversity (Z)",    length(proxies)),
           paste0("urm_tech_blind::Nonblind_URM:",    proxies)),
  setNames(rep("Non-URM $\\times$ Pro DEI/Diversity (Z)", length(proxies)),
           paste0("urm_tech_blind::Nonblind_NonURM:", proxies))
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 8),
    "Display Position FE"       = rep(chk, 8),
    "Respondent Demographic FE" = rep(chk, 8)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{9}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-5} \\\\cmidrule(lr){6-9}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, zstd, proxies, col_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, proxy_hdr)
```


```{r bh_dei_indices_urm, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")

fit_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(indices, function(p) fit_urm(dt_hr,  p))
models_eng <- lapply(indices, function(p) fit_urm(dt_eng, p))
all_models <- c(models_hr, models_eng)

dict_all <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ DEI Index",    length(indices)),
           paste0("urm_tech_blind::Nonblind_URM:",    indices)),
  setNames(rep("Non-URM $\\times$ DEI Index", length(indices)),
           paste0("urm_tech_blind::Nonblind_NonURM:", indices))
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  notes = "URM-Tech = \\{White Female, Asian Female, Hispanic Male, Hispanic Female\\}. Sample: both blind and nonblind arms. Coefficients flipped via I(-sc\\_overall\\_z) so positive => effect of blinding. Standard errors clustered by respondent.",
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 6),
    "Display Position FE"       = rep(chk, 6),
    "Respondent Demographic FE" = rep(chk, 6)
  )
)

idx_hdr <- paste(idx_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{7}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- URM Cut, Three DEI / Diversity Index Options, signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-4} \\\\cmidrule(lr){5-7}",
    " & ", idx_hdr, " & ", idx_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
## Force equal-width centered data columns (see note in indices_overall chunk).
tbl <- sub("\\{lcccccc\\}",
           "{l*{6}{>{\\\\centering\\\\arraybackslash}p{0.7in}}}",
           tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, indices, idx_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, idx_hdr)
```


\newpage
## (Triple Interaction Models) By Whether the Firm Targets URM $\times$ Respondent's DEI Priority

```{r bh_dei_targets, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")

chk <- "\\checkmark"
nox <- "$\\times$"

extralines_4 <- list(
  "Resume (Content) FE"        = rep(chk, 2),
  "Display Position FE"        = rep(chk, 2),
  "Respondent FE"              = rep(nox, 2),
  "Respondent Characteristics" = rep(chk, 2)
)

## Per-race-gender triple (TOP panel of each Index minipage).
fit_triple_22_rg <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + firm_targets_fh + I(firm_targets_fh * %s) + i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, firm_targets_fh, ref = 'Blind') + i(race_gender, I(firm_targets_fh * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx, idx, idx)),
    data = d, vcov = ~ responseid
  )))
}

## URM-cut triple (BOTTOM panel of each Index minipage).
fit_triple_22_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + firm_targets_fh + I(firm_targets_fh * %s) + i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, firm_targets_fh, ref = 'Blind') + i(urm_tech_blind, I(firm_targets_fh * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, idx, idx, idx)),
    data = d, vcov = ~ responseid
  )))
}

groups_rg <- c("White_Male"     = "White Male",
               "White_Female"   = "White Female",
               "Asian_Male"     = "Asian Male",
               "Asian_Female"   = "Asian Female",
               "Hispanic_Male"  = "Hispanic Male",
               "Hispanic_Female"= "Hispanic Female")

build_22_top <- function(idx, lbl) {
  m_hr  <- fit_triple_22_rg(dt_hr,  idx)
  m_eng <- fit_triple_22_rg(dt_eng, idx)
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_top <- setNames(
    paste0(unname(groups_rg), " $\\times$ Firm Targets URM $\\times$ DEI Index"),
    paste0("race_gender::", names(groups_rg), ":I(firm_targets_fh * ", idx, ")")
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%race_gender::.*:I\\(",
    fitstat = NA,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_top,
    notes = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- Per Race-Gender (triple terms)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.85}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

build_22_bot <- function(idx, lbl) {
  m_hr  <- fit_triple_22_urm(dt_hr,  idx)
  m_eng <- fit_triple_22_urm(dt_eng, idx)
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_trp <- c(
    "urm_tech_blind::Nonblind_URM"                                = "URM",
    "urm_tech_blind::Nonblind_NonURM"                             = "Non-URM",
    setNames("URM $\\times$ DEI Index",            paste0("urm_tech_blind::Nonblind_URM:", idx)),
    setNames("Non-URM $\\times$ DEI Index",        paste0("urm_tech_blind::Nonblind_NonURM:", idx)),
    "urm_tech_blind::Nonblind_URM:firm_targets_fh"    = "URM $\\times$ Firm Targets URM",
    "urm_tech_blind::Nonblind_NonURM:firm_targets_fh" = "Non-URM $\\times$ Firm Targets URM",
    setNames("URM $\\times$ Firm Targets URM $\\times$ DEI Index",
             paste0("urm_tech_blind::Nonblind_URM:I(firm_targets_fh * ", idx, ")")),
    setNames("Non-URM $\\times$ Firm Targets URM $\\times$ DEI Index",
             paste0("urm_tech_blind::Nonblind_NonURM:I(firm_targets_fh * ", idx, ")"))
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_tech_blind",
    fitstat = c("n", "r2", "ar2"),
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_trp,
    notes = NULL,
    extralines = extralines_4
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- URM Cut (full triple)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.85}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("Resume \\(Content\\) FE",
             "\\\\midrule\nResume (Content) FE", tbl, perl = TRUE)
  tbl <- sub("Observations",
             "\\\\midrule\nObservations", tbl, perl = TRUE)
  tbl <- gsub("(?:\\\\midrule\\s*){2,}", "\\\\midrule\n", tbl, perl = TRUE)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

top_A <- build_22_top(indices[1], idx_labels[1]); bot_A <- build_22_bot(indices[1], idx_labels[1])
top_B <- build_22_top(indices[2], idx_labels[2]); bot_B <- build_22_bot(indices[2], idx_labels[2])
top_C <- build_22_top(indices[3], idx_labels[3]); bot_C <- build_22_bot(indices[3], idx_labels[3])

cat("\\begin{table}[H]\\centering\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_A); cat("\\par\\vspace{0.3em}\n"); cat(bot_A)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_B); cat("\\par\\vspace{0.3em}\n"); cat(bot_B)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_C); cat("\\par\\vspace{0.3em}\n"); cat(bot_C)
cat("\\end{minipage}\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{\\textwidth}\\raggedright\\scriptsize\n")
cat("Top panel: per-race-gender triple regression (only the 6 triple terms shown; level dummies, $\\times$ DEI, $\\times$ Firm Targets URM slopes are estimated but suppressed). Bottom panel: URM-cut triple regression (full set of 8 coefficients). FE structure (Resume Content $\\checkmark$, Display Position $\\checkmark$, Respondent $\\times$, Respondent Characteristics $\\checkmark$) is identical across top and bottom; shown only in the bottom block.\\\\\n")
cat("Standard errors clustered by respondent.\\\\\n")
cat("\\textit{Note:} Firm Targets URM $=$ \\texttt{firm\\_targets\\_female} OR \\texttt{firm\\_targets\\_hispanic} (binary firm characteristic).\\\\\n")
cat("Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n")

rm(dt_hr, dt_eng, indices, idx_labels, chk, nox, groups_rg,
   extralines_4, fit_triple_22_rg, fit_triple_22_urm,
   build_22_top, build_22_bot,
   top_A, top_B, top_C, bot_A, bot_B, bot_C)
```

\newpage
## (Triple Interaction Models) By Respondent's Priority for DEI $\times$ Firm Attention on DEI

```{r bh_dei_triple, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

chk <- "\\checkmark"

## LHS negated so all coefficients flip at the regression level; etable does
## not respect post-hoc $coefficients overrides.
fit_triple_urm <- function(d, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, div_priority_z, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(div_priority_z * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      proxy_b, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

m_hr_r  <- fit_triple_urm(dt_hr,  "firm_attention_race_z")
m_eng_r <- fit_triple_urm(dt_eng, "firm_attention_race_z")
m_hr_g  <- fit_triple_urm(dt_hr,  "firm_attention_gender_z")
m_eng_g <- fit_triple_urm(dt_eng, "firm_attention_gender_z")

n_used <- c(
  dt_hr [!is.na(firm_attention_race_z),    uniqueN(responseid)],
  dt_eng[!is.na(firm_attention_race_z),   uniqueN(responseid)],
  dt_hr [!is.na(firm_attention_gender_z),  uniqueN(responseid)],
  dt_eng[!is.na(firm_attention_gender_z), uniqueN(responseid)]
)
n_full <- c(
  dt_hr [, uniqueN(responseid)],
  dt_eng[, uniqueN(responseid)],
  dt_hr [, uniqueN(responseid)],
  dt_eng[, uniqueN(responseid)]
)
n_drop <- n_full - n_used

models_trp <- list("HR (Race)" = m_hr_r, "Eng (Race)" = m_eng_r,
                   "HR (Gender)" = m_hr_g, "Eng (Gender)" = m_eng_g)

dict_trp <- c(
  "urm_tech_blind::Nonblind_URM"                                       = "URM",
  "urm_tech_blind::Nonblind_URM:div_priority_z"                        = "URM $\\times$ Respondent Prioritizes Diversity",
  "urm_tech_blind::Nonblind_URM:firm_attention_race_z"                 = "URM $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:firm_attention_gender_z"               = "URM $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:I(div_priority_z * firm_attention_race_z)"   = "URM $\\times$ Resp Prioritizes $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:I(div_priority_z * firm_attention_gender_z)" = "URM $\\times$ Resp Prioritizes $\\times$ Firm DEI Attn"
)

tbl_trp <- etable(
  models_trp,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = "%urm_tech_blind::Nonblind_URM",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_trp,
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 4),
    "Display Position FE"       = rep(chk, 4),
    "Respondent Demographic FE" = rep(chk, 4),
    "Respondents (used)"        = as.character(n_used),
    "Dropped (NA proxy)"        = as.character(n_drop)
  )
)

tbl_trp <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{5}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Race-DEI Attn}}",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Gender-DEI Attn}} \\\\\\\\",
    " \\\\cmidrule(lr){2-3} \\\\cmidrule(lr){4-5}",
    " & HR & Eng & HR & Eng \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_trp
)
tbl_trp <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_trp)
tbl_trp <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
  tbl_trp
)
tbl_trp <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_trp)

cat(tbl_trp)

rm(dt_hr, dt_eng, chk, fit_triple_urm, m_hr_r, m_eng_r, m_hr_g, m_eng_g,
   models_trp, dict_trp, tbl_trp, n_used, n_full, n_drop)
```


```{r bh_dei_indices_triple, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")

chk <- "\\checkmark"
nox <- "$\\times$"

shared_notes <- c(
  "Standard errors clustered by respondent.",
  "\\textit{Note:} Firm DEI Attn proxy is \\texttt{firm\\_dei\\_attention\\_z} (within-cell z-score of the equal-weight average of \\texttt{firm\\_attention\\_race\\_z} and \\texttt{firm\\_attention\\_gender\\_z}).",
  "Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group."
)
extralines_4 <- list(
  "Resume (Content) FE"        = rep(chk, 2),
  "Display Position FE"        = rep(chk, 2),
  "Respondent FE"              = rep(nox, 2),
  "Respondent Characteristics" = rep(chk, 2)
)

## Per-race-gender triple (for the TOP panel of each Index minipage).
fit_triple_rg <- function(d, idx, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + %s + I(%s * %s) + i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, I(%s * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, proxy_b, idx, proxy_b, idx, proxy_b, idx, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

## URM-cut triple (for the BOTTOM panel of each Index minipage).
fit_triple_urm <- function(d, idx, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ %s + %s + I(%s * %s) + i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(%s * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, proxy_b, idx, proxy_b, idx, proxy_b, idx, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

groups_rg <- c("White_Male"     = "White Male",
               "White_Female"   = "White Female",
               "Asian_Male"     = "Asian Male",
               "Asian_Female"   = "Asian Female",
               "Hispanic_Male"  = "Hispanic Male",
               "Hispanic_Female"= "Hispanic Female")

build_top_tbl <- function(idx, lbl) {
  m_hr  <- fit_triple_rg(dt_hr,  idx, "firm_dei_attention_z")
  m_eng <- fit_triple_rg(dt_eng, idx, "firm_dei_attention_z")
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  ## Dict: only the 6 triple terms get readable labels (one per demographic).
  dict_top <- setNames(
    paste0(unname(groups_rg), " $\\times$ DEI Index $\\times$ Firm DEI Attn"),
    paste0("race_gender::", names(groups_rg), ":I(", idx, " * firm_dei_attention_z)")
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%race_gender::.*:I\\(",
    fitstat = NA,
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_top,
    notes = NULL
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- Per Race-Gender (triple terms)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.85}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

build_bot_tbl <- function(idx, lbl) {
  m_hr  <- fit_triple_urm(dt_hr,  idx, "firm_dei_attention_z")
  m_eng <- fit_triple_urm(dt_eng, idx, "firm_dei_attention_z")
  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_trp <- c(
    "urm_tech_blind::Nonblind_URM"                         = "URM",
    "urm_tech_blind::Nonblind_NonURM"                      = "Non-URM",
    setNames("URM $\\times$ DEI Index",     paste0("urm_tech_blind::Nonblind_URM:", idx)),
    setNames("Non-URM $\\times$ DEI Index", paste0("urm_tech_blind::Nonblind_NonURM:", idx)),
    "urm_tech_blind::Nonblind_URM:firm_dei_attention_z"    = "URM $\\times$ Firm DEI Attn",
    "urm_tech_blind::Nonblind_NonURM:firm_dei_attention_z" = "Non-URM $\\times$ Firm DEI Attn",
    setNames("URM $\\times$ DEI Index $\\times$ Firm DEI Attn",
             paste0("urm_tech_blind::Nonblind_URM:I(", idx, " * firm_dei_attention_z)")),
    setNames("Non-URM $\\times$ DEI Index $\\times$ Firm DEI Attn",
             paste0("urm_tech_blind::Nonblind_NonURM:I(", idx, " * firm_dei_attention_z)"))
  )

  tbl <- etable(
    models_trp, tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_tech_blind",
    fitstat = c("n", "r2", "ar2"),
    drop.section = "fixef",
    digits = "r3", digits.stats = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_trp,
    notes = NULL,
    extralines = extralines_4
  )
  tbl <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- URM Cut (full triple)}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\textbf{HR} & \\\\textbf{Eng} \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl
  )
  tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\raggedright \\\\scriptsize", tbl)
  tbl <- sub(
    "\\\\begin\\{tabular\\}",
    "\\\\resizebox{\\\\textwidth}{!}{\\\\renewcommand{\\\\arraystretch}{0.85}\\\\begin{tabular}",
    tbl
  )
  tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)
  tbl <- sub("Resume \\(Content\\) FE",
             "\\\\midrule\nResume (Content) FE", tbl, perl = TRUE)
  tbl <- sub("Observations",
             "\\\\midrule\nObservations", tbl, perl = TRUE)
  tbl <- gsub("(?:\\\\midrule\\s*){2,}", "\\\\midrule\n", tbl, perl = TRUE)
  tbl <- sub("\\\\begin\\{table\\}\\[H\\]\\s*\\n\\\\centering\\s*\\n", "", tbl)
  tbl <- sub("\\\\end\\{table\\}\\s*$", "", tbl)
  tbl
}

top_A <- build_top_tbl(indices[1], idx_labels[1]); bot_A <- build_bot_tbl(indices[1], idx_labels[1])
top_B <- build_top_tbl(indices[2], idx_labels[2]); bot_B <- build_bot_tbl(indices[2], idx_labels[2])
top_C <- build_top_tbl(indices[3], idx_labels[3]); bot_C <- build_bot_tbl(indices[3], idx_labels[3])

cat("\\begin{table}[H]\\centering\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_A); cat("\\par\\vspace{0.3em}\n"); cat(bot_A)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_B); cat("\\par\\vspace{0.3em}\n"); cat(bot_B)
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.32\\textwidth}\\centering\n")
cat(top_C); cat("\\par\\vspace{0.3em}\n"); cat(bot_C)
cat("\\end{minipage}\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{\\textwidth}\\raggedright\\scriptsize\n")
cat("Top panel: per-race-gender triple regression (only the 6 triple terms shown; level dummies, $\\times$ DEI, $\\times$ Firm DEI Attn slopes are estimated but suppressed). Bottom panel: URM-cut triple regression (full set of 8 coefficients). FE structure (Resume Content $\\checkmark$, Display Position $\\checkmark$, Respondent $\\times$, Respondent Characteristics $\\checkmark$) is identical across top and bottom; shown only in the bottom block.\\\\\n")
cat("Standard errors clustered by respondent.\\\\\n")
cat("\\textit{Note:} Firm DEI Attn proxy is \\texttt{firm\\_dei\\_attention\\_z} (within-cell z-score of the equal-weight average of \\texttt{firm\\_attention\\_race\\_z} and \\texttt{firm\\_attention\\_gender\\_z}).\\\\\n")
cat("Positive coefficient $\\Rightarrow$ effect of blinding raises the score for that group.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n")

rm(dt_hr, dt_eng, indices, idx_labels, chk, nox, groups_rg,
   shared_notes, extralines_4, fit_triple_rg, fit_triple_urm,
   build_top_tbl, build_bot_tbl,
   top_A, top_B, top_C, bot_A, bot_B, bot_C)
```


\clearpage
# Treatment Effect: Heterogeneity by Demographics

\textcolor{blue}{\textbf{Takeaway}}: We reject the traditional own-group preference (equivalently, out-group discrimination) story.
\vspace{-0.9em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{Findings.} HR: null. Engineers: blinding raises concordant applicants by 6.9\% of a SD, lowers nonconcordant by 0.9\% of a SD.
  \item \textbf{Interpretation.} Signs run \emph{opposite} to own-group preference. Engineers rate concordant applicants \emph{higher} (nonconcordant \emph{lower}) when blinded.
\end{itemize}
\vspace{-0.9em}

## By Concordant Race (matched on detailed Asian Ethnicity)

```{r bh_heterogeneity_concordance_race, echo = FALSE, results = 'asis'}
## Tri-level variable: Blind / Nonblind-Concordant / Nonblind-Nonconcordant
## Use detailed-race concordance: Asian respondents are matched at the
## sub-ethnicity level (Chinese / Indian). Korean / Japanese / other-Asian
## respondents in nonblind are coded as always-discordant in 5_Cleaning.R,
## so they remain in the regression rather than being dropped.
firm_long_dt[, blind_concordance_race := fcase(
  treat == "blind",                                     "Blind",
  treat == "nonblind" & concordance_race_detailed == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_detailed == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race := factor(blind_concordance_race,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

## HR and Engineer regressions — same FE skeleton as Section 1.1
models_hr_bh_conc_race <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_race, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_race) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_race <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_race, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_race) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_race  <- lapply(models_hr_bh_conc_race,  flip_coef_signs)
models_eng_bh_conc_race <- lapply(models_eng_bh_conc_race, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_race, models_eng_bh_conc_race)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")  # trailing space disambiguator

coef_map_conc <- c(
  "blind_concordance_race::Nonblind_Concordant"    = "Concordant Applicant",
  "blind_concordance_race::Nonblind_Nonconcordant" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
## Place FE rows immediately after the 4 coef rows (2 coefs * (est+se)).
attr(fe_rows, "position") <- 5:8

n_hr_wah  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_race), responseid])
n_eng_wah <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_race), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_wah, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_wah, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined at the detailed race level: Asian respondents are matched at the sub-ethnicity level (Chinese / Indian). Respondents whose race is not represented in the applicant pool (e.g., Black, Other; Korean / Japanese / other-Asian whose sub-ethnicity is not Chinese or Indian) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_race, models_eng_bh_conc_race, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_wah, n_eng_wah, panel_a_lbl, panel_b_lbl)
```


## By Concordant Gender

```{r bh_heterogeneity_concordance_gender, echo = FALSE, results = 'asis'}
firm_long_dt[, blind_concordance_gender := fcase(
  treat == "blind",                              "Blind",
  treat == "nonblind" & concordance_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_gender := factor(blind_concordance_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

models_hr_bh_conc_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_gender) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_gender) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_gender  <- lapply(models_hr_bh_conc_gender,  flip_coef_signs)
models_eng_bh_conc_gender <- lapply(models_eng_bh_conc_gender, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_gender, models_eng_bh_conc_gender)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "blind_concordance_gender::Nonblind_Concordant"    = "Concordant Applicant",
  "blind_concordance_gender::Nonblind_Nonconcordant" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

n_hr_mf  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_gender), responseid])
n_eng_mf <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_gender), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_mf, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_mf, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Respondents whose gender is not represented in the applicant pool (e.g., Non-binary, Other) are treated as always-discordant in nonblind, since the applicant names are exclusively Male or Female.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_gender, models_eng_bh_conc_gender, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_mf, n_eng_mf, panel_a_lbl, panel_b_lbl)
```


\clearpage
## By Concordant Race and Gender

```{r bh_heterogeneity_concordance_broad, echo = FALSE, results = 'asis'}
## Weaker-concordance robustness check: race-gender match at the broad level.
## Asian respondents (regardless of detailed sub-group: Chinese, Indian,
## Korean, Japanese, etc.) match Asian applicants. Uses the pre-built
## `concordance_race_gender` (= 1 if race_gender == resp_race_gender at the
## {White, Asian, Hispanic} x {Male, Female} level).
firm_long_dt[, blind_concordance_race_gender := fcase(
  treat == "blind",                                   "Blind",
  treat == "nonblind" & concordance_race_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race_gender := factor(blind_concordance_race_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

models_hr_bh_conc_rg <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_rg) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_rg <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_rg) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_rg  <- lapply(models_hr_bh_conc_rg,  flip_coef_signs)
models_eng_bh_conc_rg <- lapply(models_eng_bh_conc_rg, flip_coef_signs)

all_models <- c(models_hr_bh_conc_rg, models_eng_bh_conc_rg)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "blind_concordance_race_gender::Nonblind_Concordant"    = "Concordant Applicant",
  "blind_concordance_race_gender::Nonblind_Nonconcordant" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

n_hr_wah  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_race_gender), responseid])
n_eng_wah <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_race_gender), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_wah, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_wah, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined as race-gender match at the broad level (Asian respondents are matched at the broad Asian level rather than by detailed sub-ethnicity). Respondents whose race or gender is not represented in the applicant pool (e.g., Black, Other; Non-binary, Other-gender) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_rg, models_eng_bh_conc_rg, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_wah, n_eng_wah, panel_a_lbl, panel_b_lbl)
```


## By Concordant Race and Gender (matched on detailed Asian Ethnicity)

```{r bh_heterogeneity_concordance_detailed, echo = FALSE, results = 'asis'}
## Uses the pre-built `concordance_race_gender_detailed_blind` factor from
## 5_Cleaning.R. Asian respondents whose detailed sub-ethnicity (e.g.,
## Korean, Japanese) is not represented in the applicant pool are coded as
## always-discordant in nonblind, so they are kept in the regression rather
## than dropped.

models_hr_bh_conc_det <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(concordance_race_gender_detailed_blind, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_det) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_det <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(concordance_race_gender_detailed_blind, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_det) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_det  <- lapply(models_hr_bh_conc_det,  flip_coef_signs)
models_eng_bh_conc_det <- lapply(models_eng_bh_conc_det, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_det, models_eng_bh_conc_det)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "concordance_race_gender_detailed_blind::Concordant_Group" = "Concordant Applicant",
  "concordance_race_gender_detailed_blind::Discordant_Group" = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

n_hr_det  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(concordance_race_gender_detailed_blind), responseid])
n_eng_det <- uniqueN(firm_long_dt[role == "Eng" & !is.na(concordance_race_gender_detailed_blind), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_det, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_det, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined at the detailed race-gender level: applicants are Chinese, Indian, White, or Hispanic (by gender). Respondents whose detailed race-gender is not represented in the applicant pool (e.g., Korean / Japanese / other-Asian sub-ethnicities; Black, Other-race; Non-binary, Other-gender) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_det, models_eng_bh_conc_det, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_det, n_eng_det, panel_a_lbl, panel_b_lbl)
```


\newpage
# Treatment Effect on Productivity of Hired

```{r blind_hiring_coding_quality, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

# ==============================================================================
# HELPER: Dynamic standardization relative to nonblind group at each k
# ==============================================================================
get_avg_coding_score <- function(role_filter, treat_filter, k, 
                                  pass_var_prefix, data) {
  col <- paste0(pass_var_prefix, k)
  d   <- data[role == role_filter & treat == treat_filter & get(col) == 1]
  if (nrow(d) == 0) return(NA_real_)
  mean(d$overall_score, na.rm = TRUE)
}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# ==============================================================================
results_list <- list()

for (k in 1:18) {

  # --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]

  # Dynamic standardization: relative to nonblind mean/sd at this k
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do + q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_hr)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }

  # --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]

  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do + q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_eng)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

# ==============================================================================
# PLOT
# ==============================================================================
ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    title    = "Does Blind Hiring Select Better Coders?",
    subtitle = paste("Effect of blinding on actual coding quality of selected candidates.",
                     "Standardized relative to nonblind group at each k."),
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Positive = blind hiring selects candidates with higher actual coding scores.\nSignificance: * p<0.10, ** p<0.05, *** p<0.01"
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )

rm(results_list, dt_plot, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```

```{r blind_hiring_demographic_selection, eval = FALSE, echo=FALSE, fig.width=12, fig.height=10}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# LHS: hr_passk / eng_topk (0/1 selected)
# RHS: race_gender with "Blind" as reference, then flip signs
# ==============================================================================
results_all <- list()

demo_labels <- c("White_Male", "White_Female", "Asian_Male",
                 "Asian_Female", "Hispanic_Male", "Hispanic_Female")

for (k in 1:18) {

  hr_col  <- paste0("hr_pass", k)
  eng_col <- paste0("eng_top", k)

  # --- HR ---
  tryCatch({
    m_hr <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(hr_col,
        " ~ i(race_gender, ref = 'Blind') |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income")),
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_hr)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})

  # --- Engineer ---
  tryCatch({
    m_eng <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(eng_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income +
          resp_python + resp_java")),
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_eng)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})
}

# ==============================================================================
# ASSEMBLE AND PLOT
# ==============================================================================
dt_plot <- rbindlist(results_all)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, demo  := factor(demo,  levels = c("White Male",    "White Female",
                                             "Asian Male",    "Asian Female",
                                             "Hispanic Male", "Hispanic Female"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]
dt_plot[, star_y := ifelse(estimate >= 0,
                            ci_high + 0.005,
                            ci_low  - 0.005)]

ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.6, size = 0.4, fatten = 3) +
  geom_text(aes(y = star_y, label = sig_stars),
            vjust = ifelse(dt_plot$estimate >= 0, 0, 1),
            size = 3, color = "black", show.legend = FALSE) +
  facet_grid(demo ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = seq(1, 18, by = 3),
                     name   = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.20))) +
  labs(
    title    = "Effect of Blind Hiring on Selection Probability by Demographic Group",
    subtitle = paste("Blinding effect = -(effect of revealing identity vs blind).",
                     "Positive = more likely selected under blinding."),
    y        = "Blinding Effect on Selection Probability",
    color    = "Evaluator Role",
    caption  = "Significance: * p<0.10, ** p<0.05, *** p<0.01. Base group: Blind resumes."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10),
    legend.text        = element_text(size = 9),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    strip.text.y       = element_text(angle = 0),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0),
    panel.spacing      = unit(0.4, "lines")
  )

rm(results_all, dt_plot, demo_labels, dg, k,
   hr_col, eng_col, m_hr, m_eng, ct,
   est, se, p_val, coef_nm)
```

