---
title: "Stage-by-Stage Impact of Blind Hiring"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{bbm}
  - \usepackage{array}
  - \usepackage{arydshln}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- +++++ ++++++ ++++++ Part 5-2: Analysis (Stage-by-Stage Impact of Blind Hiring) +++++ ++++++ ++++++ -->

\setcounter{section}{-1}

# Summary

\textbf{Core Thesis:}

The traditional justification for blind hiring is built on the assumption of \emph{in-group favoritism} --- the premise that majority gatekeepers harbor implicit biases against underrepresented minorities (URMs) and systematically favor candidates who look like themselves. Blind hiring is theoretically deployed to level the playing field by removing demographic ``noise'' and revealing pure technical ``signal.''

Our experiment demonstrates the \emph{exact opposite} is occurring in modern software engineering hiring.

Because majority gatekeepers organically apply an informal ``out-group premium'' to minority candidates, blinding demographic information fundamentally reshuffles hiring outcomes --- mechanically harming URMs and boosting White Males. Furthermore, this informal bias is highly elastic to formal corporate policy. When firms lack explicit diversity mandates, individual evaluators engage in \emph{compensatory bias}, informally boosting minority scores. Enforcing blind hiring in these environments destroys this potential safety net. Finally, despite claims that demographics are distracting ``noise,'' blinding resumes yielded \emph{no improvement} in the actual technical quality of the selected candidates.

\newpage

# Treatment Effect on Evaluations (Reshuffling)

\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{Finding:} Blinding demographic information during candidate evaluation \emph{reshuffles} hiring outcomes by disrupting a pre-existing system of \emph{demographic premiums and penalties}. Blind hiring removes a \emph{baseline penalty} that White Males were experiencing in the non-blind evaluations, while simultaneously stripping Hispanic candidates of an \emph{(diversity) premium}.
  \begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item \textbf{Winners: White Males.} Evaluated by Engineers, White Male overall scores mechanically rise by \textcolor{blue}{+8.5\%} of a SD under blinding.
    \item \textbf{Losers: Hispanic candidates.} When stripped of their demographic identity, Hispanic Male scores plunge by \textcolor{blue}{-11.5\%} of a SD (evaluated by HR), and Hispanic Female scores fall by \textcolor{blue}{-6.9\%} of a SD (evaluated by Engineers).
  \end{itemize}
  \item \textbf{Caveat:} Hiring is often an \emph{ordinal ranking} problem --- one candidate's gain corresponds to another's lost opportunity --- so the absence of statistical significance on a given row does not mean the corresponding group is unaffected by blinding.
\end{itemize}
\vspace{-0.9em}

```{r blind_hiring_treatment_effects_demo, echo = FALSE, results = 'asis'}
## Treatment Effects of Blind Hiring (Overall (Z) only).
## Reference category: Blind resumes. Coefficients flipped post-fit so a
## positive coefficient = effect of blinding (relative to nonblind).

m_hr_blind <- suppressMessages(suppressWarnings(
  feols(sc_overall_z ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))

m_eng_blind <- suppressMessages(suppressWarnings(
  feols(sc_overall_z ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))

flip_coef_signs <- function(model) {
  model$coefficients <- -1 * model$coefficients
  return(model)
}
## Use minimal column names; add_header_above sits above them with the
## panel labels and "Treatment Effects of Blinding for" header.
all_models <- list("HR" = flip_coef_signs(m_hr_blind),
                   "Engineer" = flip_coef_signs(m_eng_blind))

coef_map_blind <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female"
)

gof_custom_blind <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

## FE / controls footer rows. Respondent FE and Respondent Characteristics
## are placed adjacent to make the contrast visible: we do NOT soak up
## respondent heterogeneity with a fixed effect, but we DO include respondent
## demographic controls as absorbing FEs + age polynomial.
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk),
  V2 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", "HR", "Engineer")
## 6 coefs * (est+se) = 12 rows; FE rows sit immediately after.
attr(fe_rows, "position") <- 13:16

modelsummary(
  all_models,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map  = gof_custom_blind,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  add_header_above(c("Treatment Effects of Blinding for" = 1,
                     "Panel A: HR" = 1,
                     "Panel B: Engineer" = 1)) %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(16, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(m_hr_blind, m_eng_blind, all_models, coef_map_blind, gof_custom_blind,
   flip_coef_signs, chk, nox, fe_rows)
```




\clearpage
## Heterogeneity: Rejecting Traditional In-Group Favoritism
\enlargethispage{2.5in}

\begingroup\small
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}\setlength\itemindent{0pt}
  \item \textbf{Finding:} Our experiment shows that the modern tech industry actually operates on a preference for the \emph{out-group} (or preference for \emph{under-represented groups}). Because White Males make up the majority of the evaluator pool, their behavior drives the aggregate metrics. When you blind resumes, the scores of concordant (race/gender) applicants evaluated by Engineers actually rise by \textcolor{blue}{+6.9\%} of a SD ($p < 0.05$) while the scores of discordant applicants fall by \textcolor{blue}{-0.9\%} of a SD ($p < 0.05$).
  \item \textbf{Takeaway:} This shows that, under non-blinded evaluations, the majority gatekeepers were \emph{actively penalizing} candidates who looked like themselves and assigning a \emph{premium to evaluation scores of minority candidates}. Enforcing blind hiring doesn't stop discrimination against minorities; it stops the White Male majority from systematically boosting them. This explains why, in our experiment, White Male applicants are the primary beneficiaries of blind hiring: they are ``rescued'' from the baseline penalty imposed by their own demographic engineer peers.
\end{itemize}
\endgroup
\vspace{-1.4em}

```{r bh_heterogeneity_concordance_combined, echo = FALSE, results = 'asis'}
## Combined panel: three concordance specifications x two roles, all on
## sc_overall_z. Race uses detailed Asian sub-ethnicity matching; Gender is
## broad Male/Female; Race AND Gender combines the two with detailed Asian
## sub-ethnicity. Respondents whose demographic is not represented in the
## applicant pool are coded as always-discordant in nonblind, so they stay
## in the regressions rather than being dropped.

firm_long_dt[, blind_concordance_race := fcase(
  treat == "blind",                                     "Blind",
  treat == "nonblind" & concordance_race_detailed == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_detailed == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race := factor(blind_concordance_race,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

firm_long_dt[, blind_concordance_gender := fcase(
  treat == "blind",                              "Blind",
  treat == "nonblind" & concordance_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_gender := factor(blind_concordance_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

fit_overall <- function(role_, conc_var) {
  fml <- as.formula(paste0(
    "sc_overall_z ~ i(", conc_var, ", ref = 'Blind') + ",
    "resp_age + I(resp_age^2) + I(resp_age^3) | ",
    "resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income"
  ))
  suppressMessages(suppressWarnings(
    feols(fml, data = firm_long_dt[role == role_], vcov = ~ responseid)
  ))
}

m_hr_race  <- fit_overall("HR",  "blind_concordance_race")
m_hr_gen   <- fit_overall("HR",  "blind_concordance_gender")
m_hr_rg    <- fit_overall("HR",  "concordance_race_gender_detailed_blind")
m_eng_race <- fit_overall("Eng", "blind_concordance_race")
m_eng_gen  <- fit_overall("Eng", "blind_concordance_gender")
m_eng_rg   <- fit_overall("Eng", "concordance_race_gender_detailed_blind")

flip_coef_signs <- function(m) { m$coefficients <- -1 * m$coefficients; m }
all_models <- lapply(list(
  m_hr_race, m_eng_race,
  m_hr_gen,  m_eng_gen,
  m_hr_rg,   m_eng_rg
), flip_coef_signs)
## Trailing-space disambiguators so modelsummary keeps each column distinct.
names(all_models) <- c("HR", "Eng", "HR ", "Eng ", "HR  ", "Eng  ")

## Multiple raw names map to the same display label so the three
## specifications align on the same two coefficient rows.
coef_map_conc <- c(
  "blind_concordance_race::Nonblind_Concordant"               = "Concordant Applicant",
  "blind_concordance_gender::Nonblind_Concordant"             = "Concordant Applicant",
  "concordance_race_gender_detailed_blind::Concordant_Group"  = "Concordant Applicant",
  "blind_concordance_race::Nonblind_Nonconcordant"            = "Nonconcordant Applicant",
  "blind_concordance_gender::Nonblind_Nonconcordant"          = "Nonconcordant Applicant",
  "concordance_race_gender_detailed_blind::Discordant_Group"  = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:8

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Concordant Race" = 2,
                     "Concordant Gender" = 2,
                     "Concordant Race AND Gender" = 2)) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(8, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(m_hr_race, m_hr_gen, m_hr_rg, m_eng_race, m_eng_gen, m_eng_rg,
   all_models, coef_map_conc, gof_custom_conc, flip_coef_signs,
   fit_overall, chk, nox, fe_rows)
```
```{r het_pooled_master, echo = FALSE, warning = FALSE, message = FALSE}
## Master helpers shared by §7 / §8 / §9 (and their drop-age and
## drop-age + r_do_bythree subsections). The figure layout, labels, and
## extraction logic are identical across variants -- only the regression
## controls (age polynomial, position FE) and the coding-tier definition
## change.

build_aux_pooled <- function(d, coding_method = c("binary", "eqcount", "natural")) {
  coding_method <- match.arg(coding_method)
  d <- copy(d)
  d[, urm_tech_blind := fcase(
    treat == "blind",                    "Blind",
    treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
    treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
    default = NA_character_)]
  d[, urm_tech_blind := factor(urm_tech_blind,
    levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d[, race_gender := factor(race_gender,
    levels = c("Blind", "White_Male", "White_Female",
               "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female"))]
  if (coding_method == "binary") {
    d[, code_split := factor(top_half_coder, levels = c("0", "1"))]
  } else if (coding_method == "eqcount") {
    q_cuts <- quantile(d$test_case, probs = c(0.33, 0.67), na.rm = TRUE)
    d[, code_split := cut(test_case,
                          breaks = c(-Inf, q_cuts[1], q_cuts[2], Inf),
                          labels = c("Low_Coder", "Mid_Coder", "Top_Coder"),
                          include.lowest = TRUE)]
  } else {
    d[, code_split := cut(test_case,
                          breaks = c(-Inf, 5.75, 18.875, Inf),
                          labels = c("Low_Coder", "Mid_Coder", "Top_Coder"),
                          include.lowest = TRUE)]
  }
  d[, code_split := factor(code_split,
                           levels = if (coding_method == "binary")
                                       c("0", "1")
                                   else c("Low_Coder", "Mid_Coder", "Top_Coder"))]
  d
}

fit_pooled_v <- function(d, factor_col, split_col, age_terms, pos_fe) {
  fml <- as.formula(sprintf(
    "I(-sc_overall_z) ~ %s * %s + %s | resume_index + %s + resp_gender + resp_race + s2_educ + s2_income",
    factor_col, split_col, age_terms, pos_fe))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)
  ))
}

extract_pooled_te <- function(model, factor_col, split_col,
                              demo_levels_no_blind, demo_labels,
                              tier_levels, tier_labels) {
  cf <- coef(model);  V <- vcov(model)
  np <- length(cf);   cf_names <- names(cf)
  ref_tier <- tier_levels[1]
  rows <- vector("list", length(demo_levels_no_blind) * length(tier_levels))
  k <- 0L
  for (i in seq_along(demo_levels_no_blind)) {
    for (j in seq_along(tier_levels)) {
      d <- demo_levels_no_blind[i]; t <- tier_levels[j]
      v <- numeric(np)
      idx_main <- match(paste0(factor_col, d), cf_names)
      if (!is.na(idx_main)) v[idx_main] <- 1
      if (t != ref_tier) {
        idx_int <- match(paste0(factor_col, d, ":", split_col, t), cf_names)
        if (!is.na(idx_int)) v[idx_int] <- 1
      }
      est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
      p <- 2 * pnorm(-abs(est / se))
      k <- k + 1L
      rows[[k]] <- data.frame(Term = demo_labels[i], Tier = tier_labels[j],
                              Estimate = est, `Std. Error` = se, `Pr(>|t|)` = p,
                              check.names = FALSE)
    }
  }
  out <- do.call(rbind, rows)
  out$stars <- ifelse(out$`Pr(>|t|)` < 0.01, "***",
                ifelse(out$`Pr(>|t|)` < 0.05, "**",
                ifelse(out$`Pr(>|t|)` < 0.10, "*", "")))
  out$Term <- factor(out$Term, levels = demo_labels)
  out$Tier <- factor(out$Tier, levels = tier_labels)
  out
}

make_pooled_plot <- function(plot_df, title_label, color_vals, shape_vals, show_y = TRUE) {
  p <- ggplot(plot_df, aes(x = Term, y = Estimate, color = Tier, shape = Tier)) +
    geom_hline(yintercept = 0, color = "black", linewidth = 0.4) +
    geom_pointrange(aes(ymin = Estimate - 1.96 * `Std. Error`,
                        ymax = Estimate + 1.96 * `Std. Error`),
                    position = position_dodge(width = 0.6), size = 0.3) +
    geom_text(aes(label = stars, y = Estimate + 1.96 * `Std. Error` + 0.015),
              position = position_dodge(width = 0.6), size = 2.6, vjust = 0,
              color = "black", show.legend = FALSE) +
    scale_color_manual(values = color_vals) +
    scale_shape_manual(values = shape_vals) +
    coord_cartesian(ylim = c(-0.4, 0.4)) +
    labs(title = title_label, x = NULL,
         y = "Effect of Blinding on Overall Evaluation Score (Z)",
         color = "Tier:", shape = "Tier:") +
    theme_bw(base_size = 8) +
    theme(axis.text.x  = element_text(angle = 30, hjust = 1, size = 7),
          axis.title.y = element_text(size = 8),
          legend.position = "top",
          legend.title = element_text(face = "bold", size = 8),
          legend.text  = element_text(size = 7),
          plot.title   = element_text(face = "bold", size = 9),
          plot.margin  = margin(3, 6, 3, 3, "pt"))
  if (!show_y) p <- p + theme(axis.title.y = element_blank())
  p
}

run_section <- function(coding_method, age_terms, pos_fe, file_suffix, header_label) {
  rg_levels <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
                 "Hispanic_Male", "Hispanic_Female")
  rg_labels <- c("White Male", "White Female", "Asian Male", "Asian Female",
                 "Hispanic Male", "Hispanic Female")
  ut_levels <- c("Nonblind_NonURM", "Nonblind_URM")
  ut_labels <- c("Majority", "URM")
  ax_levels <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
  ax_labels <- c("Male (NH)", "Female (NH)", "Hispanic")
  gpa_levels  <- c("Low_GPA", "Mid_GPA", "Top_GPA")
  gpa_labels  <- c("Low GPA", "Mid GPA", "Top GPA")
  gpa_colors  <- c("Low GPA" = "black", "Mid GPA" = "steelblue", "Top GPA" = "indianred1")
  gpa_shapes  <- c("Low GPA" = 16, "Mid GPA" = 15, "Top GPA" = 17)
  if (coding_method == "binary") {
    cod_levels <- c("0", "1")
    cod_labels <- c("Bottom 50% Coders", "Top 50% Coders")
    cod_colors <- c("Bottom 50% Coders" = "black", "Top 50% Coders" = "indianred1")
    cod_shapes <- c("Bottom 50% Coders" = 16, "Top 50% Coders" = 17)
  } else {
    cod_levels <- c("Low_Coder", "Mid_Coder", "Top_Coder")
    cod_labels <- c("Low Coder", "Mid Coder", "Top Coder")
    cod_colors <- c("Low Coder" = "black", "Mid Coder" = "steelblue", "Top Coder" = "indianred1")
    cod_shapes <- c("Low Coder" = 16, "Mid Coder" = 15, "Top Coder" = 17)
  }

  build_role_panel <- function(d, role_label, show_y_left = TRUE) {
    m_rg_gpa <- fit_pooled_v(d, "race_gender",     "gpa_tier3",  age_terms, pos_fe)
    m_rg_cod <- fit_pooled_v(d, "race_gender",     "code_split", age_terms, pos_fe)
    m_ut_gpa <- fit_pooled_v(d, "urm_tech_blind",  "gpa_tier3",  age_terms, pos_fe)
    m_ut_cod <- fit_pooled_v(d, "urm_tech_blind",  "code_split", age_terms, pos_fe)
    m_ax_gpa <- fit_pooled_v(d, "urm_axis_blind",  "gpa_tier3",  age_terms, pos_fe)
    m_ax_cod <- fit_pooled_v(d, "urm_axis_blind",  "code_split", age_terms, pos_fe)
    df_rg_gpa <- extract_pooled_te(m_rg_gpa, "race_gender",    "gpa_tier3",  rg_levels, rg_labels, gpa_levels, gpa_labels)
    df_rg_cod <- extract_pooled_te(m_rg_cod, "race_gender",    "code_split", rg_levels, rg_labels, cod_levels, cod_labels)
    df_ut_gpa <- extract_pooled_te(m_ut_gpa, "urm_tech_blind", "gpa_tier3",  ut_levels, ut_labels, gpa_levels, gpa_labels)
    df_ut_cod <- extract_pooled_te(m_ut_cod, "urm_tech_blind", "code_split", ut_levels, ut_labels, cod_levels, cod_labels)
    df_ax_gpa <- extract_pooled_te(m_ax_gpa, "urm_axis_blind", "gpa_tier3",  ax_levels, ax_labels, gpa_levels, gpa_labels)
    df_ax_cod <- extract_pooled_te(m_ax_cod, "urm_axis_blind", "code_split", ax_levels, ax_labels, cod_levels, cod_labels)
    list(
      rg_gpa = make_pooled_plot(df_rg_gpa, paste0(role_label, ": Per-Cell, by GPA"),    gpa_colors, gpa_shapes, show_y = show_y_left),
      rg_cod = make_pooled_plot(df_rg_cod, paste0(role_label, ": Per-Cell, by Coding"), cod_colors, cod_shapes, show_y = FALSE),
      ut_gpa = make_pooled_plot(df_ut_gpa, paste0(role_label, ": URM-tech, by GPA"),    gpa_colors, gpa_shapes, show_y = show_y_left),
      ut_cod = make_pooled_plot(df_ut_cod, paste0(role_label, ": URM-tech, by Coding"), cod_colors, cod_shapes, show_y = FALSE),
      ax_gpa = make_pooled_plot(df_ax_gpa, paste0(role_label, ": URM-axis, by GPA"),    gpa_colors, gpa_shapes, show_y = show_y_left),
      ax_cod = make_pooled_plot(df_ax_cod, paste0(role_label, ": URM-axis, by Coding"), cod_colors, cod_shapes, show_y = FALSE)
    )
  }

  dt_hr  <- build_aux_pooled(firm_long_dt[role == "HR"],  coding_method)
  dt_eng <- build_aux_pooled(firm_long_dt[role == "Eng"], coding_method)
  panels_hr  <- build_role_panel(dt_hr,  "HR",  show_y_left = TRUE)
  panels_eng <- build_role_panel(dt_eng, "Eng", show_y_left = TRUE)

  fig_dir <- here("2_Reports", "figures")
  if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
  plot_file_hr  <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_HR.pdf"))
  plot_file_eng <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_Eng.pdf"))

  fig_hr <- (panels_hr$rg_gpa + panels_hr$rg_cod) /
            (panels_hr$ax_gpa + panels_hr$ax_cod) /
            (panels_hr$ut_gpa + panels_hr$ut_cod) +
            plot_layout(guides = "collect") &
            theme(legend.position = "top")
  fig_eng <- (panels_eng$rg_gpa + panels_eng$rg_cod) /
             (panels_eng$ax_gpa + panels_eng$ax_cod) /
             (panels_eng$ut_gpa + panels_eng$ut_cod) +
             plot_layout(guides = "collect") &
             theme(legend.position = "top")

  suppressMessages(suppressWarnings({
    ggsave(plot_file_hr,  plot = fig_hr,  width = 10, height = 6.2, device = "pdf")
    ggsave(plot_file_eng, plot = fig_eng, width = 10, height = 6.2, device = "pdf")
  }))

  ## Escape underscores so r_do, r_do_bythree etc. render in text mode.
  header_label_tex <- gsub("_", "\\\\_", header_label)
  cat(sprintf("\\begin{center}\\textbf{HR Evaluators (%s)}\\par\\vspace{0.1em}\n", header_label_tex))
  cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_hr, "}\\end{center}\n", sep = "")
  cat("\\clearpage\n")
  cat(sprintf("\\begin{center}\\textbf{Engineer Evaluators (%s)}\\par\\vspace{0.1em}\n", header_label_tex))
  cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_eng, "}\\end{center}\n", sep = "")
  invisible(NULL)
}
```



```{r het_pooled_cont_master, echo = FALSE, warning = FALSE, message = FALSE}
## Master helper for the continuous-quality variants in §10. Replaces the
## categorical tier interaction with a continuous z-score slope:
##   race_gender * gpa_z      (and same for urm_axis_blind, urm_tech_blind)
##   race_gender * test_case_z
## Plotted TE points: -1 SD ("Low"), 0 ("Mid"), +1 SD ("Top") of the
## standardized quality score, so the visual layout matches §6-§9 plots.
## TE(D, q) = beta_D + q * beta_{D x quality_z}; SE via v' Sigma v.
## Resume-level main effects of gpa_z and test_case_z are absorbed by the
## resume_index FE; the demographic x quality interaction is identified
## from cross-resume variation in (race_gender, quality) pairs.

build_aux_cont <- function(d) {
  d <- copy(d)
  d[, urm_tech_blind := fcase(
    treat == "blind",                    "Blind",
    treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
    treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
    default = NA_character_)]
  d[, urm_tech_blind := factor(urm_tech_blind,
    levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d[, race_gender := factor(race_gender,
    levels = c("Blind", "White_Male", "White_Female",
               "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female"))]
  d[, gpa_z := as.numeric(scale(gpa))]
  d[, test_case_z := as.numeric(scale(test_case))]
  d
}

fit_pooled_cont <- function(d, factor_col, quality_col, age_terms, pos_fe) {
  fml <- as.formula(sprintf(
    "I(-sc_overall_z) ~ %s * %s + %s | resume_index + %s + resp_gender + resp_race + s2_educ + s2_income",
    factor_col, quality_col, age_terms, pos_fe))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)
  ))
}

extract_pooled_te_cont <- function(model, factor_col, quality_col,
                                    demo_levels_no_blind, demo_labels,
                                    eval_points, eval_labels) {
  cf <- coef(model);  V <- vcov(model)
  np <- length(cf);   cf_names <- names(cf)
  rows <- vector("list", length(demo_levels_no_blind) * length(eval_points))
  k <- 0L
  for (i in seq_along(demo_levels_no_blind)) {
    for (j in seq_along(eval_points)) {
      d <- demo_levels_no_blind[i]; q <- eval_points[j]
      v <- numeric(np)
      idx_main <- match(paste0(factor_col, d), cf_names)
      if (!is.na(idx_main)) v[idx_main] <- 1
      idx_int <- match(paste0(factor_col, d, ":", quality_col), cf_names)
      if (!is.na(idx_int)) v[idx_int] <- q
      est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
      p <- 2 * pnorm(-abs(est / se))
      k <- k + 1L
      rows[[k]] <- data.frame(Term = demo_labels[i], Tier = eval_labels[j],
                              Estimate = est, `Std. Error` = se, `Pr(>|t|)` = p,
                              check.names = FALSE)
    }
  }
  out <- do.call(rbind, rows)
  out$stars <- ifelse(out$`Pr(>|t|)` < 0.01, "***",
                ifelse(out$`Pr(>|t|)` < 0.05, "**",
                ifelse(out$`Pr(>|t|)` < 0.10, "*", "")))
  out$Term <- factor(out$Term, levels = demo_labels)
  out$Tier <- factor(out$Tier, levels = eval_labels)
  out
}

run_section_cont <- function(age_terms, pos_fe, file_suffix, header_label) {
  rg_levels <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
                 "Hispanic_Male", "Hispanic_Female")
  rg_labels <- c("White Male", "White Female", "Asian Male", "Asian Female",
                 "Hispanic Male", "Hispanic Female")
  ut_levels <- c("Nonblind_NonURM", "Nonblind_URM")
  ut_labels <- c("Majority", "URM")
  ax_levels <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
  ax_labels <- c("Male (NH)", "Female (NH)", "Hispanic")

  z_pts    <- c(-1, 0, 1)
  z_labs   <- c("Low (-1 SD)", "Mid (0)", "Top (+1 SD)")
  z_colors <- c("Low (-1 SD)" = "black", "Mid (0)" = "steelblue", "Top (+1 SD)" = "indianred1")
  z_shapes <- c("Low (-1 SD)" = 16, "Mid (0)" = 15, "Top (+1 SD)" = 17)

  build_role_panel <- function(d, role_label, show_y_left = TRUE) {
    m_rg_gpa <- fit_pooled_cont(d, "race_gender",     "gpa_z",       age_terms, pos_fe)
    m_rg_cod <- fit_pooled_cont(d, "race_gender",     "test_case_z", age_terms, pos_fe)
    m_ut_gpa <- fit_pooled_cont(d, "urm_tech_blind",  "gpa_z",       age_terms, pos_fe)
    m_ut_cod <- fit_pooled_cont(d, "urm_tech_blind",  "test_case_z", age_terms, pos_fe)
    m_ax_gpa <- fit_pooled_cont(d, "urm_axis_blind",  "gpa_z",       age_terms, pos_fe)
    m_ax_cod <- fit_pooled_cont(d, "urm_axis_blind",  "test_case_z", age_terms, pos_fe)
    df_rg_gpa <- extract_pooled_te_cont(m_rg_gpa, "race_gender",    "gpa_z",       rg_levels, rg_labels, z_pts, z_labs)
    df_rg_cod <- extract_pooled_te_cont(m_rg_cod, "race_gender",    "test_case_z", rg_levels, rg_labels, z_pts, z_labs)
    df_ut_gpa <- extract_pooled_te_cont(m_ut_gpa, "urm_tech_blind", "gpa_z",       ut_levels, ut_labels, z_pts, z_labs)
    df_ut_cod <- extract_pooled_te_cont(m_ut_cod, "urm_tech_blind", "test_case_z", ut_levels, ut_labels, z_pts, z_labs)
    df_ax_gpa <- extract_pooled_te_cont(m_ax_gpa, "urm_axis_blind", "gpa_z",       ax_levels, ax_labels, z_pts, z_labs)
    df_ax_cod <- extract_pooled_te_cont(m_ax_cod, "urm_axis_blind", "test_case_z", ax_levels, ax_labels, z_pts, z_labs)
    list(
      rg_gpa = make_pooled_plot(df_rg_gpa, paste0(role_label, ": Per-Cell, by GPA"),    z_colors, z_shapes, show_y = show_y_left),
      rg_cod = make_pooled_plot(df_rg_cod, paste0(role_label, ": Per-Cell, by Coding"), z_colors, z_shapes, show_y = FALSE),
      ut_gpa = make_pooled_plot(df_ut_gpa, paste0(role_label, ": URM-tech, by GPA"),    z_colors, z_shapes, show_y = show_y_left),
      ut_cod = make_pooled_plot(df_ut_cod, paste0(role_label, ": URM-tech, by Coding"), z_colors, z_shapes, show_y = FALSE),
      ax_gpa = make_pooled_plot(df_ax_gpa, paste0(role_label, ": URM-axis, by GPA"),    z_colors, z_shapes, show_y = show_y_left),
      ax_cod = make_pooled_plot(df_ax_cod, paste0(role_label, ": URM-axis, by Coding"), z_colors, z_shapes, show_y = FALSE)
    )
  }

  dt_hr  <- build_aux_cont(firm_long_dt[role == "HR"])
  dt_eng <- build_aux_cont(firm_long_dt[role == "Eng"])
  panels_hr  <- build_role_panel(dt_hr,  "HR",  show_y_left = TRUE)
  panels_eng <- build_role_panel(dt_eng, "Eng", show_y_left = TRUE)

  fig_dir <- here("2_Reports", "figures")
  if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
  plot_file_hr  <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_HR.pdf"))
  plot_file_eng <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_Eng.pdf"))

  fig_hr <- (panels_hr$rg_gpa + panels_hr$rg_cod) /
            (panels_hr$ax_gpa + panels_hr$ax_cod) /
            (panels_hr$ut_gpa + panels_hr$ut_cod) +
            plot_layout(guides = "collect") &
            theme(legend.position = "top")
  fig_eng <- (panels_eng$rg_gpa + panels_eng$rg_cod) /
             (panels_eng$ax_gpa + panels_eng$ax_cod) /
             (panels_eng$ut_gpa + panels_eng$ut_cod) +
             plot_layout(guides = "collect") &
             theme(legend.position = "top")

  suppressMessages(suppressWarnings({
    ggsave(plot_file_hr,  plot = fig_hr,  width = 10, height = 6.2, device = "pdf")
    ggsave(plot_file_eng, plot = fig_eng, width = 10, height = 6.2, device = "pdf")
  }))

  header_label_tex <- gsub("_", "\\\\_", header_label)
  cat(sprintf("\\begin{center}\\textbf{HR Evaluators (%s)}\\par\\vspace{0.1em}\n", header_label_tex))
  cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_hr, "}\\end{center}\n", sep = "")
  cat("\\clearpage\n")
  cat(sprintf("\\begin{center}\\textbf{Engineer Evaluators (%s)}\\par\\vspace{0.1em}\n", header_label_tex))
  cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_eng, "}\\end{center}\n", sep = "")
  invisible(NULL)
}
```
\clearpage
## Heterogeneity: Where the Demographic Premium Applies (Effects by Candidate Quality)

\textit{Spec.} Single pooled regression per (demographic, quality) pair: \texttt{-sc\_overall\_z $\sim$ factor*quality\_z + linear age $|$ resume\_index + r\_do + resp FEs}, with \texttt{quality\_z} $\in \{$\texttt{gpa\_z}, \texttt{test\_case\_z}$\}$ as the standardized continuous quality variable and \texttt{factor} $\in \{$\texttt{race\_gender} (6 cells), \texttt{urm\_axis\_blind} (Male NH / Female NH / Hispanic), \texttt{urm\_tech\_blind} (Majority / URM)$\}$. Two-way cluster on \texttt{responseid + resume\_index}. Plotted TE points are at $-1$, $0$, $+1$ SD of the standardized quality score (labelled "Low / Mid / Top") via the linear combination $\hat\beta_D + q \cdot \hat\beta_{D\times \text{quality}}$, $q \in \{-1, 0, 1\}$.

```{r het_pooled_102, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.width = 11, fig.height = 6}
run_section_cont(age_terms    = "resp_age",
                 pos_fe       = "r_do",
                 file_suffix  = "102_cont_age1_rdo",
                 header_label = "Continuous quality, drop nonlinear age, r_do")
```


\clearpage
\clearpage
\clearpage
# Individual Response to Institutional Policy (Institutional Crowding Out or Compensatory Bias)

\textit{Takeaway / Summary.}
\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{The Puzzle of Individual Ideology:} The two-way relationship between an evaluator's personal DEI priority and their evaluation scores is surprisingly \emph{muted and statistically noisy}. At first glance, personal ideology appears to have little impact on how blind hiring reshuffles outcomes.
  \begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item \textbf{Compensatory Bias} (Firms with NO Diversity Mandate, see \textcolor{red}{red lines}): When a firm lacks an explicit objective policy targeting URMs, highly pro-DEI HR professionals engage in \emph{compensatory bias} --- filling the perceived institutional void by informally inflating minority candidates' scores in the baseline.
    \item \textbf{Institutional Crowding-Out} (Firms WITH a Diversity Mandate, see \textcolor{blue}{blue lines}): Conversely, when the firm explicitly mandates URM targeting, this formal policy \emph{crowds out} the evaluator's informal efforts; pro-DEI HR professionals \emph{mute} their premium to under-represented minorities' scores.
  \end{itemize}
  \item (Note the \emph{divergence between HR and Engineer results}, particularly in the triple-interaction columns.)
\end{itemize}
\vspace{0.4em}

\textit{Note on Key Index Creation.}
\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textit{Individual DEI Index (Z)}: Evaluator's personal DEI orientation, condensed into a single z-scored score. (Low = Anti-DEI, High = Pro-DEI)
  \begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{0pt}
    \item Mathematical expression: $\text{Index} = z\big(\tfrac{1}{5}\sum_{j=1}^{5} z(x_j)\big)$, z-scored within (\texttt{role}, \texttt{treat}) cells.
    \item \texttt{pro\_dei\_race} --- stated agreement that race DEI is important in hiring (Likert).
    \item \texttt{pro\_dei\_gender} --- stated agreement that gender DEI is important in hiring (Likert).
    \item \texttt{pro\_diverse} --- stated importance of working at a company with a diverse workforce (Likert).
    \item \texttt{pro\_hiring\_dei} --- stated belief that DEI initiatives help firms hire better candidates (Likert).
    \item \texttt{div\_priority} --- revealed-priority rank of ``Diversity and Representation'' in the seven-goals question.
  \end{itemize}
  \item \textit{Firm Targets Fem/His (0/1)}: Indicator for firm policy --- whether the evaluator's firm formally targets Female or Hispanic candidates in hiring.
  \begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{0pt}
    \item Mathematical expression: $\text{Idx} = \mathbb{1}\{\texttt{firm\_targets\_female} = 1 \;\lor\; \texttt{firm\_targets\_hispanic} = 1\}$.
    \item \texttt{firm\_targets\_female} --- 1 if option 6 (``Female'') was selected on \texttt{s5\_policy\_diversity} (multi-select).
    \item \texttt{firm\_targets\_hispanic} --- 1 if option 3 (``Hispanic or Latino'') was selected on the same multi-select.
  \end{itemize}
  \item \textit{Firm DEI Attn Index (Z)}: Respondent's perception of how much attention their firm currently pays to race and gender DEI in hiring, condensed into a single z-scored score.
  \begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{0pt}
    \item Mathematical expression: $\text{Index} = z\big(\tfrac{1}{2}\big(z(\texttt{race\_attn}) + z(\texttt{gender\_attn})\big)\big)$, z-scored within (\texttt{role}, \texttt{treat}) cells.
    \item \texttt{s5\_view\_dei\_race\_f} --- Likert: respondent's perception of firm's current attention to race DEI in hiring.
    \item \texttt{s5\_view\_dei\_gender\_f} --- Likert: respondent's perception of firm's current attention to gender DEI in hiring.
  \end{itemize}
\end{itemize}
\vspace{-0.6em}

\clearpage
## By Six Demographics

```{r bh_dei_combined_rg, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Replicates the §4.5 / §4.6 combined structure but using the full
## per-race-gender breakdown (six demographics, as in §4.1). Single combined
## table with three specs: simple DEI het | triple Firm Targets URM | triple
## Firm DEI Attn. DEI proxy: Index A only. Coefficients flipped post-fit so
## positive => effect of blinding raises the score for that group.
## Estimate and standard error are placed on the same line so all 36 coef
## rows + FE rows + N row fit on a single landscape page.

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

fit_simple <- function(d) {
  suppressMessages(suppressWarnings(feols(
    sc_overall_z ~ dei_index_z +
      i(race_gender, ref = "Blind") +
      i(race_gender, dei_index_z, ref = "Blind") +
      resp_age + I(resp_age^2) + I(resp_age^3)
    | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
    data = d, vcov = ~ responseid
  )))
}

fit_triple <- function(d, b) {
  fml <- as.formula(sprintf(
    "sc_overall_z ~ dei_index_z + %s + I(dei_index_z * %s) + i(race_gender, ref = 'Blind') + i(race_gender, dei_index_z, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, I(dei_index_z * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    b, b, b, b))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

m1 <- flip(fit_simple(dt_hr))
m2 <- flip(fit_simple(dt_eng))
m3 <- flip(fit_triple(dt_hr,  "firm_targets_fh"))
m4 <- flip(fit_triple(dt_eng, "firm_targets_fh"))
m5 <- flip(fit_triple(dt_hr,  "firm_dei_attention_z"))
m6 <- flip(fit_triple(dt_eng, "firm_dei_attention_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4,
                   "HR  " = m5, "Engineer  " = m6)

demos     <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female")
demo_lbls <- c("White Male", "White Female", "Asian Male", "Asian Female",
               "Hispanic Male", "Hispanic Female")

coef_map <- c(
  ## --- Block 1: single (level) terms (6 rows) ---
  setNames(demo_lbls, paste0("race_gender::", demos)),

  ## --- Block 2: two-way interactions (18 rows) ---
  ## Demo x Individual DEI Index (Z) (fills all 6 cols)
  setNames(paste0(demo_lbls, " $\\times$ Individual DEI Index (Z)"),
           paste0("race_gender::", demos, ":dei_index_z")),
  ## Demo x Firm Targets Fem/His (0/1) (cols 3-4 only)
  setNames(paste0(demo_lbls, " $\\times$ Firm Targets Fem/His (0/1)"),
           paste0("race_gender::", demos, ":firm_targets_fh")),
  ## Demo x Firm DEI Attn Index (Z) (cols 5-6 only)
  setNames(paste0(demo_lbls, " $\\times$ Firm DEI Attn Index (Z)"),
           paste0("race_gender::", demos, ":firm_dei_attention_z")),

  ## --- Block 3: three-way interactions (12 rows) ---
  setNames(paste0(demo_lbls, " $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)"),
           paste0("race_gender::", demos, ":I(dei_index_z * firm_targets_fh)")),
  setNames(paste0(demo_lbls, " $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)"),
           paste0("race_gender::", demos, ":I(dei_index_z * firm_dei_attention_z)"))
)

gof_custom <- tribble(
  ~raw,            ~clean,        ~fmt,
  "nobs",          "Observations", 0
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
## Single-line est+se format -> 36 unique coefs = 36 rows; FE rows at 37:40.
attr(fe_rows, "position") <- 37:40

## Inline est+SE format keeps the table to ~41 rows (vs. ~77 with separate
## SE row) so it fits on one landscape page.
modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(c(" " = 1,
                     "Simple DEI Heterogeneity" = 2,
                     "Triple: Firm Targets URM" = 2,
                     "Triple: Firm Pays DEI Attention" = 2)) %>%
  ## Block boundaries: single = rows 1-6; two-way = rows 7-24
  ## (Demo x DEI -> 12, Demo x FT -> 18, Demo x FA -> 24);
  ## three-way = rows 25-36 (Demo x DEI x FT -> 30, Demo x DEI x FA -> 36).
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(18, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\hdashline") %>%
  row_spec(30, extra_latex_after = "\\hdashline") %>%
  row_spec(36, extra_latex_after = "\\midrule") %>%
  row_spec(40, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

## ---------------------------------------------------------------------------
## Scissors plot for cols 3-4 of the §4.4 table (HR & Eng triple with Firm
## Targets URM), 6x2 grid: six race-gender groups by HR / Eng (12 panels).
## ---------------------------------------------------------------------------
cf_hr  <- coef(m3);  V_hr  <- vcov(m3)
cf_eng <- coef(m4);  V_eng <- vcov(m4)

cells_44_rg <- list()
for (i in seq_along(demos)) {
  cells_44_rg[[demo_lbls[i]]] <- c(
    level  = paste0("race_gender::", demos[i]),
    dei    = paste0("race_gender::", demos[i], ":dei_index_z"),
    ft     = paste0("race_gender::", demos[i], ":firm_targets_fh"),
    triple = paste0("race_gender::", demos[i], ":I(dei_index_z * firm_targets_fh)")
  )
}

dei_grid <- seq(-2, 2, length.out = 41)
plot_dt <- as.data.table(expand.grid(role  = c("HR", "Eng"),
                                     group = names(cells_44_rg),
                                     DEI   = dei_grid,
                                     FT    = c(0, 1),
                                     stringsAsFactors = FALSE))
plot_dt[, c("est", "se") := {
  ix <- unname(cells_44_rg[[group]])
  v  <- c(1, DEI, FT, DEI * FT)
  cf <- if (role == "HR") cf_hr else cf_eng
  V  <- if (role == "HR") V_hr  else V_eng
  list(sum(cf[ix] * v),
       sqrt(c(v %*% V[ix, ix] %*% v)))
}, by = .(role, group, DEI, FT)]
plot_dt[, ':='(lwr = est - 1.96 * se, upr = est + 1.96 * se)]
plot_dt[, FT_label := factor(FT, levels = c(0, 1),
                              labels = c("Firm does NOT target URM",
                                         "Firm targets URM"))]
plot_dt[, group := factor(group, levels = demo_lbls)]
plot_dt[, role := factor(role, levels = c("HR", "Eng"))]

y_lim <- range(c(plot_dt$lwr, plot_dt$upr)) * 1.05
panel_letters <- setNames(LETTERS[1:6], demo_lbls)

scissors_panel <- function(rl, grp) {
  d <- plot_dt[role == rl & group == grp]
  ggplot(d, aes(x = DEI, y = est, color = FT_label, fill = FT_label, linetype = FT_label)) +
    annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
    annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA) +
    geom_line(linewidth = 0.7) +
    annotate("text", x = 0, y = y_lim[2] * 0.93, label = "Blinding helps",
             hjust = 0.5, vjust = 1, size = 1.9, fontface = "italic", color = "darkgreen") +
    annotate("text", x = 0, y = y_lim[1] * 0.93, label = "Blinding hurts",
             hjust = 0.5, vjust = 0, size = 1.9, fontface = "italic", color = "darkred") +
    scale_color_manual(values = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_fill_manual(values  = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_linetype_manual(values = c("Firm does NOT target URM" = "dashed",
                                     "Firm targets URM"        = "solid")) +
    coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
    labs(title = paste0("Panel ", panel_letters[grp],
                        ifelse(rl == "HR", "1", "2"), ": ",
                        rl, " --- ", grp),
         x = paste0(rl, " DEI (Z)"),
         y = expression(Delta~"Z"),
         color = NULL, fill = NULL, linetype = NULL) +
    theme_bw(base_size = 6) +
    theme(legend.position  = "bottom",
          plot.title       = element_text(size = 6.5, face = "bold"),
          axis.title       = element_text(size = 6),
          axis.text        = element_text(size = 5),
          panel.grid.minor = element_blank())
}

top_row <- (scissors_panel("HR",  demo_lbls[1]) | scissors_panel("HR",  demo_lbls[2]) |
            scissors_panel("HR",  demo_lbls[3]) | scissors_panel("HR",  demo_lbls[4]) |
            scissors_panel("HR",  demo_lbls[5]) | scissors_panel("HR",  demo_lbls[6]))
bot_row <- (scissors_panel("Eng", demo_lbls[1]) | scissors_panel("Eng", demo_lbls[2]) |
            scissors_panel("Eng", demo_lbls[3]) | scissors_panel("Eng", demo_lbls[4]) |
            scissors_panel("Eng", demo_lbls[5]) | scissors_panel("Eng", demo_lbls[6]))

scissors <- top_row / bot_row +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_44_rg <- file.path(fig_dir, "8B_44_rg_scissors.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_44_rg, plot = scissors, width = 14, height = 5.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file_44_rg, "}\n", sep = "")
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize Marginal-effects ``scissors'' plot built from the §2.1 columns 3-4 (HR \\& Engineer triple with Firm Targets Fem/His), per race-gender. Top row: HR evaluators (Panels A1--F1). Bottom row: Engineer evaluators (Panels A2--F2). Lines: predicted effect of blinding on each group's overall score as a function of the rater's Individual DEI Index (Z); shaded bands are 95\\% CIs (SE clustered by respondent).\\par}\n")
cat("\\end{center}\n")

rm(dt_hr, dt_eng, fit_simple, fit_triple, flip,
   m1, m2, m3, m4, m5, m6, all_models, demos, demo_lbls,
   coef_map, gof_custom, chk, nox, fe_rows,
   cf_hr, V_hr, cf_eng, V_eng, cells_44_rg, dei_grid, plot_dt, y_lim,
   panel_letters, scissors_panel, top_row, bot_row, scissors,
   fig_dir, plot_file_44_rg)
```


\clearpage
## By Trichotomy (Majority vs Gender Minority vs Racial Minority)

```{r bh_dei_combined_axis, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Combines §4.1, §4.2, §4.3 into a single 6-column URM-axis table.
## Columns 1-2: simple DEI heterogeneity   (HR | Eng).
## Columns 3-4: triple with Firm Targets URM (firm_targets_fh).
## Columns 5-6: triple with Firm DEI Attn (firm_dei_attention_z).
## DEI proxy:  Index A only (dei_index_z).
## Coefficients flipped post-fit so positive => effect of blinding.

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

build_axis <- function(d) {
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d
}
dt_hr  <- build_axis(dt_hr)
dt_eng <- build_axis(dt_eng)

fit_simple <- function(d) {
  suppressMessages(suppressWarnings(feols(
    sc_overall_z ~ dei_index_z +
      i(urm_axis_blind, ref = "Blind") +
      i(urm_axis_blind, dei_index_z, ref = "Blind") +
      resp_age + I(resp_age^2) + I(resp_age^3)
    | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
    data = d, vcov = ~ responseid
  )))
}

fit_triple <- function(d, b) {
  fml <- as.formula(sprintf(
    "sc_overall_z ~ dei_index_z + %s + I(dei_index_z * %s) + i(urm_axis_blind, ref = 'Blind') + i(urm_axis_blind, dei_index_z, ref = 'Blind') + i(urm_axis_blind, %s, ref = 'Blind') + i(urm_axis_blind, I(dei_index_z * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    b, b, b, b))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

m1 <- flip(fit_simple(dt_hr))
m2 <- flip(fit_simple(dt_eng))
m3 <- flip(fit_triple(dt_hr,  "firm_targets_fh"))
m4 <- flip(fit_triple(dt_eng, "firm_targets_fh"))
m5 <- flip(fit_triple(dt_hr,  "firm_dei_attention_z"))
m6 <- flip(fit_triple(dt_eng, "firm_dei_attention_z"))

## Trailing-space disambiguators so modelsummary keeps each column distinct.
all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4,
                   "HR  " = m5, "Engineer  " = m6)

coef_map <- c(
  ## --- Block 1: single (level) terms (3 rows) ---
  "urm_axis_blind::Nonblind_MaleNonHisp"   = "Male (non-hispanic)",
  "urm_axis_blind::Nonblind_FemaleNonHisp" = "Female (non-hispanic)",
  "urm_axis_blind::Nonblind_Hispanic"      = "Hispanic",

  ## --- Block 2: two-way interactions (9 rows) ---
  ## Axis x Individual DEI Index (Z) (fills all 6 cols)
  "urm_axis_blind::Nonblind_MaleNonHisp:dei_index_z"   = "Male (NH) $\\times$ Individual DEI Index (Z)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:dei_index_z" = "Female (NH) $\\times$ Individual DEI Index (Z)",
  "urm_axis_blind::Nonblind_Hispanic:dei_index_z"      = "Hispanic $\\times$ Individual DEI Index (Z)",
  ## Axis x Firm Targets Fem/His (0/1) (cols 3-4 only)
  "urm_axis_blind::Nonblind_MaleNonHisp:firm_targets_fh"   = "Male (NH) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:firm_targets_fh" = "Female (NH) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_Hispanic:firm_targets_fh"      = "Hispanic $\\times$ Firm Targets Fem/His (0/1)",
  ## Axis x Firm DEI Attn Index (Z) (cols 5-6 only)
  "urm_axis_blind::Nonblind_MaleNonHisp:firm_dei_attention_z"   = "Male (NH) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:firm_dei_attention_z" = "Female (NH) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_Hispanic:firm_dei_attention_z"      = "Hispanic $\\times$ Firm DEI Attn Index (Z)",

  ## --- Block 3: three-way interactions (6 rows) ---
  "urm_axis_blind::Nonblind_MaleNonHisp:I(dei_index_z * firm_targets_fh)"   = "Male (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:I(dei_index_z * firm_targets_fh)" = "Female (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_Hispanic:I(dei_index_z * firm_targets_fh)"      = "Hispanic $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_MaleNonHisp:I(dei_index_z * firm_dei_attention_z)"   = "Male (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:I(dei_index_z * firm_dei_attention_z)" = "Female (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_Hispanic:I(dei_index_z * firm_dei_attention_z)"      = "Hispanic $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)"
)

gof_custom <- tribble(
  ~raw,            ~clean,        ~fmt,
  "nobs",          "Observations", 0
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
## 18 coefs * 2 (est+se) = 36 rows; FE rows sit at 37:40.
attr(fe_rows, "position") <- 37:40

## Row breaks: dashed line after single-term block (row 6) and before
## three-way block (row 24). 3 single * 2 = 6; (3+9) two-way * 2 = 24.
modelsummary(
  all_models,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map,
  gof_map  = gof_custom,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Simple DEI Heterogeneity" = 2,
                     "Triple: Firm Targets URM" = 2,
                     "Triple: Firm Pays DEI Attention" = 2)) %>%
  ## Block boundaries (dashed) and FE / fitstat boundaries (solid).
  ## Two-way block: 6 (after Axis x DEI) | 12 (after Axis x FT) | 18 (after Axis x FA).
  ## Three-way block: 30 (after Axis x DEI x FT, before Axis x DEI x FA).
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(18, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\hdashline") %>%
  row_spec(30, extra_latex_after = "\\hdashline") %>%
  row_spec(36, extra_latex_after = "\\midrule") %>%
  row_spec(40, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

## ---------------------------------------------------------------------------
## Scissors plot for cols 3-4 of the §4.4 table (HR & Eng triple with Firm
## Targets URM). Replicates the §4.2 scissors using m3 (HR) and m4 (Eng).
## TE_X(DEI, FT) = beta_X + beta_{X x DEI}*DEI + beta_{X x FT}*FT
##                       + beta_{X x DEI x FT}*DEI*FT
## SE via quadratic form v' Sigma v with v = (1, DEI, FT, DEI*FT).
## Coefficients are already sign-flipped, so positive = effect of blinding
## raises the score for that group.
## ---------------------------------------------------------------------------
cf_hr  <- coef(m3);  V_hr  <- vcov(m3)
cf_eng <- coef(m4);  V_eng <- vcov(m4)

cells_44 <- list(
  "Male (non-hispanic)" = c(
    level  = "urm_axis_blind::Nonblind_MaleNonHisp",
    dei    = "urm_axis_blind::Nonblind_MaleNonHisp:dei_index_z",
    ft     = "urm_axis_blind::Nonblind_MaleNonHisp:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_MaleNonHisp:I(dei_index_z * firm_targets_fh)"
  ),
  "Female (non-hispanic)" = c(
    level  = "urm_axis_blind::Nonblind_FemaleNonHisp",
    dei    = "urm_axis_blind::Nonblind_FemaleNonHisp:dei_index_z",
    ft     = "urm_axis_blind::Nonblind_FemaleNonHisp:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_FemaleNonHisp:I(dei_index_z * firm_targets_fh)"
  ),
  "Hispanic" = c(
    level  = "urm_axis_blind::Nonblind_Hispanic",
    dei    = "urm_axis_blind::Nonblind_Hispanic:dei_index_z",
    ft     = "urm_axis_blind::Nonblind_Hispanic:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_Hispanic:I(dei_index_z * firm_targets_fh)"
  )
)

dei_grid <- seq(-2, 2, length.out = 41)
plot_dt <- as.data.table(expand.grid(role  = c("HR", "Eng"),
                                     group = names(cells_44),
                                     DEI   = dei_grid,
                                     FT    = c(0, 1),
                                     stringsAsFactors = FALSE))
plot_dt[, c("est", "se") := {
  ix <- unname(cells_44[[group]])
  v  <- c(1, DEI, FT, DEI * FT)
  cf <- if (role == "HR") cf_hr else cf_eng
  V  <- if (role == "HR") V_hr  else V_eng
  list(sum(cf[ix] * v),
       sqrt(c(v %*% V[ix, ix] %*% v)))
}, by = .(role, group, DEI, FT)]
plot_dt[, ':='(lwr = est - 1.96 * se, upr = est + 1.96 * se)]
plot_dt[, FT_label := factor(FT, levels = c(0, 1),
                              labels = c("Firm does NOT target URM",
                                         "Firm targets URM"))]
plot_dt[, group := factor(group,
                          levels = c("Male (non-hispanic)",
                                     "Female (non-hispanic)",
                                     "Hispanic"))]
plot_dt[, role := factor(role, levels = c("HR", "Eng"))]

y_lim <- range(c(plot_dt$lwr, plot_dt$upr)) * 1.05
panel_letters <- c("Male (non-hispanic)"   = "A",
                   "Female (non-hispanic)" = "B",
                   "Hispanic"              = "C")

scissors_panel <- function(rl, grp) {
  d <- plot_dt[role == rl & group == grp]
  ggplot(d, aes(x = DEI, y = est, color = FT_label, fill = FT_label, linetype = FT_label)) +
    annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
    annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA) +
    geom_line(linewidth = 1) +
    annotate("text", x = 0, y = y_lim[2] * 0.93, label = "Blinding helps",
             hjust = 0.5, vjust = 1, size = 2.4, fontface = "italic", color = "darkgreen") +
    annotate("text", x = 0, y = y_lim[1] * 0.93, label = "Blinding hurts",
             hjust = 0.5, vjust = 0, size = 2.4, fontface = "italic", color = "darkred") +
    scale_color_manual(values = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_fill_manual(values  = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_linetype_manual(values = c("Firm does NOT target URM" = "dashed",
                                     "Firm targets URM"        = "solid")) +
    coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
    labs(title = paste0("Panel ", panel_letters[grp],
                        ifelse(rl == "HR", "1", "2"), ": ",
                        rl, " --- ", grp),
         x = paste0(rl, " Evaluator's Individual DEI Index (Z)"),
         y = "Effect of Blinding (Δ Overall Z-Score)",
         color = NULL, fill = NULL, linetype = NULL) +
    theme_bw(base_size = 8) +
    theme(legend.position = "bottom",
          plot.title       = element_text(size = 9, face = "bold"),
          axis.title       = element_text(size = 8),
          panel.grid.minor = element_blank())
}

scissors <- (scissors_panel("HR",  "Male (non-hispanic)") |
             scissors_panel("HR",  "Female (non-hispanic)") |
             scissors_panel("HR",  "Hispanic")) /
            (scissors_panel("Eng", "Male (non-hispanic)") |
             scissors_panel("Eng", "Female (non-hispanic)") |
             scissors_panel("Eng", "Hispanic")) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_44 <- file.path(fig_dir, "8B_44_scissors.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_44, plot = scissors, width = 11, height = 4.0, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\n")
cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_44, "}\n", sep = "")
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize Marginal-effects ``scissors'' plot built from the §2.2 columns 3-4 (HR \\& Engineer triple with Firm Targets Fem/His). Top row: HR evaluators (Panels A1, B1, C1). Bottom row: Engineer evaluators (Panels A2, B2, C2). Lines: predicted effect of blinding on each group's overall score as a function of the rater's Individual DEI Index (Z); shaded bands are 95\\% CIs from the linear combination of axis-triple coefficients (SE clustered by respondent).\\par}\n")
cat("\\end{center}\n")

rm(dt_hr, dt_eng, build_axis, fit_simple, fit_triple, flip,
   m1, m2, m3, m4, m5, m6, all_models, coef_map, gof_custom,
   chk, nox, fe_rows,
   cf_hr, V_hr, cf_eng, V_eng, cells_44, dei_grid, plot_dt, y_lim,
   panel_letters, scissors_panel, scissors, fig_dir, plot_file_44)
```


\clearpage
## By Dichotomy (Majority vs Minority)

```{r bh_dei_combined_urm, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Replicates §4.4 but using the URM-Tech dichotomy (Majority = WM+AM vs.
## Minority in Tech = WF+AF+HM+HF). Same six specs as §4.4: simple DEI het,
## triple with Firm Targets Fem/His, and triple with Firm DEI Attn Index (Z).
## DEI proxy: Index A only. Coefficients flipped post-fit so positive =>
## effect of blinding raises the score for that group.

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

build_urm <- function(d) {
  d[, urm_tech_blind := fcase(
    treat == "blind",                    "Blind",
    treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
    treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
    default = NA_character_)]
  d[, urm_tech_blind := factor(urm_tech_blind,
    levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
  d
}
dt_hr  <- build_urm(dt_hr)
dt_eng <- build_urm(dt_eng)

fit_simple <- function(d) {
  suppressMessages(suppressWarnings(feols(
    sc_overall_z ~ dei_index_z +
      i(urm_tech_blind, ref = "Blind") +
      i(urm_tech_blind, dei_index_z, ref = "Blind") +
      resp_age + I(resp_age^2) + I(resp_age^3)
    | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
    data = d, vcov = ~ responseid
  )))
}

fit_triple <- function(d, b) {
  fml <- as.formula(sprintf(
    "sc_overall_z ~ dei_index_z + %s + I(dei_index_z * %s) + i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, dei_index_z, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(dei_index_z * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    b, b, b, b))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

m1 <- flip(fit_simple(dt_hr))
m2 <- flip(fit_simple(dt_eng))
m3 <- flip(fit_triple(dt_hr,  "firm_targets_fh"))
m4 <- flip(fit_triple(dt_eng, "firm_targets_fh"))
m5 <- flip(fit_triple(dt_hr,  "firm_dei_attention_z"))
m6 <- flip(fit_triple(dt_eng, "firm_dei_attention_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4,
                   "HR  " = m5, "Engineer  " = m6)

maj_lbl <- "Majority (WM+AM)"
min_lbl <- "Minority in Tech (WF+AF+HM+HF)"

coef_map <- c(
  ## --- Block 1: single (level) terms (2 rows) ---
  "urm_tech_blind::Nonblind_NonURM" = maj_lbl,
  "urm_tech_blind::Nonblind_URM"    = min_lbl,

  ## --- Block 2: two-way interactions (6 rows) ---
  ## Axis x Individual DEI Index (Z) (fills all 6 cols)
  "urm_tech_blind::Nonblind_NonURM:dei_index_z" = paste0(maj_lbl, " $\\times$ Individual DEI Index (Z)"),
  "urm_tech_blind::Nonblind_URM:dei_index_z"    = paste0(min_lbl, " $\\times$ Individual DEI Index (Z)"),
  ## Axis x Firm Targets Fem/His (0/1) (cols 3-4 only)
  "urm_tech_blind::Nonblind_NonURM:firm_targets_fh" = paste0(maj_lbl, " $\\times$ Firm Targets Fem/His (0/1)"),
  "urm_tech_blind::Nonblind_URM:firm_targets_fh"    = paste0(min_lbl, " $\\times$ Firm Targets Fem/His (0/1)"),
  ## Axis x Firm DEI Attn Index (Z) (cols 5-6 only)
  "urm_tech_blind::Nonblind_NonURM:firm_dei_attention_z" = paste0(maj_lbl, " $\\times$ Firm DEI Attn Index (Z)"),
  "urm_tech_blind::Nonblind_URM:firm_dei_attention_z"    = paste0(min_lbl, " $\\times$ Firm DEI Attn Index (Z)"),

  ## --- Block 3: three-way interactions (4 rows) ---
  "urm_tech_blind::Nonblind_NonURM:I(dei_index_z * firm_targets_fh)"      = paste0(maj_lbl, " $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)"),
  "urm_tech_blind::Nonblind_URM:I(dei_index_z * firm_targets_fh)"         = paste0(min_lbl, " $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)"),
  "urm_tech_blind::Nonblind_NonURM:I(dei_index_z * firm_dei_attention_z)" = paste0(maj_lbl, " $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)"),
  "urm_tech_blind::Nonblind_URM:I(dei_index_z * firm_dei_attention_z)"    = paste0(min_lbl, " $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)")
)

gof_custom <- tribble(
  ~raw,            ~clean,        ~fmt,
  "nobs",          "Observations", 0
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
## 12 coefs * 2 (est+se) = 24 rows; FE rows sit at 25:28.
attr(fe_rows, "position") <- 25:28

modelsummary(
  all_models,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map,
  gof_map  = gof_custom,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Simple DEI Heterogeneity" = 2,
                     "Triple: Firm Targets URM" = 2,
                     "Triple: Firm Pays DEI Attention" = 2)) %>%
  ## Block boundaries (dashed) and FE / fitstat boundaries (solid).
  ## Two-way block: 4 (after single) | 8 (after Axis x DEI) | 12 (after Axis x FT) | 16 (end of two-way).
  ## Three-way block: 20 (after Axis x DEI x FT) | 24 (end of three-way / before FE).
  row_spec(4,  extra_latex_after = "\\hdashline") %>%
  row_spec(8,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(16, extra_latex_after = "\\hdashline") %>%
  row_spec(20, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\midrule") %>%
  row_spec(28, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

## ---------------------------------------------------------------------------
## Scissors plot for cols 3-4 of the §4.5 table (HR & Eng triple with Firm
## Targets URM), 2x2 grid: Majority / Minority in Tech, by HR / Eng.
## ---------------------------------------------------------------------------
cf_hr  <- coef(m3);  V_hr  <- vcov(m3)
cf_eng <- coef(m4);  V_eng <- vcov(m4)

cells_45 <- list()
cells_45[[maj_lbl]] <- c(
  level  = "urm_tech_blind::Nonblind_NonURM",
  dei    = "urm_tech_blind::Nonblind_NonURM:dei_index_z",
  ft     = "urm_tech_blind::Nonblind_NonURM:firm_targets_fh",
  triple = "urm_tech_blind::Nonblind_NonURM:I(dei_index_z * firm_targets_fh)"
)
cells_45[[min_lbl]] <- c(
  level  = "urm_tech_blind::Nonblind_URM",
  dei    = "urm_tech_blind::Nonblind_URM:dei_index_z",
  ft     = "urm_tech_blind::Nonblind_URM:firm_targets_fh",
  triple = "urm_tech_blind::Nonblind_URM:I(dei_index_z * firm_targets_fh)"
)

dei_grid <- seq(-2, 2, length.out = 41)
plot_dt <- as.data.table(expand.grid(role  = c("HR", "Eng"),
                                     group = names(cells_45),
                                     DEI   = dei_grid,
                                     FT    = c(0, 1),
                                     stringsAsFactors = FALSE))
plot_dt[, c("est", "se") := {
  ix <- unname(cells_45[[group]])
  v  <- c(1, DEI, FT, DEI * FT)
  cf <- if (role == "HR") cf_hr else cf_eng
  V  <- if (role == "HR") V_hr  else V_eng
  list(sum(cf[ix] * v),
       sqrt(c(v %*% V[ix, ix] %*% v)))
}, by = .(role, group, DEI, FT)]
plot_dt[, ':='(lwr = est - 1.96 * se, upr = est + 1.96 * se)]
plot_dt[, FT_label := factor(FT, levels = c(0, 1),
                              labels = c("Firm does NOT target URM",
                                         "Firm targets URM"))]
plot_dt[, group := factor(group, levels = c(maj_lbl, min_lbl))]
plot_dt[, role := factor(role, levels = c("HR", "Eng"))]

y_lim <- range(c(plot_dt$lwr, plot_dt$upr)) * 1.05
panel_letters <- setNames(c("A", "B"), c(maj_lbl, min_lbl))

scissors_panel <- function(rl, grp) {
  d <- plot_dt[role == rl & group == grp]
  ggplot(d, aes(x = DEI, y = est, color = FT_label, fill = FT_label, linetype = FT_label)) +
    annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
    annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA) +
    geom_line(linewidth = 1) +
    annotate("text", x = 0, y = y_lim[2] * 0.93, label = "Blinding helps",
             hjust = 0.5, vjust = 1, size = 2.4, fontface = "italic", color = "darkgreen") +
    annotate("text", x = 0, y = y_lim[1] * 0.93, label = "Blinding hurts",
             hjust = 0.5, vjust = 0, size = 2.4, fontface = "italic", color = "darkred") +
    scale_color_manual(values = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_fill_manual(values  = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_linetype_manual(values = c("Firm does NOT target URM" = "dashed",
                                     "Firm targets URM"        = "solid")) +
    coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
    labs(title = paste0("Panel ", panel_letters[grp],
                        ifelse(rl == "HR", "1", "2"), ": ",
                        rl, " --- ", grp),
         x = paste0(rl, " Evaluator's Individual DEI Index (Z)"),
         y = "Effect of Blinding (Δ Overall Z-Score)",
         color = NULL, fill = NULL, linetype = NULL) +
    theme_bw(base_size = 8) +
    theme(legend.position = "bottom",
          plot.title       = element_text(size = 9, face = "bold"),
          axis.title       = element_text(size = 8),
          panel.grid.minor = element_blank())
}

scissors <- (scissors_panel("HR",  maj_lbl) | scissors_panel("HR",  min_lbl)) /
            (scissors_panel("Eng", maj_lbl) | scissors_panel("Eng", min_lbl)) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_45 <- file.path(fig_dir, "8B_45_scissors.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_45, plot = scissors, width = 8, height = 4.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\n")
cat("\\includegraphics[width=0.85\\textwidth]{", plot_file_45, "}\n", sep = "")
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize Marginal-effects ``scissors'' plot built from the §2.3 columns 3-4 (HR \\& Engineer triple with Firm Targets Fem/His) under the URM-Tech dichotomy. Top row: HR evaluators (Panels A1, B1). Bottom row: Engineer evaluators (Panels A2, B2). Lines: predicted effect of blinding on each group's overall score as a function of the rater's Individual DEI Index (Z); shaded bands are 95\\% CIs (SE clustered by respondent).\\par}\n")
cat("\\end{center}\n")

rm(dt_hr, dt_eng, build_urm, fit_simple, fit_triple, flip,
   m1, m2, m3, m4, m5, m6, all_models, coef_map, gof_custom,
   chk, nox, fe_rows, maj_lbl, min_lbl,
   cf_hr, V_hr, cf_eng, V_eng, cells_45, dei_grid, plot_dt, y_lim,
   panel_letters, scissors_panel, scissors, fig_dir, plot_file_45)
```


\clearpage
```{r perception_triple_helpers, echo = FALSE, warning = FALSE, message = FALSE}
## Shared §8 helpers: fit + flip + scissors-data + scissors-plot.

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

fit_simple_p <- function(d, factor_col) {
  fml <- as.formula(sprintf(
    "sc_overall_z ~ perc_role + i(%s, ref = 'Blind') + i(%s, perc_role, ref = 'Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    factor_col, factor_col))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)))
}

fit_triple_p <- function(d, factor_col, third_col) {
  fml <- as.formula(sprintf(
    paste0("sc_overall_z ~ perc_role + %s + I(perc_role * %s) + ",
           "i(%s, ref = 'Blind') + ",
           "i(%s, perc_role, ref = 'Blind') + ",
           "i(%s, %s, ref = 'Blind') + ",
           "i(%s, I(perc_role * %s), ref = 'Blind') + ",
           "resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income"),
    third_col, third_col,
    factor_col,
    factor_col,
    factor_col, third_col,
    factor_col, third_col))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)))
}

## TE_X(p, q) = beta_X + p*beta_{X:perc} + q*beta_{X:Z} + p*q*beta_{X:perc:Z}
## Returns long-format scissors data with role/demo/Perc/Z and 95% CI.
## Coefs that fixest dropped due to collinearity (e.g. the Eng 3-way Demo:perc:Z
## when only 1 rebel sits in nonblind) are treated as constrained-to-zero in the
## linear combination. The SE is computed from the sub-vcov of the present coefs
## only, so the rebel "Misaligned" line ends up with the same slope in Z as the
## "Aligned" line (no differential slope is identified) plus the perc shift.
build_scissors_dt <- function(model, factor_col, third_col,
                              demos, demo_lbls, role_lbl, z_grid,
                              perc_grid = c(0, 1)) {
  cf <- coef(model);  V <- vcov(model)
  rows <- list()
  for (i in seq_along(demos)) {
    nm_lvl    <- paste0(factor_col, "::", demos[i])
    nm_lvl_p  <- paste0(factor_col, "::", demos[i], ":perc_role")
    nm_lvl_z  <- paste0(factor_col, "::", demos[i], ":", third_col)
    nm_lvl_pz <- paste0(factor_col, "::", demos[i], ":I(perc_role * ", third_col, ")")
    ix      <- c(nm_lvl, nm_lvl_p, nm_lvl_z, nm_lvl_pz)
    present <- ix %in% names(cf)
    if (!present[1]) next  # no main demo coef -> nothing to plot
    cfi <- ifelse(present, as.numeric(cf[ix]), 0)
    cfi[is.na(cfi)] <- 0
    ix_pres <- ix[present]
    Vi      <- V[ix_pres, ix_pres, drop = FALSE]
    for (p in perc_grid) {
      for (q in z_grid) {
        v       <- c(1, p, q, p * q)
        v_pres  <- v[present]
        est <- sum(v * cfi)
        var_v <- as.numeric(t(v_pres) %*% Vi %*% v_pres)
        se  <- sqrt(max(0, var_v))
        rows[[length(rows) + 1L]] <- data.frame(
          role = role_lbl, demo = demo_lbls[i],
          Perc = p, Z = q, est = est,
          lwr = est - 1.96 * se, upr = est + 1.96 * se,
          stringsAsFactors = FALSE)
      }
    }
  }
  do.call(rbind, rows)
}

## Two-row scissors grid (HR top, Eng bottom). Per-row legends: each role's
## row has its own collected legend strip with role-specific labels (HR row:
## HR-aligned/misaligned-with-Eng; Eng row: Eng-aligned/misaligned-with-HR).
## "Blinding Boosts/Penalizes [demographic]" annotations are panel-specific.
## y_lim from est range only with a ±2 hard cap so thin-cell CI explosions
## don't squash visible signal; ribbons that exceed get clipped by
## coord_cartesian, central est lines stay visible.
make_scissors_grid <- function(plot_dt, demo_lbls, x_lab, ncol_panels,
                               hr_low_label   = "HR who feel aligned with Eng",
                               hr_high_label  = "HR who feel highly misaligned with Eng",
                               eng_low_label  = "Eng who feel aligned with HR",
                               eng_high_label = "Eng who feel highly misaligned with HR") {
  plot_dt <- as.data.frame(plot_dt)
  plot_dt$role <- factor(plot_dt$role, levels = c("HR", "Eng"))
  plot_dt$demo <- factor(plot_dt$demo, levels = demo_lbls)

  perc_vals <- sort(unique(plot_dt$Perc[!is.na(plot_dt$Perc)]))
  perc_low_val <- perc_vals[1]

  y_lim <- range(plot_dt$est, na.rm = TRUE) * 1.5
  y_lim[1] <- max(min(y_lim[1], -0.5), -2)
  y_lim[2] <- min(max(y_lim[2],  0.5),  2)

  panel_one <- function(rl, dm) {
    d <- plot_dt[plot_dt$role == rl & plot_dt$demo == dm, ]
    if (rl == "HR") {
      low_lab    <- hr_low_label
      high_lab   <- hr_high_label
      high_color <- "steelblue"
    } else {
      low_lab    <- eng_low_label
      high_lab   <- eng_high_label
      high_color <- "indianred"
    }
    d$bucket <- factor(
      ifelse(d$Perc == perc_low_val, low_lab, high_lab),
      levels = c(low_lab, high_lab))
    bcol <- setNames(c("gray40", high_color), c(low_lab, high_lab))
    blty <- setNames(c("dashed", "solid"),    c(low_lab, high_lab))

    ggplot(d, aes(x = Z, y = est, color = bucket, fill = bucket, linetype = bucket)) +
      annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
      annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
      geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA, na.rm = TRUE) +
      geom_line(linewidth = 0.7, na.rm = TRUE) +
      annotate("text", x = 0, y = y_lim[2] * 0.93, label = paste0("Blinding Boosts ", dm),
               hjust = 0.5, vjust = 1, size = 1.9, fontface = "italic", color = "darkgreen") +
      annotate("text", x = 0, y = y_lim[1] * 0.93, label = paste0("Blinding Penalizes ", dm),
               hjust = 0.5, vjust = 0, size = 1.9, fontface = "italic", color = "darkred") +
      scale_color_manual(   name = NULL, values = bcol) +
      scale_fill_manual(    name = NULL, values = bcol) +
      scale_linetype_manual(name = NULL, values = blty) +
      guides(fill = "none") +
      coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
      labs(title = paste0(rl, " --- ", dm),
           x = x_lab, y = "Effect of Blinding (Z)") +
      theme_bw(base_size = 7) +
      theme(legend.position  = "bottom",
            plot.title       = element_text(size = 7.5, face = "bold"),
            axis.title       = element_text(size = 6.5),
            axis.text        = element_text(size = 5.5),
            panel.grid.minor = element_blank())
  }

  hr_panels  <- lapply(demo_lbls, function(dm) panel_one("HR",  dm))
  eng_panels <- lapply(demo_lbls, function(dm) panel_one("Eng", dm))

  hr_grid  <- wrap_plots(hr_panels,  ncol = ncol_panels) +
              plot_layout(guides = "collect") &
              theme(legend.position = "bottom")
  eng_grid <- wrap_plots(eng_panels, ncol = ncol_panels) +
              plot_layout(guides = "collect") &
              theme(legend.position = "bottom")

  hr_grid / eng_grid
}
```
# Inter-Departmental Backlash and Compensation: Signed Directional Index

\textit{Spec.} Triple-interaction model with a \textbf{signed, DEI-specific, directional} perception index per role: positive end captures the role-appropriate ``misalignment in the bad direction'' (HR overreach for Eng; Eng undercare for HR); negative end captures the opposite direction. Both directions are continuous, not thresholded.

\textit{Survey directional structure (used directly).} The multi-select options \texttt{aligndiff\{role\}\_1..6} record which DEI dimensions the respondent flagged, and the items themselves are directional:
\begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{1pt}\setlength\partopsep{0pt}
  \item Options 1 / 4: counterpart places \emph{higher} priority on gender / racial diversity (rebellion-relevant for Eng; over-care-relevant for HR).
  \item Options 2 / 5: counterpart places \emph{lower} priority on gender / racial diversity (under-care-relevant for HR; opposite-direction signal for Eng).
  \item Options 3 / 6: counterpart places priority on \emph{different} groups (no direction --- ignored here).
\end{itemize}

\textit{Index construction} (per role; respondent-level then merged back):
\begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{1pt}\setlength\partopsep{0pt}
  \item \textbf{Eng (HR Overreach direction).} Likert: \texttt{s5\_hr\_influence} (1--4, ``to what extent does HR push DEI in hiring''; higher = more push). Directional count: $(\texttt{aligndiffeng}_1 + \texttt{aligndiffeng}_4) - (\texttt{aligndiffeng}_2 + \texttt{aligndiffeng}_5)$ (positive = HR cares more on race/gender DEI; negative = HR cares less). Composite: \texttt{eng\_dir = s5\_hr\_influence + 0.5 $\cdot$ directional\_count}, then z-scored within Eng.
  \item \textbf{HR (Eng Undercare direction).} Likert: \texttt{-s5\_engineer\_care} (negated 0--4 ``to what extent does Eng prioritize DEI''; higher negated = Eng cares less). Directional count: $(\texttt{aligndiffhr}_2 + \texttt{aligndiffhr}_5) - (\texttt{aligndiffhr}_1 + \texttt{aligndiffhr}_4)$ (positive = Eng cares less on race/gender DEI; negative = Eng cares more). Composite: \texttt{hr\_dir = -s5\_engineer\_care + 0.5 $\cdot$ directional\_count}, then z-scored within HR.
  \item \texttt{misalign\_z} = \texttt{eng\_dir\_z} for Eng rows / \texttt{hr\_dir\_z} for HR rows, used as \texttt{perc\_role} in the regressions. Sample inclusion: drop only respondents NA on the Likert anchor (\texttt{s5\_hr\_influence} for Eng / \texttt{s5\_engineer\_care} for HR).
\end{itemize}

\textbf{Substantive interpretation.} \texttt{perc\_role} $> 0$ = ``rebellion conditions'' for Eng / ``compensation conditions'' for HR; \texttt{perc\_role} $< 0$ = the opposite direction (Eng who think HR underreaches; HR who think Eng overcares). Triple-interaction slopes can therefore be read as: \emph{how does the effect of blinding on group X change as the rater moves from ``counterpart cares too little on DEI'' to ``counterpart cares too much on DEI''?}

```{r perception_dir_data, echo = FALSE, warning = FALSE, message = FALSE}
## §11: signed directional misalignment index.
extra_perc <- c("s5_view_align", "s5_view_aligndiffeng", "s5_view_aligndiffhr",
                "s5_hr_influence", "s5_engineer_care",
                grep("^aligndiff(hr|eng)_", names(firm_dt), value = TRUE))
extra_perc <- intersect(extra_perc, names(firm_dt))

fld <- merge(firm_long_dt,
             firm_dt[, c("responseid", extra_perc), with = FALSE],
             by = "responseid", all.x = TRUE)

fld[, urm_axis_blind := fcase(
       treat == "blind",                                                            "Blind",
       treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
       treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
       treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
       default = NA_character_)]
fld[, urm_axis_blind := factor(urm_axis_blind,
       levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
fld[, urm_tech_blind := fcase(
       treat == "blind",                    "Blind",
       treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
       treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
       default = NA_character_)]
fld[, urm_tech_blind := factor(urm_tech_blind,
       levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
fld[, race_gender := factor(race_gender,
       levels = c("Blind", "White_Male", "White_Female",
                  "Asian_Male", "Asian_Female",
                  "Hispanic_Male", "Hispanic_Female"))]

resp_dt <- unique(fld[, c("responseid", "role", extra_perc), with = FALSE])

## Cast to plain numeric.
for (col in extra_perc) {
  if (col %in% names(resp_dt)) {
    set(resp_dt, j = col, value = suppressWarnings(as.numeric(resp_dt[[col]])))
  }
}

## Defensive 99 -> NA on the Likert items used in the index.
for (col in c("s5_hr_influence", "s5_engineer_care", "s5_view_align")) {
  if (col %in% names(resp_dt)) {
    resp_dt[get(col) == 99, (col) := NA_real_]
  }
}

z <- function(x) {
  if (sum(!is.na(x)) < 2) return(rep(NA_real_, length(x)))
  mu <- mean(x, na.rm = TRUE); sg <- sd(x, na.rm = TRUE)
  if (!is.finite(sg) || sg == 0) return(rep(0, length(x)))
  (x - mu) / sg
}

## Eng HR-Overreach direction:
##   Likert (s5_hr_influence) + 0.5 * (gender+racial overreach - underreach)
resp_dt[role == "Eng",
        eng_dir_count := (aligndiffeng_1 + aligndiffeng_4) -
                         (aligndiffeng_2 + aligndiffeng_5)]
resp_dt[role == "Eng",
        eng_dir_raw := s5_hr_influence + 0.5 * eng_dir_count]
resp_dt[role == "Eng", eng_dir_z := z(eng_dir_raw)]

## HR Eng-Undercare direction:
##   negated Likert (-s5_engineer_care) + 0.5 * (gender+racial undercare - overcare)
resp_dt[role == "HR",
        hr_dir_count := (aligndiffhr_2 + aligndiffhr_5) -
                        (aligndiffhr_1 + aligndiffhr_4)]
resp_dt[role == "HR",
        hr_dir_raw := -s5_engineer_care + 0.5 * hr_dir_count]
resp_dt[role == "HR", hr_dir_z := z(hr_dir_raw)]

## Stitch into a single misalign_z column.
resp_dt[, misalign_z := NA_real_]
resp_dt[role == "Eng", misalign_z := eng_dir_z]
resp_dt[role == "HR",  misalign_z := hr_dir_z]

fld <- merge(fld, resp_dt[, .(responseid, misalign_z)],
             by = "responseid", all.x = TRUE)

dt_hr  <- fld[role == "HR"  & !is.na(misalign_z)]
dt_eng <- fld[role == "Eng" & !is.na(misalign_z)]
dt_hr [, perc_role := misalign_z]
dt_eng[, perc_role := misalign_z]

n_h_idx <- uniqueN(dt_hr$responseid)
n_e_idx <- uniqueN(dt_eng$responseid)
```


\clearpage
## By Six Demographics

```{r perception_dir_rg, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
demos     <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female")
demo_lbls <- c("White Male", "White Female", "Asian Male", "Asian Female",
               "Hispanic Male", "Hispanic Female")
fcol      <- "race_gender"

m1 <- flip(fit_simple_p (dt_hr,  fcol))
m2 <- flip(fit_simple_p (dt_eng, fcol))
m3 <- flip(fit_triple_p (dt_hr,  fcol, "dei_index_z"))
m4 <- flip(fit_triple_p (dt_eng, fcol, "dei_index_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4)

coef_map <- c(
  setNames(demo_lbls, paste0(fcol, "::", demos)),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z)"),
           paste0(fcol, "::", demos, ":perc_role")),
  setNames(paste0(demo_lbls, " $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":dei_index_z")),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z) $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":I(perc_role * dei_index_z)"))
)

gof_custom <- tribble(
  ~raw,                 ~clean,                  ~fmt,
  "nobs",               "Observations",          0,
  "r.squared",          "R$^2$",                 3,
  "adj.r.squared",      "Adj. R$^2$",            3,
  "r2.within",          "R$^2$ Within",          3,
  "r2.within.adjusted", "Adj. R$^2$ Within",     3
)
chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
attr(fe_rows, "position") <- 25:28

modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Simple Dir Het." = 2,
                     "Triple: Dir x Own DEI" = 2)) %>%
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(18, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\midrule") %>%
  row_spec(28, extra_latex_after = "\\midrule") %>%
  footnote(general = sprintf(
            "Dir Idx (Z) = signed directional misalignment index: for Eng, HR Overreach direction (Likert + 0.5 times signed multi-select); for HR, Eng Undercare direction. Z-scored within role. Positive = rebellion conditions for Eng / compensation conditions for HR; negative = opposite. n = %d HR, %d Eng. Coefs flipped post-fit so positive = effect of blinding raises the score. Two-way cluster on responseid and resume index.",
            n_h_idx, n_e_idx),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

z_grid <- seq(-2, 2, length.out = 41)
df_dei <- rbind(
  build_scissors_dt(m3, fcol, "dei_index_z", demos, demo_lbls, "HR",  z_grid, perc_grid = c(-1, 1)),
  build_scissors_dt(m4, fcol, "dei_index_z", demos, demo_lbls, "Eng", z_grid, perc_grid = c(-1, 1)))
fig_dei <- make_scissors_grid(df_dei, demo_lbls, "Own DEI Index (Z)",
                              ncol_panels = 6,
                              hr_low_label   = "HR perceives Eng overcaring on DEI",
                              hr_high_label  = "HR perceives Eng undercaring on DEI",
                              eng_low_label  = "Eng perceives HR underreaching on DEI",
                              eng_high_label = "Eng perceives HR overreaching on DEI")

fig_dir <- here("2_Reports", "figures")
plot_file_dei <- file.path(fig_dir, "8B_perception_dir_dei_rg.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_dei, plot = fig_dei, width = 14, height = 6.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\\textbf{Dir Idx (signed) $\\times$ Own DEI Index --- Per Race-Gender (6 cells)}\\par\\vspace{0.1em}\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file_dei, "}\\par\\vspace{0.1em}\n", sep = "")
cat("{\\raggedright\\scriptsize Top row: HR (high Dir = perceives Eng undercare = compensation conditions). Bottom row: Eng (high Dir = perceives HR overreach = rebellion conditions). Bands = 95\\% CI.\\par}\n")
cat("\\end{center}\n")

rm(m1, m2, m3, m4, all_models, demos, demo_lbls, fcol,
   coef_map, gof_custom, chk, nox, fe_rows,
   z_grid, df_dei, fig_dei,
   plot_file_dei, fig_dir)
```


\clearpage
## By Trichotomy (Majority vs Gender Minority vs Racial Minority)

```{r perception_dir_axis, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
demos     <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
demo_lbls <- c("Male (NH)", "Female (NH)", "Hispanic")
fcol      <- "urm_axis_blind"

m1 <- flip(fit_simple_p (dt_hr,  fcol))
m2 <- flip(fit_simple_p (dt_eng, fcol))
m3 <- flip(fit_triple_p (dt_hr,  fcol, "dei_index_z"))
m4 <- flip(fit_triple_p (dt_eng, fcol, "dei_index_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4)

coef_map <- c(
  setNames(demo_lbls, paste0(fcol, "::", demos)),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z)"),
           paste0(fcol, "::", demos, ":perc_role")),
  setNames(paste0(demo_lbls, " $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":dei_index_z")),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z) $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":I(perc_role * dei_index_z)"))
)

gof_custom <- tribble(
  ~raw,                 ~clean,                  ~fmt,
  "nobs",               "Observations",          0,
  "r.squared",          "R$^2$",                 3,
  "adj.r.squared",      "Adj. R$^2$",            3,
  "r2.within",          "R$^2$ Within",          3,
  "r2.within.adjusted", "Adj. R$^2$ Within",     3
)
chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
attr(fe_rows, "position") <- 13:16

modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  add_header_above(c(" " = 1,
                     "Simple Dir Het." = 2,
                     "Triple: Dir x Own DEI" = 2)) %>%
  row_spec(3,  extra_latex_after = "\\hdashline") %>%
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(9,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(16, extra_latex_after = "\\midrule") %>%
  footnote(general = sprintf(
            "Dir Idx (Z) = signed directional misalignment index. n = %d HR, %d Eng. Coefs flipped post-fit so positive = effect of blinding raises the score. Two-way cluster on responseid and resume index.",
            n_h_idx, n_e_idx),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

z_grid <- seq(-2, 2, length.out = 41)
df_dei <- rbind(
  build_scissors_dt(m3, fcol, "dei_index_z", demos, demo_lbls, "HR",  z_grid, perc_grid = c(-1, 1)),
  build_scissors_dt(m4, fcol, "dei_index_z", demos, demo_lbls, "Eng", z_grid, perc_grid = c(-1, 1)))
fig_dei <- make_scissors_grid(df_dei, demo_lbls, "Own DEI Index (Z)",
                              ncol_panels = 3,
                              hr_low_label   = "HR perceives Eng overcaring on DEI",
                              hr_high_label  = "HR perceives Eng undercaring on DEI",
                              eng_low_label  = "Eng perceives HR underreaching on DEI",
                              eng_high_label = "Eng perceives HR overreaching on DEI")

fig_dir <- here("2_Reports", "figures")
plot_file_dei <- file.path(fig_dir, "8B_perception_dir_dei_axis.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_dei, plot = fig_dei, width = 11, height = 6.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\\textbf{Dir Idx (signed) $\\times$ Own DEI Index --- URM-Axis Trichotomy}\\par\\vspace{0.1em}\n")
cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_dei, "}\\par\\vspace{0.1em}\n", sep = "")
cat("{\\raggedright\\scriptsize Top row: HR (high Dir = compensation conditions). Bottom row: Eng (high Dir = rebellion conditions). Bands = 95\\% CI.\\par}\n")
cat("\\end{center}\n")

rm(m1, m2, m3, m4, all_models, demos, demo_lbls, fcol,
   coef_map, gof_custom, chk, nox, fe_rows,
   z_grid, df_dei, fig_dei,
   plot_file_dei, fig_dir)
```


\clearpage
## By Dichotomy (Majority vs Minority)

```{r perception_dir_utech, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
demos     <- c("Nonblind_NonURM", "Nonblind_URM")
demo_lbls <- c("Majority", "URM in Tech")
fcol      <- "urm_tech_blind"

m1 <- flip(fit_simple_p (dt_hr,  fcol))
m2 <- flip(fit_simple_p (dt_eng, fcol))
m3 <- flip(fit_triple_p (dt_hr,  fcol, "dei_index_z"))
m4 <- flip(fit_triple_p (dt_eng, fcol, "dei_index_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4)

coef_map <- c(
  setNames(demo_lbls, paste0(fcol, "::", demos)),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z)"),
           paste0(fcol, "::", demos, ":perc_role")),
  setNames(paste0(demo_lbls, " $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":dei_index_z")),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z) $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":I(perc_role * dei_index_z)"))
)

gof_custom <- tribble(
  ~raw,                 ~clean,                  ~fmt,
  "nobs",               "Observations",          0,
  "r.squared",          "R$^2$",                 3,
  "adj.r.squared",      "Adj. R$^2$",            3,
  "r2.within",          "R$^2$ Within",          3,
  "r2.within.adjusted", "Adj. R$^2$ Within",     3
)
chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
attr(fe_rows, "position") <- 9:12

modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 9) %>%
  add_header_above(c(" " = 1,
                     "Simple Dir Het." = 2,
                     "Triple: Dir x Own DEI" = 2)) %>%
  row_spec(2,  extra_latex_after = "\\hdashline") %>%
  row_spec(4,  extra_latex_after = "\\hdashline") %>%
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(8,  extra_latex_after = "\\midrule") %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  footnote(general = sprintf(
            "Dir Idx (Z) = signed directional misalignment index. n = %d HR, %d Eng. Coefs flipped post-fit so positive = effect of blinding raises the score. Two-way cluster on responseid and resume index.",
            n_h_idx, n_e_idx),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

z_grid <- seq(-2, 2, length.out = 41)
df_dei <- rbind(
  build_scissors_dt(m3, fcol, "dei_index_z", demos, demo_lbls, "HR",  z_grid, perc_grid = c(-1, 1)),
  build_scissors_dt(m4, fcol, "dei_index_z", demos, demo_lbls, "Eng", z_grid, perc_grid = c(-1, 1)))
fig_dei <- make_scissors_grid(df_dei, demo_lbls, "Own DEI Index (Z)",
                              ncol_panels = 2,
                              hr_low_label   = "HR perceives Eng overcaring on DEI",
                              hr_high_label  = "HR perceives Eng undercaring on DEI",
                              eng_low_label  = "Eng perceives HR underreaching on DEI",
                              eng_high_label = "Eng perceives HR overreaching on DEI")

fig_dir <- here("2_Reports", "figures")
plot_file_dei <- file.path(fig_dir, "8B_perception_dir_dei_utech.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_dei, plot = fig_dei, width = 8, height = 6.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\\textbf{Dir Idx (signed) $\\times$ Own DEI Index --- URM-Tech Dichotomy}\\par\\vspace{0.1em}\n")
cat("\\includegraphics[width=0.75\\textwidth]{", plot_file_dei, "}\\par\\vspace{0.1em}\n", sep = "")
cat("{\\raggedright\\scriptsize Top row: HR (high Dir = compensation conditions). Bottom row: Eng (high Dir = rebellion conditions). Bands = 95\\% CI.\\par}\n")
cat("\\end{center}\n")

rm(m1, m2, m3, m4, all_models, demos, demo_lbls, fcol,
   coef_map, gof_custom, chk, nox, fe_rows,
   z_grid, df_dei, fig_dei,
   plot_file_dei, fig_dir,
   fld, dt_hr, dt_eng, resp_dt, eng_items, hr_items, extra_perc,
   n_h_idx, n_e_idx, z,
   flip, fit_simple_p, fit_triple_p, build_scissors_dt, make_scissors_grid)
```

\newpage
# Treatment Effect on Productivity of Hired (The Efficiency Myth)

\vspace{-0.4em}

\textbf{Signal Extraction Remains Flat (S5.1.):} Removing demographic information (or noise) does \emph{not} meaningfully improve their ability to identify top ability candidates.

\textbf{Quality of Hires Does Not Improve (S5.2.):} Blind hiring has a \emph{null} effect on the actual coding quality of the hired cohort.
\vspace{-1em}

## Does Blinding Lead to More Accurate Coding Skill Evaluations?

\textcolor{blue}{\textbf{Specification}}:
\vspace{-0.7em}
$$
\text{Hiring Evaluation Score (Z)} \sim \text{True Coding Ability (Z)} \times \mathbbm{1}[\text{Blind arm}] \mid \text{Respondent FE} + \text{Display Position FE}.
$$
\vspace{-1.4em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item $H_0\!: \beta = 0$ --- the evaluator extracts \emph{no signal} from true coding ability.
    \item $H_0\!: \beta = 1$ --- the evaluator is \emph{perfectly calibrated}: a $1$ SD rise in true ability produces exactly a $1$ SD rise in the rating, with no shrinkage.
\end{itemize}

```{r blind_hiring_signal_extraction, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Pooled z-score of the lab coding score (constant within resume_index)
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]

## Two pooled interacted regressions --- one per role. Since treat is
## between-respondent, responseid FE absorbs the main effect of treat but
## leaves both the main slope on true_coding_z (identified from within-
## respondent variation, by definition the nonblind arm's slope since
## nonblind is the reference) and the interaction slope identifiable.
m_hr  <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))

## Extract arm-specific slopes, SEs, and the four tests (H0: beta = 0 / 1
## for each arm) from a single pooled model. beta_nonblind = main coef;
## beta_blind = main + interaction; SE(beta_blind) via linear-combination
## formula using the full vcov matrix.
extract_stats <- function(m) {
  ct    <- coeftable(m)
  V     <- vcov(m)
  main_name <- "true_coding_z"
  int_name  <- "true_coding_z:treat::blind"

  b_main <- ct[main_name, "Estimate"]
  s_main <- ct[main_name, "Std. Error"]
  b_int  <- ct[int_name,  "Estimate"]
  s_int  <- ct[int_name,  "Std. Error"]
  cov_mi <- V[main_name, int_name]

  b_nb <- b_main
  s_nb <- s_main
  b_b  <- b_main + b_int
  s_b  <- sqrt(s_main^2 + s_int^2 + 2 * cov_mi)

  pval <- function(t) 2 * (1 - pnorm(abs(t)))
  p_nb_0 <- pval(b_nb / s_nb)
  p_nb_1 <- pval((b_nb - 1) / s_nb)
  p_b_0  <- pval(b_b  / s_b)
  p_b_1  <- pval((b_b  - 1) / s_b)
  ## H0: beta_blind = beta_nonblind is the same as H0: beta_interaction = 0,
  ## so we read its p-value directly off the interaction coefficient.
  p_eq   <- ct[int_name, 4]

  fs <- fitstat(m, c("r2", "ar2"), simplify = TRUE)
  list(b_nb = unname(b_nb), s_nb = unname(s_nb),
       b_b  = unname(b_b),  s_b  = unname(s_b),
       p_nb_0 = p_nb_0, p_nb_1 = p_nb_1,
       p_b_0  = p_b_0,  p_b_1  = p_b_1,
       p_eq   = unname(p_eq),
       n = m$nobs, r2 = unname(fs["r2"]), ar2 = unname(fs["ar2"]))
}

s_hr  <- extract_stats(m_hr)
s_eng <- extract_stats(m_eng)

## Formatting helpers.
sig_stars <- function(p) {
  if (is.na(p))        ""
  else if (p < 0.01)   "***"
  else if (p < 0.05)   "**"
  else if (p < 0.10)   "*"
  else                 ""
}
fmt_p <- function(p) {
  if (is.na(p)) return("")
  pstr <- if (p < 0.001) "$<\\!0.001$" else sprintf("%.3f", p)
  paste0("p = ", pstr, sig_stars(p))
}

chk <- "\\checkmark"
nox <- "$\\times$"

cell_col <- function(s) c(
  sprintf("%.3f~(%.3f)", s$b_nb, s$s_nb),
  sprintf("%.3f~(%.3f)", s$b_b,  s$s_b),
  format(s$n,   big.mark = ","),
  sprintf("%.3f", s$r2),
  sprintf("%.3f", s$ar2),
  nox, chk, chk, nox
)

tbl <- data.frame(
  lbl = c("$\\hat\\beta_{\\text{nonblind}}$ (slope, nonblind arm)",
          "$\\hat\\beta_{\\text{blind}}$ (slope, blind arm)",
          "Observations",
          "$R^2$",
          "Adj. $R^2$",
          "Resume (Content) FE",
          "Display Position FE",
          "Respondent FE",
          "Respondent Characteristics"),
  HR  = cell_col(s_hr),
  Eng = cell_col(s_eng),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
names(tbl) <- c(" ", "HR", "Engineer")

## Build the plot and save it to disk so we can include it via
## \includegraphics inside a LaTeX minipage layout.
plot_data <- data.frame(
  role = factor(c("HR", "HR", "Engineer", "Engineer"),
                levels = c("HR", "Engineer")),
  arm  = factor(c("Nonblind", "Blind", "Nonblind", "Blind"),
                levels = c("Nonblind", "Blind")),
  est  = c(s_hr$b_nb,  s_hr$b_b,  s_eng$b_nb, s_eng$b_b),
  se   = c(s_hr$s_nb,  s_hr$s_b,  s_eng$s_nb, s_eng$s_b)
)
plot_data$ci_lo <- plot_data$est - 1.96 * plot_data$se
plot_data$ci_hi <- plot_data$est + 1.96 * plot_data$se

p_signal <- ggplot(plot_data, aes(x = est, y = arm, color = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.2, linewidth = 0.8) +
  geom_point(size = 3) +
  facet_wrap(~ role, ncol = 1, strip.position = "left") +
  scale_x_continuous(limits = c(-0.05, 1.1), breaks = seq(0, 1, 0.2)) +
  scale_color_manual(values = c("Nonblind" = "#d62728", "Blind" = "#1f77b4")) +
  labs(x = expression(hat(beta)*": slope of evaluator rating on true coding ability"),
       y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0, face = "bold"))

## Save plot to disk so we can include it via \includegraphics inside a
## LaTeX minipage (table on left, plot on right).
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file <- file.path(fig_dir, "8B_signal_extraction.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file, plot = p_signal, width = 4.5, height = 2.6, device = "pdf")
))

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[c]{0.50\\textwidth}\n")
cat("\\centering\n")
cat("{\\fontsize{7}{9}\\selectfont\n")

## Plain kable + row_spec (no kable_styling, since kable_styling adds an
## inner \\begin{table} wrapper that LaTeX rejects inside a minipage).
print(
  kable(tbl, format = "latex", booktabs = TRUE, escape = FALSE,
        align = "lcc", row.names = FALSE) %>%
    row_spec(2, extra_latex_after = "\\midrule") %>%
    row_spec(5, extra_latex_after = "\\midrule")
)

cat("}\n")
cat("\\end{minipage}%\n")
cat("\\begin{minipage}[c]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file, "}\n", sep = "")
cat("\\end{minipage}\n")

cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{0.98\\textwidth}\\scriptsize\n")
cat("Cluster-robust standard errors (by respondent) shown in parentheses next to each $\\hat\\beta$.\\\\\n")
cat("Stars on p-values: * $p<0.10$, ** $p<0.05$, *** $p<0.01$.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

rm(m_hr, m_eng, s_hr, s_eng,
   extract_stats, sig_stars, fmt_p, cell_col,
   chk, nox, tbl, plot_data, p_signal, plot_file, fig_dir)
```

## Does Blinding Lead to Selection of More Productive Coders?


```{r blind_hiring_coding_quality, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

# ==============================================================================
# HELPER: Dynamic standardization relative to nonblind group at each k
# ==============================================================================
get_avg_coding_score <- function(role_filter, treat_filter, k, 
                                  pass_var_prefix, data) {
  col <- paste0(pass_var_prefix, k)
  d   <- data[role == role_filter & treat == treat_filter & get(col) == 1]
  if (nrow(d) == 0) return(NA_real_)
  mean(d$overall_score, na.rm = TRUE)
}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# ==============================================================================
results_list <- list()

for (k in 1:18) {

  # --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]

  # Dynamic standardization: relative to nonblind mean/sd at this k
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_hr)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }

  # --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]

  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_eng)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

# ==============================================================================
# PLOT
# ==============================================================================
ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.3, 0.3)) +
  labs(
    subtitle = paste("Treatment effect on true productivity measure (coding lab evaluation)",
                     "of selected candidates, standardized relative to selected candidates",
                     "under no blinding at each k"),
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Positive = blind hiring selects candidates with higher actual coding scores.\nSignificance: * p<0.10, ** p<0.05, *** p<0.01"
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )

rm(results_list, dt_plot, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```


\clearpage
## Does Blinding's Productivity Effect Differ by Evaluator's DEI Orientation?

Same per-$k$ loop as §4.2, but the regression interacts \texttt{treat} with the respondent's z-scored DEI index (\texttt{dei\_index\_z}, the canonical Individual DEI Index from §2). The treatment effect at each $k$ is then evaluated at low ($-1$ SD), mid ($0$), and high ($+1$ SD) of the DEI index distribution via the linear combination $\hat\beta_{\text{blind}} + q\hat\beta_{\text{blind}\times\text{DEI}}$, with 95\% CIs from $\sqrt{v'\Sigma v}$ where $v = (1, q)$. The substantive question: do pro-DEI respondents pick more productive candidates under blinding than anti-DEI respondents do?

```{r blind_hiring_coding_quality_by_dei, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=8}

results_list <- list()
dei_pts <- c(-1, 0, 1)
dei_lbl <- c("Low DEI (-1 SD)", "Mid DEI (0)", "High DEI (+1 SD)")

for (k in 1:18) {

  ## --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * dei_index_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      cf <- coef(m_hr); V <- vcov(m_hr)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("dei_index_z:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(dei_pts)) {
          q <- dei_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "HR Stage", k = k, dei_level = dei_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se,
            p_val = 2 * pnorm(-abs(est / se))
          )
        }
      }
    }, error = function(e) {})
  }

  ## --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]
  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * dei_index_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      cf <- coef(m_eng); V <- vcov(m_eng)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("dei_index_z:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(dei_pts)) {
          q <- dei_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "Engineer Stage", k = k, dei_level = dei_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se,
            p_val = 2 * pnorm(-abs(est / se))
          )
        }
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, dei_level := factor(dei_level, levels = dei_lbl)]

ggplot(dt_plot, aes(x = k, y = estimate, color = dei_level, fill = dei_level)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.18, color = NA) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.3) +
  facet_grid(dei_level ~ Stage) +
  scale_color_manual(values = c("Low DEI (-1 SD)"  = "#D9534F",
                                "Mid DEI (0)"      = "gray40",
                                "High DEI (+1 SD)" = "#4C72B0"),
                     guide = "none") +
  scale_fill_manual( values = c("Low DEI (-1 SD)"  = "#D9534F",
                                "Mid DEI (0)"      = "gray40",
                                "High DEI (+1 SD)" = "#4C72B0"),
                     guide = "none") +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.3, 0.3)) +
  labs(
    subtitle = "TE on hired candidates' actual coding score, by respondent's DEI index level",
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Rows: TE evaluated at -1, 0, +1 SD of the within-role z-scored DEI index. Columns: HR vs Engineer. Bands: 95% CI from the linear combination of treat::blind and treat::blind:dei_index_z."
  ) +
  theme_bw() +
  theme(
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 11),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )

rm(results_list, dt_plot, dei_pts, dei_lbl, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   cf, V, idx_main, idx_int, est, se, q, v, j)
```

```{r blind_hiring_demographic_selection, eval = FALSE, echo=FALSE, fig.width=12, fig.height=10}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# LHS: hr_passk / eng_topk (0/1 selected)
# RHS: race_gender with "Blind" as reference, then flip signs
# ==============================================================================
results_all <- list()

demo_labels <- c("White_Male", "White_Female", "Asian_Male",
                 "Asian_Female", "Hispanic_Male", "Hispanic_Female")

for (k in 1:18) {

  hr_col  <- paste0("hr_pass", k)
  eng_col <- paste0("eng_top", k)

  # --- HR ---
  tryCatch({
    m_hr <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(hr_col,
        " ~ i(race_gender, ref = 'Blind') |
          q_version + resp_gender + resp_race + s2_educ + s2_income")),
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_hr)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})

  # --- Engineer ---
  tryCatch({
    m_eng <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(eng_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          q_version + resp_gender + resp_race + s2_educ + s2_income +
          resp_python + resp_java")),
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_eng)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})
}

# ==============================================================================
# ASSEMBLE AND PLOT
# ==============================================================================
dt_plot <- rbindlist(results_all)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, demo  := factor(demo,  levels = c("White Male",    "White Female",
                                             "Asian Male",    "Asian Female",
                                             "Hispanic Male", "Hispanic Female"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]
dt_plot[, star_y := ifelse(estimate >= 0,
                            ci_high + 0.005,
                            ci_low  - 0.005)]

ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.6, size = 0.4, fatten = 3) +
  geom_text(aes(y = star_y, label = sig_stars),
            vjust = ifelse(dt_plot$estimate >= 0, 0, 1),
            size = 3, color = "black", show.legend = FALSE) +
  facet_grid(demo ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = seq(1, 18, by = 3),
                     name   = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.20))) +
  labs(
    title    = "Effect of Blind Hiring on Selection Probability by Demographic Group",
    subtitle = paste("Blinding effect = -(effect of revealing identity vs blind).",
                     "Positive = more likely selected under blinding."),
    y        = "Blinding Effect on Selection Probability",
    color    = "Evaluator Role",
    caption  = "Significance: * p<0.10, ** p<0.05, *** p<0.01. Base group: Blind resumes."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10),
    legend.text        = element_text(size = 9),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    strip.text.y       = element_text(angle = 0),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0),
    panel.spacing      = unit(0.4, "lines")
  )

rm(results_all, dt_plot, demo_labels, dg, k,
   hr_col, eng_col, m_hr, m_eng, ct,
   est, se, p_val, coef_nm)
```




