---
title: "Stage-by-Stage Impact of Blind Hiring"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}  
  - \usepackage{float}  
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- +++++ ++++++ ++++++ Part 5-2: Analysis (Stage-by-Stage Impact of Blind Hiring) +++++ ++++++ ++++++ -->


# Impact of Blind Hiring on Evaluations

## On All Dimensions (Z)

\textcolor{blue}{\textbf{Takeaway}}: Our experiment demonstrates that withholding demographic information \emph{reshuffles} candidates' relative evaluations across stages. In the HR resume-screening stage, Hispanic Male candidates are the largest losers: under blinding, their overall evaluation scores fall by 11.8\% of a standard deviation relative to when their identity is revealed (significant at the 5\% level). In the Engineer technical evaluation stage, the largest gainers are White Male candidates, whose scores rise by 8.5\% of a SD under blinding (significant at the 1\% level), while most other demographic groups lose ground. A standard caveat applies: because hiring is often an ordinal ranking problem --- where one candidate's gain necessarily corresponds to another candidate's lost opportunity --- the absence of statistical significance on a given row does not mean the corresponding group is unaffected by blinding.

```{r blind_hiring_treatment_effects_demo, echo = FALSE, results = 'asis'}
## Treatment Effects of Blind Hiring
## Reference: Blind resumes (baseline)
## Shows effect of revealing each demographic vs. keeping it blind

## HR Models (with sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_hr_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do_bythree + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))
names(models_hr_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

## Engineer Models (no sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_eng_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do_bythree + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))
names(models_eng_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

## Flip coefficient signs so a positive coefficient = effect of blinding.
flip_coef_signs <- function(model) {
  model$coefficients <- -1 * model$coefficients
  return(model)
}
models_hr_blind  <- lapply(models_hr_blind,  flip_coef_signs)
models_eng_blind <- lapply(models_eng_blind, flip_coef_signs)

## Coefficient map - ONLY show demographic coefficients
coef_map_blind <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female"
)

## Custom gof_map
gof_custom_blind <- tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "Observations",   0,
  "r.squared", "R2",             3
)

## FE / controls footer rows (displayed inside the table). Respondent FE and
## Respondent Characteristics are placed adjacent to make the contrast visible:
## we do NOT soak up respondent heterogeneity with a fixed effect, but we DO
## include respondent demographic controls as absorbing FEs + age polynomial.
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows_hr <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_hr) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

fe_rows_eng <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_eng) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel A: HR}\n\n")

modelsummary(
  models_hr_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_hr,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7)

cat("\\end{minipage}\n")
cat("\\hfill\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel B: Engineer}\n\n")

modelsummary(
  models_eng_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_eng,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7)

cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

cat("\\vspace{-0.2cm}\n\n")
cat("\\scriptsize\n\n")
cat("\\textit{Standard errors clustered by respondent.}\n\n")
cat("\\textit{Note on Interpreting Coefficients:} The underlying regression uses Blind resumes as the reference category, so raw coefficients capture (nonblind $-$ blind) or the effect of being blinded for each demographic on relative overall evaluation scores. We then multiply by $-1$ to report (blind $-$ nonblind), aligning the sign convention with the standard \"effect of blinding\" framing: positive $\\Rightarrow$ blinding raises the relative score for that demographic. \"Respondent Characteristics\" comprises age (with polynomial), gender, race, education, and income.\n\n")
cat("\\normalsize\n\n")

## Clean up
rm(models_hr_blind, models_eng_blind, coef_map_blind, gof_custom_blind, flip_coef_signs,
   chk, nox, fe_rows_hr, fe_rows_eng)
```


## Does Blinding Lead to More Accurate Coding Evaluations?

\textcolor{blue}{\textbf{Takeaway}}: Evaluators do extract signal about candidates' actual coding ability --- Engineers much more strongly than HR, consistent with Engineers seeing the code while HR sees only the resume. Blinding, however, does \emph{not} meaningfully change this signal-extraction ability in either role: the $\texttt{true\_coding\_z} \times \texttt{blind}$ interaction is small, negative, and statistically insignificant for both HR and Engineers. If blinding --- which in our experiment amounts to removing random, uninformative demographic noise --- improved signal-extraction ability, we would expect a positive and statistically significant interaction term. In short, blinding \emph{reshuffles} who receives high scores (Section 1.1) but does not change \emph{how well} those scores track actual coding skill.

\textcolor{blue}{\textbf{Specification}}: For each role, we fit
$$
\text{Hiring Evaluation Score (Z)} \sim \text{True Coding Ability (Z)} \times \mathbb{1}[\text{Blind}] \mid \text{Respondent FE} + \text{Display Position FE}.
$$
The main slope on True Coding Ability (Z) is the evaluator's signal sensitivity in the non-blind arm; the interaction is the shift in sensitivity under blinding. Resume-content FE is deliberately absent, because True Coding Ability (Z) is constant within a resume (one lab-measured score per resume) and a resume FE would absorb the RHS entirely.

```{r blind_hiring_signal_extraction, echo = FALSE, results = 'asis'}
## Pooled z-score of the lab coding score (constant within resume_index)
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]

## HR and Engineer, same spec
## Note: respondent-level controls (age polynomial, gender, race, educ, income)
## are all perfectly collinear with responseid FE, so they are absorbed rather
## than separately identified. We drop them from the formula to keep the
## reported FE footer honest.
m_hr_sig <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do_bythree,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))

m_eng_sig <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do_bythree,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))

models_sig <- list("HR" = m_hr_sig, "Engineer" = m_eng_sig)

coef_map_sig <- c(
  "true_coding_z"              = "True Coding Score (Z)",
  "true_coding_z:treat::blind" = "True Coding Score (Z) $\\times$ Blind"
)

gof_custom_sig <- tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "Observations",   0,
  "r.squared", "R2",             3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows_sig <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(nox, chk, chk, nox),
  c(nox, chk, chk, nox),
  stringsAsFactors = FALSE
)
names(fe_rows_sig) <- c("term", "HR", "Engineer")

cat("\\begin{table}[H]\n")
cat("\\centering\n")

modelsummary(
  models_sig,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_sig,
  gof_map = gof_custom_sig,
  add_rows = fe_rows_sig,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:70%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8)

cat("\\end{table}\n\n")

cat("\\vspace{-0.2cm}\n\n")
cat("\\scriptsize\n\n")
cat("\\textit{Standard errors clustered by respondent.}\n\n")
cat("\\textit{Note on Interpreting Coefficients:} The main slope on \"True Coding Score (Z)\" is the evaluator's signal sensitivity in the non-blind arm --- a 1 SD increase in actual coding ability maps into a $\\hat\\beta$ SD increase in the assigned coding rating. The interaction row is the shift in that sensitivity under blinding: positive $\\Rightarrow$ blinding sharpens rating-to-truth tracking, negative $\\Rightarrow$ blinding dulls it. The \"Resume (Content) FE\" row is marked as not included because $\\texttt{overall\\_score}$ is a resume-level property (one lab score per resume), so a resume-content FE would absorb the RHS and leave the main slope unidentified. \"Respondent Characteristics\" is marked as not included because respondent-level variables (age, gender, race, education, income) are all perfectly collinear with the respondent FE and therefore absorbed by it.\n\n")
cat("\\normalsize\n\n")

rm(m_hr_sig, m_eng_sig, models_sig, coef_map_sig, gof_custom_sig,
   chk, nox, fe_rows_sig)
```


\newpage
# Stage-by-Stage Impact of Blind Hiring on Coding Outcomes

```{r blind_hiring_coding_quality, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

# ==============================================================================
# HELPER: Dynamic standardization relative to nonblind group at each k
# ==============================================================================
get_avg_coding_score <- function(role_filter, treat_filter, k, 
                                  pass_var_prefix, data) {
  col <- paste0(pass_var_prefix, k)
  d   <- data[role == role_filter & treat == treat_filter & get(col) == 1]
  if (nrow(d) == 0) return(NA_real_)
  mean(d$overall_score, na.rm = TRUE)
}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# ==============================================================================
results_list <- list()

for (k in 1:18) {

  # --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]

  # Dynamic standardization: relative to nonblind mean/sd at this k
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do_bythree + q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_hr)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }

  # --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]

  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do_bythree + q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_eng)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

# ==============================================================================
# PLOT
# ==============================================================================
ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    title    = "Does Blind Hiring Select Better Coders?",
    subtitle = paste("Effect of blinding on actual coding quality of selected candidates.",
                     "Standardized relative to nonblind group at each k."),
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Positive = blind hiring selects candidates with higher actual coding scores.\nSignificance: * p<0.10, ** p<0.05, *** p<0.01"
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )

rm(results_list, dt_plot, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```

```{r blind_hiring_demographic_selection, eval = FALSE, echo=FALSE, fig.width=12, fig.height=10}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# LHS: hr_passk / eng_topk (0/1 selected)
# RHS: race_gender with "Blind" as reference, then flip signs
# ==============================================================================
results_all <- list()

demo_labels <- c("White_Male", "White_Female", "Asian_Male",
                 "Asian_Female", "Hispanic_Male", "Hispanic_Female")

for (k in 1:18) {

  hr_col  <- paste0("hr_pass", k)
  eng_col <- paste0("eng_top", k)

  # --- HR ---
  tryCatch({
    m_hr <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(hr_col,
        " ~ i(race_gender, ref = 'Blind') |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income")),
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_hr)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})

  # --- Engineer ---
  tryCatch({
    m_eng <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(eng_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          r_do_bythree + q_version + resp_gender + resp_race + s2_educ + s2_income +
          resp_python + resp_java")),
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_eng)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})
}

# ==============================================================================
# ASSEMBLE AND PLOT
# ==============================================================================
dt_plot <- rbindlist(results_all)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, demo  := factor(demo,  levels = c("White Male",    "White Female",
                                             "Asian Male",    "Asian Female",
                                             "Hispanic Male", "Hispanic Female"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]
dt_plot[, star_y := ifelse(estimate >= 0,
                            ci_high + 0.005,
                            ci_low  - 0.005)]

ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.6, size = 0.4, fatten = 3) +
  geom_text(aes(y = star_y, label = sig_stars),
            vjust = ifelse(dt_plot$estimate >= 0, 0, 1),
            size = 3, color = "black", show.legend = FALSE) +
  facet_grid(demo ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = seq(1, 18, by = 3),
                     name   = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.20))) +
  labs(
    title    = "Effect of Blind Hiring on Selection Probability by Demographic Group",
    subtitle = paste("Blinding effect = -(effect of revealing identity vs blind).",
                     "Positive = more likely selected under blinding."),
    y        = "Blinding Effect on Selection Probability",
    color    = "Evaluator Role",
    caption  = "Significance: * p<0.10, ** p<0.05, *** p<0.01. Base group: Blind resumes."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10),
    legend.text        = element_text(size = 9),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    strip.text.y       = element_text(angle = 0),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0),
    panel.spacing      = unit(0.4, "lines")
  )

rm(results_all, dt_plot, demo_labels, dg, k,
   hr_col, eng_col, m_hr, m_eng, ct,
   est, se, p_val, coef_nm)
```

