---
title: "Stage-by-Stage Impact of Blind Hiring"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{bbm}
  - \usepackage{array}
  - \usepackage{arydshln}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- +++++ ++++++ ++++++ Part 5-2: Analysis (Stage-by-Stage Impact of Blind Hiring) +++++ ++++++ ++++++ -->

\setcounter{section}{-1}

# Summary

\newpage

# Treatment Effect of Blinding on Hiring Outcomes (Stage-by-Stage Analysis)

## Blinding Disrupts Pre-Existing System of Demographic Premiums and Penalties

\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{Finding (i):} Blinding demographic information during candidate evaluation \emph{disrupts} a pre-existing system of \emph{demographic premiums and penalties}.
  \item \textbf{Finding (ii):} Blind hiring removes the \emph{baseline premium and penalty} that different demographic groups were experiencing at different phases of the hiring pipeline.
  \begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item \textbf{Winners: Hispanic Female in Resume-Screening (Phase 1) and White Male in Technical-Evaluation (Phase 2).} Blinding removes the baseline \emph{penalty} these groups received under non-blind evaluations. Their evaluation scores rise by \textcolor{blue}{+8.7\%} and \textcolor{blue}{+8.6\%} of a SD respectively.
    \item \textbf{Losers: Hispanic Male in Phase 1 and Hispanic Female in Phase 2.} Blinding removes the baseline \emph{premium} these groups received under non-blind evaluations. Their evaluation scores fall by \textcolor{red}{-11.5\%} and \textcolor{red}{-6.9\%} of a SD respectively.
  \end{itemize}
  \item \textbf{Caveat:} Hiring is often an \emph{ordinal ranking} problem --- one candidate's gain corresponds to another's lost opportunity --- so the absence of statistical significance on a given row does not mean the corresponding group is unaffected by blinding.
\end{itemize}
\vspace{-0.9em}

```{r blind_hiring_treatment_effects_demo, echo = FALSE, results = 'asis'}
## Treatment Effects of Blind Hiring (Overall (Z) only).
## Reference category: Blind resumes. Coefficients flipped post-fit so a
## positive coefficient = effect of blinding (relative to nonblind).

m_hr_blind <- suppressMessages(suppressWarnings(
  feols(sc_overall_z ~
          i(race_gender, ref = "Blind") +
          resp_age
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))

m_eng_blind <- suppressMessages(suppressWarnings(
  feols(sc_overall_z ~
          i(race_gender, ref = "Blind") +
          resp_age
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income + resp_python + resp_java,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))

flip_coef_signs <- function(model) {
  model$coefficients <- -1 * model$coefficients
  return(model)
}
## Use minimal column names; add_header_above sits above them with the
## panel labels and "Treatment Effects of Blinding for" header.
all_models <- list("HR" = flip_coef_signs(m_hr_blind),
                   "Engineer" = flip_coef_signs(m_eng_blind))

coef_map_blind <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female"
)

gof_custom_blind <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

## FE / controls footer rows. Respondent FE and Respondent Characteristics
## are placed adjacent to make the contrast visible: we do NOT soak up
## respondent heterogeneity with a fixed effect, but we DO include respondent
## demographic controls as absorbing FEs + age polynomial.
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, nox, chk),
  V2 = c(chk, chk, nox, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", "HR", "Engineer")
## 6 coefs * (est+se) = 12 rows; FE rows (5) sit immediately after at 13:17.
attr(fe_rows, "position") <- 13:17

modelsummary(
  all_models,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map  = gof_custom_blind,
  add_rows = fe_rows,
  escape   = FALSE,
  title    = "Effect of Blinding on Overall Evaluation Score by Race-Gender (Resume-Screening vs Technical-Evaluation Phase)",
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  add_header_above(c(" " = 1,
                     "Panel A: Resume-Screening Phase" = 1,
                     "Panel B: Technical-Evaluation Phase" = 1)) %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(17, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(m_hr_blind, m_eng_blind, all_models, coef_map_blind, gof_custom_blind,
   flip_coef_signs, chk, nox, fe_rows)
```




\clearpage
### Heterogeneity: Rejecting Traditional In-Group Favoritism
\enlargethispage{2.5in}

\begingroup\small
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}\setlength\itemindent{0pt}
  \item \textbf{Findings:} Our experiment demonstrates that engineers in the I.T. industry, when hiring for early-career software engineer roles, operate on a preference for the \emph{out-group} (i.e., a preference for \emph{under-represented groups}).
  \begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item When demographic information is blinded, the scores of \emph{concordant} (race/gender) applicants evaluated by Engineers rise by \textcolor{blue}{+6.9\%} of a SD ($p < 0.05$), while the scores of \emph{discordant} applicants fall by \textcolor{red}{-0.9\%} of a SD ($p < 0.05$).
    \item White Males make up the majority of the evaluator pool for engineers, and their behavior drives the aggregate results.
  \end{itemize}
  \item \textbf{Takeaway:} The majority gatekeepers were \emph{actively penalizing} candidates who looked like themselves and assigning a \emph{premium to evaluation scores of minority candidates} when such demographic information is visible. Enforcing blind hiring stops the majority group, White Males, from systematically boosting the minority candidates. This explains why, in our experiment, White Male applicants are the primary beneficiaries of blind hiring: they are ``rescued'' from the baseline penalty imposed by their own demographic engineer peers.
\end{itemize}
\endgroup
\vspace{-1.4em}

```{r bh_heterogeneity_concordance_combined, echo = FALSE, results = 'asis'}
## Combined panel: three concordance specifications x two roles, all on
## sc_overall_z. Race uses detailed Asian sub-ethnicity matching; Gender is
## broad Male/Female; Race AND Gender combines the two with detailed Asian
## sub-ethnicity. Respondents whose demographic is not represented in the
## applicant pool are coded as always-discordant in nonblind, so they stay
## in the regressions rather than being dropped.

firm_long_dt[, blind_concordance_race := fcase(
  treat == "blind",                                     "Blind",
  treat == "nonblind" & concordance_race_detailed == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_detailed == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race := factor(blind_concordance_race,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

firm_long_dt[, blind_concordance_gender := fcase(
  treat == "blind",                              "Blind",
  treat == "nonblind" & concordance_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_gender := factor(blind_concordance_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

fit_overall <- function(role_, conc_var) {
  ## Eng spec adds resp_python + resp_java FEs (Eng-only respondent traits);
  ## redundant under responseid FE but this spec doesn't have responseid FE.
  extra_fe <- if (role_ == "Eng") " + resp_python + resp_java" else ""
  fml <- as.formula(paste0(
    "sc_overall_z ~ i(", conc_var, ", ref = 'Blind') + ",
    "resp_age | ",
    "resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    extra_fe
  ))
  suppressMessages(suppressWarnings(
    feols(fml, data = firm_long_dt[role == role_], vcov = ~ responseid)
  ))
}

m_hr_race  <- fit_overall("HR",  "blind_concordance_race")
m_hr_gen   <- fit_overall("HR",  "blind_concordance_gender")
m_hr_rg    <- fit_overall("HR",  "concordance_race_gender_detailed_blind")
m_eng_race <- fit_overall("Eng", "blind_concordance_race")
m_eng_gen  <- fit_overall("Eng", "blind_concordance_gender")
m_eng_rg   <- fit_overall("Eng", "concordance_race_gender_detailed_blind")

flip_coef_signs <- function(m) { m$coefficients <- -1 * m$coefficients; m }
## Order: left panel = HR (Resume-Screening Phase) with three concordance
## specs (Race, Gender, Race+Gender), right panel = Eng (Technical-Evaluation
## Phase) with same three specs in same order.
all_models <- lapply(list(
  m_hr_race,  m_hr_gen,  m_hr_rg,
  m_eng_race, m_eng_gen, m_eng_rg
), flip_coef_signs)
## Trailing-space disambiguators so modelsummary keeps each column distinct.
names(all_models) <- c("Race", "Gender", "Race+Gender",
                       "Race ", "Gender ", "Race+Gender ")

## Multiple raw names map to the same display label so the three
## specifications align on the same two coefficient rows.
coef_map_conc <- c(
  "blind_concordance_race::Nonblind_Concordant"               = "Concordant Applicant",
  "blind_concordance_gender::Nonblind_Concordant"             = "Concordant Applicant",
  "concordance_race_gender_detailed_blind::Concordant_Group"  = "Concordant Applicant",
  "blind_concordance_race::Nonblind_Nonconcordant"            = "Nonconcordant Applicant",
  "blind_concordance_gender::Nonblind_Nonconcordant"          = "Nonconcordant Applicant",
  "concordance_race_gender_detailed_blind::Discordant_Group"  = "Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, nox, chk), V2 = c(chk, chk, nox, nox, chk),
  V3 = c(chk, chk, nox, nox, chk), V4 = c(chk, chk, nox, nox, chk),
  V5 = c(chk, chk, nox, nox, chk), V6 = c(chk, chk, nox, nox, chk),
  stringsAsFactors = FALSE
)
attr(fe_rows, "position") <- 5:9

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  title    = "Effect of Blinding on Overall Evaluation Score by Evaluator-Candidate Concordance (Race / Gender / Race+Gender)",
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Panel A: Resume-Screening Phase" = 3,
                     "Panel B: Technical-Evaluation Phase" = 3)) %>%
  row_spec(4, extra_latex_after = "\\midrule") %>%
  row_spec(9, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(m_hr_race, m_hr_gen, m_hr_rg, m_eng_race, m_eng_gen, m_eng_rg,
   all_models, coef_map_conc, gof_custom_conc, flip_coef_signs,
   fit_overall, chk, nox, fe_rows)
```
```{r het_pooled_master, echo = FALSE, warning = FALSE, message = FALSE}
## Master helpers shared by §7 / §8 / §9 (and their drop-age and
## drop-age + r_do_bythree subsections). The figure layout, labels, and
## extraction logic are identical across variants -- only the regression
## controls (age polynomial, position FE) and the coding-tier definition
## change.

build_aux_pooled <- function(d, coding_method = c("binary", "eqcount", "natural")) {
  coding_method <- match.arg(coding_method)
  d <- copy(d)
  d[, urm_tech_blind := fcase(
    treat == "blind",                    "Blind",
    treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
    treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
    default = NA_character_)]
  d[, urm_tech_blind := factor(urm_tech_blind,
    levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d[, race_gender := factor(race_gender,
    levels = c("Blind", "White_Male", "White_Female",
               "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female"))]
  if (coding_method == "binary") {
    d[, code_split := factor(top_half_coder, levels = c("0", "1"))]
  } else if (coding_method == "eqcount") {
    q_cuts <- quantile(d$test_case, probs = c(0.33, 0.67), na.rm = TRUE)
    d[, code_split := cut(test_case,
                          breaks = c(-Inf, q_cuts[1], q_cuts[2], Inf),
                          labels = c("Low_Coder", "Mid_Coder", "Top_Coder"),
                          include.lowest = TRUE)]
  } else {
    d[, code_split := cut(test_case,
                          breaks = c(-Inf, 5.75, 18.875, Inf),
                          labels = c("Low_Coder", "Mid_Coder", "Top_Coder"),
                          include.lowest = TRUE)]
  }
  d[, code_split := factor(code_split,
                           levels = if (coding_method == "binary")
                                       c("0", "1")
                                   else c("Low_Coder", "Mid_Coder", "Top_Coder"))]
  d
}

fit_pooled_v <- function(d, factor_col, split_col, age_terms, pos_fe) {
  fml <- as.formula(sprintf(
    "I(-sc_overall_z) ~ %s * %s + %s | resume_index + %s + resp_gender + resp_race + s2_educ + s2_income",
    factor_col, split_col, age_terms, pos_fe))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)
  ))
}

extract_pooled_te <- function(model, factor_col, split_col,
                              demo_levels_no_blind, demo_labels,
                              tier_levels, tier_labels) {
  cf <- coef(model);  V <- vcov(model)
  np <- length(cf);   cf_names <- names(cf)
  ref_tier <- tier_levels[1]
  rows <- vector("list", length(demo_levels_no_blind) * length(tier_levels))
  k <- 0L
  for (i in seq_along(demo_levels_no_blind)) {
    for (j in seq_along(tier_levels)) {
      d <- demo_levels_no_blind[i]; t <- tier_levels[j]
      v <- numeric(np)
      idx_main <- match(paste0(factor_col, d), cf_names)
      if (!is.na(idx_main)) v[idx_main] <- 1
      if (t != ref_tier) {
        idx_int <- match(paste0(factor_col, d, ":", split_col, t), cf_names)
        if (!is.na(idx_int)) v[idx_int] <- 1
      }
      est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
      p <- 2 * pnorm(-abs(est / se))
      k <- k + 1L
      rows[[k]] <- data.frame(Term = demo_labels[i], Tier = tier_labels[j],
                              Estimate = est, `Std. Error` = se, `Pr(>|t|)` = p,
                              check.names = FALSE)
    }
  }
  out <- do.call(rbind, rows)
  out$stars <- ifelse(out$`Pr(>|t|)` < 0.01, "***",
                ifelse(out$`Pr(>|t|)` < 0.05, "**",
                ifelse(out$`Pr(>|t|)` < 0.10, "*", "")))
  out$Term <- factor(out$Term, levels = demo_labels)
  out$Tier <- factor(out$Tier, levels = tier_labels)
  out
}

make_pooled_plot <- function(plot_df, title_label, color_vals, shape_vals, show_y = TRUE) {
  ## Always include the y title on every sub-panel; patchwork's
  ## `axis_titles = "collect"` in run_section / run_section_cont
  ## consolidates the identical labels into a single one per page.
  p <- ggplot(plot_df, aes(x = Term, y = Estimate, color = Tier, shape = Tier)) +
    geom_hline(yintercept = 0, color = "black", linewidth = 0.4) +
    geom_pointrange(aes(ymin = Estimate - 1.96 * `Std. Error`,
                        ymax = Estimate + 1.96 * `Std. Error`),
                    position = position_dodge(width = 0.6), size = 0.3) +
    geom_text(aes(label = stars, y = Estimate + 1.96 * `Std. Error` + 0.015),
              position = position_dodge(width = 0.6), size = 2.6, vjust = 0,
              color = "black", show.legend = FALSE) +
    scale_color_manual(values = color_vals) +
    scale_shape_manual(values = shape_vals) +
    coord_cartesian(ylim = c(-0.3, 0.3)) +
    labs(title = title_label, x = NULL,
         y = "Effect of Blinding on Overall Evaluation Score (SD)",
         color = "Tier:", shape = "Tier:") +
    theme_bw(base_size = 8) +
    theme(axis.text.x  = element_text(angle = 30, hjust = 1, size = 7),
          axis.title.y = element_text(size = 8),
          legend.position = "top",
          legend.title = element_text(face = "bold", size = 8),
          legend.text  = element_text(size = 7),
          plot.title   = element_text(face = "bold", size = 9),
          plot.margin  = margin(3, 6, 3, 3, "pt"))
  ## show_y arg retained for back-compat but no longer used: y title is
  ## kept on every panel and consolidated by patchwork at the page level.
  p
}

run_section <- function(coding_method, age_terms, pos_fe, file_suffix, header_label) {
  rg_levels <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
                 "Hispanic_Male", "Hispanic_Female")
  rg_labels <- c("White Male", "White Female", "Asian Male", "Asian Female",
                 "Hispanic Male", "Hispanic Female")
  ut_levels <- c("Nonblind_NonURM", "Nonblind_URM")
  ut_labels <- c("Majority", "URM")
  ax_levels <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
  ax_labels <- c("Male (NH)", "Female (NH)", "Hispanic")
  gpa_levels  <- c("Low_GPA", "Mid_GPA", "Top_GPA")
  gpa_labels  <- c("Low GPA", "Mid GPA", "Top GPA")
  gpa_colors  <- c("Low GPA" = "black", "Mid GPA" = "steelblue", "Top GPA" = "indianred1")
  gpa_shapes  <- c("Low GPA" = 16, "Mid GPA" = 15, "Top GPA" = 17)
  if (coding_method == "binary") {
    cod_levels <- c("0", "1")
    cod_labels <- c("Bottom 50% Coders", "Top 50% Coders")
    cod_colors <- c("Bottom 50% Coders" = "black", "Top 50% Coders" = "indianred1")
    cod_shapes <- c("Bottom 50% Coders" = 16, "Top 50% Coders" = 17)
  } else {
    cod_levels <- c("Low_Coder", "Mid_Coder", "Top_Coder")
    cod_labels <- c("Low Coder", "Mid Coder", "Top Coder")
    cod_colors <- c("Low Coder" = "black", "Mid Coder" = "steelblue", "Top Coder" = "indianred1")
    cod_shapes <- c("Low Coder" = 16, "Mid Coder" = 15, "Top Coder" = 17)
  }

  build_role_panel <- function(d, role_label, show_y_left = TRUE) {
    m_rg_gpa <- fit_pooled_v(d, "race_gender",     "gpa_tier3",  age_terms, pos_fe)
    m_rg_cod <- fit_pooled_v(d, "race_gender",     "code_split", age_terms, pos_fe)
    m_ut_gpa <- fit_pooled_v(d, "urm_tech_blind",  "gpa_tier3",  age_terms, pos_fe)
    m_ut_cod <- fit_pooled_v(d, "urm_tech_blind",  "code_split", age_terms, pos_fe)
    m_ax_gpa <- fit_pooled_v(d, "urm_axis_blind",  "gpa_tier3",  age_terms, pos_fe)
    m_ax_cod <- fit_pooled_v(d, "urm_axis_blind",  "code_split", age_terms, pos_fe)
    df_rg_gpa <- extract_pooled_te(m_rg_gpa, "race_gender",    "gpa_tier3",  rg_levels, rg_labels, gpa_levels, gpa_labels)
    df_rg_cod <- extract_pooled_te(m_rg_cod, "race_gender",    "code_split", rg_levels, rg_labels, cod_levels, cod_labels)
    df_ut_gpa <- extract_pooled_te(m_ut_gpa, "urm_tech_blind", "gpa_tier3",  ut_levels, ut_labels, gpa_levels, gpa_labels)
    df_ut_cod <- extract_pooled_te(m_ut_cod, "urm_tech_blind", "code_split", ut_levels, ut_labels, cod_levels, cod_labels)
    df_ax_gpa <- extract_pooled_te(m_ax_gpa, "urm_axis_blind", "gpa_tier3",  ax_levels, ax_labels, gpa_levels, gpa_labels)
    df_ax_cod <- extract_pooled_te(m_ax_cod, "urm_axis_blind", "code_split", ax_levels, ax_labels, cod_levels, cod_labels)
    list(
      rg_gpa = make_pooled_plot(df_rg_gpa, paste0(role_label, ": Per-Cell, by GPA"),    gpa_colors, gpa_shapes, show_y = show_y_left),
      rg_cod = make_pooled_plot(df_rg_cod, paste0(role_label, ": Per-Cell, by Coding"), cod_colors, cod_shapes, show_y = FALSE),
      ut_gpa = make_pooled_plot(df_ut_gpa, paste0(role_label, ": URM-tech, by GPA"),    gpa_colors, gpa_shapes, show_y = show_y_left),
      ut_cod = make_pooled_plot(df_ut_cod, paste0(role_label, ": URM-tech, by Coding"), cod_colors, cod_shapes, show_y = FALSE),
      ax_gpa = make_pooled_plot(df_ax_gpa, paste0(role_label, ": URM-axis, by GPA"),    gpa_colors, gpa_shapes, show_y = show_y_left),
      ax_cod = make_pooled_plot(df_ax_cod, paste0(role_label, ": URM-axis, by Coding"), cod_colors, cod_shapes, show_y = FALSE)
    )
  }

  dt_hr  <- build_aux_pooled(firm_long_dt[role == "HR"],  coding_method)
  dt_eng <- build_aux_pooled(firm_long_dt[role == "Eng"], coding_method)
  panels_hr  <- build_role_panel(dt_hr,  "HR",  show_y_left = TRUE)
  panels_eng <- build_role_panel(dt_eng, "Eng", show_y_left = TRUE)

  fig_dir <- here("2_Reports", "figures")
  if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
  plot_file_hr  <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_HR.pdf"))
  plot_file_eng <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_Eng.pdf"))

  fig_hr <- (panels_hr$rg_gpa + panels_hr$rg_cod) /
            (panels_hr$ax_gpa + panels_hr$ax_cod) /
            (panels_hr$ut_gpa + panels_hr$ut_cod) +
            plot_layout(guides = "collect", axis_titles = "collect") &
            theme(legend.position = "top")
  fig_eng <- (panels_eng$rg_gpa + panels_eng$rg_cod) /
             (panels_eng$ax_gpa + panels_eng$ax_cod) /
             (panels_eng$ut_gpa + panels_eng$ut_cod) +
             plot_layout(guides = "collect", axis_titles = "collect") &
             theme(legend.position = "top")

  suppressMessages(suppressWarnings({
    ggsave(plot_file_hr,  plot = fig_hr,  width = 10, height = 6.2, device = "pdf")
    ggsave(plot_file_eng, plot = fig_eng, width = 10, height = 6.2, device = "pdf")
  }))

  ## Escape underscores so r_do, r_do_bythree etc. render in text mode.
  header_label_tex <- gsub("_", "\\\\_", header_label)
  cat(sprintf("\\begin{center}\\textbf{HR Evaluators (%s)}\\par\\vspace{0.1em}\n", header_label_tex))
  cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_hr, "}\\end{center}\n", sep = "")
  cat("\\clearpage\n")
  cat(sprintf("\\begin{center}\\textbf{Engineer Evaluators (%s)}\\par\\vspace{0.1em}\n", header_label_tex))
  cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_eng, "}\\end{center}\n", sep = "")
  invisible(NULL)
}
```



```{r het_pooled_cont_master, echo = FALSE, warning = FALSE, message = FALSE}
## Master helper for the continuous-quality variants in §10. Replaces the
## categorical tier interaction with a continuous z-score slope:
##   race_gender * gpa_z      (and same for urm_axis_blind, urm_tech_blind)
##   race_gender * test_case_z
## Plotted TE points: -1 SD ("Low"), 0 ("Mid"), +1 SD ("Top") of the
## standardized quality score, so the visual layout matches §6-§9 plots.
## TE(D, q) = beta_D + q * beta_{D x quality_z}; SE via v' Sigma v.
## Resume-level main effects of gpa_z and test_case_z are absorbed by the
## resume_index FE; the demographic x quality interaction is identified
## from cross-resume variation in (race_gender, quality) pairs.

build_aux_cont <- function(d) {
  d <- copy(d)
  d[, urm_tech_blind := fcase(
    treat == "blind",                    "Blind",
    treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
    treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
    default = NA_character_)]
  d[, urm_tech_blind := factor(urm_tech_blind,
    levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d[, race_gender := factor(race_gender,
    levels = c("Blind", "White_Male", "White_Female",
               "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female"))]
  d[, gpa_z := as.numeric(scale(gpa))]
  d[, test_case_z := as.numeric(scale(test_case))]
  d
}

fit_pooled_cont <- function(d, factor_col, quality_col, age_terms, pos_fe) {
  fml <- as.formula(sprintf(
    "I(-sc_overall_z) ~ %s * %s + %s | resume_index + %s + resp_gender + resp_race + s2_educ + s2_income",
    factor_col, quality_col, age_terms, pos_fe))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)
  ))
}

extract_pooled_te_cont <- function(model, factor_col, quality_col,
                                    demo_levels_no_blind, demo_labels,
                                    eval_points, eval_labels) {
  cf <- coef(model);  V <- vcov(model)
  np <- length(cf);   cf_names <- names(cf)
  rows <- vector("list", length(demo_levels_no_blind) * length(eval_points))
  k <- 0L
  for (i in seq_along(demo_levels_no_blind)) {
    for (j in seq_along(eval_points)) {
      d <- demo_levels_no_blind[i]; q <- eval_points[j]
      v <- numeric(np)
      idx_main <- match(paste0(factor_col, d), cf_names)
      if (!is.na(idx_main)) v[idx_main] <- 1
      idx_int <- match(paste0(factor_col, d, ":", quality_col), cf_names)
      if (!is.na(idx_int)) v[idx_int] <- q
      est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
      p <- 2 * pnorm(-abs(est / se))
      k <- k + 1L
      rows[[k]] <- data.frame(Term = demo_labels[i], Tier = eval_labels[j],
                              Estimate = est, `Std. Error` = se, `Pr(>|t|)` = p,
                              check.names = FALSE)
    }
  }
  out <- do.call(rbind, rows)
  out$stars <- ifelse(out$`Pr(>|t|)` < 0.01, "***",
                ifelse(out$`Pr(>|t|)` < 0.05, "**",
                ifelse(out$`Pr(>|t|)` < 0.10, "*", "")))
  out$Term <- factor(out$Term, levels = demo_labels)
  out$Tier <- factor(out$Tier, levels = eval_labels)
  out
}

run_section_cont <- function(age_terms, pos_fe, file_suffix, header_label) {
  rg_levels <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
                 "Hispanic_Male", "Hispanic_Female")
  rg_labels <- c("White Male", "White Female", "Asian Male", "Asian Female",
                 "Hispanic Male", "Hispanic Female")
  ut_levels <- c("Nonblind_NonURM", "Nonblind_URM")
  ut_labels <- c("Majority", "URM")
  ax_levels <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
  ax_labels <- c("Male (NH)", "Female (NH)", "Hispanic")

  z_pts    <- c(-1, 0, 1)
  z_labs   <- c("Low (-1 SD)", "Mid (0)", "Top (+1 SD)")
  z_colors <- c("Low (-1 SD)" = "black", "Mid (0)" = "steelblue", "Top (+1 SD)" = "indianred1")
  z_shapes <- c("Low (-1 SD)" = 16, "Mid (0)" = 15, "Top (+1 SD)" = 17)

  build_role_panel <- function(d, role_label, show_y_left = TRUE) {
    m_rg_gpa <- fit_pooled_cont(d, "race_gender",     "gpa_z",       age_terms, pos_fe)
    m_rg_cod <- fit_pooled_cont(d, "race_gender",     "test_case_z", age_terms, pos_fe)
    m_ut_gpa <- fit_pooled_cont(d, "urm_tech_blind",  "gpa_z",       age_terms, pos_fe)
    m_ut_cod <- fit_pooled_cont(d, "urm_tech_blind",  "test_case_z", age_terms, pos_fe)
    m_ax_gpa <- fit_pooled_cont(d, "urm_axis_blind",  "gpa_z",       age_terms, pos_fe)
    m_ax_cod <- fit_pooled_cont(d, "urm_axis_blind",  "test_case_z", age_terms, pos_fe)
    df_rg_gpa <- extract_pooled_te_cont(m_rg_gpa, "race_gender",    "gpa_z",       rg_levels, rg_labels, z_pts, z_labs)
    df_rg_cod <- extract_pooled_te_cont(m_rg_cod, "race_gender",    "test_case_z", rg_levels, rg_labels, z_pts, z_labs)
    df_ut_gpa <- extract_pooled_te_cont(m_ut_gpa, "urm_tech_blind", "gpa_z",       ut_levels, ut_labels, z_pts, z_labs)
    df_ut_cod <- extract_pooled_te_cont(m_ut_cod, "urm_tech_blind", "test_case_z", ut_levels, ut_labels, z_pts, z_labs)
    df_ax_gpa <- extract_pooled_te_cont(m_ax_gpa, "urm_axis_blind", "gpa_z",       ax_levels, ax_labels, z_pts, z_labs)
    df_ax_cod <- extract_pooled_te_cont(m_ax_cod, "urm_axis_blind", "test_case_z", ax_levels, ax_labels, z_pts, z_labs)
    ## Column titles only on row 1 (act as column headers); rows 2-3 use
    ## NULL titles. Y-axis title appears only on ax_gpa (middle-row, left
    ## column) and is stripped from all other panels so it is not repeated.
    title_gpa <- paste0(role_label, ": Treatment Heterogeneity by GPA")
    title_cod <- paste0(role_label, ": Treatment Heterogeneity by Coding Ability")
    list(
      rg_gpa = make_pooled_plot(df_rg_gpa, title_gpa, z_colors, z_shapes) + labs(y = NULL),
      rg_cod = make_pooled_plot(df_rg_cod, title_cod, z_colors, z_shapes) + labs(y = NULL),
      ax_gpa = make_pooled_plot(df_ax_gpa, NULL,      z_colors, z_shapes),
      ax_cod = make_pooled_plot(df_ax_cod, NULL,      z_colors, z_shapes) + labs(y = NULL),
      ut_gpa = make_pooled_plot(df_ut_gpa, NULL,      z_colors, z_shapes) + labs(y = NULL),
      ut_cod = make_pooled_plot(df_ut_cod, NULL,      z_colors, z_shapes) + labs(y = NULL)
    )
  }

  dt_hr  <- build_aux_cont(firm_long_dt[role == "HR"])
  dt_eng <- build_aux_cont(firm_long_dt[role == "Eng"])
  panels_hr  <- build_role_panel(dt_hr,  "HR",  show_y_left = TRUE)
  panels_eng <- build_role_panel(dt_eng, "Eng", show_y_left = TRUE)

  fig_dir <- here("2_Reports", "figures")
  if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
  plot_file_hr  <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_HR.pdf"))
  plot_file_eng <- file.path(fig_dir, paste0("8B_het_", file_suffix, "_Eng.pdf"))

  ## Drop axis_titles="collect": y-axis title is now manually placed on
  ## ax_gpa only (see build_role_panel), so collection is unnecessary.
  ## plot.title.position="plot" + hjust=0.5 anchors the title to the full
  ## plot region (not the data panel), so titles in the left column are not
  ## pushed off-center by the y-axis text/title that occupies ax_gpa.
  fig_hr <- (panels_hr$rg_gpa + panels_hr$rg_cod) /
            (panels_hr$ax_gpa + panels_hr$ax_cod) +
            plot_layout(guides = "collect") &
            theme(legend.position    = "top",
                  plot.title.position = "plot",
                  plot.title          = element_text(face = "bold", size = 9, hjust = 0.5))
  fig_eng <- (panels_eng$rg_gpa + panels_eng$rg_cod) /
             (panels_eng$ax_gpa + panels_eng$ax_cod) +
             plot_layout(guides = "collect") &
             theme(legend.position    = "top",
                   plot.title.position = "plot",
                   plot.title          = element_text(face = "bold", size = 9, hjust = 0.5))

  ## Save shorter (height=4 instead of 6.2) so both HR and Eng fit on the
  ## same page as the §1.1.2 write-up.
  suppressMessages(suppressWarnings({
    ggsave(plot_file_hr,  plot = fig_hr,  width = 10, height = 4, device = "pdf")
    ggsave(plot_file_eng, plot = fig_eng, width = 10, height = 4, device = "pdf")
  }))

  ## Single-page layout: write-up | rule | HR | rule | Eng. No \clearpage.
  cat("\\noindent\\rule{\\textwidth}{0.4pt}\\par\\vspace{0.1em}\n")
  cat("\\noindent\\begin{minipage}{\\linewidth}\\centering\\small\\textbf{HR Evaluators -- Resume Screening Stage}\\par\\vspace{0.05em}\n")
  cat("\\includegraphics[width=\\textwidth]{", plot_file_hr, "}\\end{minipage}\n", sep = "")
  cat("\\par\\vspace{0.1em}\\noindent\\rule{\\textwidth}{0.4pt}\\par\\vspace{0.1em}\n")
  cat("\\noindent\\begin{minipage}{\\linewidth}\\centering\\small\\textbf{Engineer Evaluators -- Technical Evaluation}\\par\\vspace{0.05em}\n")
  cat("\\includegraphics[width=\\textwidth]{", plot_file_eng, "}\\end{minipage}\n", sep = "")
  invisible(NULL)
}
```
\clearpage
### Heterogeneity: Where the Demographic Premium Applies (Effects by Candidate Quality)

\begingroup\footnotesize\linespread{0.95}\selectfont
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{-2pt}\setlength\partopsep{0pt}\setlength\itemindent{0pt}\setlength\leftmargin{1em}
  \item \textbf{Findings:} The blinding effect on evaluation scores diverges across visible candidate quality --- GPA and Coding Ability (the success rate of the submitted code) --- within the same demographic group. The implicit out-group premium documented in §1.1.1 is concentrated at the \emph{top} of the ability distribution.
  \begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{-2pt}\setlength\partopsep{0pt}\setlength\leftmargin{1em}
    \item \textbf{Minorities.} In the \emph{resume-screening} phase, blinding removes the \textbf{premium} \textbf{Hispanic Females} previously received at all low, mid, high ability tiers, as defined by visible ability cues (\textbf{GPA} and \textbf{code success rate}). In the \emph{technical-evaluation} phase, blinding hurts \textbf{gender and racial minorities} by removing the \textbf{premium} they previously received under nonblind.
    \item \textbf{Majority (White Male mirror).} Blinding raises \textbf{White Male} evaluation scores roughly \emph{uniformly} across all ability tiers in both phases. The in-group discount evaluators apply to their own demographic under nonblind is a \textbf{flat demographic shift} --- not conditional on the candidate's observable ability. Blinding removes that shift, helping \textbf{White Males} equally at low, mid, and high ability tiers.
    \item \textbf{Takeaway.} Evaluators' demographic adjustments under nonblind are \emph{threshold-based}: \textbf{minorities} receive a \textbf{premium only when} they clear a high visible-ability bar --- concentrated at the \emph{top} of the GPA / code-success-rate distribution. Evaluators appear to want to advance minority candidates \textbf{but not at the cost of quality}, reserving the premium for the strongest-on-paper minorities and giving nothing to the rest. The mirror \textbf{penalty} applied to \textbf{White Males} is structurally different: it is \emph{unconditional}, a flat shift across ability tiers. Blinding removes both adjustments simultaneously.
  \end{itemize}
\end{itemize}
\endgroup
\vspace{-0.5em}

```{r het_pooled_102, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE, fig.width = 10, fig.height = 4}
run_section_cont(age_terms    = "resp_age",
                 pos_fe       = "r_do",
                 file_suffix  = "102_cont_age1_rdo",
                 header_label = "Continuous quality, drop nonlinear age, r_do")
```


\clearpage
## Blinding Reshuffles Demographics of Hired (Composition Effect)

\begingroup\footnotesize\linespread{0.95}\selectfont
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{-2pt}\setlength\partopsep{0pt}\setlength\itemindent{0pt}\setlength\leftmargin{1em}
  \item \textbf{Findings:} Mirroring the per-resume rating effects in §1.1, blinding reshuffles who advances at each phase.
  \begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{-2pt}\setlength\partopsep{0pt}\setlength\leftmargin{1em}
    \item \emph{Resume-screening phase:} \textbf{Hispanic Females} gain a higher pass rate to the next round; \textbf{Hispanic Males} lose.
    \item \emph{Technical-evaluation phase:} \textbf{White Males} gain at the hiring stage; \textbf{Asian Females} and \textbf{Hispanic Females} lose.
  \end{itemize}
\end{itemize}
\endgroup
\vspace{-0.5em}

```{r blind_hiring_demographic_selection, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=11, fig.height=7, out.width="0.95\\textwidth", fig.align="center"}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# LHS: hr_passk / eng_topk (0/1 selected)
# RHS: race_gender with "Blind" as reference, then flip signs
# ==============================================================================
results_all <- list()

demo_labels <- c("White_Male", "White_Female", "Asian_Male",
                 "Asian_Female", "Hispanic_Male", "Hispanic_Female")

for (k in 1:18) {

  hr_col  <- paste0("hr_pass", k)
  eng_col <- paste0("eng_top", k)

  # --- HR ---
  tryCatch({
    m_hr <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(hr_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          resume_index + resp_gender + resp_race + s2_educ + s2_income")),
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_hr)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})

  # --- Engineer ---
  tryCatch({
    m_eng <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(eng_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          resume_index + resp_gender + resp_race + s2_educ + s2_income +
          resp_python + resp_java")),
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_eng)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})
}

# ==============================================================================
# ASSEMBLE AND PLOT
# ==============================================================================
dt_plot <- rbindlist(results_all)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, demo  := factor(demo,  levels = c("White Male",    "White Female",
                                             "Asian Male",    "Asian Female",
                                             "Hispanic Male", "Hispanic Female"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]
dt_plot[, star_y := ifelse(estimate >= 0,
                            ci_high + 0.005,
                            ci_low  - 0.005)]

ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.6, size = 0.4, fatten = 3) +
  geom_text(aes(y = star_y, label = sig_stars),
            vjust = ifelse(dt_plot$estimate >= 0, 0, 1),
            size = 3, color = "black", show.legend = FALSE) +
  facet_grid(demo ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18,
                     name   = "Number of Top Candidates Selected (K)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.20))) +
  labs(
    title    = "Effect of Blind Hiring on Selection Probability by Demographic Group",
    subtitle = paste("Blinding effect = -(effect of revealing identity vs blind).",
                     "Positive = more likely selected under blinding."),
    y        = "Blinding Effect on Selection Probability",
    color    = "Evaluator Role",
    caption  = "Significance: * p<0.10, ** p<0.05, *** p<0.01. Base group: Blind resumes."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10),
    legend.text        = element_text(size = 9),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    strip.text.y       = element_text(angle = 0),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0),
    panel.spacing      = unit(0.4, "lines")
  )

rm(results_all, dt_plot, demo_labels, dg, k,
   hr_col, eng_col, m_hr, m_eng, ct,
   est, se, p_val, coef_nm)
```


\clearpage
# Effect of Blinding on Evaluation Behavior


## Time Spent Per Resume and Material Engagement

\begingroup\footnotesize\linespread{0.95}\selectfont
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{-2pt}\setlength\partopsep{0pt}\setlength\itemindent{0pt}\setlength\leftmargin{1em}
  \item \textbf{Findings:} Blinding does not change the \textbf{time} evaluators spend per resume in either phase. It does, however, change \textbf{what they engage with}: \textbf{Engineer evaluators} open candidates' resume PDF and coding scripts at a $\sim$10 pp higher rate under blinding than under nonblind.
\end{itemize}
\endgroup
\vspace{-0.5em}

```{r blind_2p1_sidebyside, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
## Derived vars (used by both tables).
firm_long_dt[, ok_ton          := !is.na(timeonpage) & timeonpage <= 600]
firm_long_dt[, blind           := as.integer(treat == "blind")]
firm_long_dt[, test_case_z     := as.numeric(scale(test_case))]
firm_long_dt[, open_code1_or_2 := as.integer(
  (!is.na(open_code1) & open_code1 == 1) | (!is.na(open_code2) & open_code2 == 1))]

build_kbl <- function(models, coef_map, fe_rows, header_panels, font, footnote_text) {
  modelsummary(
    models,
    stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
    coef_map = coef_map,
    gof_map  = tribble(~raw, ~clean, ~fmt,
                        "nobs",          "Observations", 0,
                        "r.squared",     "R$^2$",        3,
                        "adj.r.squared", "Adj. R$^2$",   3),
    add_rows = fe_rows,
    escape   = FALSE,
    output   = "kableExtra"
  ) %>%
    kable_styling(latex_options = "HOLD_position", font_size = font) %>%
    add_header_above(header_panels) %>%
    row_spec(1, extra_latex_after = "\\hdashline") %>%
    row_spec(5, extra_latex_after = "\\midrule") %>%
    row_spec(10, extra_latex_after = "\\midrule") %>%
    footnote(general = footnote_text, general_title = "",
             threeparttable = TRUE, footnote_as_chunk = FALSE, escape = FALSE)
}

strip_table_env <- function(kbl) {
  s <- paste(as.character(kbl), collapse = "\n")
  s <- gsub("\\\\begin\\{table\\}[^\n]*\n?", "", s)
  s <- gsub("\\\\end\\{table\\}\\s*", "", s)
  s
}

## ---------------- Time spent (HR + Eng, 4 cols) -----------------
fit_t <- function(role_lab, het = FALSE) {
  d <- firm_long_dt[role == role_lab & ok_ton]
  if (het) d <- d[!is.na(test_case_z)]
  if (het) { d <- copy(d); d[, q_int := blind * test_case_z] }
  fe_extra <- if (role_lab == "Eng") " + resp_python + resp_java" else ""
  rhs <- if (het) "blind + q_int + resp_age" else "blind + resp_age"
  feols(as.formula(sprintf("timeonpage ~ %s | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s",
                            rhs, fe_extra)),
        data = d, vcov = ~ responseid)
}
m_t_hr1  <- fit_t("HR",  FALSE);  m_t_hr2  <- fit_t("HR",  TRUE)
m_t_eng1 <- fit_t("Eng", FALSE);  m_t_eng2 <- fit_t("Eng", TRUE)
nb_mean_hr  <- mean(firm_long_dt[role == "HR"  & treat == "nonblind" & ok_ton, timeonpage], na.rm = TRUE)
nb_mean_eng <- mean(firm_long_dt[role == "Eng" & treat == "nonblind" & ok_ton, timeonpage], na.rm = TRUE)

chk <- "\\checkmark"; nox <- "$\\times$"
chk_mc <- "\\makecell[c]{\\checkmark}"; nox_mc <- "\\makecell[c]{$\\times$}"
fe_rows_t <- data.frame(
  term = c("Nonblind Group Mean (Seconds)",
           "Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "\\makecell[l]{Respondent Age (Cont)\\\\\\quad and Demographic FEs}"),
  V1 = c(sprintf("%.1f", nb_mean_hr),  chk, chk, nox, nox, chk_mc),
  V2 = c(sprintf("%.1f", nb_mean_hr),  chk, chk, nox, nox, chk_mc),
  V3 = c(sprintf("%.1f", nb_mean_eng), chk, chk, nox, nox, chk_mc),
  V4 = c(sprintf("%.1f", nb_mean_eng), chk, chk, nox, nox, chk_mc),
  stringsAsFactors = FALSE)
names(fe_rows_t) <- c("term", "(1)", "(2)", "(3)", "(4)")
attr(fe_rows_t, "position") <- c(1, 6, 7, 8, 9, 10)

time_kbl <- build_kbl(
  list("(1)" = m_t_hr1, "(2)" = m_t_hr2, "(3)" = m_t_eng1, "(4)" = m_t_eng2),
  c("blind" = "Blind Treatment",
    "q_int" = "Blind $\\times$ Coding Ability (Z)"),
  fe_rows_t,
  c(" " = 1, "Panel A: Resume-Screening Phase" = 2, "Panel B: Technical-Evaluation Phase" = 2),
  font = 7,
  footnote_text = "Outcome in seconds. Standard errors clustered by respondent."
)
time_str <- strip_table_env(time_kbl)

## ---------------- Open rates (Eng only, 4 cols) -----------------
eng <- firm_long_dt[role == "Eng"]
fit_o <- function(dv, het = FALSE) {
  d <- eng
  if (het) d <- d[!is.na(test_case_z)]
  if (het) { d <- copy(d); d[, q_int := blind * test_case_z] }
  rhs <- if (het) "blind + q_int + resp_age" else "blind + resp_age"
  feols(as.formula(sprintf("%s ~ %s | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income + resp_python + resp_java",
                            dv, rhs)),
        data = d, vcov = ~ responseid)
}
m_or1  <- fit_o("open_resume",     FALSE); m_or2  <- fit_o("open_resume",     TRUE)
m_oc1  <- fit_o("open_code1_or_2", FALSE); m_oc2  <- fit_o("open_code1_or_2", TRUE)
nb_mean_or <- mean(eng[treat == "nonblind", open_resume],     na.rm = TRUE)
nb_mean_oc <- mean(eng[treat == "nonblind", open_code1_or_2], na.rm = TRUE)

fe_rows_o <- data.frame(
  term = c("Nonblind Group Mean (Open Rate)",
           "Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "\\makecell[l]{Respondent Age (Cont)\\\\\\quad and Demographic FEs}"),
  V1 = c(sprintf("%.3f", nb_mean_or), chk, chk, nox, nox, chk_mc),
  V2 = c(sprintf("%.3f", nb_mean_or), chk, chk, nox, nox, chk_mc),
  V3 = c(sprintf("%.3f", nb_mean_oc), chk, chk, nox, nox, chk_mc),
  V4 = c(sprintf("%.3f", nb_mean_oc), chk, chk, nox, nox, chk_mc),
  stringsAsFactors = FALSE)
names(fe_rows_o) <- c("term", "(1)", "(2)", "(3)", "(4)")
attr(fe_rows_o, "position") <- c(1, 6, 7, 8, 9, 10)

open_kbl <- build_kbl(
  list("(1)" = m_or1, "(2)" = m_or2, "(3)" = m_oc1, "(4)" = m_oc2),
  c("blind" = "Blind Treatment",
    "q_int" = "Blind $\\times$ Coding Ability (Z)"),
  fe_rows_o,
  c(" " = 1, "Panel A: Open Resume" = 2, "Panel B: Open Codes (1/2)" = 2),
  font = 6,
  footnote_text = "Outcome is 0/1 (file opened). Standard errors clustered by respondent."
)
open_str <- strip_table_env(open_kbl)

## ---------------- Side-by-side layout (60% / 40%) ---------------
cat("```{=latex}\n")
cat("\\noindent\\begin{minipage}[t]{0.60\\textwidth}\\centering\n")
cat("\\refstepcounter{table}\\textbf{Table~\\thetable: Effect of Blinding on Time Spent Per Resume}\\par\\smallskip\n")
cat(time_str, "\n", sep = "")
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.39\\textwidth}\\centering\n")
cat("\\refstepcounter{table}\\textbf{Table~\\thetable: Material Engagement (Engineer Only)}\\par\\smallskip\n")
cat(open_str, "\n", sep = "")
cat("\\end{minipage}\n")
cat("```\n")

rm(m_t_hr1, m_t_hr2, m_t_eng1, m_t_eng2, m_or1, m_or2, m_oc1, m_oc2,
   nb_mean_hr, nb_mean_eng, nb_mean_or, nb_mean_oc,
   fe_rows_t, fe_rows_o, time_kbl, open_kbl, time_str, open_str,
   build_kbl, strip_table_env, fit_t, fit_o, eng, chk, nox)
```


\clearpage
## Signal Substitution -- Re-weighting of Visible Resume Cues

\textbf{Question:} What visible resume signals does the evaluator lean on more (or less) under blinding?

\textbf{Specification:}
\vspace{-0.7em}
$$
\begin{aligned}
\text{Overall\_Evaluation\_Score~(Z)}_{ij} \;\sim\;& \sum_{s \in \mathcal{S}_{\text{role}}} \boldsymbol{\beta_s}\,\text{Signal}_s^i \times \mathbbm{1}[\text{Blind}]_j \;\Big|\; \text{Resume\_ID~FE}_i + \text{Respondent\_ID~FE}_j + \text{Display\_Order~FE}_{ij} \\[2pt]
& \text{Two-way clustered SEs on (responseid, resume\_id).}
\end{aligned}
$$
\vspace{-1em}
\enlargethispage{2.5in}

```{r signal_substitution_pooled, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

if (!"resume_id" %in% names(firm_long_dt)) {
  firm_long_dt[, resume_id := paste(resume_ver, resume_index, sep = "_")]
}

## ---------------------------------------------------------------------------
## Visible-signal sets, by evaluator role.
##  Removed for collinearity / no within-sample variation:
##    - `python`, `java`: listed by every one of the 18 candidates
##      (constants), so absorbed by resume_index FE -- no identification.
##    - `q1_cplusplus`, `q2_cplusplus`: zero for every candidate (no one
##      submitted in C++), so trivially dropped.
##    - `q1_java`, `q2_java`, `q1_python`, `q2_python`: collinear with the
##      listed-language binaries in this 18-resume sample (fixest drops them).
##  Removed for endogeneity / interpretability:
##    - `code_opt_out`: students self-select into opting out based on their
##      own (unobserved) code quality, so the "validity" of this signal is
##      mechanically driven by the consent design rather than by anything the
##      evaluator could rationally use. Coefficient was never significant in
##      either §2.2 or §3, so dropping it loses no statistical content.
## ---------------------------------------------------------------------------
hr_signals <- c("gpa_z",
                "num_proj", "num_exp", "num_lead", "num_awards",
                "work_1000", "work_1000_twice", "work_newstartup",
                "work_research", "work_teaching",
                "javascript", "c_base", "cplusplus", "csharp", "sql")

eng_only   <- c("test_case_z")

eng_signals <- c(hr_signals, eng_only)

fml_hr <- as.formula(paste0(
  "sc_overall_z ~ (", paste(hr_signals, collapse = " + "),
  ") * i(treat, ref = 'nonblind') | resume_index + responseid + r_do"
))
fml_eng <- as.formula(paste0(
  "sc_overall_z ~ (", paste(eng_signals, collapse = " + "),
  ") * i(treat, ref = 'nonblind') | resume_index + responseid + r_do"
))

m_hr  <- suppressMessages(suppressWarnings(
  feols(fml_hr,  data = firm_long_dt[role == "HR"],
        vcov = ~ responseid + resume_id)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(fml_eng, data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid + resume_id)
))

models_list <- list("HR" = m_hr, "Engineer" = m_eng)

## ---------------------------------------------------------------------------
## Display labels and grouping for the forest plot + coef_map for the table.
## ---------------------------------------------------------------------------
signal_meta <- data.table(
  raw     = c(hr_signals, eng_only),
  display = c("GPA (Z)",
              "\\# Projects", "\\# Experiences", "\\# Leadership", "\\# Awards",
              "Top-1000 Firm", "Top-1000 Firm (2x)", "New Startup",
              "Research Position", "Teaching Position",
              "JavaScript (listed)",
              "C (listed)", "C++ (listed)", "C\\# (listed)", "SQL (listed)",
              "Test Cases (Z)"),
  group   = c("Academic",
              rep("Resume Counts",     4),
              rep("Job Prestige",      5),
              rep("Languages Listed",  5),
              rep("Code Signal (Eng-only)", 1))
)
signal_meta[, group := factor(group, levels = c("Academic", "Resume Counts",
                                                "Job Prestige", "Languages Listed",
                                                "Code Signal (Eng-only)"))]

coef_map <- setNames(signal_meta$display, paste0(signal_meta$raw, ":treat::blind"))

## ---------------------------------------------------------------------------
## FE / GoF scaffolding per project convention. Resume content (resume_index),
## display position (r_do), and respondent (responseid) FEs are all absorbed,
## which is the whole point of the spec. Respondent Characteristics and
## Q-version FE are dominated by Respondent FE, so listed `nox`.
## ---------------------------------------------------------------------------
chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, chk, nox),
  V2 = c(chk, chk, nox, chk, nox),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(models_list))
## Inline est+se format -> 16 unique coef rows; FE rows (5) inserted at
## 17:21 (between the coef block and the GoF block, so Adj R^2 stays
## adjacent to Obs / R^2 in the rendered table).
attr(fe_rows, "position") <- 17:21

gof_map <- list(
  list("raw" = "nobs",          "clean" = "Obs.",       "fmt" = function(x) format(x, big.mark = ",")),
  list("raw" = "r.squared",     "clean" = "$R^2$",      "fmt" = function(x) sprintf("%.3f", x)),
  list("raw" = "adj.r.squared", "clean" = "Adj. $R^2$", "fmt" = function(x) sprintf("%.3f", x))
)

ms_tex <- modelsummary(
  models_list,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  output    = "kableExtra",
  coef_map  = coef_map,
  gof_map   = gof_map,
  add_rows  = fe_rows,
  stars     = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
  escape    = FALSE,
  align     = "lcc"
) |> kableExtra::kable_styling(
       latex_options = c("HOLD_position"),
       font_size = 6, full_width = FALSE
     ) |> kableExtra::pack_rows("Academic",                  1,  1,  hline_after = FALSE) |>
        kableExtra::pack_rows("Resume Counts",             2,  5,  hline_after = FALSE) |>
        kableExtra::pack_rows("Job Prestige",              6, 10,  hline_after = FALSE) |>
        kableExtra::pack_rows("Languages Listed",         11, 15,  hline_after = FALSE) |>
        kableExtra::pack_rows("Code Signal (Eng-only)",   16, 16,  hline_after = FALSE) |>
        kableExtra::row_spec(16, extra_latex_after = "\\midrule") |>
        kableExtra::row_spec(21, extra_latex_after = "\\midrule")

## ---------------------------------------------------------------------------
## Forest plot of signal x Blind coefficients, faceted by role and grouped.
## ---------------------------------------------------------------------------
extract_signals <- function(m, role_label) {
  ct <- coeftable(m)
  blind_terms <- grep(":treat::blind$", rownames(ct), value = TRUE)
  if (length(blind_terms) == 0L) return(NULL)
  data.table(
    role     = role_label,
    raw      = sub(":treat::blind$", "", blind_terms),
    estimate = ct[blind_terms, "Estimate"],
    se       = ct[blind_terms, "Std. Error"],
    p_val    = ct[blind_terms, 4]
  )
}

dt_plot <- rbind(extract_signals(m_hr,  "HR Stage"),
                 extract_signals(m_eng, "Engineer Stage"))
dt_plot[, ci_low  := estimate - 1.96 * se]
dt_plot[, ci_high := estimate + 1.96 * se]

## Drop LaTeX escapes from display labels for the plot (gg can't parse \\#).
signal_meta_plot <- copy(signal_meta)
signal_meta_plot[, display_plot := gsub("\\\\#", "#", display)]
dt_plot <- dt_plot[signal_meta_plot, on = "raw", nomatch = NULL]
dt_plot[, role := factor(role, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, signal_factor := factor(display_plot,
                                   levels = rev(unique(signal_meta_plot$display_plot)))]
dt_plot[, sig_stars := fcase(p_val < 0.01, "***", p_val < 0.05, "**", p_val < 0.10, "*", default = "")]
dt_plot[, sig_color := fcase(p_val < 0.05, "Sig (p<0.05)", default = "n.s.")]

p_obj <- ggplot(dt_plot, aes(x = estimate, y = signal_factor, color = sig_color)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
  geom_pointrange(aes(xmin = ci_low, xmax = ci_high), size = 0.3, fatten = 2) +
  geom_text(aes(label = sig_stars, x = ci_high), hjust = -0.3, size = 2.4, color = "black") +
  facet_grid(group ~ role, scales = "free_y", space = "free_y") +
  scale_color_manual(values = c("Sig (p<0.05)" = "#C44E52", "n.s." = "gray40"),
                     name = NULL) +
  labs(x = "Coef. on Signal × Blind", y = NULL) +
  theme_bw(base_size = 6) +
  theme(
    legend.position    = "bottom",
    legend.key.size    = unit(0.25, "cm"),
    legend.text        = element_text(size = 5),
    strip.text.x       = element_text(face = "bold", size = 6),
    strip.text.y       = element_text(face = "bold", size = 5, angle = 0),
    axis.text.y        = element_text(size = 5),
    axis.text.x        = element_text(size = 5),
    axis.title.x       = element_text(size = 6),
    panel.grid.minor   = element_blank(),
    plot.margin        = margin(2, 2, 2, 2, "pt")
  )

## Save plot, strip kableExtra's \begin{table}/\caption/\end{table} so the
## tabular fits inside a minipage, and lay out side-by-side.
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file <- file.path(fig_dir, "8B_signal_substitution_sidebyside.pdf")
suppressMessages(suppressWarnings({
  ggsave(plot_file, plot = p_obj, width = 4, height = 4.2, device = "pdf")
}))

ms_str <- paste(as.character(ms_tex), collapse = "\n")
ms_str <- gsub("\\\\begin\\{table\\}[^\n]*\n?", "", ms_str)
ms_str <- gsub("\\\\caption\\{[^}]*\\}\n?", "",   ms_str)
ms_str <- gsub("\\\\end\\{table\\}\\s*", "",      ms_str)

cat("```{=latex}\n")
cat("\\noindent\\begin{minipage}[t]{0.52\\textwidth}\\centering\n")
cat("\\refstepcounter{table}\\textbf{Table~\\thetable: Signal Substitution}\\par\n")
cat("{\\small \\textit{Blinding: Change in Signal Weights on Evaluator-Assigned Overall Scores}}\\par\\smallskip\n")
cat(ms_str, "\n", sep = "")
cat("\\end{minipage}\\hfill\n")
cat("\\begin{minipage}[t]{0.46\\textwidth}\\centering\n")
cat("\\refstepcounter{figure}\\textbf{Figure~\\thefigure: Signal Substitution}\\par\n")
cat("{\\small \\textit{Blinding: Change in Signal Weights on Evaluator-Assigned Overall Scores}}\\par\\smallskip\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file, "}\n", sep = "")
cat("\\end{minipage}\n")
cat("```\n")

rm(hr_signals, eng_only, eng_signals, fml_hr, fml_eng, m_hr, m_eng, models_list,
   signal_meta, signal_meta_plot, coef_map, fe_rows, chk, nox, gof_map, ms_tex,
   p_obj, dt_plot, extract_signals, plot_file, fig_dir, ms_str)
```

\clearpage
## Re-weighing of Internal Rubric -- Coding / Fit / Stay Dimension Aggregation

\textbf{Question:} Do the weights evaluators place on the three sub-dimension ratings (Coding Skill, Fit, Stay) shift under blinding?

\textbf{Specification:}
\vspace{-0.7em}
$$
\begin{aligned}
\text{Overall\_Evaluation\_Score~(Z)}_{ij} \;\sim\;& \sum_{d \in \{\text{Coding\_Skill},\,\text{Fit},\,\text{Stay}\}} \big(\beta_d + \boldsymbol{\gamma_d}\,\mathbbm{1}[\text{Blind}]_j\big)\,\text{Score}_d^i \\
& \;\Big|\; \text{Resume\_ID~FE}_i + \text{Respondent\_ID~FE}_j + \text{Display\_Order~FE}_{ij} \\[2pt]
& \text{Two-way clustered SEs on (responseid, resume\_id).}
\end{aligned}
$$
\vspace{-1em}

```{r internal_rubric_shift, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

if (!"resume_id" %in% names(firm_long_dt)) {
  firm_long_dt[, resume_id := paste(resume_ver, resume_index, sep = "_")]
}

m_hr <- suppressMessages(suppressWarnings(
  feols(sc_overall_z ~ (sc_coding_z + sc_fit_z + sc_stay_z) * i(treat, ref = "nonblind")
        | responseid + resume_index + r_do,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid + resume_id)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(sc_overall_z ~ (sc_coding_z + sc_fit_z + sc_stay_z) * i(treat, ref = "nonblind")
        | responseid + resume_index + r_do,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid + resume_id)
))

models_list <- list("HR" = m_hr, "Engineer" = m_eng)

coef_map <- c(
  "sc_coding_z"              = "Coding (Z)",
  "sc_fit_z"                 = "Fit (Z)",
  "sc_stay_z"                = "Stay (Z)",
  "sc_coding_z:treat::blind" = "Coding $\\times$ Blind",
  "sc_fit_z:treat::blind"    = "Fit $\\times$ Blind",
  "sc_stay_z:treat::blind"   = "Stay $\\times$ Blind"
)

chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, chk, nox),
  V2 = c(chk, chk, nox, chk, nox),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(models_list))
## Inline est+se -> 6 unique coef rows; FE rows (5) at 7:11.
attr(fe_rows, "position") <- 7:11

gof_map <- list(
  list("raw" = "nobs",          "clean" = "Obs.",       "fmt" = function(x) format(x, big.mark = ",")),
  list("raw" = "r.squared",     "clean" = "$R^2$",      "fmt" = function(x) sprintf("%.3f", x)),
  list("raw" = "adj.r.squared", "clean" = "Adj. $R^2$", "fmt" = function(x) sprintf("%.3f", x))
)

ms_tex <- modelsummary(
  models_list,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  output    = "kableExtra",
  coef_map  = coef_map,
  gof_map   = gof_map,
  add_rows  = fe_rows,
  stars     = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
  escape    = FALSE,
  align     = "lcc",
  title     = "Internal Rubric Shift"
) |> kableExtra::kable_styling(
       latex_options = c("HOLD_position"),
       font_size = 8, full_width = FALSE
     ) |> kableExtra::pack_rows("Sub-dimension level (nonblind baseline)", 1, 3, hline_after = FALSE) |>
        kableExtra::pack_rows("Re-weighting under Blind Evaluation", 4, 6, hline_after = FALSE) |>
        kableExtra::row_spec(6,  extra_latex_after = "\\midrule") |>
        kableExtra::row_spec(11, extra_latex_after = "\\midrule")
print(ms_tex)

rm(m_hr, m_eng, models_list, coef_map, fe_rows, chk, nox, gof_map, ms_tex)
```

\clearpage
# Signal Validity: Are Visible Signals Predictive of True Coding Ability?

\textit{(NEED TO RE-RUN WITH ALL 69 STUDENT RESUMES)}

\textbf{Why this matters.} §2.2 shows that under blinding, evaluators reweight their attention onto visible resume signals --- but a positive weight-shift only counts as rational signal substitution if those signals \emph{actually predict} true productivity. If the signals blinding pushes evaluators toward have zero validity, the §2.2 effect is just \emph{credentialism} (the flight-to-credentials hypothesis). This section provides the validity benchmark.


\textbf{Question:} Among the visible resume signals evaluators rely on, which actually predict true productivity?

\textbf{Specification:}
\vspace{-0.7em}
$$
\begin{aligned}
\text{True\_Productivity\_Score~(Z)}_{i} \;\sim\;& \alpha + \boldsymbol{\gamma_s}\,\text{Signal}_s^i + \varepsilon_i,\quad i = 1, \dots, 18 \\[2pt]
& \text{One univariate OLS per signal at the resume level; HC1 robust SE.}
\end{aligned}
$$
\vspace{-1em}
```{r signal_validity_pooled, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=11, fig.height=7}

if (!"resume_id" %in% names(firm_long_dt)) {
  firm_long_dt[, resume_id := paste(resume_ver, resume_index, sep = "_")]
}
## true_coding_z is canonically built in §6 (Productivity of Hired); this
## section now runs before that, so build it defensively here if missing.
if (!"true_coding_z" %in% names(firm_long_dt)) {
  firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                    sd(overall_score, na.rm = TRUE)]
}

## ---------------------------------------------------------------------------
## Same visible-signal sets as §2.2. python / java / q1+q2 language indicators
## omitted (constants or collinear, see §2.2 caption); code_opt_out omitted as
## endogenous (students self-select into opting out based on their own code
## quality, so its 'validity' is mechanically driven by the consent design).
## ---------------------------------------------------------------------------
hr_signals <- c("gpa_z",
                "num_proj", "num_exp", "num_lead", "num_awards",
                "work_1000", "work_1000_twice", "work_newstartup",
                "work_research", "work_teaching",
                "javascript", "c_base", "cplusplus", "csharp", "sql")

eng_only   <- c("test_case_z")
all_signals <- c(hr_signals, eng_only)

signal_meta <- data.table(
  raw     = all_signals,
  display = c("GPA (Z)",
              "\\# Projects", "\\# Experiences", "\\# Leadership", "\\# Awards",
              "Top-1000 Firm", "Top-1000 Firm (2x)", "New Startup",
              "Research Position", "Teaching Position",
              "JavaScript (listed)",
              "C (listed)", "C++ (listed)", "C\\# (listed)", "SQL (listed)",
              "Test Cases (Z)"),
  group   = c("Academic",
              rep("Resume Counts",     4),
              rep("Job Prestige",      5),
              rep("Languages Listed",  5),
              rep("Code Signal (Eng-only)", 1))
)

## ---------------------------------------------------------------------------
## Resume-level data (one row per unique resume_index). Univariate validity
## is identified at the cross-resume level (N = 18); 5,238 candidate-evaluator
## panel rows are just 291 replications of these 18 cross-resume points.
## ---------------------------------------------------------------------------
resume_dt <- unique(firm_long_dt[, c("resume_index", "true_coding_z", all_signals),
                                 with = FALSE])

## ---------------------------------------------------------------------------
## Univariate validity regressions: one OLS per signal. HC1 robust SE.
## ---------------------------------------------------------------------------
univ_results <- rbindlist(lapply(all_signals, function(s) {
  fml <- as.formula(paste0("true_coding_z ~ ", s))
  m <- tryCatch(feols(fml, data = resume_dt, vcov = "hetero"),
                error = function(e) NULL)
  if (is.null(m) || !s %in% rownames(coeftable(m)))
    return(data.table(raw = s, val_est = NA_real_, val_se = NA_real_,
                      val_p = NA_real_, val_r2 = NA_real_, val_n = NA_integer_))
  ct <- coeftable(m)
  data.table(raw = s,
             val_est = ct[s, "Estimate"],
             val_se  = ct[s, "Std. Error"],
             val_p   = ct[s, 4],
             val_r2  = fitstat(m, "r2",   verbose = FALSE)$r2,
             val_n   = nobs(m))
}))
univ_results <- univ_results[signal_meta, on = "raw"]
univ_results[, group := factor(group, levels = c("Academic", "Resume Counts",
                                                  "Job Prestige", "Languages Listed",
                                                  "Code Signal (Eng-only)"))]

## ---------------------------------------------------------------------------
## §5 weight-shift regressions, re-fit here so we can extract signal x Blind
## coefficients for the §5 vs §6 scatter (the §5 chunk rm()'d its objects).
## ---------------------------------------------------------------------------
fml_wt_hr <- as.formula(paste0(
  "sc_overall_z ~ (", paste(hr_signals, collapse = " + "),
  ") * i(treat, ref = 'nonblind') | resume_index + responseid + r_do"))
fml_wt_eng <- as.formula(paste0(
  "sc_overall_z ~ (", paste(c(hr_signals, eng_only), collapse = " + "),
  ") * i(treat, ref = 'nonblind') | resume_index + responseid + r_do"))

m_wt_hr  <- suppressMessages(suppressWarnings(
  feols(fml_wt_hr,  data = firm_long_dt[role == "HR"],
        vcov = ~ responseid + resume_id)))
m_wt_eng <- suppressMessages(suppressWarnings(
  feols(fml_wt_eng, data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid + resume_id)))

extract_weight <- function(m, role_label) {
  ct <- coeftable(m)
  blind_terms <- grep(":treat::blind$", rownames(ct), value = TRUE)
  if (length(blind_terms) == 0L) return(NULL)
  data.table(
    role = role_label,
    raw  = sub(":treat::blind$", "", blind_terms),
    wt_est = ct[blind_terms, "Estimate"],
    wt_se  = ct[blind_terms, "Std. Error"]
  )
}
dt_wt <- rbind(extract_weight(m_wt_hr,  "HR Stage"),
               extract_weight(m_wt_eng, "Engineer Stage"))

## ---------------------------------------------------------------------------
## Univariate validity table. Custom kable (single-column estimate (SE) +
## R^2 + N), pack_rows by signal group.
## ---------------------------------------------------------------------------
fmt_cell <- function(est, se, p) {
  star <- fcase(p < 0.01, "***", p < 0.05, "**", p < 0.10, "*", default = "")
  sprintf("%.3f%s (%.3f)", est, star, se)
}
tbl <- data.table(
  Signal      = univ_results$display,
  Estimate    = mapply(fmt_cell, univ_results$val_est, univ_results$val_se, univ_results$val_p),
  `$R^2$`     = sprintf("%.3f", univ_results$val_r2),
  `Obs.`      = format(univ_results$val_n, big.mark = ",")
)
print(
  kable(tbl, format = "latex", booktabs = TRUE, escape = FALSE,
        align = c("l", "c", "c", "c"),
        caption = "Signal Validity --- univariate cross-resume slope of True Productivity Score (Z) on each visible signal.") %>%
    kable_styling(latex_options = c("HOLD_position"),
                  font_size = 8, full_width = FALSE) %>%
    pack_rows("Academic",                1,  1,  hline_after = FALSE) %>%
    pack_rows("Resume Counts",           2,  5,  hline_after = FALSE) %>%
    pack_rows("Job Prestige",            6, 10,  hline_after = FALSE) %>%
    pack_rows("Languages Listed",       11, 15,  hline_after = FALSE) %>%
    pack_rows("Code Signal (Eng-only)", 16, 16,  hline_after = FALSE)
)

## ---------------------------------------------------------------------------
## §5 vs §6 scatter. x-axis = §5 multivariate signal x Blind coef (per role);
## y-axis = §6 univariate validity coef (same value for both roles since
## truth doesn't depend on the evaluator). Quadrants tell the storyline.
## ---------------------------------------------------------------------------
dt_scatter <- merge(dt_wt,
                    univ_results[, .(raw, val_est, val_se,
                                      display_plot = gsub("\\\\#", "#", display),
                                      group)],
                    by = "raw")
dt_scatter[, role := factor(role, levels = c("HR Stage", "Engineer Stage"))]

p_scatter <- ggplot(dt_scatter, aes(x = wt_est, y = val_est, color = group)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.5) +
  geom_errorbarh(aes(xmin = wt_est  - 1.96 * wt_se,  xmax = wt_est  + 1.96 * wt_se),
                 height = 0, alpha = 0.4, linewidth = 0.4) +
  geom_errorbar(aes(ymin  = val_est - 1.96 * val_se, ymax = val_est + 1.96 * val_se),
                width = 0,  alpha = 0.4, linewidth = 0.4) +
  geom_point(size = 2.4) +
  ggrepel::geom_text_repel(aes(label = display_plot),
                            size = 2.7, max.overlaps = 25, force = 2,
                            box.padding = 0.4, segment.alpha = 0.5,
                            color = "gray20") +
  facet_wrap(~ role, ncol = 2, scales = "fixed") +
  scale_color_manual(values = c("Academic"            = "#9E5BB7",
                                "Resume Counts"       = "#4C72B0",
                                "Job Prestige"        = "#C44E52",
                                "Languages Listed"    = "#55A868",
                                "Code Signal (Eng-only)" = "#DD8452"),
                     name = NULL) +
  labs(
    subtitle = "Signal weight shift under blinding vs. signal validity for true productivity",
    x = "Change in evaluator's weight on this signal under blinding  --  blinding makes evaluators weigh the signal MORE (right) / LESS (left)",
    y = "How well this signal predicts true productivity  --  predictive (up) / not predictive (near 0)",
    caption = "Top-right quadrant: rational re-weighting (blinding shifts evaluators toward genuinely predictive signals). Top-left: missed opportunity (signal is predictive but evaluators weigh it less under blinding). Bottom-right: flight to credentials (blinding shifts toward signals with no validity). Bottom-left: rational drop. Vertical bars: 95% CI on the weight-shift coefficient; horizontal bars: 95% CI on the validity slope."
  ) +
  theme_bw() +
  theme(
    legend.position = "bottom",
    plot.subtitle   = element_text(size = 10, color = "gray30"),
    strip.text      = element_text(face = "bold", size = 11),
    plot.caption    = element_text(size = 8, hjust = 0)
  )
print(p_scatter)

rm(hr_signals, eng_only, all_signals, signal_meta, resume_dt, univ_results,
   fml_wt_hr, fml_wt_eng, m_wt_hr, m_wt_eng, extract_weight,
   dt_wt, dt_scatter, fmt_cell, tbl, p_scatter)
```





\clearpage
# Individual Response to Institutional Policy (Institutional Crowding Out or Compensatory Bias)

\textit{Takeaway / Summary.}
\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textbf{The Puzzle of Individual Ideology:} The two-way relationship between an evaluator's personal DEI priority and their evaluation scores is surprisingly \emph{muted and statistically noisy}. At first glance, personal ideology appears to have little impact on how blind hiring reshuffles outcomes.
  \begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item \textbf{Compensatory Bias} (Firms with NO Diversity Mandate, see \textcolor{red}{red lines}): When a firm lacks an explicit objective policy targeting URMs, highly pro-DEI HR professionals engage in \emph{compensatory bias} --- filling the perceived institutional void by informally inflating minority candidates' scores in the baseline.
    \item \textbf{Institutional Crowding-Out} (Firms WITH a Diversity Mandate, see \textcolor{blue}{blue lines}): Conversely, when the firm explicitly mandates URM targeting, this formal policy \emph{crowds out} the evaluator's informal efforts; pro-DEI HR professionals \emph{mute} their premium to under-represented minorities' scores.
  \end{itemize}
  \item (Note the \emph{divergence between HR and Engineer results}, particularly in the triple-interaction columns.)
\end{itemize}
\vspace{0.4em}

\textit{Note on Key Index Creation.}
\begin{itemize}\setlength\itemsep{2pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
  \item \textit{Individual DEI Index (Z)}: Evaluator's personal DEI orientation, condensed into a single z-scored score. (Low = Anti-DEI, High = Pro-DEI)
  \begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{0pt}
    \item Mathematical expression: $\text{Index} = z\big(\tfrac{1}{5}\sum_{j=1}^{5} z(x_j)\big)$, z-scored within (\texttt{role}, \texttt{treat}) cells.
    \item \texttt{pro\_dei\_race} --- stated agreement that race DEI is important in hiring (Likert).
    \item \texttt{pro\_dei\_gender} --- stated agreement that gender DEI is important in hiring (Likert).
    \item \texttt{pro\_diverse} --- stated importance of working at a company with a diverse workforce (Likert).
    \item \texttt{pro\_hiring\_dei} --- stated belief that DEI initiatives help firms hire better candidates (Likert).
    \item \texttt{div\_priority} --- revealed-priority rank of ``Diversity and Representation'' in the seven-goals question.
  \end{itemize}
  \item \textit{Firm Targets Fem/His (0/1)}: Indicator for firm policy --- whether the evaluator's firm formally targets Female or Hispanic candidates in hiring.
  \begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{0pt}
    \item Mathematical expression: $\text{Idx} = \mathbb{1}\{\texttt{firm\_targets\_female} = 1 \;\lor\; \texttt{firm\_targets\_hispanic} = 1\}$.
    \item \texttt{firm\_targets\_female} --- 1 if option 6 (``Female'') was selected on \texttt{s5\_policy\_diversity} (multi-select).
    \item \texttt{firm\_targets\_hispanic} --- 1 if option 3 (``Hispanic or Latino'') was selected on the same multi-select.
  \end{itemize}
  \item \textit{Firm DEI Attn Index (Z)}: Respondent's perception of how much attention their firm currently pays to race and gender DEI in hiring, condensed into a single z-scored score.
  \begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{0pt}
    \item Mathematical expression: $\text{Index} = z\big(\tfrac{1}{2}\big(z(\texttt{race\_attn}) + z(\texttt{gender\_attn})\big)\big)$, z-scored within (\texttt{role}, \texttt{treat}) cells.
    \item \texttt{s5\_view\_dei\_race\_f} --- Likert: respondent's perception of firm's current attention to race DEI in hiring.
    \item \texttt{s5\_view\_dei\_gender\_f} --- Likert: respondent's perception of firm's current attention to gender DEI in hiring.
  \end{itemize}
\end{itemize}
\vspace{-0.6em}

\clearpage
## By Six Demographics

```{r bh_dei_combined_rg, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Replicates the §4.5 / §4.6 combined structure but using the full
## per-race-gender breakdown (six demographics, as in §4.1). Single combined
## table with three specs: simple DEI het | triple Firm Targets URM | triple
## Firm DEI Attn. DEI proxy: Index A only. Coefficients flipped post-fit so
## positive => effect of blinding raises the score for that group.
## Estimate and standard error are placed on the same line so all 36 coef
## rows + FE rows + N row fit on a single landscape page.

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

fit_simple <- function(d) {
  extra_fe <- if (any(d$role == "Eng")) " + resp_python + resp_java" else ""
  fml <- as.formula(paste0(
    "sc_overall_z ~ dei_index_z + i(race_gender, ref = 'Blind') + i(race_gender, dei_index_z, ref = 'Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    extra_fe))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}

fit_triple <- function(d, b) {
  extra_fe <- if (any(d$role == "Eng")) " + resp_python + resp_java" else ""
  fml <- as.formula(sprintf(
    "sc_overall_z ~ dei_index_z + %s + I(dei_index_z * %s) + i(race_gender, ref = 'Blind') + i(race_gender, dei_index_z, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + i(race_gender, I(dei_index_z * %s), ref = 'Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s",
    b, b, b, b, extra_fe))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

m1 <- flip(fit_simple(dt_hr))
m2 <- flip(fit_simple(dt_eng))
m3 <- flip(fit_triple(dt_hr,  "firm_targets_fh"))
m4 <- flip(fit_triple(dt_eng, "firm_targets_fh"))
m5 <- flip(fit_triple(dt_hr,  "firm_dei_attention_z"))
m6 <- flip(fit_triple(dt_eng, "firm_dei_attention_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4,
                   "HR  " = m5, "Engineer  " = m6)

demos     <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female")
demo_lbls <- c("White Male", "White Female", "Asian Male", "Asian Female",
               "Hispanic Male", "Hispanic Female")

coef_map <- c(
  ## --- Block 1: single (level) terms (6 rows) ---
  setNames(demo_lbls, paste0("race_gender::", demos)),

  ## --- Block 2: two-way interactions (18 rows) ---
  ## Demo x Individual DEI Index (Z) (fills all 6 cols)
  setNames(paste0(demo_lbls, " $\\times$ Individual DEI Index (Z)"),
           paste0("race_gender::", demos, ":dei_index_z")),
  ## Demo x Firm Targets Fem/His (0/1) (cols 3-4 only)
  setNames(paste0(demo_lbls, " $\\times$ Firm Targets Fem/His (0/1)"),
           paste0("race_gender::", demos, ":firm_targets_fh")),
  ## Demo x Firm DEI Attn Index (Z) (cols 5-6 only)
  setNames(paste0(demo_lbls, " $\\times$ Firm DEI Attn Index (Z)"),
           paste0("race_gender::", demos, ":firm_dei_attention_z")),

  ## --- Block 3: three-way interactions (12 rows) ---
  setNames(paste0(demo_lbls, " $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)"),
           paste0("race_gender::", demos, ":I(dei_index_z * firm_targets_fh)")),
  setNames(paste0(demo_lbls, " $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)"),
           paste0("race_gender::", demos, ":I(dei_index_z * firm_dei_attention_z)"))
)

gof_custom <- tribble(
  ~raw,            ~clean,        ~fmt,
  "nobs",          "Observations", 0
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, nox, chk), V2 = c(chk, chk, nox, nox, chk),
  V3 = c(chk, chk, nox, nox, chk), V4 = c(chk, chk, nox, nox, chk),
  V5 = c(chk, chk, nox, nox, chk), V6 = c(chk, chk, nox, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
## Single-line est+se format -> 36 unique coefs = 36 rows; FE rows (5) sit at 37:41.
attr(fe_rows, "position") <- 37:41

## Inline est+SE format keeps the table to ~42 rows (vs. ~77 with separate
## SE row) so it fits on one landscape page.
modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  title     = "DEI Heterogeneity in the Effect of Blinding on Overall Evaluation Score, by Race-Gender (6 cells): Simple, Triple-with-Firm-Targets-URM, Triple-with-Firm-Pays-DEI-Attention.",
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(c(" " = 1,
                     "Simple DEI Heterogeneity" = 2,
                     "Triple: Firm Targets URM" = 2,
                     "Triple: Firm Pays DEI Attention" = 2)) %>%
  ## Block boundaries: single = rows 1-6; two-way = rows 7-24
  ## (Demo x DEI -> 12, Demo x FT -> 18, Demo x FA -> 24);
  ## three-way = rows 25-36 (Demo x DEI x FT -> 30, Demo x DEI x FA -> 36).
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(18, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\hdashline") %>%
  row_spec(30, extra_latex_after = "\\hdashline") %>%
  row_spec(36, extra_latex_after = "\\midrule") %>%
  row_spec(41, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

## ---------------------------------------------------------------------------
## Scissors plot for cols 3-4 of the §4.4 table (HR & Eng triple with Firm
## Targets URM), 6x2 grid: six race-gender groups by HR / Eng (12 panels).
## ---------------------------------------------------------------------------
cf_hr  <- coef(m3);  V_hr  <- vcov(m3)
cf_eng <- coef(m4);  V_eng <- vcov(m4)

cells_44_rg <- list()
for (i in seq_along(demos)) {
  cells_44_rg[[demo_lbls[i]]] <- c(
    level  = paste0("race_gender::", demos[i]),
    dei    = paste0("race_gender::", demos[i], ":dei_index_z"),
    ft     = paste0("race_gender::", demos[i], ":firm_targets_fh"),
    triple = paste0("race_gender::", demos[i], ":I(dei_index_z * firm_targets_fh)")
  )
}

dei_grid <- seq(-2, 2, length.out = 41)
plot_dt <- as.data.table(expand.grid(role  = c("HR", "Eng"),
                                     group = names(cells_44_rg),
                                     DEI   = dei_grid,
                                     FT    = c(0, 1),
                                     stringsAsFactors = FALSE))
plot_dt[, c("est", "se") := {
  ix <- unname(cells_44_rg[[group]])
  v  <- c(1, DEI, FT, DEI * FT)
  cf <- if (role == "HR") cf_hr else cf_eng
  V  <- if (role == "HR") V_hr  else V_eng
  list(sum(cf[ix] * v),
       sqrt(c(v %*% V[ix, ix] %*% v)))
}, by = .(role, group, DEI, FT)]
plot_dt[, ':='(lwr = est - 1.96 * se, upr = est + 1.96 * se)]
plot_dt[, FT_label := factor(FT, levels = c(0, 1),
                              labels = c("Firm does NOT target URM",
                                         "Firm targets URM"))]
plot_dt[, group := factor(group, levels = demo_lbls)]
plot_dt[, role := factor(role, levels = c("HR", "Eng"))]

y_lim <- range(c(plot_dt$lwr, plot_dt$upr)) * 1.05
panel_letters <- setNames(LETTERS[1:6], demo_lbls)

scissors_panel <- function(rl, grp) {
  d <- plot_dt[role == rl & group == grp]
  ggplot(d, aes(x = DEI, y = est, color = FT_label, fill = FT_label, linetype = FT_label)) +
    annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
    annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA) +
    geom_line(linewidth = 0.7) +
    annotate("text", x = 0, y = y_lim[2] * 0.93, label = "Blinding helps",
             hjust = 0.5, vjust = 1, size = 1.9, fontface = "italic", color = "darkgreen") +
    annotate("text", x = 0, y = y_lim[1] * 0.93, label = "Blinding hurts",
             hjust = 0.5, vjust = 0, size = 1.9, fontface = "italic", color = "darkred") +
    scale_color_manual(values = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_fill_manual(values  = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_linetype_manual(values = c("Firm does NOT target URM" = "dashed",
                                     "Firm targets URM"        = "solid")) +
    coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
    labs(title = paste0("Panel ", panel_letters[grp],
                        ifelse(rl == "HR", "1", "2"), ": ",
                        rl, " --- ", grp),
         x = paste0(rl, " DEI (Z)"),
         y = expression(Delta~"Z"),
         color = NULL, fill = NULL, linetype = NULL) +
    theme_bw(base_size = 6) +
    theme(legend.position  = "bottom",
          plot.title       = element_text(size = 6.5, face = "bold"),
          axis.title       = element_text(size = 6),
          axis.text        = element_text(size = 5),
          panel.grid.minor = element_blank())
}

top_row <- (scissors_panel("HR",  demo_lbls[1]) | scissors_panel("HR",  demo_lbls[2]) |
            scissors_panel("HR",  demo_lbls[3]) | scissors_panel("HR",  demo_lbls[4]) |
            scissors_panel("HR",  demo_lbls[5]) | scissors_panel("HR",  demo_lbls[6]))
bot_row <- (scissors_panel("Eng", demo_lbls[1]) | scissors_panel("Eng", demo_lbls[2]) |
            scissors_panel("Eng", demo_lbls[3]) | scissors_panel("Eng", demo_lbls[4]) |
            scissors_panel("Eng", demo_lbls[5]) | scissors_panel("Eng", demo_lbls[6]))

scissors <- top_row / bot_row +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_44_rg <- file.path(fig_dir, "8B_44_rg_scissors.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_44_rg, plot = scissors, width = 14, height = 5.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file_44_rg, "}\n", sep = "")
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize Marginal-effects ``scissors'' plot built from the §2.1 columns 3-4 (HR \\& Engineer triple with Firm Targets Fem/His), per race-gender. Top row: HR evaluators (Panels A1--F1). Bottom row: Engineer evaluators (Panels A2--F2). Lines: predicted effect of blinding on each group's overall score as a function of the rater's Individual DEI Index (Z); shaded bands are 95\\% CIs (SE clustered by respondent).\\par}\n")
cat("\\end{center}\n")

rm(dt_hr, dt_eng, fit_simple, fit_triple, flip,
   m1, m2, m3, m4, m5, m6, all_models, demos, demo_lbls,
   coef_map, gof_custom, chk, nox, fe_rows,
   cf_hr, V_hr, cf_eng, V_eng, cells_44_rg, dei_grid, plot_dt, y_lim,
   panel_letters, scissors_panel, top_row, bot_row, scissors,
   fig_dir, plot_file_44_rg)
```


\clearpage
## By Trichotomy (Majority vs Gender Minority vs Racial Minority)

```{r bh_dei_combined_axis, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Combines §4.1, §4.2, §4.3 into a single 6-column URM-axis table.
## Columns 1-2: simple DEI heterogeneity   (HR | Eng).
## Columns 3-4: triple with Firm Targets URM (firm_targets_fh).
## Columns 5-6: triple with Firm DEI Attn (firm_dei_attention_z).
## DEI proxy:  Index A only (dei_index_z).
## Coefficients flipped post-fit so positive => effect of blinding.

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
dt_eng[, firm_targets_fh := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]

build_axis <- function(d) {
  d[, urm_axis_blind := fcase(
    treat == "blind",                                                            "Blind",
    treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
    treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
    treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
    default = NA_character_)]
  d[, urm_axis_blind := factor(urm_axis_blind,
    levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
  d
}
dt_hr  <- build_axis(dt_hr)
dt_eng <- build_axis(dt_eng)

fit_simple <- function(d) {
  extra_fe <- if (any(d$role == "Eng")) " + resp_python + resp_java" else ""
  fml <- as.formula(paste0(
    "sc_overall_z ~ dei_index_z + i(urm_axis_blind, ref = 'Blind') + i(urm_axis_blind, dei_index_z, ref = 'Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
    extra_fe))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}
fit_triple <- function(d, b) {
  extra_fe <- if (any(d$role == "Eng")) " + resp_python + resp_java" else ""
  fml <- as.formula(sprintf(
    "sc_overall_z ~ dei_index_z + %s + I(dei_index_z * %s) + i(urm_axis_blind, ref = 'Blind') + i(urm_axis_blind, dei_index_z, ref = 'Blind') + i(urm_axis_blind, %s, ref = 'Blind') + i(urm_axis_blind, I(dei_index_z * %s), ref = 'Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s",
    b, b, b, b, extra_fe))
  suppressMessages(suppressWarnings(feols(fml, data = d, vcov = ~ responseid)))
}

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

m1 <- flip(fit_simple(dt_hr))
m2 <- flip(fit_simple(dt_eng))
m3 <- flip(fit_triple(dt_hr,  "firm_targets_fh"))
m4 <- flip(fit_triple(dt_eng, "firm_targets_fh"))
m5 <- flip(fit_triple(dt_hr,  "firm_dei_attention_z"))
m6 <- flip(fit_triple(dt_eng, "firm_dei_attention_z"))

## Trailing-space disambiguators so modelsummary keeps each column distinct.
all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4,
                   "HR  " = m5, "Engineer  " = m6)

coef_map <- c(
  ## --- Block 1: single (level) terms (3 rows) ---
  "urm_axis_blind::Nonblind_MaleNonHisp"   = "Male (non-hispanic)",
  "urm_axis_blind::Nonblind_FemaleNonHisp" = "Female (non-hispanic)",
  "urm_axis_blind::Nonblind_Hispanic"      = "Hispanic",

  ## --- Block 2: two-way interactions (9 rows) ---
  ## Axis x Individual DEI Index (Z) (fills all 6 cols)
  "urm_axis_blind::Nonblind_MaleNonHisp:dei_index_z"   = "Male (NH) $\\times$ Individual DEI Index (Z)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:dei_index_z" = "Female (NH) $\\times$ Individual DEI Index (Z)",
  "urm_axis_blind::Nonblind_Hispanic:dei_index_z"      = "Hispanic $\\times$ Individual DEI Index (Z)",
  ## Axis x Firm Targets Fem/His (0/1) (cols 3-4 only)
  "urm_axis_blind::Nonblind_MaleNonHisp:firm_targets_fh"   = "Male (NH) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:firm_targets_fh" = "Female (NH) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_Hispanic:firm_targets_fh"      = "Hispanic $\\times$ Firm Targets Fem/His (0/1)",
  ## Axis x Firm DEI Attn Index (Z) (cols 5-6 only)
  "urm_axis_blind::Nonblind_MaleNonHisp:firm_dei_attention_z"   = "Male (NH) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:firm_dei_attention_z" = "Female (NH) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_Hispanic:firm_dei_attention_z"      = "Hispanic $\\times$ Firm DEI Attn Index (Z)",

  ## --- Block 3: three-way interactions (6 rows) ---
  "urm_axis_blind::Nonblind_MaleNonHisp:I(dei_index_z * firm_targets_fh)"   = "Male (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:I(dei_index_z * firm_targets_fh)" = "Female (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_Hispanic:I(dei_index_z * firm_targets_fh)"      = "Hispanic $\\times$ Individual DEI Index (Z) $\\times$ Firm Targets Fem/His (0/1)",
  "urm_axis_blind::Nonblind_MaleNonHisp:I(dei_index_z * firm_dei_attention_z)"   = "Male (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_FemaleNonHisp:I(dei_index_z * firm_dei_attention_z)" = "Female (NH) $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)",
  "urm_axis_blind::Nonblind_Hispanic:I(dei_index_z * firm_dei_attention_z)"      = "Hispanic $\\times$ Individual DEI Index (Z) $\\times$ Firm DEI Attn Index (Z)"
)

gof_custom <- tribble(
  ~raw,            ~clean,        ~fmt,
  "nobs",          "Observations", 0
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, nox, chk), V2 = c(chk, chk, nox, nox, chk),
  V3 = c(chk, chk, nox, nox, chk), V4 = c(chk, chk, nox, nox, chk),
  V5 = c(chk, chk, nox, nox, chk), V6 = c(chk, chk, nox, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
## 18 coefs * 2 (est+se) = 36 rows; FE rows (5) sit at 37:41.
attr(fe_rows, "position") <- 37:41

## Row breaks: dashed line after single-term block (row 6) and before
## three-way block (row 24). 3 single * 2 = 6; (3+9) two-way * 2 = 24.
modelsummary(
  all_models,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map,
  gof_map  = gof_custom,
  add_rows = fe_rows,
  escape   = FALSE,
  title    = "DEI Heterogeneity in the Effect of Blinding on Overall Evaluation Score, by URM Axis (Male NH / Female NH / Hispanic): Simple, Triple-with-Firm-Targets-URM, Triple-with-Firm-Pays-DEI-Attention.",
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Simple DEI Heterogeneity" = 2,
                     "Triple: Firm Targets URM" = 2,
                     "Triple: Firm Pays DEI Attention" = 2)) %>%
  ## Block boundaries (dashed) and FE / fitstat boundaries (solid).
  ## Two-way block: 6 (after Axis x DEI) | 12 (after Axis x FT) | 18 (after Axis x FA).
  ## Three-way block: 30 (after Axis x DEI x FT, before Axis x DEI x FA).
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(18, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\hdashline") %>%
  row_spec(30, extra_latex_after = "\\hdashline") %>%
  row_spec(36, extra_latex_after = "\\midrule") %>%
  row_spec(41, extra_latex_after = "\\midrule") %>%
  footnote(general = "Standard errors clustered by respondent.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

## ---------------------------------------------------------------------------
## Scissors plot for cols 3-4 of the §4.4 table (HR & Eng triple with Firm
## Targets URM). Replicates the §4.2 scissors using m3 (HR) and m4 (Eng).
## TE_X(DEI, FT) = beta_X + beta_{X x DEI}*DEI + beta_{X x FT}*FT
##                       + beta_{X x DEI x FT}*DEI*FT
## SE via quadratic form v' Sigma v with v = (1, DEI, FT, DEI*FT).
## Coefficients are already sign-flipped, so positive = effect of blinding
## raises the score for that group.
## ---------------------------------------------------------------------------
cf_hr  <- coef(m3);  V_hr  <- vcov(m3)
cf_eng <- coef(m4);  V_eng <- vcov(m4)

cells_44 <- list(
  "Male (non-hispanic)" = c(
    level  = "urm_axis_blind::Nonblind_MaleNonHisp",
    dei    = "urm_axis_blind::Nonblind_MaleNonHisp:dei_index_z",
    ft     = "urm_axis_blind::Nonblind_MaleNonHisp:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_MaleNonHisp:I(dei_index_z * firm_targets_fh)"
  ),
  "Female (non-hispanic)" = c(
    level  = "urm_axis_blind::Nonblind_FemaleNonHisp",
    dei    = "urm_axis_blind::Nonblind_FemaleNonHisp:dei_index_z",
    ft     = "urm_axis_blind::Nonblind_FemaleNonHisp:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_FemaleNonHisp:I(dei_index_z * firm_targets_fh)"
  ),
  "Hispanic" = c(
    level  = "urm_axis_blind::Nonblind_Hispanic",
    dei    = "urm_axis_blind::Nonblind_Hispanic:dei_index_z",
    ft     = "urm_axis_blind::Nonblind_Hispanic:firm_targets_fh",
    triple = "urm_axis_blind::Nonblind_Hispanic:I(dei_index_z * firm_targets_fh)"
  )
)

dei_grid <- seq(-2, 2, length.out = 41)
plot_dt <- as.data.table(expand.grid(role  = c("HR", "Eng"),
                                     group = names(cells_44),
                                     DEI   = dei_grid,
                                     FT    = c(0, 1),
                                     stringsAsFactors = FALSE))
plot_dt[, c("est", "se") := {
  ix <- unname(cells_44[[group]])
  v  <- c(1, DEI, FT, DEI * FT)
  cf <- if (role == "HR") cf_hr else cf_eng
  V  <- if (role == "HR") V_hr  else V_eng
  list(sum(cf[ix] * v),
       sqrt(c(v %*% V[ix, ix] %*% v)))
}, by = .(role, group, DEI, FT)]
plot_dt[, ':='(lwr = est - 1.96 * se, upr = est + 1.96 * se)]
plot_dt[, FT_label := factor(FT, levels = c(0, 1),
                              labels = c("Firm does NOT target URM",
                                         "Firm targets URM"))]
plot_dt[, group := factor(group,
                          levels = c("Male (non-hispanic)",
                                     "Female (non-hispanic)",
                                     "Hispanic"))]
plot_dt[, role := factor(role, levels = c("HR", "Eng"))]

y_lim <- range(c(plot_dt$lwr, plot_dt$upr)) * 1.05
panel_letters <- c("Male (non-hispanic)"   = "A",
                   "Female (non-hispanic)" = "B",
                   "Hispanic"              = "C")

scissors_panel <- function(rl, grp) {
  d <- plot_dt[role == rl & group == grp]
  ggplot(d, aes(x = DEI, y = est, color = FT_label, fill = FT_label, linetype = FT_label)) +
    annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
    annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
    geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA) +
    geom_line(linewidth = 1) +
    annotate("text", x = 0, y = y_lim[2] * 0.93, label = "Blinding helps",
             hjust = 0.5, vjust = 1, size = 2.4, fontface = "italic", color = "darkgreen") +
    annotate("text", x = 0, y = y_lim[1] * 0.93, label = "Blinding hurts",
             hjust = 0.5, vjust = 0, size = 2.4, fontface = "italic", color = "darkred") +
    scale_color_manual(values = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_fill_manual(values  = c("Firm does NOT target URM" = "firebrick",
                                  "Firm targets URM"        = "steelblue")) +
    scale_linetype_manual(values = c("Firm does NOT target URM" = "dashed",
                                     "Firm targets URM"        = "solid")) +
    coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
    labs(title = paste0("Panel ", panel_letters[grp],
                        ifelse(rl == "HR", "1", "2"), ": ",
                        rl, " --- ", grp),
         x = paste0(rl, " Evaluator's Individual DEI Index (Z)"),
         y = "Effect of Blinding (Δ Overall Z-Score)",
         color = NULL, fill = NULL, linetype = NULL) +
    theme_bw(base_size = 8) +
    theme(legend.position = "bottom",
          plot.title       = element_text(size = 9, face = "bold"),
          axis.title       = element_text(size = 8),
          panel.grid.minor = element_blank())
}

scissors <- (scissors_panel("HR",  "Male (non-hispanic)") |
             scissors_panel("HR",  "Female (non-hispanic)") |
             scissors_panel("HR",  "Hispanic")) /
            (scissors_panel("Eng", "Male (non-hispanic)") |
             scissors_panel("Eng", "Female (non-hispanic)") |
             scissors_panel("Eng", "Hispanic")) +
  plot_layout(guides = "collect") &
  theme(legend.position = "bottom")

fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file_44 <- file.path(fig_dir, "8B_44_scissors.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_44, plot = scissors, width = 11, height = 4.0, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\n")
cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_44, "}\n", sep = "")
cat("\\par\\vspace{0.1em}\n")
cat("{\\raggedright\\scriptsize Marginal-effects ``scissors'' plot built from the §2.2 columns 3-4 (HR \\& Engineer triple with Firm Targets Fem/His). Top row: HR evaluators (Panels A1, B1, C1). Bottom row: Engineer evaluators (Panels A2, B2, C2). Lines: predicted effect of blinding on each group's overall score as a function of the rater's Individual DEI Index (Z); shaded bands are 95\\% CIs from the linear combination of axis-triple coefficients (SE clustered by respondent).\\par}\n")
cat("\\end{center}\n")

rm(dt_hr, dt_eng, build_axis, fit_simple, fit_triple, flip,
   m1, m2, m3, m4, m5, m6, all_models, coef_map, gof_custom,
   chk, nox, fe_rows,
   cf_hr, V_hr, cf_eng, V_eng, cells_44, dei_grid, plot_dt, y_lim,
   panel_letters, scissors_panel, scissors, fig_dir, plot_file_44)
```


\clearpage
```{r perception_triple_helpers, echo = FALSE, warning = FALSE, message = FALSE}
## Shared §8 helpers: fit + flip + scissors-data + scissors-plot.

flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

fit_simple_p <- function(d, factor_col) {
  extra_fe <- if (any(d$role == "Eng")) " + resp_python + resp_java" else ""
  fml <- as.formula(sprintf(
    "sc_overall_z ~ perc_role + i(%s, ref = 'Blind') + i(%s, perc_role, ref = 'Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s",
    factor_col, factor_col, extra_fe))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)))
}

fit_triple_p <- function(d, factor_col, third_col) {
  extra_fe <- if (any(d$role == "Eng")) " + resp_python + resp_java" else ""
  fml <- as.formula(sprintf(
    paste0("sc_overall_z ~ perc_role + %s + I(perc_role * %s) + ",
           "i(%s, ref = 'Blind') + ",
           "i(%s, perc_role, ref = 'Blind') + ",
           "i(%s, %s, ref = 'Blind') + ",
           "i(%s, I(perc_role * %s), ref = 'Blind') + ",
           "resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s"),
    third_col, third_col,
    factor_col,
    factor_col,
    factor_col, third_col,
    factor_col, third_col, extra_fe))
  suppressMessages(suppressWarnings(
    feols(fml, data = d, vcov = ~ responseid + resume_index)))
}

## TE_X(p, q) = beta_X + p*beta_{X:perc} + q*beta_{X:Z} + p*q*beta_{X:perc:Z}
## Returns long-format scissors data with role/demo/Perc/Z and 95% CI.
## Coefs that fixest dropped due to collinearity (e.g. the Eng 3-way Demo:perc:Z
## when only 1 rebel sits in nonblind) are treated as constrained-to-zero in the
## linear combination. The SE is computed from the sub-vcov of the present coefs
## only, so the rebel "Misaligned" line ends up with the same slope in Z as the
## "Aligned" line (no differential slope is identified) plus the perc shift.
build_scissors_dt <- function(model, factor_col, third_col,
                              demos, demo_lbls, role_lbl, z_grid,
                              perc_grid = c(0, 1)) {
  cf <- coef(model);  V <- vcov(model)
  rows <- list()
  for (i in seq_along(demos)) {
    nm_lvl    <- paste0(factor_col, "::", demos[i])
    nm_lvl_p  <- paste0(factor_col, "::", demos[i], ":perc_role")
    nm_lvl_z  <- paste0(factor_col, "::", demos[i], ":", third_col)
    nm_lvl_pz <- paste0(factor_col, "::", demos[i], ":I(perc_role * ", third_col, ")")
    ix      <- c(nm_lvl, nm_lvl_p, nm_lvl_z, nm_lvl_pz)
    present <- ix %in% names(cf)
    if (!present[1]) next  # no main demo coef -> nothing to plot
    cfi <- ifelse(present, as.numeric(cf[ix]), 0)
    cfi[is.na(cfi)] <- 0
    ix_pres <- ix[present]
    Vi      <- V[ix_pres, ix_pres, drop = FALSE]
    for (p in perc_grid) {
      for (q in z_grid) {
        v       <- c(1, p, q, p * q)
        v_pres  <- v[present]
        est <- sum(v * cfi)
        var_v <- as.numeric(t(v_pres) %*% Vi %*% v_pres)
        se  <- sqrt(max(0, var_v))
        rows[[length(rows) + 1L]] <- data.frame(
          role = role_lbl, demo = demo_lbls[i],
          Perc = p, Z = q, est = est,
          lwr = est - 1.96 * se, upr = est + 1.96 * se,
          stringsAsFactors = FALSE)
      }
    }
  }
  do.call(rbind, rows)
}

## Two-row scissors grid (HR top, Eng bottom). Per-row legends: each role's
## row has its own collected legend strip with role-specific labels (HR row:
## HR-aligned/misaligned-with-Eng; Eng row: Eng-aligned/misaligned-with-HR).
## "Blinding Boosts/Penalizes [demographic]" annotations are panel-specific.
## y_lim from est range only with a ±2 hard cap so thin-cell CI explosions
## don't squash visible signal; ribbons that exceed get clipped by
## coord_cartesian, central est lines stay visible.
make_scissors_grid <- function(plot_dt, demo_lbls, x_lab, ncol_panels,
                               hr_low_label   = "HR who feel aligned with Eng",
                               hr_high_label  = "HR who feel highly misaligned with Eng",
                               eng_low_label  = "Eng who feel aligned with HR",
                               eng_high_label = "Eng who feel highly misaligned with HR") {
  plot_dt <- as.data.frame(plot_dt)
  plot_dt$role <- factor(plot_dt$role, levels = c("HR", "Eng"))
  plot_dt$demo <- factor(plot_dt$demo, levels = demo_lbls)

  perc_vals <- sort(unique(plot_dt$Perc[!is.na(plot_dt$Perc)]))
  perc_low_val <- perc_vals[1]

  y_lim <- range(plot_dt$est, na.rm = TRUE) * 1.5
  y_lim[1] <- max(min(y_lim[1], -0.5), -2)
  y_lim[2] <- min(max(y_lim[2],  0.5),  2)

  panel_one <- function(rl, dm) {
    d <- plot_dt[plot_dt$role == rl & plot_dt$demo == dm, ]
    if (rl == "HR") {
      low_lab    <- hr_low_label
      high_lab   <- hr_high_label
      high_color <- "steelblue"
    } else {
      low_lab    <- eng_low_label
      high_lab   <- eng_high_label
      high_color <- "indianred"
    }
    d$bucket <- factor(
      ifelse(d$Perc == perc_low_val, low_lab, high_lab),
      levels = c(low_lab, high_lab))
    bcol <- setNames(c("gray40", high_color), c(low_lab, high_lab))
    blty <- setNames(c("dashed", "solid"),    c(low_lab, high_lab))

    ggplot(d, aes(x = Z, y = est, color = bucket, fill = bucket, linetype = bucket)) +
      annotate("rect", xmin = -2, xmax = 2, ymin = 0,        ymax = y_lim[2], fill = "#e8f4ea", alpha = 0.4) +
      annotate("rect", xmin = -2, xmax = 2, ymin = y_lim[1], ymax = 0,        fill = "#fbeaea", alpha = 0.4) +
      geom_hline(yintercept = 0, linetype = "dashed", color = "gray30", linewidth = 0.4) +
      geom_ribbon(aes(ymin = lwr, ymax = upr), alpha = 0.15, color = NA, na.rm = TRUE) +
      geom_line(linewidth = 0.7, na.rm = TRUE) +
      annotate("text", x = 0, y = y_lim[2] * 0.93, label = paste0("Blinding Boosts ", dm),
               hjust = 0.5, vjust = 1, size = 1.9, fontface = "italic", color = "darkgreen") +
      annotate("text", x = 0, y = y_lim[1] * 0.93, label = paste0("Blinding Penalizes ", dm),
               hjust = 0.5, vjust = 0, size = 1.9, fontface = "italic", color = "darkred") +
      scale_color_manual(   name = NULL, values = bcol) +
      scale_fill_manual(    name = NULL, values = bcol) +
      scale_linetype_manual(name = NULL, values = blty) +
      guides(fill = "none") +
      coord_cartesian(xlim = c(-2, 2), ylim = y_lim) +
      labs(title = paste0(rl, " --- ", dm),
           x = x_lab, y = "Effect of Blinding (Z)") +
      theme_bw(base_size = 7) +
      theme(legend.position  = "bottom",
            plot.title       = element_text(size = 7.5, face = "bold"),
            axis.title       = element_text(size = 6.5),
            axis.text        = element_text(size = 5.5),
            panel.grid.minor = element_blank())
  }

  hr_panels  <- lapply(demo_lbls, function(dm) panel_one("HR",  dm))
  eng_panels <- lapply(demo_lbls, function(dm) panel_one("Eng", dm))

  hr_grid  <- wrap_plots(hr_panels,  ncol = ncol_panels) +
              plot_layout(guides = "collect") &
              theme(legend.position = "bottom")
  eng_grid <- wrap_plots(eng_panels, ncol = ncol_panels) +
              plot_layout(guides = "collect") &
              theme(legend.position = "bottom")

  hr_grid / eng_grid
}
```
# Inter-Departmental Backlash and Compensation: Signed Directional Index

\textit{Spec.} Triple-interaction model with a \textbf{signed, DEI-specific, directional} perception index per role: positive end captures the role-appropriate ``misalignment in the bad direction'' (HR overreach for Eng; Eng undercare for HR); negative end captures the opposite direction. Both directions are continuous, not thresholded.

\textit{Survey directional structure (used directly).} The multi-select options \texttt{aligndiff\{role\}\_1..6} record which DEI dimensions the respondent flagged, and the items themselves are directional:
\begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{1pt}\setlength\partopsep{0pt}
  \item Options 1 / 4: counterpart places \emph{higher} priority on gender / racial diversity (rebellion-relevant for Eng; over-care-relevant for HR).
  \item Options 2 / 5: counterpart places \emph{lower} priority on gender / racial diversity (under-care-relevant for HR; opposite-direction signal for Eng).
  \item Options 3 / 6: counterpart places priority on \emph{different} groups (no direction --- ignored here).
\end{itemize}

\textit{Index construction} (per role; respondent-level then merged back):
\begin{itemize}\setlength\itemsep{1pt}\setlength\parskip{0pt}\setlength\topsep{1pt}\setlength\partopsep{0pt}
  \item \textbf{Eng (HR Overreach direction).} Likert: \texttt{s5\_hr\_influence} (1--4, ``to what extent does HR push DEI in hiring''; higher = more push). Directional count: $(\texttt{aligndiffeng}_1 + \texttt{aligndiffeng}_4) - (\texttt{aligndiffeng}_2 + \texttt{aligndiffeng}_5)$ (positive = HR cares more on race/gender DEI; negative = HR cares less). Composite: \texttt{eng\_dir = s5\_hr\_influence + 0.5 $\cdot$ directional\_count}, then z-scored within Eng.
  \item \textbf{HR (Eng Undercare direction).} Likert: \texttt{-s5\_engineer\_care} (negated 0--4 ``to what extent does Eng prioritize DEI''; higher negated = Eng cares less). Directional count: $(\texttt{aligndiffhr}_2 + \texttt{aligndiffhr}_5) - (\texttt{aligndiffhr}_1 + \texttt{aligndiffhr}_4)$ (positive = Eng cares less on race/gender DEI; negative = Eng cares more). Composite: \texttt{hr\_dir = -s5\_engineer\_care + 0.5 $\cdot$ directional\_count}, then z-scored within HR.
  \item \texttt{misalign\_z} = \texttt{eng\_dir\_z} for Eng rows / \texttt{hr\_dir\_z} for HR rows, used as \texttt{perc\_role} in the regressions. Sample inclusion: drop only respondents NA on the Likert anchor (\texttt{s5\_hr\_influence} for Eng / \texttt{s5\_engineer\_care} for HR).
\end{itemize}

\textbf{Substantive interpretation.} \texttt{perc\_role} $> 0$ = ``rebellion conditions'' for Eng / ``compensation conditions'' for HR; \texttt{perc\_role} $< 0$ = the opposite direction (Eng who think HR underreaches; HR who think Eng overcares). Triple-interaction slopes can therefore be read as: \emph{how does the effect of blinding on group X change as the rater moves from ``counterpart cares too little on DEI'' to ``counterpart cares too much on DEI''?}

```{r perception_dir_data, echo = FALSE, warning = FALSE, message = FALSE}
## §11: signed directional misalignment index.
extra_perc <- c("s5_view_align", "s5_view_aligndiffeng", "s5_view_aligndiffhr",
                "s5_hr_influence", "s5_engineer_care",
                grep("^aligndiff(hr|eng)_", names(firm_dt), value = TRUE))
extra_perc <- intersect(extra_perc, names(firm_dt))

fld <- merge(firm_long_dt,
             firm_dt[, c("responseid", extra_perc), with = FALSE],
             by = "responseid", all.x = TRUE)

fld[, urm_axis_blind := fcase(
       treat == "blind",                                                            "Blind",
       treat == "nonblind" & race_gender %in% c("White_Male", "Asian_Male"),         "Nonblind_MaleNonHisp",
       treat == "nonblind" & race_gender %in% c("White_Female", "Asian_Female"),     "Nonblind_FemaleNonHisp",
       treat == "nonblind" & race_gender %in% c("Hispanic_Male", "Hispanic_Female"), "Nonblind_Hispanic",
       default = NA_character_)]
fld[, urm_axis_blind := factor(urm_axis_blind,
       levels = c("Blind", "Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic"))]
fld[, urm_tech_blind := fcase(
       treat == "blind",                    "Blind",
       treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
       treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
       default = NA_character_)]
fld[, urm_tech_blind := factor(urm_tech_blind,
       levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
fld[, race_gender := factor(race_gender,
       levels = c("Blind", "White_Male", "White_Female",
                  "Asian_Male", "Asian_Female",
                  "Hispanic_Male", "Hispanic_Female"))]

resp_dt <- unique(fld[, c("responseid", "role", extra_perc), with = FALSE])

## Cast to plain numeric.
for (col in extra_perc) {
  if (col %in% names(resp_dt)) {
    set(resp_dt, j = col, value = suppressWarnings(as.numeric(resp_dt[[col]])))
  }
}

## Defensive 99 -> NA on the Likert items used in the index.
for (col in c("s5_hr_influence", "s5_engineer_care", "s5_view_align")) {
  if (col %in% names(resp_dt)) {
    resp_dt[get(col) == 99, (col) := NA_real_]
  }
}

z <- function(x) {
  if (sum(!is.na(x)) < 2) return(rep(NA_real_, length(x)))
  mu <- mean(x, na.rm = TRUE); sg <- sd(x, na.rm = TRUE)
  if (!is.finite(sg) || sg == 0) return(rep(0, length(x)))
  (x - mu) / sg
}

## Eng HR-Overreach direction:
##   Likert (s5_hr_influence) + 0.5 * (gender+racial overreach - underreach)
resp_dt[role == "Eng",
        eng_dir_count := (aligndiffeng_1 + aligndiffeng_4) -
                         (aligndiffeng_2 + aligndiffeng_5)]
resp_dt[role == "Eng",
        eng_dir_raw := s5_hr_influence + 0.5 * eng_dir_count]
resp_dt[role == "Eng", eng_dir_z := z(eng_dir_raw)]

## HR Eng-Undercare direction:
##   negated Likert (-s5_engineer_care) + 0.5 * (gender+racial undercare - overcare)
resp_dt[role == "HR",
        hr_dir_count := (aligndiffhr_2 + aligndiffhr_5) -
                        (aligndiffhr_1 + aligndiffhr_4)]
resp_dt[role == "HR",
        hr_dir_raw := -s5_engineer_care + 0.5 * hr_dir_count]
resp_dt[role == "HR", hr_dir_z := z(hr_dir_raw)]

## Stitch into a single misalign_z column.
resp_dt[, misalign_z := NA_real_]
resp_dt[role == "Eng", misalign_z := eng_dir_z]
resp_dt[role == "HR",  misalign_z := hr_dir_z]

fld <- merge(fld, resp_dt[, .(responseid, misalign_z)],
             by = "responseid", all.x = TRUE)

## Also persist misalign_z on firm_long_dt so §4.5 (productivity heterogeneity
## by misalignment) can reference it without rebuilding the whole index.
if ("misalign_z" %in% names(firm_long_dt)) firm_long_dt[, misalign_z := NULL]
firm_long_dt <- merge(firm_long_dt, resp_dt[, .(responseid, misalign_z)],
                      by = "responseid", all.x = TRUE)

dt_hr  <- fld[role == "HR"  & !is.na(misalign_z)]
dt_eng <- fld[role == "Eng" & !is.na(misalign_z)]
dt_hr [, perc_role := misalign_z]
dt_eng[, perc_role := misalign_z]

n_h_idx <- uniqueN(dt_hr$responseid)
n_e_idx <- uniqueN(dt_eng$responseid)
```


\clearpage
## By Six Demographics

```{r perception_dir_rg, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
demos     <- c("White_Male", "White_Female", "Asian_Male", "Asian_Female",
               "Hispanic_Male", "Hispanic_Female")
demo_lbls <- c("White Male", "White Female", "Asian Male", "Asian Female",
               "Hispanic Male", "Hispanic Female")
fcol      <- "race_gender"

m1 <- flip(fit_simple_p (dt_hr,  fcol))
m2 <- flip(fit_simple_p (dt_eng, fcol))
m3 <- flip(fit_triple_p (dt_hr,  fcol, "dei_index_z"))
m4 <- flip(fit_triple_p (dt_eng, fcol, "dei_index_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4)

coef_map <- c(
  setNames(demo_lbls, paste0(fcol, "::", demos)),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z)"),
           paste0(fcol, "::", demos, ":perc_role")),
  setNames(paste0(demo_lbls, " $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":dei_index_z")),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z) $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":I(perc_role * dei_index_z)"))
)

gof_custom <- tribble(
  ~raw,                 ~clean,                  ~fmt,
  "nobs",               "Observations",          0,
  "r.squared",          "R$^2$",                 3,
  "adj.r.squared",      "Adj. R$^2$",            3,
  "r2.within",          "R$^2$ Within",          3,
  "r2.within.adjusted", "Adj. R$^2$ Within",     3
)
chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, nox, chk), V2 = c(chk, chk, nox, nox, chk),
  V3 = c(chk, chk, nox, nox, chk), V4 = c(chk, chk, nox, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
attr(fe_rows, "position") <- 25:29

modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7) %>%
  add_header_above(c(" " = 1,
                     "Simple Dir Het." = 2,
                     "Triple: Dir x Own DEI" = 2)) %>%
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\hdashline") %>%
  row_spec(18, extra_latex_after = "\\hdashline") %>%
  row_spec(24, extra_latex_after = "\\midrule") %>%
  row_spec(29, extra_latex_after = "\\midrule") %>%
  footnote(general = sprintf(
            "Dir Idx (Z) = signed directional misalignment index: for Eng, HR Overreach direction (Likert + 0.5 times signed multi-select); for HR, Eng Undercare direction. Z-scored within role. Positive = rebellion conditions for Eng / compensation conditions for HR; negative = opposite. n = %d HR, %d Eng. Coefs flipped post-fit so positive = effect of blinding raises the score. Two-way cluster on responseid and resume index.",
            n_h_idx, n_e_idx),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

z_grid <- seq(-2, 2, length.out = 41)
df_dei <- rbind(
  build_scissors_dt(m3, fcol, "dei_index_z", demos, demo_lbls, "HR",  z_grid, perc_grid = c(-1, 1)),
  build_scissors_dt(m4, fcol, "dei_index_z", demos, demo_lbls, "Eng", z_grid, perc_grid = c(-1, 1)))
fig_dei <- make_scissors_grid(df_dei, demo_lbls, "Own DEI Index (Z)",
                              ncol_panels = 6,
                              hr_low_label   = "HR perceives Eng overcaring on DEI",
                              hr_high_label  = "HR perceives Eng undercaring on DEI",
                              eng_low_label  = "Eng perceives HR underreaching on DEI",
                              eng_high_label = "Eng perceives HR overreaching on DEI")

fig_dir <- here("2_Reports", "figures")
plot_file_dei <- file.path(fig_dir, "8B_perception_dir_dei_rg.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_dei, plot = fig_dei, width = 14, height = 6.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\\textbf{Dir Idx (signed) $\\times$ Own DEI Index --- Per Race-Gender (6 cells)}\\par\\vspace{0.1em}\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file_dei, "}\\par\\vspace{0.1em}\n", sep = "")
cat("{\\raggedright\\scriptsize Top row: HR (high Dir = perceives Eng undercare = compensation conditions). Bottom row: Eng (high Dir = perceives HR overreach = rebellion conditions). Bands = 95\\% CI.\\par}\n")
cat("\\end{center}\n")

rm(m1, m2, m3, m4, all_models, demos, demo_lbls, fcol,
   coef_map, gof_custom, chk, nox, fe_rows,
   z_grid, df_dei, fig_dei,
   plot_file_dei, fig_dir)
```


\clearpage
## By Trichotomy (Majority vs Gender Minority vs Racial Minority)

```{r perception_dir_axis, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
demos     <- c("Nonblind_MaleNonHisp", "Nonblind_FemaleNonHisp", "Nonblind_Hispanic")
demo_lbls <- c("Male (NH)", "Female (NH)", "Hispanic")
fcol      <- "urm_axis_blind"

m1 <- flip(fit_simple_p (dt_hr,  fcol))
m2 <- flip(fit_simple_p (dt_eng, fcol))
m3 <- flip(fit_triple_p (dt_hr,  fcol, "dei_index_z"))
m4 <- flip(fit_triple_p (dt_eng, fcol, "dei_index_z"))

all_models <- list("HR" = m1, "Engineer" = m2,
                   "HR " = m3, "Engineer " = m4)

coef_map <- c(
  setNames(demo_lbls, paste0(fcol, "::", demos)),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z)"),
           paste0(fcol, "::", demos, ":perc_role")),
  setNames(paste0(demo_lbls, " $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":dei_index_z")),
  setNames(paste0(demo_lbls, " $\\times$ Dir Idx (Z) $\\times$ Own DEI Index (Z)"),
           paste0(fcol, "::", demos, ":I(perc_role * dei_index_z)"))
)

gof_custom <- tribble(
  ~raw,                 ~clean,                  ~fmt,
  "nobs",               "Observations",          0,
  "r.squared",          "R$^2$",                 3,
  "adj.r.squared",      "Adj. R$^2$",            3,
  "r2.within",          "R$^2$ Within",          3,
  "r2.within.adjusted", "Adj. R$^2$ Within",     3
)
chk <- "\\checkmark"; nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, chk, nox, nox, chk), V2 = c(chk, chk, nox, nox, chk),
  V3 = c(chk, chk, nox, nox, chk), V4 = c(chk, chk, nox, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(all_models))
attr(fe_rows, "position") <- 13:17

modelsummary(
  all_models,
  estimate  = "{estimate}{stars} ({std.error})",
  statistic = NULL,
  stars     = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map  = coef_map,
  gof_map   = gof_custom,
  add_rows  = fe_rows,
  escape    = FALSE,
  output    = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  add_header_above(c(" " = 1,
                     "Simple Dir Het." = 2,
                     "Triple: Dir x Own DEI" = 2)) %>%
  row_spec(3,  extra_latex_after = "\\hdashline") %>%
  row_spec(6,  extra_latex_after = "\\hdashline") %>%
  row_spec(9,  extra_latex_after = "\\hdashline") %>%
  row_spec(12, extra_latex_after = "\\midrule") %>%
  row_spec(17, extra_latex_after = "\\midrule") %>%
  footnote(general = sprintf(
            "Dir Idx (Z) = signed directional misalignment index. n = %d HR, %d Eng. Coefs flipped post-fit so positive = effect of blinding raises the score. Two-way cluster on responseid and resume index.",
            n_h_idx, n_e_idx),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

z_grid <- seq(-2, 2, length.out = 41)
df_dei <- rbind(
  build_scissors_dt(m3, fcol, "dei_index_z", demos, demo_lbls, "HR",  z_grid, perc_grid = c(-1, 1)),
  build_scissors_dt(m4, fcol, "dei_index_z", demos, demo_lbls, "Eng", z_grid, perc_grid = c(-1, 1)))
fig_dei <- make_scissors_grid(df_dei, demo_lbls, "Own DEI Index (Z)",
                              ncol_panels = 3,
                              hr_low_label   = "HR perceives Eng overcaring on DEI",
                              hr_high_label  = "HR perceives Eng undercaring on DEI",
                              eng_low_label  = "Eng perceives HR underreaching on DEI",
                              eng_high_label = "Eng perceives HR overreaching on DEI")

fig_dir <- here("2_Reports", "figures")
plot_file_dei <- file.path(fig_dir, "8B_perception_dir_dei_axis.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file_dei, plot = fig_dei, width = 11, height = 6.5, device = "pdf")
))

cat("\\clearpage\n")
cat("\\begin{center}\\textbf{Dir Idx (signed) $\\times$ Own DEI Index --- URM-Axis Trichotomy}\\par\\vspace{0.1em}\n")
cat("\\includegraphics[width=0.95\\textwidth]{", plot_file_dei, "}\\par\\vspace{0.1em}\n", sep = "")
cat("{\\raggedright\\scriptsize Top row: HR (high Dir = compensation conditions). Bottom row: Eng (high Dir = rebellion conditions). Bands = 95\\% CI.\\par}\n")
cat("\\end{center}\n")

rm(m1, m2, m3, m4, all_models, demos, demo_lbls, fcol,
   coef_map, gof_custom, chk, nox, fe_rows,
   z_grid, df_dei, fig_dei,
   plot_file_dei, fig_dir)
```


\newpage
# Treatment Effect on Productivity of Hired (The Efficiency Myth)

## Does Blinding Lead to More Accurate Coding Skill Evaluations?

\textbf{Takeaway:} Removing demographic information (or noise) does \emph{not} meaningfully improve evaluators' ability to identify top-ability candidates --- signal extraction remains flat.

\textcolor{blue}{\textbf{Specification}}:
\vspace{-0.7em}
$$
\text{Hiring Evaluation Score (Z)} \sim \text{True Coding Ability (Z)} \times \mathbbm{1}[\text{Blind arm}] \mid \text{Respondent FE} + \text{Display Position FE}.
$$
\vspace{-1.4em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item $H_0\!: \beta = 0$ --- the evaluator extracts \emph{no signal} from true coding ability.
    \item $H_0\!: \beta = 1$ --- the evaluator is \emph{perfectly calibrated}: a $1$ SD rise in true ability produces exactly a $1$ SD rise in the rating, with no shrinkage.
\end{itemize}

```{r blind_hiring_signal_extraction, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}
## Pooled z-score of the lab coding score (constant within resume_index)
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]

## Two pooled interacted regressions --- one per role. Since treat is
## between-respondent, responseid FE absorbs the main effect of treat but
## leaves both the main slope on true_coding_z (identified from within-
## respondent variation, by definition the nonblind arm's slope since
## nonblind is the reference) and the interaction slope identifiable.
m_hr  <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))

## Extract arm-specific slopes, SEs, and the four tests (H0: beta = 0 / 1
## for each arm) from a single pooled model. beta_nonblind = main coef;
## beta_blind = main + interaction; SE(beta_blind) via linear-combination
## formula using the full vcov matrix.
extract_stats <- function(m) {
  ct    <- coeftable(m)
  V     <- vcov(m)
  main_name <- "true_coding_z"
  int_name  <- "true_coding_z:treat::blind"

  b_main <- ct[main_name, "Estimate"]
  s_main <- ct[main_name, "Std. Error"]
  b_int  <- ct[int_name,  "Estimate"]
  s_int  <- ct[int_name,  "Std. Error"]
  cov_mi <- V[main_name, int_name]

  b_nb <- b_main
  s_nb <- s_main
  b_b  <- b_main + b_int
  s_b  <- sqrt(s_main^2 + s_int^2 + 2 * cov_mi)

  pval <- function(t) 2 * (1 - pnorm(abs(t)))
  p_nb_0 <- pval(b_nb / s_nb)
  p_nb_1 <- pval((b_nb - 1) / s_nb)
  p_b_0  <- pval(b_b  / s_b)
  p_b_1  <- pval((b_b  - 1) / s_b)
  ## H0: beta_blind = beta_nonblind is the same as H0: beta_interaction = 0,
  ## so we read its p-value directly off the interaction coefficient.
  p_eq   <- ct[int_name, 4]

  fs <- fitstat(m, c("r2", "ar2"), simplify = TRUE)
  list(b_nb = unname(b_nb), s_nb = unname(s_nb),
       b_b  = unname(b_b),  s_b  = unname(s_b),
       p_nb_0 = p_nb_0, p_nb_1 = p_nb_1,
       p_b_0  = p_b_0,  p_b_1  = p_b_1,
       p_eq   = unname(p_eq),
       n = m$nobs, r2 = unname(fs["r2"]), ar2 = unname(fs["ar2"]))
}

s_hr  <- extract_stats(m_hr)
s_eng <- extract_stats(m_eng)

## Formatting helpers.
sig_stars <- function(p) {
  if (is.na(p))        ""
  else if (p < 0.01)   "***"
  else if (p < 0.05)   "**"
  else if (p < 0.10)   "*"
  else                 ""
}
fmt_p <- function(p) {
  if (is.na(p)) return("")
  pstr <- if (p < 0.001) "$<\\!0.001$" else sprintf("%.3f", p)
  paste0("p = ", pstr, sig_stars(p))
}

chk <- "\\checkmark"
nox <- "$\\times$"

cell_col <- function(s) c(
  sprintf("%.3f~(%.3f)", s$b_nb, s$s_nb),
  sprintf("%.3f~(%.3f)", s$b_b,  s$s_b),
  format(s$n,   big.mark = ","),
  sprintf("%.3f", s$r2),
  sprintf("%.3f", s$ar2),
  nox, chk, chk, nox
)

tbl <- data.frame(
  lbl = c("$\\hat\\beta_{\\text{nonblind}}$ (slope, nonblind arm)",
          "$\\hat\\beta_{\\text{blind}}$ (slope, blind arm)",
          "Observations",
          "$R^2$",
          "Adj. $R^2$",
          "Resume (Content) FE",
          "Display Position FE",
          "Respondent FE",
          "Respondent Characteristics"),
  HR  = cell_col(s_hr),
  Eng = cell_col(s_eng),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
names(tbl) <- c(" ", "HR", "Engineer")

## Build the plot and save it to disk so we can include it via
## \includegraphics inside a LaTeX minipage layout.
plot_data <- data.frame(
  role = factor(c("HR", "HR", "Engineer", "Engineer"),
                levels = c("HR", "Engineer")),
  arm  = factor(c("Nonblind", "Blind", "Nonblind", "Blind"),
                levels = c("Nonblind", "Blind")),
  est  = c(s_hr$b_nb,  s_hr$b_b,  s_eng$b_nb, s_eng$b_b),
  se   = c(s_hr$s_nb,  s_hr$s_b,  s_eng$s_nb, s_eng$s_b)
)
plot_data$ci_lo <- plot_data$est - 1.96 * plot_data$se
plot_data$ci_hi <- plot_data$est + 1.96 * plot_data$se

p_signal <- ggplot(plot_data, aes(x = est, y = arm, color = arm)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey50") +
  geom_errorbarh(aes(xmin = ci_lo, xmax = ci_hi), height = 0.2, linewidth = 0.8) +
  geom_point(size = 3) +
  facet_wrap(~ role, ncol = 1, strip.position = "left") +
  scale_x_continuous(limits = c(-0.05, 1.1), breaks = seq(0, 1, 0.2)) +
  scale_color_manual(values = c("Nonblind" = "#d62728", "Blind" = "#1f77b4")) +
  labs(x = expression(hat(beta)*": slope of evaluator rating on true coding ability"),
       y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom",
        panel.grid.minor = element_blank(),
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 0, face = "bold"))

## Save plot to disk so we can include it via \includegraphics inside a
## LaTeX minipage (table on left, plot on right).
fig_dir <- here("2_Reports", "figures")
if (!dir.exists(fig_dir)) dir.create(fig_dir, recursive = TRUE)
plot_file <- file.path(fig_dir, "8B_signal_extraction.pdf")
suppressMessages(suppressWarnings(
  ggsave(plot_file, plot = p_signal, width = 4.5, height = 2.6, device = "pdf")
))

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[c]{0.50\\textwidth}\n")
cat("\\centering\n")
cat("{\\fontsize{7}{9}\\selectfont\n")

## Plain kable + row_spec (no kable_styling, since kable_styling adds an
## inner \\begin{table} wrapper that LaTeX rejects inside a minipage).
print(
  kable(tbl, format = "latex", booktabs = TRUE, escape = FALSE,
        align = "lcc", row.names = FALSE) %>%
    row_spec(2, extra_latex_after = "\\midrule") %>%
    row_spec(5, extra_latex_after = "\\midrule")
)

cat("}\n")
cat("\\end{minipage}%\n")
cat("\\begin{minipage}[c]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\includegraphics[width=\\textwidth]{", plot_file, "}\n", sep = "")
cat("\\end{minipage}\n")

cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{0.98\\textwidth}\\scriptsize\n")
cat("Cluster-robust standard errors (by respondent) shown in parentheses next to each $\\hat\\beta$.\\\\\n")
cat("Stars on p-values: * $p<0.10$, ** $p<0.05$, *** $p<0.01$.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

rm(m_hr, m_eng, s_hr, s_eng,
   extract_stats, sig_stars, fmt_p, cell_col,
   chk, nox, tbl, plot_data, p_signal, plot_file, fig_dir)
```

```{r prod_het_table_helper, echo=FALSE}
## Vectorised cell formatter for the per-k underlying-data tables in
## sections 4.2-4.6: prints "estimate*** (se)" with two-sided z-test
## stars (* p<.10, ** p<.05, *** p<.01). NA inputs render as "---".
## Defined in its own chunk so it survives the per-section rm() calls.
fmt_te_vec <- function(est, se) {
  out <- rep("---", length(est))
  ok  <- !is.na(est) & !is.na(se) & se > 0
  if (any(ok)) {
    z    <- est[ok] / se[ok]
    p    <- 2 * pnorm(-abs(z))
    star <- ifelse(p < 0.01, "***",
            ifelse(p < 0.05, "**",
            ifelse(p < 0.10, "*", "")))
    out[ok] <- sprintf("%.3f%s (%.3f)", est[ok], star, se[ok])
  }
  out
}
```

\clearpage
## Does Blinding Lead to Selection of More Productive Coders?

\textbf{Takeaway:} Blind hiring has a \emph{null} effect on the actual coding quality of the hired cohort.

```{r blind_hiring_coding_quality, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

# ==============================================================================
# HELPER: Dynamic standardization relative to nonblind group at each k
# ==============================================================================
get_avg_coding_score <- function(role_filter, treat_filter, k, 
                                  pass_var_prefix, data) {
  col <- paste0(pass_var_prefix, k)
  d   <- data[role == role_filter & treat == treat_filter & get(col) == 1]
  if (nrow(d) == 0) return(NA_real_)
  mean(d$overall_score, na.rm = TRUE)
}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# ==============================================================================
results_list <- list()

for (k in 1:18) {

  # --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]

  # Dynamic standardization: relative to nonblind mean/sd at this k
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_hr)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }

  # --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]

  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_eng)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

# ==============================================================================
# PLOT
# ==============================================================================
p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.3, 0.3)) +
  labs(
    subtitle = paste("Treatment effect on true productivity measure (coding lab evaluation)",
                     "of selected candidates, standardized relative to selected candidates",
                     "under no blinding at each k"),
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Positive = blind hiring selects candidates with higher actual coding scores.\nSignificance: * p<0.10, ** p<0.05, *** p<0.01"
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Underlying per-k estimate table that drives the plot above.
## Cells: estimate*** (clustered SE). Rows = k; columns = HR vs Engineer.
## ---------------------------------------------------------------------------
dt_plot[, se   := (ci_high - estimate) / 1.96]
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ Stage, value.var = "cell")
setnames(tbl, "k", "$k$")

rm(results_list, dt_plot, tbl, p_obj, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```


\clearpage
### Decomposition of Treatment Effect on Productivity

```{r blind_hiring_coding_quality_components, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=12}

components     <- c("test_case", "readability", "time_efficiency", "space_efficiency", "runtime")
component_lbls <- c(test_case        = "Test Cases",
                    readability      = "Readability",
                    time_efficiency  = "Time Efficiency",
                    space_efficiency = "Space Efficiency",
                    runtime          = "Runtime")

results_list <- list()

for (cmp in components) {
  for (k in 1:18) {

    ## --- HR ---
    hr_col  <- paste0("hr_pass", k)
    hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1 & !is.na(get(cmp))]
    ctrl_mean_hr <- hr_data[treat == "nonblind", mean(get(cmp), na.rm = TRUE)]
    ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(get(cmp),   na.rm = TRUE)]
    if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
      hr_data[, std_outcome := (get(cmp) - ctrl_mean_hr) / ctrl_sd_hr]
      tryCatch({
        m_hr <- suppressMessages(suppressWarnings(
          feols(std_outcome ~ i(treat, ref = "nonblind") + resp_age |
                  q_version + resp_gender + resp_race + s2_educ + s2_income,
                data = hr_data, vcov = ~ responseid)
        ))
        ct <- coeftable(m_hr)
        if ("treat::blind" %in% rownames(ct)) {
          est <- ct["treat::blind", "Estimate"]; se <- ct["treat::blind", "Std. Error"]; p_val <- ct["treat::blind", 4]
          results_list[[length(results_list) + 1L]] <- data.table(
            component = component_lbls[cmp], Stage = "HR Stage", k = k,
            estimate = est, se = se,
            ci_low = est - 1.96 * se, ci_high = est + 1.96 * se, p_val = p_val
          )
        }
      }, error = function(e) {})
    }

    ## --- Engineer ---
    eng_col  <- paste0("eng_top", k)
    eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1 & !is.na(get(cmp))]
    ctrl_mean_eng <- eng_data[treat == "nonblind", mean(get(cmp), na.rm = TRUE)]
    ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(get(cmp),   na.rm = TRUE)]
    if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
      eng_data[, std_outcome := (get(cmp) - ctrl_mean_eng) / ctrl_sd_eng]
      tryCatch({
        m_eng <- suppressMessages(suppressWarnings(
          feols(std_outcome ~ i(treat, ref = "nonblind") + resp_age |
                  q_version + resp_gender + resp_race + s2_educ + s2_income +
                  resp_python + resp_java,
                data = eng_data, vcov = ~ responseid)
        ))
        ct <- coeftable(m_eng)
        if ("treat::blind" %in% rownames(ct)) {
          est <- ct["treat::blind", "Estimate"]; se <- ct["treat::blind", "Std. Error"]; p_val <- ct["treat::blind", 4]
          results_list[[length(results_list) + 1L]] <- data.table(
            component = component_lbls[cmp], Stage = "Engineer Stage", k = k,
            estimate = est, se = se,
            ci_low = est - 1.96 * se, ci_high = est + 1.96 * se, p_val = p_val
          )
        }
      }, error = function(e) {})
    }
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage     := factor(Stage,     levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, component := factor(component, levels = unname(component_lbls))]
dt_plot[, sig_stars := fcase(p_val < 0.01, "***", p_val < 0.05, "**", p_val < 0.10, "*", default = "")]

p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.5, size = 0.4, fatten = 3) +
  ## Clamp the star's y-position to stay inside the y-axis cap so the star
  ## remains visible even when ci_high overshoots ±0.6.
  geom_text(aes(y = pmin(pmax(ci_high, -0.55), 0.55), label = sig_stars),
            vjust = -0.5, size = 3, color = "black", show.legend = FALSE) +
  facet_grid(component ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0"),
                     guide = "none") +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.6, 0.6)) +
  labs(
    subtitle = "Per-component decomposition of TE on selected candidate quality (each component standardized per k relative to nonblind)",
    y       = "Effect on Component Score (SD, relative to nonblind)",
    caption = "Visibility: engineers see test_case directly; HR sees none. Readability / time / space are unobserved by both sides (latent lab measurements).\nSignificance: * p<0.10, ** p<0.05, *** p<0.01."
  ) +
  theme_bw() +
  theme(
    plot.subtitle      = element_text(size = 9, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    panel.grid.minor.x = element_blank(),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## Underlying per-k coefficient table.
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ component + Stage, value.var = "cell")
col_order <- c("k", as.vector(outer(c("HR Stage", "Engineer Stage"), unname(component_lbls),
                                     function(s, c) paste(c, s, sep = "_"))))
col_order <- intersect(col_order, names(tbl))
setcolorder(tbl, col_order)
disp <- c("$k$", rep(c("HR", "Eng"), times = length(components)))
setnames(tbl, col_order, disp[seq_along(col_order)])

rm(results_list, dt_plot, tbl, p_obj, components, component_lbls, col_order, disp,
   cmp, k, hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```


\clearpage
## Does Blinding's Productivity Effect Differ by Evaluator's DEI Orientation?

```{r blind_hiring_coding_quality_by_dei, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=6, out.width="0.95\\textwidth", fig.align="center"}

results_list <- list()
dei_pts <- c(-1, 0, 1)
dei_lbl <- c("Low DEI (-1 SD)", "Mid DEI (0)", "High DEI (+1 SD)")

for (k in 1:18) {

  ## --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * dei_index_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      cf <- coef(m_hr); V <- vcov(m_hr)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("dei_index_z:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(dei_pts)) {
          q <- dei_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "HR Stage", k = k, dei_level = dei_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se,
            p_val = 2 * pnorm(-abs(est / se))
          )
        }
      }
    }, error = function(e) {})
  }

  ## --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]
  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * dei_index_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      cf <- coef(m_eng); V <- vcov(m_eng)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("dei_index_z:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(dei_pts)) {
          q <- dei_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "Engineer Stage", k = k, dei_level = dei_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se,
            p_val = 2 * pnorm(-abs(est / se))
          )
        }
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, dei_level := factor(dei_level, levels = dei_lbl)]

p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = dei_level, fill = dei_level)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.18, color = NA) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.3) +
  facet_grid(dei_level ~ Stage) +
  scale_color_manual(values = c("Low DEI (-1 SD)"  = "#D9534F",
                                "Mid DEI (0)"      = "gray40",
                                "High DEI (+1 SD)" = "#4C72B0"),
                     guide = "none") +
  scale_fill_manual( values = c("Low DEI (-1 SD)"  = "#D9534F",
                                "Mid DEI (0)"      = "gray40",
                                "High DEI (+1 SD)" = "#4C72B0"),
                     guide = "none") +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.3, 0.3)) +
  labs(
    subtitle = "TE on hired candidates' actual coding score, by respondent's DEI index level",
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Rows: TE evaluated at -1, 0, +1 SD of the within-role z-scored DEI index. Columns: HR vs Engineer. Bands: 95% CI from the linear combination of treat::blind and treat::blind:dei_index_z."
  ) +
  theme_bw() +
  theme(
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 11),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Underlying per-k estimate table: rows = k, cols = HR/Eng x DEI level.
## Cells: estimate*** (clustered SE) from the linear combination at each
## (k, role, DEI point). add_header_above splits HR vs Engineer.
## ---------------------------------------------------------------------------
dt_plot[, se   := (ci_high - estimate) / 1.96]
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ Stage + dei_level, value.var = "cell")
col_order <- c("k",
  "HR Stage_Low DEI (-1 SD)",       "HR Stage_Mid DEI (0)",       "HR Stage_High DEI (+1 SD)",
  "Engineer Stage_Low DEI (-1 SD)", "Engineer Stage_Mid DEI (0)", "Engineer Stage_High DEI (+1 SD)")
col_order <- intersect(col_order, names(tbl))
setcolorder(tbl, col_order)
disp <- c("$k$",
  "Low (-1 SD)", "Mid (0)", "High (+1 SD)",
  "Low (-1 SD)", "Mid (0)", "High (+1 SD)")
setnames(tbl, col_order, disp[seq_along(col_order)])

rm(results_list, dt_plot, tbl, p_obj, dei_pts, dei_lbl, col_order, disp, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   cf, V, idx_main, idx_int, est, se, q, v, j)
```


\clearpage
## Does Blinding's Productivity Effect Differ by Firm DEI-Targeting Policy?

```{r blind_hiring_coding_quality_by_firmtarget, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=6}

results_list <- list()
ft_pts <- c(0, 1)
ft_lbl <- c("Firm does NOT target Fem/His", "Firm DOES target Fem/His")

## Build firm_targets_fh on firm_long_dt if not already present.
if (!"firm_targets_fh" %in% names(firm_long_dt)) {
  firm_long_dt[, firm_targets_fh := as.integer(
    firm_targets_female == 1L | firm_targets_hispanic == 1L)]
}

for (k in 1:18) {

  ## --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1 & !is.na(firm_targets_fh)]
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * firm_targets_fh + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      cf <- coef(m_hr); V <- vcov(m_hr)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("firm_targets_fh:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(ft_pts)) {
          q <- ft_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "HR Stage", k = k, ft_level = ft_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se
          )
        }
      }
    }, error = function(e) {})
  }

  ## --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1 & !is.na(firm_targets_fh)]
  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * firm_targets_fh + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      cf <- coef(m_eng); V <- vcov(m_eng)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("firm_targets_fh:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(ft_pts)) {
          q <- ft_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "Engineer Stage", k = k, ft_level = ft_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se
          )
        }
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, ft_level := factor(ft_level, levels = ft_lbl)]

p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = ft_level, fill = ft_level)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.18, color = NA) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.3) +
  facet_grid(ft_level ~ Stage) +
  scale_color_manual(values = c("Firm does NOT target Fem/His" = "#D9534F",
                                "Firm DOES target Fem/His"     = "#4C72B0"),
                     guide = "none") +
  scale_fill_manual( values = c("Firm does NOT target Fem/His" = "#D9534F",
                                "Firm DOES target Fem/His"     = "#4C72B0"),
                     guide = "none") +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.3, 0.3)) +
  labs(
    subtitle = "TE on hired candidates' actual coding score, by firm DEI-targeting policy",
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Rows: firm DOES vs does NOT formally target Female or Hispanic candidates. Columns: HR vs Engineer. Bands: 95% CI."
  ) +
  theme_bw() +
  theme(
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 11),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Underlying per-k estimate table: rows = k, cols = HR/Eng x firm-target
## (No / Yes). Cells: estimate*** (clustered SE).
## ---------------------------------------------------------------------------
dt_plot[, se   := (ci_high - estimate) / 1.96]
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ Stage + ft_level, value.var = "cell")
col_order <- c("k",
  "HR Stage_Firm does NOT target Fem/His",       "HR Stage_Firm DOES target Fem/His",
  "Engineer Stage_Firm does NOT target Fem/His", "Engineer Stage_Firm DOES target Fem/His")
col_order <- intersect(col_order, names(tbl))
setcolorder(tbl, col_order)
disp <- c("$k$",
  "Does NOT target", "DOES target",
  "Does NOT target", "DOES target")
setnames(tbl, col_order, disp[seq_along(col_order)])

rm(results_list, dt_plot, tbl, p_obj, ft_pts, ft_lbl, col_order, disp, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   cf, V, idx_main, idx_int, est, se, q, v, j)
```


\clearpage
## Does Blinding's Productivity Effect Differ by Inter-Departmental DEI Misalignment?

```{r blind_hiring_coding_quality_by_misalign, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=6, out.width="0.95\\textwidth", fig.align="center"}

results_list <- list()
ms_pts <- c(-1, 0, 1)
ms_lbl <- c("Low Misalign (-1 SD)", "Mid Misalign (0)", "High Misalign (+1 SD)")

for (k in 1:18) {

  ## --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1 & !is.na(misalign_z)]
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * misalign_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      cf <- coef(m_hr); V <- vcov(m_hr)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("misalign_z:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(ms_pts)) {
          q <- ms_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "HR Stage", k = k, ms_level = ms_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se
          )
        }
      }
    }, error = function(e) {})
  }

  ## --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1 & !is.na(misalign_z)]
  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * misalign_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      cf <- coef(m_eng); V <- vcov(m_eng)
      idx_main <- match("treat::blind", names(cf))
      idx_int  <- match("misalign_z:treat::blind", names(cf))
      if (!is.na(idx_main) && !is.na(idx_int)) {
        for (j in seq_along(ms_pts)) {
          q <- ms_pts[j]
          v <- numeric(length(cf))
          v[idx_main] <- 1; v[idx_int] <- q
          est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
          results_list[[length(results_list) + 1L]] <- data.table(
            Stage = "Engineer Stage", k = k, ms_level = ms_lbl[j],
            estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se
          )
        }
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, ms_level := factor(ms_level, levels = ms_lbl)]

p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = ms_level, fill = ms_level)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.18, color = NA) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.3) +
  facet_grid(ms_level ~ Stage) +
  scale_color_manual(values = c("Low Misalign (-1 SD)"  = "#5BC0DE",
                                "Mid Misalign (0)"       = "gray40",
                                "High Misalign (+1 SD)"  = "#D9534F"),
                     guide = "none") +
  scale_fill_manual( values = c("Low Misalign (-1 SD)"  = "#5BC0DE",
                                "Mid Misalign (0)"       = "gray40",
                                "High Misalign (+1 SD)"  = "#D9534F"),
                     guide = "none") +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.3, 0.3)) +
  labs(
    subtitle = "TE on hired candidates' actual coding score, by signed directional misalignment index",
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Rows: TE evaluated at -1, 0, +1 SD of the within-role z-scored signed directional misalignment index from §3. Columns: HR vs Engineer. Bands: 95% CI."
  ) +
  theme_bw() +
  theme(
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 11),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Underlying per-k estimate table: rows = k, cols = HR/Eng x misalign
## level. Cells: estimate*** (clustered SE).
## ---------------------------------------------------------------------------
dt_plot[, se   := (ci_high - estimate) / 1.96]
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ Stage + ms_level, value.var = "cell")
col_order <- c("k",
  "HR Stage_Low Misalign (-1 SD)",       "HR Stage_Mid Misalign (0)",       "HR Stage_High Misalign (+1 SD)",
  "Engineer Stage_Low Misalign (-1 SD)", "Engineer Stage_Mid Misalign (0)", "Engineer Stage_High Misalign (+1 SD)")
col_order <- intersect(col_order, names(tbl))
setcolorder(tbl, col_order)
disp <- c("$k$",
  "Low (-1 SD)", "Mid (0)", "High (+1 SD)",
  "Low (-1 SD)", "Mid (0)", "High (+1 SD)")
setnames(tbl, col_order, disp[seq_along(col_order)])

rm(results_list, dt_plot, tbl, p_obj, ms_pts, ms_lbl, col_order, disp, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   cf, V, idx_main, idx_int, est, se, q, v, j)
```


\clearpage
## Does Blinding's Productivity Effect Vary Jointly by DEI Orientation and Inter-Departmental Misalignment?

```{r blind_hiring_coding_quality_by_dei_x_misalign, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=6, out.width="0.95\\textwidth", fig.align="center"}

results_list <- list()
dei_pts <- c(-1, 0, 1)
dei_lbl <- c("Low DEI (-1 SD)", "Mid DEI (0)", "High DEI (+1 SD)")
ms_pts  <- c(-1, 0, 1)
ms_lbl  <- c("Low Misalign (-1 SD)", "Mid Misalign (0)", "High Misalign (+1 SD)")

for (k in 1:18) {

  ## --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1 &
                          !is.na(dei_index_z) & !is.na(misalign_z)]
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * dei_index_z * misalign_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      cf <- coef(m_hr); V <- vcov(m_hr)
      idx_main <- match("treat::blind",                        names(cf))
      idx_dei  <- match("dei_index_z:treat::blind",            names(cf))
      idx_ms   <- match("misalign_z:treat::blind",             names(cf))
      idx_dms  <- match("dei_index_z:misalign_z:treat::blind", names(cf))
      if (!is.na(idx_main)) {
        for (jd in seq_along(dei_pts)) {
          for (jm in seq_along(ms_pts)) {
            d <- dei_pts[jd]; mm <- ms_pts[jm]
            v <- numeric(length(cf))
            v[idx_main] <- 1
            if (!is.na(idx_dei)) v[idx_dei] <- d
            if (!is.na(idx_ms))  v[idx_ms]  <- mm
            if (!is.na(idx_dms)) v[idx_dms] <- d * mm
            est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
            results_list[[length(results_list) + 1L]] <- data.table(
              Stage = "HR Stage", k = k,
              dei_level = dei_lbl[jd], ms_level = ms_lbl[jm],
              estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se
            )
          }
        }
      }
    }, error = function(e) {})
  }

  ## --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1 &
                           !is.na(dei_index_z) & !is.na(misalign_z)]
  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") * dei_index_z * misalign_z + resp_age |
                q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      cf <- coef(m_eng); V <- vcov(m_eng)
      idx_main <- match("treat::blind",                        names(cf))
      idx_dei  <- match("dei_index_z:treat::blind",            names(cf))
      idx_ms   <- match("misalign_z:treat::blind",             names(cf))
      idx_dms  <- match("dei_index_z:misalign_z:treat::blind", names(cf))
      if (!is.na(idx_main)) {
        for (jd in seq_along(dei_pts)) {
          for (jm in seq_along(ms_pts)) {
            d <- dei_pts[jd]; mm <- ms_pts[jm]
            v <- numeric(length(cf))
            v[idx_main] <- 1
            if (!is.na(idx_dei)) v[idx_dei] <- d
            if (!is.na(idx_ms))  v[idx_ms]  <- mm
            if (!is.na(idx_dms)) v[idx_dms] <- d * mm
            est <- sum(v * cf); se <- sqrt(c(v %*% V %*% v))
            results_list[[length(results_list) + 1L]] <- data.table(
              Stage = "Engineer Stage", k = k,
              dei_level = dei_lbl[jd], ms_level = ms_lbl[jm],
              estimate = est, ci_low = est - 1.96 * se, ci_high = est + 1.96 * se
            )
          }
        }
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage     := factor(Stage,     levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, dei_level := factor(dei_level, levels = dei_lbl)]
dt_plot[, ms_level  := factor(ms_level,  levels = ms_lbl)]

p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = dei_level, fill = dei_level)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = 0.15, color = NA) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 1.1) +
  facet_grid(ms_level ~ Stage) +
  scale_color_manual(values = c("Low DEI (-1 SD)"  = "#D9534F",
                                "Mid DEI (0)"      = "gray40",
                                "High DEI (+1 SD)" = "#4C72B0"),
                     name = "Respondent DEI Index") +
  scale_fill_manual( values = c("Low DEI (-1 SD)"  = "#D9534F",
                                "Mid DEI (0)"      = "gray40",
                                "High DEI (+1 SD)" = "#4C72B0"),
                     name = "Respondent DEI Index") +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  coord_cartesian(ylim = c(-0.4, 0.4)) +
  labs(
    subtitle = "TE on hired candidates' actual coding score, by DEI index x signed directional misalignment",
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Rows: misalignment index at -1/0/+1 SD. Columns: HR vs Engineer. Within panel: respondent DEI index at -1/0/+1 SD. Bands: 95% CI from v' Sigma v with v selecting (treat::blind, treat::blind:dei_z, treat::blind:misalign_z, treat::blind:dei_z:misalign_z); coefs dropped for collinearity are treated as constrained to zero. Y-cap +/-0.4 SD."
  ) +
  theme_bw() +
  theme(
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 11),
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 9),
    legend.text        = element_text(size = 9),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Underlying per-k estimate table for the triple interaction.
## Rows = k. Columns: 18 cells per row (HR x 3 misalign x 3 DEI, then
## Eng x 3 misalign x 3 DEI). Two header rows group by Role (top) and
## by Misalign level (middle); the inner column labels are the DEI level.
## Cells: estimate*** (clustered SE).
## ---------------------------------------------------------------------------
dt_plot[, se   := (ci_high - estimate) / 1.96]
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ Stage + ms_level + dei_level, value.var = "cell")

stages_order <- c("HR Stage", "Engineer Stage")
ms_order     <- c("Low Misalign (-1 SD)", "Mid Misalign (0)", "High Misalign (+1 SD)")
dei_order    <- c("Low DEI (-1 SD)",      "Mid DEI (0)",      "High DEI (+1 SD)")
col_order <- c("k",
  unlist(lapply(stages_order, function(st)
    unlist(lapply(ms_order, function(ms)
      paste(st, ms, dei_order, sep = "_"))))))
col_order <- intersect(col_order, names(tbl))
setcolorder(tbl, col_order)
disp <- c("$k$", rep(c("L", "M", "H"), times = 6))
setnames(tbl, col_order, disp[seq_along(col_order)])

rm(results_list, dt_plot, tbl, p_obj,
   dei_pts, dei_lbl, ms_pts, ms_lbl,
   stages_order, ms_order, dei_order, col_order, disp, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   cf, V, idx_main, idx_dei, idx_ms, idx_dms,
   est, se, d, mm, v, jd, jm)
```


