---
title: "Stage-by-Stage Impact of Blind Hiring"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{bbm}
  - \usepackage{array}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


<!-- +++++ ++++++ ++++++ Part 5-2: Analysis (Stage-by-Stage Impact of Blind Hiring) +++++ ++++++ ++++++ -->


# Treatment Effect on Evaluations

## On All Dimensions (Z)

\textcolor{blue}{\textbf{Takeaway}}: Blinding demographic information \emph{reshuffles} candidates' relative evaluations. In the HR resume screening stage, Hispanic Male candidates are the largest losers: under blinding, their overall evaluation scores fall by \textcolor{blue}{11.5\%} of a standard deviation relative to when their identity is revealed. In the Engineer technical evaluation stage, the largest gainers are White Male candidates, whose scores rise by \textcolor{blue}{8.5\%} of a SD under blinding, while Hispanic Females' scores lose by \textcolor{blue}{6.9\%} of a SD. However, because hiring is often an ordinal ranking problem --- where one candidate's gain necessarily corresponds to another candidate's lost opportunity --- the absence of statistical significance on a given row does not mean the corresponding group is unaffected by blind hiring.

```{r blind_hiring_treatment_effects_demo, echo = FALSE, results = 'asis'}
## Treatment Effects of Blind Hiring
## Reference: Blind resumes (baseline)
## Shows effect of revealing each demographic vs. keeping it blind

## HR Models (with sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_hr_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"], vcov = ~ responseid)
))
names(models_hr_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

## Engineer Models (no sc_advance) - WITH RESPONDENT CHARACTERISTICS
models_eng_blind <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"], vcov = ~ responseid)
))
names(models_eng_blind) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

## Flip coefficient signs so a positive coefficient = effect of blinding.
flip_coef_signs <- function(model) {
  model$coefficients <- -1 * model$coefficients
  return(model)
}
models_hr_blind  <- lapply(models_hr_blind,  flip_coef_signs)
models_eng_blind <- lapply(models_eng_blind, flip_coef_signs)

## Coefficient map - ONLY show demographic coefficients
coef_map_blind <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female"
)

## Custom gof_map
gof_custom_blind <- tribble(
  ~raw,        ~clean,          ~fmt,
  "nobs",      "Observations",   0,
  "r.squared", "R2",             3
)

## FE / controls footer rows (displayed inside the table). Respondent FE and
## Respondent Characteristics are placed adjacent to make the contrast visible:
## we do NOT soak up respondent heterogeneity with a fixed effect, but we DO
## include respondent demographic controls as absorbing FEs + age polynomial.
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows_hr <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_hr) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

fe_rows_eng <- data.frame(
  c("Resume (Content) FE", "Display Position FE", "Respondent FE", "Respondent Characteristics"),
  c(chk, chk, nox, chk), c(chk, chk, nox, chk), c(chk, chk, nox, chk),
  c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows_eng) <- c("term", "Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

cat("\\begin{table}[H]\n")
cat("\\centering\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel A: HR}\n\n")

modelsummary(
  models_hr_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_hr,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7)

cat("\\end{minipage}\n")
cat("\\hfill\n")
cat("\\begin{minipage}[t]{0.48\\textwidth}\n")
cat("\\centering\n")
cat("\\textbf{Panel B: Engineer}\n\n")

modelsummary(
  models_eng_blind,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_blind,
  gof_map = gof_custom_blind,
  add_rows = fe_rows_eng,
  escape = FALSE,
  output = "kableExtra",
  table.attr = "style='width:100%;'"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 7)

cat("\\end{minipage}\n")
cat("\\par\\vspace{0.4em}\n")
cat("\\noindent\\begin{minipage}{0.96\\textwidth}\\scriptsize\n")
cat("\\textit{Standard errors clustered by respondent.} \\textit{Note on Interpreting Coefficients:} The underlying regression uses Blind resumes as the reference category, so raw coefficients capture (nonblind $-$ blind) or the effect of being blinded for each demographic on standardized overall evaluation scores. We then multiply by $-1$ to report (blind $-$ nonblind), aligning the sign convention with the standard \"effect of blinding\" framing. positive coefficient $\\Rightarrow$ blinding raises the score for that demographic.\n")
cat("\\end{minipage}\n")
cat("\\end{table}\n\n")

## Clean up
rm(models_hr_blind, models_eng_blind, coef_map_blind, gof_custom_blind, flip_coef_signs,
   chk, nox, fe_rows_hr, fe_rows_eng)
```


\newpage
## Does Blinding Lead to More Accurate Coding Evaluations?

\textcolor{blue}{\textbf{Takeaway}}: Evaluators do extract signal about candidates' actual coding ability --- Engineers much more strongly than HR, consistent with Engineers seeing the code while HR sees only the resume. Blinding, however, does \emph{not} meaningfully change this signal-extraction ability in either role: the $\texttt{true\_coding\_z} \times \texttt{blind}$ interaction is small, negative, and statistically insignificant for both HR and Engineers. If blinding --- which in our experiment amounts to removing random, uninformative demographic noise --- improved signal-extraction ability, we would expect a positive and statistically significant interaction term. In short, blinding \emph{reshuffles} who receives high scores (Section 1.1) but does not change \emph{how well} those scores track actual coding skill.

\textcolor{blue}{\textbf{Specification}}: For each role $\in \{\text{HR}, \text{Engineer}\}$, we fit
$$
\text{Hiring Evaluation Score (Z)} \sim \text{True Coding Ability (Z)} \times \mathbbm{1}[\text{Blind arm}] \mid \text{Respondent FE} + \text{Display Position FE}.
$$

In each of the four cells we test two nulls:

\begin{itemize}
    \item $H_0\!: \beta = 0$ --- the evaluator extracts \emph{no signal} from true coding ability.
    \item $H_0\!: \beta = 1$ --- the evaluator is \emph{perfectly calibrated}: a $1$ SD rise in true ability produces exactly a $1$ SD rise in the rating, with no shrinkage.
\end{itemize}

\noindent Running both tests separately by arm reveals whether blinding changes the evaluator's calibration, not merely whether signal is extracted at all.

```{r blind_hiring_signal_extraction, echo = FALSE, results = 'asis'}
## Pooled z-score of the lab coding score (constant within resume_index)
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]

## Two pooled interacted regressions --- one per role. Since treat is
## between-respondent, responseid FE absorbs the main effect of treat but
## leaves both the main slope on true_coding_z (identified from within-
## respondent variation, by definition the nonblind arm's slope since
## nonblind is the reference) and the interaction slope identifiable.
m_hr  <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
m_eng <- suppressMessages(suppressWarnings(
  feols(sc_coding_z ~ true_coding_z * i(treat, ref = "nonblind")
        | responseid + r_do,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))

## Extract arm-specific slopes, SEs, and the four tests (H0: beta = 0 / 1
## for each arm) from a single pooled model. beta_nonblind = main coef;
## beta_blind = main + interaction; SE(beta_blind) via linear-combination
## formula using the full vcov matrix.
extract_stats <- function(m) {
  ct    <- coeftable(m)
  V     <- vcov(m)
  main_name <- "true_coding_z"
  int_name  <- "true_coding_z:treat::blind"

  b_main <- ct[main_name, "Estimate"]
  s_main <- ct[main_name, "Std. Error"]
  b_int  <- ct[int_name,  "Estimate"]
  s_int  <- ct[int_name,  "Std. Error"]
  cov_mi <- V[main_name, int_name]

  b_nb <- b_main
  s_nb <- s_main
  b_b  <- b_main + b_int
  s_b  <- sqrt(s_main^2 + s_int^2 + 2 * cov_mi)

  pval <- function(t) 2 * (1 - pnorm(abs(t)))
  p_nb_0 <- pval(b_nb / s_nb)
  p_nb_1 <- pval((b_nb - 1) / s_nb)
  p_b_0  <- pval(b_b  / s_b)
  p_b_1  <- pval((b_b  - 1) / s_b)
  ## H0: beta_blind = beta_nonblind is the same as H0: beta_interaction = 0,
  ## so we read its p-value directly off the interaction coefficient.
  p_eq   <- ct[int_name, 4]

  fs <- fitstat(m, c("r2", "ar2"), simplify = TRUE)
  list(b_nb = unname(b_nb), s_nb = unname(s_nb),
       b_b  = unname(b_b),  s_b  = unname(s_b),
       p_nb_0 = p_nb_0, p_nb_1 = p_nb_1,
       p_b_0  = p_b_0,  p_b_1  = p_b_1,
       p_eq   = unname(p_eq),
       n = m$nobs, r2 = unname(fs["r2"]), ar2 = unname(fs["ar2"]))
}

s_hr  <- extract_stats(m_hr)
s_eng <- extract_stats(m_eng)

## Formatting helpers.
sig_stars <- function(p) {
  if (is.na(p))        ""
  else if (p < 0.01)   "***"
  else if (p < 0.05)   "**"
  else if (p < 0.10)   "*"
  else                 ""
}
fmt_p <- function(p) {
  if (is.na(p)) return("")
  pstr <- if (p < 0.001) "$<\\!0.001$" else sprintf("%.3f", p)
  paste0("p = ", pstr, sig_stars(p))
}

chk <- "\\checkmark"
nox <- "$\\times$"

cell_col <- function(s) c(
  sprintf("%.3f~(%.3f)", s$b_nb, s$s_nb),
  sprintf("%.3f~(%.3f)", s$b_b,  s$s_b),
  fmt_p(s$p_nb_0),
  fmt_p(s$p_nb_1),
  fmt_p(s$p_b_0),
  fmt_p(s$p_b_1),
  fmt_p(s$p_eq),
  format(s$n,   big.mark = ","),
  sprintf("%.3f", s$r2),
  sprintf("%.3f", s$ar2),
  nox, chk, chk, nox
)

tbl <- data.frame(
  lbl = c("$\\hat\\beta_{\\text{nonblind}}$ (slope, nonblind arm)",
          "$\\hat\\beta_{\\text{blind}}$ (slope, blind arm)",
          "$H_0\\!: \\beta_{\\text{nonblind}} = 0$",
          "$H_0\\!: \\beta_{\\text{nonblind}} = 1$",
          "$H_0\\!: \\beta_{\\text{blind}} = 0$",
          "$H_0\\!: \\beta_{\\text{blind}} = 1$",
          "$H_0\\!: \\beta_{\\text{blind}} = \\beta_{\\text{nonblind}}$",
          "Observations",
          "$R^2$",
          "Adj. $R^2$",
          "Resume (Content) FE",
          "Display Position FE",
          "Respondent FE",
          "Respondent Characteristics"),
  HR  = cell_col(s_hr),
  Eng = cell_col(s_eng),
  stringsAsFactors = FALSE,
  check.names = FALSE
)
names(tbl) <- c(" ", "HR", "Engineer")

cat("\\begin{table}[H]\n")
cat("\\centering\n")

kable(tbl, format = "latex", booktabs = TRUE, escape = FALSE,
      align = "lcc", row.names = FALSE) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  row_spec(2, extra_latex_after = "\\midrule") %>%
  row_spec(7, extra_latex_after = "\\midrule") %>%
  footnote(general = "Cluster-robust standard errors (by respondent) shown in parentheses next to each $\\\\hat\\\\beta$. Stars on p-values: * $p<0.10$, ** $p<0.05$, *** $p<0.01$. \\\\textit{Note:} Both arm-specific slopes come from a single pooled interacted regression per role, \\\\texttt{sc\\\\_coding\\\\_z \\\\textasciitilde\\\\ true\\\\_coding\\\\_z * i(treat, ref = 'nonblind') | responseid + r\\\\_do}; $\\\\hat\\\\beta_{\\\\text{nonblind}}$ is read off the main coefficient, and $\\\\hat\\\\beta_{\\\\text{blind}}$ is computed as (main + interaction) with SE derived via the standard linear-combination formula using the estimated variance--covariance matrix. The ``Resume (Content) FE'' row is marked as not included because $\\\\texttt{overall\\\\_score}$ is a resume-level property (one lab score per resume), so a resume-content FE would absorb the RHS and leave the main slope unidentified. ``Respondent Characteristics'' is marked as not included because respondent-level variables (age, gender, race, education, income) are all perfectly collinear with the respondent FE and therefore absorbed by it.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = TRUE, escape = FALSE)

cat("\\end{table}\n\n")

rm(m_hr, m_eng, s_hr, s_eng,
   extract_stats, sig_stars, fmt_p, cell_col,
   chk, nox, tbl)
```


\clearpage
# Treatment Effect: Heterogeneity by Demographics

\textcolor{blue}{\textbf{Takeaway}}: For HR, the effect of blinding does not vary with respondent--applicant demographic concordance. For Engineers, heterogeneity in the treatment effect emerges as the concordance definition tightens. On detailed race--gender, the finest cut of own-group similarity, blinding raises concordant applicants' Overall scores while reducing the nonconcordant group's scores. Concretely: candidates with concordant race and gender profiles gain 7.1\% of a SD, and those with nonconcordant profiles lose 1.1\% of a SD, on their evaluation scores under blinding. This is consistent with the earlier finding in \texttt{8A\_Preferences.pdf} \S2 that Engineers in our sample penalize candidates who match them on race and gender --- a pattern driven mainly by White Male Engineers' assignment of a premium to non-White candidates.

## By Concordant Race

```{r bh_heterogeneity_concordance_race, echo = FALSE, results = 'asis'}
## Tri-level variable: Blind / Nonblind-Concordant / Nonblind-Nonconcordant
## Use detailed-race concordance: Asian respondents are matched at the
## sub-ethnicity level (Chinese / Indian). Korean / Japanese / other-Asian
## respondents in nonblind are coded as always-discordant in 5_Cleaning.R,
## so they remain in the regression rather than being dropped.
firm_long_dt[, blind_concordance_race := fcase(
  treat == "blind",                                     "Blind",
  treat == "nonblind" & concordance_race_detailed == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_detailed == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race := factor(blind_concordance_race,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

## HR and Engineer regressions — same FE skeleton as Section 1.1
models_hr_bh_conc_race <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_race, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_race) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_race <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_race, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_race) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_race  <- lapply(models_hr_bh_conc_race,  flip_coef_signs)
models_eng_bh_conc_race <- lapply(models_eng_bh_conc_race, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_race, models_eng_bh_conc_race)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")  # trailing space disambiguator

coef_map_conc <- c(
  "blind_concordance_race::Nonblind_Concordant"    = "Effect of Blinding on Concordant Applicant",
  "blind_concordance_race::Nonblind_Nonconcordant" = "Effect of Blinding on Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)

n_hr_wah  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_race), responseid])
n_eng_wah <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_race), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_wah, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_wah, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(7, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined at the detailed race level: Asian respondents are matched at the sub-ethnicity level (Chinese / Indian). Respondents whose race is not represented in the applicant pool (e.g., Black, Other; Korean / Japanese / other-Asian whose sub-ethnicity is not Chinese or Indian) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_race, models_eng_bh_conc_race, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_wah, n_eng_wah, panel_a_lbl, panel_b_lbl)
```


## By Concordant Gender

```{r bh_heterogeneity_concordance_gender, echo = FALSE, results = 'asis'}
firm_long_dt[, blind_concordance_gender := fcase(
  treat == "blind",                              "Blind",
  treat == "nonblind" & concordance_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_gender := factor(blind_concordance_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

models_hr_bh_conc_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_gender) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_gender <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_gender) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_gender  <- lapply(models_hr_bh_conc_gender,  flip_coef_signs)
models_eng_bh_conc_gender <- lapply(models_eng_bh_conc_gender, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_gender, models_eng_bh_conc_gender)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "blind_concordance_gender::Nonblind_Concordant"    = "Effect of Blinding on Concordant Applicant",
  "blind_concordance_gender::Nonblind_Nonconcordant" = "Effect of Blinding on Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)

n_hr_mf  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_gender), responseid])
n_eng_mf <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_gender), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_mf, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_mf, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(7, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Respondents whose gender is not represented in the applicant pool (e.g., Non-binary, Other) are treated as always-discordant in nonblind, since the applicant names are exclusively Male or Female.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_gender, models_eng_bh_conc_gender, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_mf, n_eng_mf, panel_a_lbl, panel_b_lbl)
```


\clearpage
## By Concordant Race and Gender

```{r bh_heterogeneity_concordance_broad, echo = FALSE, results = 'asis'}
## Weaker-concordance robustness check: race-gender match at the broad level.
## Asian respondents (regardless of detailed sub-group: Chinese, Indian,
## Korean, Japanese, etc.) match Asian applicants. Uses the pre-built
## `concordance_race_gender` (= 1 if race_gender == resp_race_gender at the
## {White, Asian, Hispanic} x {Male, Female} level).
firm_long_dt[, blind_concordance_race_gender := fcase(
  treat == "blind",                                   "Blind",
  treat == "nonblind" & concordance_race_gender == 1, "Nonblind_Concordant",
  treat == "nonblind" & concordance_race_gender == 0, "Nonblind_Nonconcordant",
  default = NA_character_
)]
firm_long_dt[, blind_concordance_race_gender := factor(blind_concordance_race_gender,
  levels = c("Blind", "Nonblind_Concordant", "Nonblind_Nonconcordant"))]

models_hr_bh_conc_rg <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(blind_concordance_race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_rg) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_rg <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(blind_concordance_race_gender, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_rg) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_rg  <- lapply(models_hr_bh_conc_rg,  flip_coef_signs)
models_eng_bh_conc_rg <- lapply(models_eng_bh_conc_rg, flip_coef_signs)

all_models <- c(models_hr_bh_conc_rg, models_eng_bh_conc_rg)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "blind_concordance_race_gender::Nonblind_Concordant"    = "Effect of Blinding on Concordant Applicant",
  "blind_concordance_race_gender::Nonblind_Nonconcordant" = "Effect of Blinding on Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)

n_hr_wah  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(blind_concordance_race_gender), responseid])
n_eng_wah <- uniqueN(firm_long_dt[role == "Eng" & !is.na(blind_concordance_race_gender), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_wah, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_wah, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(7, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined as race-gender match at the broad level (Asian respondents are matched at the broad Asian level rather than by detailed sub-ethnicity). Respondents whose race or gender is not represented in the applicant pool (e.g., Black, Other; Non-binary, Other-gender) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_rg, models_eng_bh_conc_rg, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_wah, n_eng_wah, panel_a_lbl, panel_b_lbl)
```


## By Concordant Race and Gender (matched on detailed Asian Ethnicity)

```{r bh_heterogeneity_concordance_detailed, echo = FALSE, results = 'asis'}
## Uses the pre-built `concordance_race_gender_detailed_blind` factor from
## 5_Cleaning.R. Asian respondents whose detailed sub-ethnicity (e.g.,
## Korean, Japanese) is not represented in the applicant pool are coded as
## always-discordant in nonblind, so they are kept in the regression rather
## than dropped.

models_hr_bh_conc_det <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z, sc_advance) ~
          i(concordance_race_gender_detailed_blind, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
))
names(models_hr_bh_conc_det) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)", "Advance (0/1)")

models_eng_bh_conc_det <- suppressMessages(suppressWarnings(
  feols(c(sc_coding_z, sc_fit_z, sc_stay_z, sc_overall_z) ~
          i(concordance_race_gender_detailed_blind, ref = "Blind") +
          resp_age + I(resp_age^2) + I(resp_age^3)
        | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
))
names(models_eng_bh_conc_det) <- c("Coding (Z)", "Fit (Z)", "Stay (Z)", "Overall (Z)")

flip_coef_signs <- function(model) { model$coefficients <- -1 * model$coefficients; return(model) }
models_hr_bh_conc_det  <- lapply(models_hr_bh_conc_det,  flip_coef_signs)
models_eng_bh_conc_det <- lapply(models_eng_bh_conc_det, flip_coef_signs)

## Combine into one model list for a single wide table.
all_models <- c(models_hr_bh_conc_det, models_eng_bh_conc_det)
names(all_models) <- c("Coding", "Fit", "Stay", "Overall", "Advance",
                       "Coding ", "Fit ", "Stay ", "Overall ")

coef_map_conc <- c(
  "concordance_race_gender_detailed_blind::Concordant_Group" = "Effect of Blinding on Concordant Applicant",
  "concordance_race_gender_detailed_blind::Discordant_Group" = "Effect of Blinding on Nonconcordant Applicant"
)

gof_custom_conc <- tribble(
  ~raw,            ~clean,          ~fmt,
  "nobs",          "Observations",   0,
  "r.squared",     "R$^2$",          3,
  "adj.r.squared", "Adj. R$^2$",     3
)

chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Resume (Content) FE", "Display Position FE",
           "Respondent FE", "Respondent Characteristics"),
  V1 = c(chk, chk, nox, chk), V2 = c(chk, chk, nox, chk),
  V3 = c(chk, chk, nox, chk), V4 = c(chk, chk, nox, chk),
  V5 = c(chk, chk, nox, chk), V6 = c(chk, chk, nox, chk),
  V7 = c(chk, chk, nox, chk), V8 = c(chk, chk, nox, chk),
  V9 = c(chk, chk, nox, chk),
  stringsAsFactors = FALSE
)

n_hr_det  <- uniqueN(firm_long_dt[role == "HR"  & !is.na(concordance_race_gender_detailed_blind), responseid])
n_eng_det <- uniqueN(firm_long_dt[role == "Eng" & !is.na(concordance_race_gender_detailed_blind), responseid])

panel_a_lbl <- paste0("Panel A: HR (N = ", n_hr_det, ")")
panel_b_lbl <- paste0("Panel B: Engineer (N = ", n_eng_det, ")")

modelsummary(
  all_models,
  stars = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_conc,
  gof_map  = gof_custom_conc,
  add_rows = fe_rows,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 6) %>%
  add_header_above(setNames(c(1, 5, 4), c(" ", panel_a_lbl, panel_b_lbl))) %>%
  row_spec(7, extra_latex_after = "\\midrule") %>%
  footnote(general = c(
             "Standard errors clustered by respondent.",
             "\\\\textit{Note:} Concordance is defined at the detailed race-gender level: applicants are Chinese, Indian, White, or Hispanic (by gender). Respondents whose detailed race-gender is not represented in the applicant pool (e.g., Korean / Japanese / other-Asian sub-ethnicities; Black, Other-race; Non-binary, Other-gender) are treated as always-discordant in nonblind.",
             "Coefficients are flipped so positive $\\\\Rightarrow$ blinding raises the score for that concordance group relative to the nonblind outcome."
           ),
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(models_hr_bh_conc_det, models_eng_bh_conc_det, all_models,
   coef_map_conc, gof_custom_conc, flip_coef_signs, chk, nox, fe_rows,
   n_hr_det, n_eng_det, panel_a_lbl, panel_b_lbl)
```


\clearpage
# Treatment Effect: Heterogeneity by DEI / Diversity Preferences

\textcolor{blue}{\textbf{Takeaway}}: [To be filled after first render. Parallel to 8A \S3, we ask whether the effect of blinding on evaluation scores varies with (a) respondent DEI / diversity preferences, (b) whether the respondent's firm targets the same demographic as the applicant, and (c) the triple interaction of respondent DEI priority with firm DEI attention.]

\vspace{0.2em}

\noindent \textit{Sign convention}: Throughout \S3, all displayed coefficients are \emph{flipped} so that positive $\Rightarrow$ blinding raises the relative score for that demographic (mirroring the convention in \S1.1). The underlying regressions use Blind as the reference category for \texttt{race\_gender}; multiplying by $-1$ converts (nonblind $-$ blind) into (blind $-$ nonblind), i.e.\ the effect of blinding.


## (2-way Interaction Models) By Individual DEI / Diversity Variables

\textcolor{blue}{\textbf{Takeaway}}: Mirroring 8A \S3's null on preference heterogeneity, most individual DEI / diversity proxies do not meaningfully moderate the effect of blinding on demographic groups. Two exceptions stand out. For HR, respondent-perceived firm DEI attention interacts strongly with the blinding effect on Hispanic Male applicants ($+0.188^{***}$ for Firm Race DEI Attention; $+0.133^{***}$ for Firm Gender DEI Attention) --- a firm-level substitution pattern in which HR evaluators at firms with high DEI attention penalize Hispanic Males under nonblind, and blinding mechanically recovers those penalties. For Engineers, individual-level pro-DEI proxies (Race DEI, Gender DEI, Diverse Workplace, Diversity Priority) consistently interact \emph{negatively} with the blinding effect on Hispanic Males ($-0.057$ to $-0.081$, $p < 0.05$ or tighter on each) --- an individual-level DEI-premium pattern in which pro-DEI Engineers are more generous to Hispanic Males under nonblind. The two channels operate in different places: firm-level substitution for HR; individual-level DEI premium for Engineers.

```{r bh_dei_overall, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

proxies <- c(
  "pro_dei_race_z",
  "pro_dei_gender_z",
  "pro_diverse_z",
  "div_priority_z",
  "firm_attention_race_z",
  "firm_attention_gender_z"
)
col_labels <- c("Race DEI", "Gender DEI", "Diverse Wkpl", "Div Goal",
                "Firm Race Attn", "Firm Gender Attn")

## LHS is negated so that all coefficients flip at the regression level;
## etable (unlike modelsummary) ignores post-hoc overrides of $coefficients,
## so we flip via I(-sc_overall_z) instead of via a flip_coef_signs wrapper.
fit_one <- function(d, pr) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      pr)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(proxies, function(p) fit_one(dt_hr,  p))
models_eng <- lapply(proxies, function(p) fit_one(dt_eng, p))
all_models <- c(models_hr, models_eng)

groups <- c("White_Male"      = "White Male",
            "White_Female"    = "White Female",
            "Asian_Male"      = "Asian Male",
            "Asian_Female"    = "Asian Female",
            "Hispanic_Male"   = "Hispanic Male",
            "Hispanic_Female" = "Hispanic Female")

dict_main  <- setNames(unname(groups), paste0("race_gender::", names(groups)))
dict_inter <- unlist(lapply(proxies, function(p) {
  setNames(paste0(unname(groups), " $\\times$ Pro DEI/Diversity (Z)"),
           paste0("race_gender::", names(groups), ":", p))
}))
dict_all <- c(dict_main, dict_inter)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%race_gender",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume (Content) FE"      = rep(chk, 12),
    "Display Position FE"      = rep(chk, 12),
    "Respondent Demographic FE" = rep(chk, 12)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")

tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{13}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{6}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-7} \\\\cmidrule(lr){8-13}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)

tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, proxies, col_labels, fit_one,
   models_hr, models_eng, all_models, groups, dict_main, dict_inter, dict_all,
   chk, tbl, proxy_hdr)
```


\newpage
\noindent \textbf{Reproduction with three DEI / Diversity Index Options.} The same regression as above, replacing the six individual DEI proxies with three composite indices: \textit{Index A: Stated} --- the four-item average of stated DEI views; \textit{Index B: Stated + Revealed} --- equal-weight composite of Index A and the revealed-priority ranking of ``Diversity and Representation'' from the goals question; \textit{Index C: PC1} --- first principal component of the same five items.

```{r bh_dei_indices_overall, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")

fit_one <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(race_gender, ref = 'Blind') + i(race_gender, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(indices, function(p) fit_one(dt_hr,  p))
models_eng <- lapply(indices, function(p) fit_one(dt_eng, p))
all_models <- c(models_hr, models_eng)

groups <- c("White_Male"     = "White Male",
            "White_Female"   = "White Female",
            "Asian_Male"     = "Asian Male",
            "Asian_Female"   = "Asian Female",
            "Hispanic_Male"  = "Hispanic Male",
            "Hispanic_Female"= "Hispanic Female")

dict_main  <- setNames(unname(groups), paste0("race_gender::", names(groups)))
dict_inter <- unlist(lapply(indices, function(p) {
  setNames(paste0(unname(groups), " $\\times$ DEI Index"),
           paste0("race_gender::", names(groups), ":", p))
}))
dict_all <- c(dict_main, dict_inter)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%race_gender",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  notes = "Index A is the existing four-item average of stated DEI views. Index B averages Index A with the respondent's revealed-priority ranking of ``Diversity and Representation'' from the seven-goals question. Index C is the first principal component of the same five items, sign-aligned so higher = more pro-DEI. Coefficients are flipped via I(-sc\\_overall\\_z) so positive => effect of blinding. Standard errors clustered by respondent. Sample: both blind and nonblind arms.",
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 6),
    "Display Position FE"       = rep(chk, 6),
    "Respondent Demographic FE" = rep(chk, 6)
  )
)

idx_hdr <- paste(idx_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{7}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- Three DEI / Diversity Index Options, signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-4} \\\\cmidrule(lr){5-7}",
    " & ", idx_hdr, " & ", idx_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
## Force equal-width centered data columns (the 6 model columns); the auto-width
## `c` columns can become uneven when a multicolumn spanning header on one panel
## is wider than the other.
tbl <- sub("\\{lcccccc\\}",
           "{l*{6}{>{\\\\centering\\\\arraybackslash}p{0.7in}}}",
           tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, indices, idx_labels, fit_one, models_hr, models_eng, all_models,
   groups, dict_main, dict_inter, dict_all, chk, tbl, idx_hdr)
```


```{r bh_dei_urm, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

zstd <- function(x) (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)

## Combined indices: row-mean of two z-scored measures, re-standardized within sample.
dt_hr [, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_eng[, pro_dei_view_z   := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("pro_dei_race_z", "pro_dei_gender_z")]
dt_hr [, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]
dt_eng[, firm_attention_z := zstd(rowMeans(as.matrix(.SD), na.rm = FALSE)),
       .SDcols = c("firm_attention_race_z", "firm_attention_gender_z")]

proxies    <- c("pro_dei_view_z", "pro_diverse_z", "div_priority_z", "firm_attention_z")
col_labels <- c("DEI Views (R \\\\& G)", "Diverse Wkpl", "Div Goal", "Firm DEI Attn (R \\\\& G)")

## Here we build a URM-tech x Blind indicator by hand.
## urm_tech_blind_factor: Blind / Nonblind-URM / Nonblind-NonURM
dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                           "Blind",
  treat == "nonblind" & urm_tech == 1,         "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0,         "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                           "Blind",
  treat == "nonblind" & urm_tech == 1,         "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0,         "Nonblind_NonURM",
  default = NA_character_
)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

## LHS negated so coefficients flip at the regression level (etable does not
## respect post-hoc overrides of $coefficients).
fit_urm <- function(d, pr) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      pr)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(proxies, function(p) fit_urm(dt_hr,  p))
models_eng <- lapply(proxies, function(p) fit_urm(dt_eng, p))
all_models <- c(models_hr, models_eng)

dict_all <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM (WF, AF, HM, HF)",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ Pro DEI/Diversity (Z)",    length(proxies)),
           paste0("urm_tech_blind::Nonblind_URM:",    proxies)),
  setNames(rep("Non-URM $\\times$ Pro DEI/Diversity (Z)", length(proxies)),
           paste0("urm_tech_blind::Nonblind_NonURM:", proxies))
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 8),
    "Display Position FE"       = rep(chk, 8),
    "Respondent Demographic FE" = rep(chk, 8)
  )
)

proxy_hdr <- paste(col_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{9}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{4}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-5} \\\\cmidrule(lr){6-9}",
    " & ", proxy_hdr, " & ", proxy_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, zstd, proxies, col_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, proxy_hdr)
```


\newpage
\noindent \textbf{Reproduction (URM cut) with three DEI / Diversity Index Options.}

```{r bh_dei_indices_urm, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")

fit_urm <- function(d, idx) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx)),
    data = d, vcov = ~ responseid
  )))
}

models_hr  <- lapply(indices, function(p) fit_urm(dt_hr,  p))
models_eng <- lapply(indices, function(p) fit_urm(dt_eng, p))
all_models <- c(models_hr, models_eng)

dict_all <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM (WF, AF, HM, HF)",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ DEI Index",    length(indices)),
           paste0("urm_tech_blind::Nonblind_URM:",    indices)),
  setNames(rep("Non-URM $\\times$ DEI Index", length(indices)),
           paste0("urm_tech_blind::Nonblind_NonURM:", indices))
)

chk <- "\\checkmark"

tbl <- etable(
  all_models,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H",
  depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_all,
  notes = "URM-Tech = \\{White Female, Asian Female, Hispanic Male, Hispanic Female\\}. Sample: both blind and nonblind arms. Coefficients flipped via I(-sc\\_overall\\_z) so positive => effect of blinding. Standard errors clustered by respondent.",
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 6),
    "Display Position FE"       = rep(chk, 6),
    "Respondent Demographic FE" = rep(chk, 6)
  )
)

idx_hdr <- paste(idx_labels, collapse = " & ")
tbl <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{7}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- URM Cut, Three DEI / Diversity Index Options, signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel A: HR}}",
    " & \\\\multicolumn{3}{c}{\\\\textbf{Panel B: Engineer}} \\\\\\\\",
    " \\\\cmidrule(lr){2-4} \\\\cmidrule(lr){5-7}",
    " & ", idx_hdr, " & ", idx_hdr, " \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl
)
tbl <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl)
## Force equal-width centered data columns (see note in indices_overall chunk).
tbl <- sub("\\{lcccccc\\}",
           "{l*{6}{>{\\\\centering\\\\arraybackslash}p{0.7in}}}",
           tbl)
tbl <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl
)
tbl <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl)

cat(tbl)

rm(dt_hr, dt_eng, indices, idx_labels, fit_urm,
   models_hr, models_eng, all_models, dict_all, chk, tbl, idx_hdr)
```


\vspace{0.6em}
\noindent \textbf{Visual: URM--Non-URM gap under nonblind by DEI Index (Indices A, B, C).} Each row is one of the three DEI indices; columns are role. The single curve in each panel plots the URM--Non-URM premium under nonblind --- exactly the gap that blinding eliminates by random assignment. Positive values: URM rated higher than Non-URM under nonblind. Negative values: Non-URM rated higher. Shaded band is the 95\% CI; the dashed line at zero marks where blinding has no reshuffling effect.

```{r bh_dei_indices_urm_plot, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 8.5, fig.align = 'center'}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

fit_dei <- function(d, idx_var) {
  feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx_var)),
    data = d, vcov = ~ responseid)
}

## Gap = URM - NonURM under nonblind, in raw scale. Model is in flipped scale;
## gap_raw uses -1 on URM and +1 on NonURM contrast vectors.
compute_gap_dei <- function(model, role_label, idx_var) {
  cf <- coef(model); vc <- vcov(model)
  c_urm    <- "urm_tech_blind::Nonblind_URM"
  c_nurm   <- "urm_tech_blind::Nonblind_NonURM"
  c_urm_x  <- paste0("urm_tech_blind::Nonblind_URM:",    idx_var)
  c_nurm_x <- paste0("urm_tech_blind::Nonblind_NonURM:", idx_var)
  idx_grid <- seq(-2, 2, by = 0.1)
  out_list <- vector("list", length(idx_grid))
  for (i in seq_along(idx_grid)) {
    iv <- idx_grid[i]
    a <- setNames(numeric(length(cf)), names(cf))
    a[c_urm]    <- -1
    a[c_nurm]   <-  1
    a[c_urm_x]  <- -iv
    a[c_nurm_x] <-  iv
    out_list[[i]] <- data.table(
      role    = role_label,
      idx_val = iv,
      gap     = sum(a * cf),
      se      = sqrt(as.numeric(t(a) %*% vc %*% a))
    )
  }
  rbindlist(out_list)
}

indices_to_plot <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels      <- c("Index A", "Index B", "Index C")

dat_all <- rbindlist(lapply(seq_along(indices_to_plot), function(k) {
  iv  <- indices_to_plot[k]
  lbl <- idx_labels[k]
  m_hr  <- fit_dei(dt_hr,  iv)
  m_eng <- fit_dei(dt_eng, iv)
  d <- rbind(compute_gap_dei(m_hr,  "HR",       iv),
             compute_gap_dei(m_eng, "Engineer", iv))
  d[, idx_label := lbl]
  d
}))

dat_all[, ci_lo := gap - 1.96 * se]
dat_all[, ci_hi := gap + 1.96 * se]
dat_all[, role  := factor(role, levels = c("HR", "Engineer"))]
dat_all[, idx_label := factor(idx_label, levels = idx_labels)]

p_3_1 <- ggplot(dat_all, aes(x = idx_val, y = gap)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_ribbon(aes(ymin = ci_lo, ymax = ci_hi), fill = "steelblue", alpha = 0.25) +
  geom_line(color = "steelblue", linewidth = 1.2) +
  facet_grid(idx_label ~ role) +
  labs(x = "DEI Index (z-score)",
       y = "URM − Non-URM gap under nonblind") +
  theme_minimal(base_size = 11) +
  theme(panel.grid.minor = element_blank(),
        strip.text = element_text(face = "bold"))

print(p_3_1)

rm(dt_hr, dt_eng, fit_dei, compute_gap_dei, indices_to_plot, idx_labels,
   dat_all, p_3_1)
```


\newpage
## (2-way Interaction Models) By Whether the Firm Targets the Same Applicant Demographic

\textcolor{blue}{\textbf{Takeaway}}: The substitution hypothesis is a \emph{null} at the level it can be cleanly tested. The bottom table's URM-aggregate match coefficient (URM $\times$ Firm Targets URM) is insignificant in both roles, and so is the Non-URM spillover. The top table is descriptive only: per-demographic match cells are identified off too few respondents to support inference (we restrict it to the URM-aligned dimensions Female and Hispanic and drop the rest, since White / Asian / Male match cells are either non-URM-aligned or fire on $\le 2$ unique respondents per role). The one mover --- Engineer's \texttt{applicant female $\times$ firm targets female} --- points in the substitution direction but is identified off $\approx 5$ respondents and should be read as suggestive. The cleaner Engineer signal lives in the \emph{main effects}: blinding \emph{lowers} URM applicants' Overall scores and \emph{raises} Non-URM scores (significant at the $5\%$ level), reproducing the Engineer non-concordance premium documented in \S1.1 and \S2 net of firm-targeting controls.

```{r bh_dei_targets, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

## Applicant-match indicators (0 for Blind resumes, since demo is hidden).
## Only Female and Hispanic match interactions are tested in the top table:
##  - White / Asian / Male match cells are identified off too few respondents
##    (1-2 per role for White and Asian; ~11-18 for Male) and Asian / Male are
##    not URM-aligned target dimensions in our tech context.
##  - Female and Hispanic are the URM-side dimensions where the substitution
##    hypothesis has a well-defined prediction.
prep <- function(d) {
  d[, appl_female   := as.integer(treat == "nonblind" & gender == "Female")]
  d[, appl_hispanic := as.integer(treat == "nonblind" & race   == "Hispanic")]
  d[, firm_targets_fh  := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L)]
  d[, firm_targets_fhb := as.integer(firm_targets_female == 1L | firm_targets_hispanic == 1L | firm_targets_black == 1L)]
  invisible(d)
}
prep(dt_hr); prep(dt_eng)

chk <- "\\checkmark"

## ---------- TOP: joint four-match regression per role ----------
## LHS is negated so all coefficients flip at the regression level; etable
## does not respect post-hoc $coefficients overrides.
fit_match_joint <- function(d) {
  suppressMessages(suppressWarnings(feols(
    I(-sc_overall_z) ~ i(race_gender, ref = "Blind")
                 + appl_female   : firm_targets_female
                 + appl_hispanic : firm_targets_hispanic
                 + resp_age + I(resp_age^2) + I(resp_age^3)
                 | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income,
    data = d, vcov = ~ responseid
  )))
}

m_hr_t  <- fit_match_joint(dt_hr)
m_eng_t <- fit_match_joint(dt_eng)

dict_t <- c(
  "race_gender::White_Male"             = "White Male",
  "race_gender::White_Female"           = "White Female",
  "race_gender::Asian_Male"             = "Asian Male",
  "race_gender::Asian_Female"           = "Asian Female",
  "race_gender::Hispanic_Male"          = "Hispanic Male",
  "race_gender::Hispanic_Female"        = "Hispanic Female",
  "appl_female:firm_targets_female"     = "Applicant Female $\\times$ Firm Targets Female",
  "appl_hispanic:firm_targets_hispanic" = "Applicant Hispanic $\\times$ Firm Targets Hispanic"
)

tbl_t <- etable(
  list("HR" = m_hr_t, "Engineer" = m_eng_t),
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = c("%race_gender", "%appl_"),
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_t,
  notes = "Each Applicant X x Firm Targets X is a match interaction, identified off applicant rows whose demographic equals the firm's targeting dimension. Standard errors clustered by respondent. Sample: both blind and nonblind arms.",
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 2),
    "Display Position FE"       = rep(chk, 2),
    "Respondent Demographic FE" = rep(chk, 2)
  )
)

tbl_t <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{3}{c}{\\\\textbf{Firm Targets $\\\\times$ Same Applicant Demographic --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\textbf{Panel A: HR} & \\\\textbf{Panel B: Engineer} \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_t
)
tbl_t <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_t)
tbl_t <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
  tbl_t
)
tbl_t <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_t)

cat(tbl_t)

## ---------- BOTTOM: URM-Tech x Combined firm-target dummy ----------
dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
## Factor-level order is local to this chunk and controls the etable display
## order: Non-URM main, URM main, then Non-URM:firm_targets_fh (spillover),
## then URM:firm_targets_fh (match) -- matches the table's narrative arc.
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_NonURM", "Nonblind_URM"))]

fit_urm_t <- function(d, target_var) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      target_var)),
    data = d, vcov = ~ responseid
  )))
}

targets      <- c("firm_targets_fh")
col_labels_b <- c("Targets F or H")

models_hr_b  <- lapply(targets, function(t) fit_urm_t(dt_hr,  t))
models_eng_b <- lapply(targets, function(t) fit_urm_t(dt_eng, t))
all_models_b <- c(models_hr_b, models_eng_b)

dict_b <- c(
  "urm_tech_blind::Nonblind_URM"    = "URM (WF, AF, HM, HF)",
  "urm_tech_blind::Nonblind_NonURM" = "Non-URM",
  setNames(rep("URM $\\times$ Firm Targets URM",                       length(targets)),
           paste0("urm_tech_blind::Nonblind_URM:",    targets)),
  setNames(rep("Non-URM $\\times$ Firm Targets URM (spillover)",       length(targets)),
           paste0("urm_tech_blind::Nonblind_NonURM:", targets))
)

tbl_b <- etable(
  all_models_b,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = "%urm_tech_blind",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_b,
  notes = "URM = \\{WF, AF, HM, HF\\}. ``Firm Targets URM'' => firm\\_targets\\_female = 1 OR firm\\_targets\\_hispanic = 1. The URM row is the aggregate match; the Non-URM row is a spillover test (does targeting URM groups also shift the blinding effect on Non-URM applicants?). Standard errors clustered by respondent. Sample: both blind and nonblind arms.",
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 2),
    "Display Position FE"       = rep(chk, 2),
    "Respondent Demographic FE" = rep(chk, 2)
  )
)

tbl_b <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{3}{c}{\\\\textbf{URM-Tech Binary Cut $\\\\times$ Firm Targets (Female OR Hispanic) --- signs flipped}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\textbf{Panel A: HR} & \\\\textbf{Panel B: Engineer} \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_b
)
tbl_b <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_b)
tbl_b <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{2pt}\\\\renewcommand{\\\\arraystretch}{0.82}\\\\begin{tabular}",
  tbl_b
)
tbl_b <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_b)

cat(tbl_b)

rm(dt_hr, dt_eng, prep, fit_match_joint, m_hr_t, m_eng_t,
   dict_t, tbl_t, fit_urm_t, targets, col_labels_b,
   models_hr_b, models_eng_b, all_models_b, dict_b, tbl_b, chk)
```



\newpage
## (Triple Interaction Models) By Respondent's Priority for DEI $\times$ Firm Attention on DEI

\textcolor{blue}{\textbf{Takeaway}}: For HR, the alignment of respondent's DEI priority with firm's DEI attention substitutes for blinding: at pro-DEI individuals $\times$ pro-DEI firms, blinding has near-zero effect on either URM or Non-URM applicants, while at anti-DEI $\times$ anti-DEI it flips a $\sim 0.40$ SD nonblind premium favoring Non-URM (URM $\times$ DEI Index $\times$ Firm DEI Attn $= +0.09^{***}$; Non-URM mirror $= -0.19^{***}$). Engineers show null moderation on both groups --- DEI-driven heterogeneity in treatment effects lives in HR's evaluations, not Engineers'.

\textcolor{blue}{\textbf{Hypothesis}}: Same \textbf{Substitution vs.\ Backlash} structure as 8A \S3, now applied to the blinding effect on URM applicants.

\begin{itemize}
    \item \textbf{Substitution}: When the firm already prioritizes DEI, respondents who \emph{also} personally prioritize DEI absorb the firm's push and ease off their own URM premium under nonblind. Blinding therefore bites \emph{less} for them (small effect of blinding on URM), because their nonblind ratings were already closer to the demographically blind baseline. \emph{Expect a negative sign on the triple interaction term.}
    \item \textbf{Backlash}: When the firm prioritizes DEI, respondents who do \emph{not} personally prioritize DEI react by marking URM applicants lower under nonblind. Blinding therefore bites \emph{more} for them (large positive effect of blinding on URM). \emph{Expect a positive sign on the triple interaction term.}
\end{itemize}

```{r bh_dei_triple, eval = FALSE, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_
)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

chk <- "\\checkmark"

## LHS negated so all coefficients flip at the regression level; etable does
## not respect post-hoc $coefficients overrides.
fit_triple_urm <- function(d, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, div_priority_z, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(div_priority_z * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      proxy_b, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

m_hr_r  <- fit_triple_urm(dt_hr,  "firm_attention_race_z")
m_eng_r <- fit_triple_urm(dt_eng, "firm_attention_race_z")
m_hr_g  <- fit_triple_urm(dt_hr,  "firm_attention_gender_z")
m_eng_g <- fit_triple_urm(dt_eng, "firm_attention_gender_z")

n_used <- c(
  dt_hr [!is.na(firm_attention_race_z),    uniqueN(responseid)],
  dt_eng[!is.na(firm_attention_race_z),   uniqueN(responseid)],
  dt_hr [!is.na(firm_attention_gender_z),  uniqueN(responseid)],
  dt_eng[!is.na(firm_attention_gender_z), uniqueN(responseid)]
)
n_full <- c(
  dt_hr [, uniqueN(responseid)],
  dt_eng[, uniqueN(responseid)],
  dt_hr [, uniqueN(responseid)],
  dt_eng[, uniqueN(responseid)]
)
n_drop <- n_full - n_used

models_trp <- list("HR (Race)" = m_hr_r, "Eng (Race)" = m_eng_r,
                   "HR (Gender)" = m_hr_g, "Eng (Gender)" = m_eng_g)

dict_trp <- c(
  "urm_tech_blind::Nonblind_URM"                                       = "URM (WF, AF, HM, HF)",
  "urm_tech_blind::Nonblind_URM:div_priority_z"                        = "URM $\\times$ Respondent Prioritizes Diversity",
  "urm_tech_blind::Nonblind_URM:firm_attention_race_z"                 = "URM $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:firm_attention_gender_z"               = "URM $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:I(div_priority_z * firm_attention_race_z)"   = "URM $\\times$ Resp Prioritizes $\\times$ Firm DEI Attn",
  "urm_tech_blind::Nonblind_URM:I(div_priority_z * firm_attention_gender_z)" = "URM $\\times$ Resp Prioritizes $\\times$ Firm DEI Attn"
)

tbl_trp <- etable(
  models_trp,
  tex = TRUE, style.tex = style.tex("aer"),
  placement = "H", depvar = FALSE,
  keep = "%urm_tech_blind::Nonblind_URM",
  fitstat = c("n", "ar2"),
  drop.section = "fixef",
  digits = 3, se.below = TRUE,
  signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
  dict = dict_trp,
  extralines = list(
    "Resume (Content) FE"       = rep(chk, 4),
    "Display Position FE"       = rep(chk, 4),
    "Respondent Demographic FE" = rep(chk, 4),
    "Respondents (used)"        = as.character(n_used),
    "Dropped (NA proxy)"        = as.character(n_drop)
  )
)

tbl_trp <- sub(
  "\\\\toprule",
  paste0(
    "\\\\multicolumn{5}{c}{\\\\textbf{Outcome Var: Assigned Overall Score (Z) --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
    "\\\\toprule",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Race-DEI Attn}}",
    " & \\\\multicolumn{2}{c}{\\\\textbf{Firm Gender-DEI Attn}} \\\\\\\\",
    " \\\\cmidrule(lr){2-3} \\\\cmidrule(lr){4-5}",
    " & HR & Eng & HR & Eng \\\\\\\\ \\\\addlinespace[2pt]"
  ),
  tbl_trp
)
tbl_trp <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_trp)
tbl_trp <- sub(
  "\\\\begin\\{tabular\\}",
  "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
  tbl_trp
)
tbl_trp <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_trp)

cat(tbl_trp)

rm(dt_hr, dt_eng, chk, fit_triple_urm, m_hr_r, m_eng_r, m_hr_g, m_eng_g,
   models_trp, dict_trp, tbl_trp, n_used, n_full, n_drop)
```


\newpage
\noindent \textbf{Reproduction with three DEI / Diversity Index Options.} The same triple-interaction structure as above, but replacing the single revealed-priority variable (\texttt{div\_priority\_z}) with each of three composite DEI indices in turn. One sub-table per index; each reports HR vs.\ Eng under the combined firm-DEI-attention-level proxy (\texttt{firm\_dei\_attention\_z}).

```{r bh_dei_indices_triple, echo = FALSE, results = 'asis', warning = FALSE, message = FALSE}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

indices    <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels <- c("Index A", "Index B", "Index C")
chk <- "\\checkmark"

fit_triple_urm <- function(d, idx, proxy_b) {
  suppressMessages(suppressWarnings(feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, I(%s * %s), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx, proxy_b, idx, proxy_b)),
    data = d, vcov = ~ responseid
  )))
}

for (k in seq_along(indices)) {
  idx <- indices[k]; lbl <- idx_labels[k]

  m_hr  <- fit_triple_urm(dt_hr,  idx, "firm_dei_attention_z")
  m_eng <- fit_triple_urm(dt_eng, idx, "firm_dei_attention_z")

  models_trp <- list("HR" = m_hr, "Eng" = m_eng)

  dict_trp <- c(
    "urm_tech_blind::Nonblind_URM"                                        = "URM (WF, AF, HM, HF)",
    "urm_tech_blind::Nonblind_NonURM"                                     = "Non-URM",
    setNames("URM $\\times$ DEI Index",                                       paste0("urm_tech_blind::Nonblind_URM:", idx)),
    setNames("Non-URM $\\times$ DEI Index",                                   paste0("urm_tech_blind::Nonblind_NonURM:", idx)),
    "urm_tech_blind::Nonblind_URM:firm_dei_attention_z"                   = "URM $\\times$ Firm DEI Attn",
    "urm_tech_blind::Nonblind_NonURM:firm_dei_attention_z"                = "Non-URM $\\times$ Firm DEI Attn",
    setNames("URM $\\times$ DEI Index $\\times$ Firm DEI Attn",
             paste0("urm_tech_blind::Nonblind_URM:I(", idx, " * firm_dei_attention_z)")),
    setNames("Non-URM $\\times$ DEI Index $\\times$ Firm DEI Attn",
             paste0("urm_tech_blind::Nonblind_NonURM:I(", idx, " * firm_dei_attention_z)"))
  )

  tbl_trp <- etable(
    models_trp,
    tex = TRUE, style.tex = style.tex("aer"),
    placement = "H", depvar = FALSE,
    keep = "%urm_tech_blind",
    fitstat = c("n", "ar2"),
    drop.section = "fixef",
    digits = 3, se.below = TRUE,
    signif.code = c("***" = 0.01, "**" = 0.05, "*" = 0.1),
    dict = dict_trp,
    notes = "Firm DEI Attn proxy is firm\\_dei\\_attention\\_z (within-cell z-score of the equal-weight average of firm\\_attention\\_race\\_z and firm\\_attention\\_gender\\_z). Coefficients flipped via I(-sc\\_overall\\_z) so positive => effect of blinding. Standard errors clustered by respondent. Sample: both arms.",
    extralines = list(
      "Resume (Content) FE"       = rep(chk, 2),
      "Display Position FE"       = rep(chk, 2),
      "Respondent Demographic FE" = rep(chk, 2)
    )
  )

  tbl_trp <- sub(
    "\\\\toprule",
    paste0(
      "\\\\multicolumn{3}{c}{\\\\textbf{", lbl, " --- signs flipped so + $\\\\Rightarrow$ effect of blinding}} \\\\\\\\ ",
      "\\\\toprule",
      " & \\\\multicolumn{2}{c}{\\\\textbf{Firm DEI Attn Lvl}} \\\\\\\\",
      " \\\\cmidrule(lr){2-3}",
      " & HR & Eng \\\\\\\\ \\\\addlinespace[2pt]"
    ),
    tbl_trp
  )
  tbl_trp <- gsub("\\\\par \\\\raggedright", "\\\\par \\\\centering \\\\footnotesize", tbl_trp)
  tbl_trp <- sub(
    "\\\\begin\\{tabular\\}",
    "{\\\\scriptsize\\\\setlength{\\\\tabcolsep}{3pt}\\\\renewcommand{\\\\arraystretch}{0.88}\\\\begin{tabular}",
    tbl_trp
  )
  tbl_trp <- sub("\\\\end\\{tabular\\}", "\\\\end{tabular}}", tbl_trp)

  cat(tbl_trp)
  cat("\\vspace{0.5em}\n\n")
}

rm(dt_hr, dt_eng, indices, idx_labels, chk, fit_triple_urm,
   m_hr, m_eng, models_trp, dict_trp, tbl_trp, idx, lbl, k)
```


\vspace{0.6em}
\noindent \textbf{Visual: URM--Non-URM gap under nonblind by DEI Index $\times$ Firm DEI Attn.} One figure per DEI index (A, B, C). Each panel plots the URM--Non-URM premium under nonblind = the gap blinding eliminates. Rows: Firm DEI Attn fixed at $+1$ SD (high, top) and $-1$ SD (low, bottom). Columns: role. Substitution shows up as the HR gap curve flattening toward zero in the top-right region (high firm DEI attn, high individual DEI Index).

```{r bh_dei_indices_triple_plot, echo = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 6.0, fig.align = 'center'}

dt_hr  <- firm_long_dt[role == "HR"]
dt_eng <- firm_long_dt[role == "Eng"]

dt_hr [, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_eng[, urm_tech_blind := fcase(
  treat == "blind",                    "Blind",
  treat == "nonblind" & urm_tech == 1, "Nonblind_URM",
  treat == "nonblind" & urm_tech == 0, "Nonblind_NonURM",
  default = NA_character_)]
dt_hr [, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]
dt_eng[, urm_tech_blind := factor(urm_tech_blind,
  levels = c("Blind", "Nonblind_URM", "Nonblind_NonURM"))]

fit_triple_for_plot <- function(d, idx_var) {
  feols(
    as.formula(sprintf(
      "I(-sc_overall_z) ~ i(urm_tech_blind, ref = 'Blind') + i(urm_tech_blind, %s, ref = 'Blind') + i(urm_tech_blind, firm_dei_attention_z, ref = 'Blind') + i(urm_tech_blind, I(%s * firm_dei_attention_z), ref = 'Blind') + resp_age + I(resp_age^2) + I(resp_age^3) | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income",
      idx_var, idx_var)),
    data = d, vcov = ~ responseid)
}

compute_gap_triple <- function(model, role_label, idx_var) {
  cf <- coef(model); vc <- vcov(model)
  cn <- list(
    urm  = "urm_tech_blind::Nonblind_URM",
    nurm = "urm_tech_blind::Nonblind_NonURM",
    urm_idx  = paste0("urm_tech_blind::Nonblind_URM:",    idx_var),
    nurm_idx = paste0("urm_tech_blind::Nonblind_NonURM:", idx_var),
    urm_firm  = "urm_tech_blind::Nonblind_URM:firm_dei_attention_z",
    nurm_firm = "urm_tech_blind::Nonblind_NonURM:firm_dei_attention_z",
    urm_iaf  = paste0("urm_tech_blind::Nonblind_URM:I(",    idx_var, " * firm_dei_attention_z)"),
    nurm_iaf = paste0("urm_tech_blind::Nonblind_NonURM:I(", idx_var, " * firm_dei_attention_z)")
  )
  idx_grid  <- seq(-2, 2, by = 0.1)
  firm_grid <- c(-1, 1)
  out_list <- list()
  k <- 1
  for (fv in firm_grid) for (iv in idx_grid) {
    a <- setNames(numeric(length(cf)), names(cf))
    a[cn$urm]      <- -1
    a[cn$nurm]     <-  1
    a[cn$urm_idx]  <- -iv
    a[cn$nurm_idx] <-  iv
    a[cn$urm_firm]  <- -fv
    a[cn$nurm_firm] <-  fv
    a[cn$urm_iaf]  <- -(iv * fv)
    a[cn$nurm_iaf] <-  (iv * fv)
    out_list[[k]] <- data.table(
      role     = role_label,
      idx_val  = iv,
      firm_val = fv,
      gap      = sum(a * cf),
      se       = sqrt(as.numeric(t(a) %*% vc %*% a))
    )
    k <- k + 1
  }
  rbindlist(out_list)
}

indices_to_plot <- c("dei_index_A_z", "dei_index_B_z", "dei_index_C_z")
idx_labels      <- c("Index A", "Index B", "Index C")

for (k in seq_along(indices_to_plot)) {
  iv  <- indices_to_plot[k]
  lbl <- idx_labels[k]

  m_hr  <- fit_triple_for_plot(dt_hr,  iv)
  m_eng <- fit_triple_for_plot(dt_eng, iv)

  dat <- rbind(compute_gap_triple(m_hr,  "HR",       iv),
               compute_gap_triple(m_eng, "Engineer", iv))
  dat[, ci_lo := gap - 1.96 * se]
  dat[, ci_hi := gap + 1.96 * se]
  dat[, role  := factor(role, levels = c("HR", "Engineer"))]
  dat[, firm_label := factor(
    ifelse(firm_val < 0, "Low Firm DEI Attn (−1 SD)", "High Firm DEI Attn (+1 SD)"),
    levels = c("High Firm DEI Attn (+1 SD)", "Low Firm DEI Attn (−1 SD)"))]

  p_3_3 <- ggplot(dat, aes(x = idx_val, y = gap)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
    geom_ribbon(aes(ymin = ci_lo, ymax = ci_hi), fill = "steelblue", alpha = 0.25) +
    geom_line(color = "steelblue", linewidth = 1.2) +
    facet_grid(firm_label ~ role) +
    labs(x = paste0("DEI ", lbl, " (z-score)"),
         y = "URM − Non-URM gap under nonblind",
         title = lbl) +
    theme_minimal(base_size = 11) +
    theme(panel.grid.minor = element_blank(),
          strip.text = element_text(face = "bold"),
          plot.title = element_text(face = "bold", size = 13, hjust = 0.5))

  print(p_3_3)
}

rm(dt_hr, dt_eng, fit_triple_for_plot, compute_gap_triple,
   indices_to_plot, idx_labels, m_hr, m_eng, dat, p_3_3, iv, lbl, k)
```


\newpage
# Treatment Effect on Productivity of Hired

```{r blind_hiring_coding_quality, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

# ==============================================================================
# HELPER: Dynamic standardization relative to nonblind group at each k
# ==============================================================================
get_avg_coding_score <- function(role_filter, treat_filter, k, 
                                  pass_var_prefix, data) {
  col <- paste0(pass_var_prefix, k)
  d   <- data[role == role_filter & treat == treat_filter & get(col) == 1]
  if (nrow(d) == 0) return(NA_real_)
  mean(d$overall_score, na.rm = TRUE)
}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# ==============================================================================
results_list <- list()

for (k in 1:18) {

  # --- HR ---
  hr_col  <- paste0("hr_pass", k)
  hr_data <- firm_long_dt[role == "HR" & get(hr_col) == 1]

  # Dynamic standardization: relative to nonblind mean/sd at this k
  ctrl_mean_hr <- hr_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_hr   <- hr_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_hr) && ctrl_sd_hr > 0) {
    hr_data[, overall_score_std := (overall_score - ctrl_mean_hr) / ctrl_sd_hr]

    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do + q_version + resp_gender + resp_race + s2_educ + s2_income,
              data = hr_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_hr)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }

  # --- Engineer ---
  eng_col  <- paste0("eng_top", k)
  eng_data <- firm_long_dt[role == "Eng" & get(eng_col) == 1]

  ctrl_mean_eng <- eng_data[treat == "nonblind", mean(overall_score, na.rm = TRUE)]
  ctrl_sd_eng   <- eng_data[treat == "nonblind", sd(overall_score,   na.rm = TRUE)]

  if (!is.na(ctrl_sd_eng) && ctrl_sd_eng > 0) {
    eng_data[, overall_score_std := (overall_score - ctrl_mean_eng) / ctrl_sd_eng]

    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(overall_score_std ~ i(treat, ref = "nonblind") + resp_age |
                r_do + q_version + resp_gender + resp_race + s2_educ + s2_income +
                resp_python + resp_java,
              data = eng_data, vcov = ~ responseid)
      ))
      ct <- coeftable(m_eng)
      if ("treat::blind" %in% rownames(ct)) {
        est   <- ct["treat::blind", "Estimate"]
        se    <- ct["treat::blind", "Std. Error"]
        p_val <- ct["treat::blind", 4]
        results_list[[length(results_list) + 1]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

# ==============================================================================
# PLOT
# ==============================================================================
ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.15))) +
  labs(
    title    = "Does Blind Hiring Select Better Coders?",
    subtitle = paste("Effect of blinding on actual coding quality of selected candidates.",
                     "Standardized relative to nonblind group at each k."),
    y       = "Effect on Actual Coding Score (SD, relative to nonblind)",
    caption = "Positive = blind hiring selects candidates with higher actual coding scores.\nSignificance: * p<0.10, ** p<0.05, *** p<0.01"
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )

rm(results_list, dt_plot, k,
   hr_col, hr_data, ctrl_mean_hr, ctrl_sd_hr, m_hr, ct,
   eng_col, eng_data, ctrl_mean_eng, ctrl_sd_eng, m_eng,
   est, se, p_val)
```

```{r blind_hiring_demographic_selection, eval = FALSE, echo=FALSE, fig.width=12, fig.height=10}

# ==============================================================================
# COMPUTE TREATMENT EFFECT AT EACH K
# LHS: hr_passk / eng_topk (0/1 selected)
# RHS: race_gender with "Blind" as reference, then flip signs
# ==============================================================================
results_all <- list()

demo_labels <- c("White_Male", "White_Female", "Asian_Male",
                 "Asian_Female", "Hispanic_Male", "Hispanic_Female")

for (k in 1:18) {

  hr_col  <- paste0("hr_pass", k)
  eng_col <- paste0("eng_top", k)

  # --- HR ---
  tryCatch({
    m_hr <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(hr_col,
        " ~ i(race_gender, ref = 'Blind') |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income")),
        data = firm_long_dt[role == "HR"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_hr)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "HR Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})

  # --- Engineer ---
  tryCatch({
    m_eng <- suppressMessages(suppressWarnings(
      feols(as.formula(paste0(eng_col,
        " ~ i(race_gender, ref = 'Blind') + resp_age |
          r_do + q_version + resp_gender + resp_race + s2_educ + s2_income +
          resp_python + resp_java")),
        data = firm_long_dt[role == "Eng"],
        vcov = ~ responseid)
    ))
    ct <- coeftable(m_eng)
    for (dg in demo_labels) {
      coef_nm <- paste0("race_gender::", dg)
      if (coef_nm %in% rownames(ct)) {
        est   <- -ct[coef_nm, "Estimate"]      # flip sign
        se    <-  ct[coef_nm, "Std. Error"]
        p_val <-  ct[coef_nm, 4]
        results_all[[length(results_all) + 1]] <- data.table(
          demo  = gsub("_", " ", dg),
          Stage = "Engineer Stage", k = k,
          estimate = est,
          ci_low   = est - 1.96 * se,
          ci_high  = est + 1.96 * se,
          p_val    = p_val
        )
      }
    }
  }, error = function(e) {})
}

# ==============================================================================
# ASSEMBLE AND PLOT
# ==============================================================================
dt_plot <- rbindlist(results_all)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, demo  := factor(demo,  levels = c("White Male",    "White Female",
                                             "Asian Male",    "Asian Female",
                                             "Hispanic Male", "Hispanic Female"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]
dt_plot[, star_y := ifelse(estimate >= 0,
                            ci_high + 0.005,
                            ci_low  - 0.005)]

ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.6) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.6, size = 0.4, fatten = 3) +
  geom_text(aes(y = star_y, label = sig_stars),
            vjust = ifelse(dt_plot$estimate >= 0, 0, 1),
            size = 3, color = "black", show.legend = FALSE) +
  facet_grid(demo ~ Stage) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = seq(1, 18, by = 3),
                     name   = "Number of Candidates Selected (k)") +
  scale_y_continuous(expand = expansion(mult = c(0.05, 0.20))) +
  labs(
    title    = "Effect of Blind Hiring on Selection Probability by Demographic Group",
    subtitle = paste("Blinding effect = -(effect of revealing identity vs blind).",
                     "Positive = more likely selected under blinding."),
    y        = "Blinding Effect on Selection Probability",
    color    = "Evaluator Role",
    caption  = "Significance: * p<0.10, ** p<0.05, *** p<0.01. Base group: Blind resumes."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    legend.title       = element_text(face = "bold", size = 10),
    legend.text        = element_text(size = 9),
    plot.title         = element_text(face = "bold", size = 13),
    plot.subtitle      = element_text(size = 10, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 10),
    strip.text.y       = element_text(angle = 0),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0),
    panel.spacing      = unit(0.4, "lines")
  )

rm(results_all, dt_plot, demo_labels, dg, k,
   hr_col, eng_col, m_hr, m_eng, ct,
   est, se, p_val, coef_nm)
```

