---
title: "Blind Hiring -- Exploratory / Robustness Results"
output:
  pdf_document:
    number_sections: true
header-includes:
  - \usepackage{booktabs}
  - \usepackage{threeparttable}
  - \usepackage{float}
  - \usepackage{bbm}
  - \usepackage{array}
  - \usepackage{arydshln}
geometry: margin=0.5in, landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

\setcounter{section}{0}

```{r exploratory_helpers, echo=FALSE}
## Vectorised cell formatter (mirrors helper in 8B_Stage_BH.Rmd).
fmt_te_vec <- function(est, se) {
  out <- rep("---", length(est))
  ok  <- !is.na(est) & !is.na(se) & se > 0
  if (any(ok)) {
    z    <- est[ok] / se[ok]
    p    <- 2 * pnorm(-abs(z))
    star <- ifelse(p < 0.01, "***",
            ifelse(p < 0.05, "**",
            ifelse(p < 0.10, "*", "")))
    out[ok] <- sprintf("%.3f%s (%.3f)", est[ok], star, se[ok])
  }
  out
}
## Build derived columns the cut sections rely on (canonically built in
## 8B_Stage_BH.Rmd, but this Rmd runs independently).
firm_long_dt[, true_coding_z := (overall_score - mean(overall_score, na.rm = TRUE)) /
                                  sd(overall_score, na.rm = TRUE)]
if (!"resume_id" %in% names(firm_long_dt)) {
  firm_long_dt[, resume_id := paste(resume_ver, resume_index, sep = "_")]
}
if (!"firm_targets_fh" %in% names(firm_long_dt)) {
  firm_long_dt[, firm_targets_fh := as.integer(
    firm_targets_female == 1L | firm_targets_hispanic == 1L)]
}

## Reproduce misalign_z (signed directional misalignment index from §5 of
## the main Rmd; Alt A.1 / Alt B in this exploratory file use it).
{
  extra_perc <- c("s5_view_align", "s5_view_aligndiffeng", "s5_view_aligndiffhr",
                  "s5_hr_influence", "s5_engineer_care",
                  grep("^aligndiff(hr|eng)_", names(firm_dt), value = TRUE))
  extra_perc <- intersect(extra_perc, names(firm_dt))
  resp_dt <- unique(firm_long_dt[, .(responseid, role)])
  resp_dt <- merge(resp_dt, firm_dt[, c("responseid", extra_perc), with = FALSE],
                   by = "responseid", all.x = TRUE)
  for (col in extra_perc) {
    set(resp_dt, j = col, value = suppressWarnings(as.numeric(resp_dt[[col]])))
  }
  for (col in c("s5_hr_influence", "s5_engineer_care", "s5_view_align")) {
    if (col %in% names(resp_dt)) resp_dt[get(col) == 99, (col) := NA_real_]
  }
  z <- function(x) {
    if (sum(!is.na(x)) < 2) return(rep(NA_real_, length(x)))
    mu <- mean(x, na.rm = TRUE); sg <- sd(x, na.rm = TRUE)
    if (!is.finite(sg) || sg == 0) return(rep(0, length(x)))
    (x - mu) / sg
  }
  resp_dt[role == "Eng",
          eng_dir_count := (aligndiffeng_1 + aligndiffeng_4) -
                           (aligndiffeng_2 + aligndiffeng_5)]
  resp_dt[role == "Eng", eng_dir_raw := s5_hr_influence + 0.5 * eng_dir_count]
  resp_dt[role == "Eng", eng_dir_z := z(eng_dir_raw)]
  resp_dt[role == "HR",
          hr_dir_count := (aligndiffhr_2 + aligndiffhr_5) -
                          (aligndiffhr_1 + aligndiffhr_4)]
  resp_dt[role == "HR", hr_dir_raw := -s5_engineer_care + 0.5 * hr_dir_count]
  resp_dt[role == "HR", hr_dir_z := z(hr_dir_raw)]
  resp_dt[, misalign_z := NA_real_]
  resp_dt[role == "Eng", misalign_z := eng_dir_z]
  resp_dt[role == "HR",  misalign_z := hr_dir_z]
  if ("misalign_z" %in% names(firm_long_dt)) firm_long_dt[, misalign_z := NULL]
  firm_long_dt <- merge(firm_long_dt, resp_dt[, .(responseid, misalign_z)],
                        by = "responseid", all.x = TRUE)
  rm(resp_dt, extra_perc, z)
}
```

\clearpage
## Alternative A.1 (HR only): Candidate-Level Selection Probability Model with \texttt{sc\_advance}

The per-$k$ loop in §4.2--§4.6 suffers from extreme discrete-sampling variance at the boundaries (at $k{=}1$ a single tie-break injects pure noise into the dependent variable; at $k{=}18$ the pools collapse to identical sets). For HR, we have a natural binary --- \texttt{sc\_advance}, the actual decision to advance a candidate to the engineering stage --- which lets us re-estimate the same selection question on the full candidate-evaluator panel without any $k$ threshold:
\vspace{-0.7em}
$$
\underbrace{\text{sc\_advance}_{ij}}_{\text{HR's advance decision}}
\;\sim\;
\text{TrueCoding}_i \times \mathbbm{1}[\text{Blind}]_j \times \text{Moderator}_j
\;\Big|\;
\text{Respondent FE},\;
\text{cluster on Respondent}.
$$

\vspace{-0.6em}
\textbf{Why HR only here:} \texttt{sc\_advance} is HR's natural single-decision ``move forward'' binary; engineers do not produce a comparable single-shot binary on the firm side --- they instead deliver an \emph{ordering} over the 18 resumes, from which any binary is necessarily a top-$k$ thresholding (which is exactly the §4.2 design we are trying to escape). For the engineer side we therefore push the analogous ``does blinding strengthen the link between true ability and selection'' question into a $k$-loop variant in §4.8 below.

With respondent FE, all between-respondent terms (\texttt{treat::blind}, the moderator main effect, and their two-way interaction) are absorbed; identification of the within-respondent slopes and their cross-products comes from variation in true coding ability across the 18 resumes a respondent rates. The substantive coefficients of interest are:

\vspace{-0.6em}
\begin{itemize}\setlength\itemsep{0pt}\setlength\parskip{0pt}\setlength\topsep{0pt}\setlength\partopsep{0pt}
    \item \textbf{True Coding $\times$ Blind} --- the central efficiency claim. $>0$ means blinding tightens the link between objective ability and being advanced.
    \item \textbf{True Coding $\times$ Blind $\times$ M} --- whether blinding's tightening of that link itself depends on the moderator (DEI orientation, firm DEI policy, or inter-departmental DEI misalignment).
\end{itemize}

```{r alt_a_selection_probability_lpm, echo=FALSE, results='asis', warning=FALSE, message=FALSE}

## ---------------------------------------------------------------------------
## Build firm_targets_fh and resume_id on firm_long_dt if not already
## present. resume_id = (resume_ver, resume_index) -- the unique stimulus
## the respondent saw. There are 144 such combos (8 vers x 18 positions),
## which is enough for CGM two-way clustering on (responseid, resume_id).
## ---------------------------------------------------------------------------
if (!"firm_targets_fh" %in% names(firm_long_dt)) {
  firm_long_dt[, firm_targets_fh := as.integer(
    firm_targets_female == 1L | firm_targets_hispanic == 1L)]
}
if (!"resume_id" %in% names(firm_long_dt)) {
  firm_long_dt[, resume_id := paste(resume_ver, resume_index, sep = "_")]
}
stopifnot("sc_advance" %in% names(firm_long_dt),
          "true_coding_z" %in% names(firm_long_dt),
          "dei_index_z" %in% names(firm_long_dt),
          "misalign_z" %in% names(firm_long_dt))

hr_dt <- firm_long_dt[role == "HR"]

## ---------------------------------------------------------------------------
## Four LPMs (HR only): pooled + three heterogeneity triples (DEI Index,
## Firm Targets Fem/His, Misalign). Respondent FE absorbs all between-
## respondent terms; r_do FE absorbs display-order / fatigue effects on the
## advance decision; the surviving coefficients are the within-respondent
## true-coding-z terms (main slope + Blind shift + M shift + triple).
## Two-way clustered SE on (responseid, resume_id).
## Resume-content FE (resume_id) is intentionally NOT absorbed: it would
## kill the True Coding (Z) main-effect row, which is substantive here.
## ---------------------------------------------------------------------------
m_hr_pool <- feols(sc_advance ~ true_coding_z * i(treat, ref = "nonblind") | responseid + r_do,
                   data = hr_dt, vcov = ~ responseid + resume_id)
m_hr_dei  <- feols(sc_advance ~ true_coding_z * i(treat, ref = "nonblind") * dei_index_z | responseid + r_do,
                   data = hr_dt[!is.na(dei_index_z)], vcov = ~ responseid + resume_id)
m_hr_ft   <- feols(sc_advance ~ true_coding_z * i(treat, ref = "nonblind") * firm_targets_fh | responseid + r_do,
                   data = hr_dt[!is.na(firm_targets_fh)], vcov = ~ responseid + resume_id)
m_hr_ms   <- feols(sc_advance ~ true_coding_z * i(treat, ref = "nonblind") * misalign_z | responseid + r_do,
                   data = hr_dt[!is.na(misalign_z)], vcov = ~ responseid + resume_id)

models_list <- list(
  "(1) Pooled"           = m_hr_pool,
  "(2) DEI Index"        = m_hr_dei,
  "(3) Firm Targets F/H" = m_hr_ft,
  "(4) Misalign (Z)"     = m_hr_ms
)

## Multiple raw coef names map to the same display label so the four
## "True Coding x ..." rows align across moderators in the combined table.
coef_map <- c(
  "true_coding_z"                              = "True Coding (Z)",
  "true_coding_z:treat::blind"                 = "True Coding $\\times$ Blind",
  "true_coding_z:dei_index_z"                  = "True Coding $\\times$ M",
  "true_coding_z:firm_targets_fh"              = "True Coding $\\times$ M",
  "true_coding_z:misalign_z"                   = "True Coding $\\times$ M",
  "true_coding_z:dei_index_z:treat::blind"     = "True Coding $\\times$ Blind $\\times$ M",
  "true_coding_z:firm_targets_fh:treat::blind" = "True Coding $\\times$ Blind $\\times$ M",
  "true_coding_z:misalign_z:treat::blind"      = "True Coding $\\times$ Blind $\\times$ M"
)

## ---------------------------------------------------------------------------
## FE / GoF scaffolding per project convention: FE rows (incl. intentional
## X for Resume Content FE), midrule, then Obs / R^2 / Adj R^2.
## ---------------------------------------------------------------------------
chk <- "\\checkmark"
nox <- "$\\times$"
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(chk, nox, nox, chk, nox),
  V2 = c(chk, nox, nox, chk, nox),
  V3 = c(chk, nox, nox, chk, nox),
  V4 = c(chk, nox, nox, chk, nox),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(models_list))
## Coef block: 4 unique display labels x (est+se on separate lines) = 8 rows.
## Inject 5 FE rows immediately after at positions 9:13.
attr(fe_rows, "position") <- 9:13

gof_map <- list(
  list("raw" = "nobs",         "clean" = "Obs.",       "fmt" = function(x) format(x, big.mark = ",")),
  list("raw" = "r.squared",    "clean" = "$R^2$",      "fmt" = function(x) sprintf("%.3f", x)),
  list("raw" = "adj.r.squared","clean" = "Adj. $R^2$", "fmt" = function(x) sprintf("%.3f", x))
)

rm(hr_dt, m_hr_pool, m_hr_dei, m_hr_ft, m_hr_ms,
   models_list, coef_map, gof_map, fe_rows, chk, nox)
```


\clearpage
## Alternative A.2 ($k$-loop): Selection Probability for Both Roles, Looping over $k$

\textbf{Relationship to §4.2--§4.6:} Because engineers do not give a single advance/no-advance decision, the analog of §4.7 for engineers requires picking a binary --- and the only natural ones are the $k$-thresholded indicators \texttt{hr\_pass$_k$} / \texttt{eng\_top$_k$}. Doing so produces what is essentially the LHS$\leftrightarrow$RHS \emph{dual} of §4.2: where §4.2 conditions on the selected pool and asks ``\emph{Is the average true coding score of the selected $k$ higher under blinding?},'' §4.8 instead uses the full candidate-evaluator panel and asks ``\emph{Is true coding ability a stronger predictor of being one of the selected $k$ under blinding?}'' Mathematically the two are not identical (different estimands and different units), but they are tightly linked: if blinding raises the average true score of the chosen $k$, it must be (approximately) because blinding has steepened the within-respondent gradient of selection probability on true ability. The advantage of the dual specification is that the panel sample size at every $k$ is the full $N{\approx}5{,}238$ candidate-evaluator observations, which compresses the standard errors that explode in §4.2 at low $k$.

\vspace{-0.5em}
$$
\underbrace{\text{Selected}^{(k)}_{ij}}_{\substack{\text{HR: }\texttt{hr\_pass}_k\\\text{Eng: }\texttt{eng\_top}_k}}
\;\sim\;
\text{TrueCoding}_i \times \mathbbm{1}[\text{Blind}]_j
\;\Big|\;
\text{Respondent FE},\;
\text{cluster on Respondent},
\quad k = 1,\dots,18.
$$

\vspace{-0.6em}
The plotted quantity is the per-$k$ \texttt{true\_coding\_z}~$\times$~\texttt{treat::blind} coefficient: the change in the within-respondent linear-probability slope of selection on true coding ability when going from non-blind to blind review. Positive means blinding tightens the ability-selection link. Bands are 95\% CIs from clustered SEs on respondent.

```{r alt_a2_selection_prob_kloop, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=5}

## Build resume_id (= unique stimulus identity) if not already present
## from the Alternative A.1 chunk; needed for two-way cluster.
if (!"resume_id" %in% names(firm_long_dt)) {
  firm_long_dt[, resume_id := paste(resume_ver, resume_index, sep = "_")]
}

results_list <- list()

for (k in 1:18) {

  ## --- HR ---
  hr_col  <- paste0("hr_pass", k)
  if (hr_col %in% names(firm_long_dt)) {
    tryCatch({
      m_hr <- suppressMessages(suppressWarnings(
        feols(as.formula(paste0(hr_col,
                " ~ true_coding_z * i(treat, ref = 'nonblind') | responseid + r_do")),
              data = firm_long_dt[role == "HR"],
              vcov = ~ responseid + resume_id)
      ))
      ct <- coeftable(m_hr)
      key <- "true_coding_z:treat::blind"
      if (key %in% rownames(ct)) {
        est   <- ct[key, "Estimate"]
        se    <- ct[key, "Std. Error"]
        p_val <- ct[key, 4]
        results_list[[length(results_list) + 1L]] <- data.table(
          Stage = "HR Stage", k = k,
          estimate = est, se = se,
          ci_low = est - 1.96 * se, ci_high = est + 1.96 * se,
          p_val = p_val
        )
      }
    }, error = function(e) {})
  }

  ## --- Engineer ---
  eng_col <- paste0("eng_top", k)
  if (eng_col %in% names(firm_long_dt)) {
    tryCatch({
      m_eng <- suppressMessages(suppressWarnings(
        feols(as.formula(paste0(eng_col,
                " ~ true_coding_z * i(treat, ref = 'nonblind') | responseid + r_do")),
              data = firm_long_dt[role == "Eng"],
              vcov = ~ responseid + resume_id)
      ))
      ct <- coeftable(m_eng)
      key <- "true_coding_z:treat::blind"
      if (key %in% rownames(ct)) {
        est   <- ct[key, "Estimate"]
        se    <- ct[key, "Std. Error"]
        p_val <- ct[key, 4]
        results_list[[length(results_list) + 1L]] <- data.table(
          Stage = "Engineer Stage", k = k,
          estimate = est, se = se,
          ci_low = est - 1.96 * se, ci_high = est + 1.96 * se,
          p_val = p_val
        )
      }
    }, error = function(e) {})
  }
}

dt_plot <- rbindlist(results_list)
dt_plot[, Stage := factor(Stage, levels = c("HR Stage", "Engineer Stage"))]
dt_plot[, sig_stars := fcase(
  p_val < 0.01, "***",
  p_val < 0.05, "**",
  p_val < 0.10, "*",
  default = ""
)]

p_obj <- ggplot(dt_plot, aes(x = k, y = estimate, color = Stage)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50", linewidth = 0.8) +
  geom_pointrange(aes(ymin = ci_low, ymax = ci_high),
                  linewidth = 0.8, size = 0.6, fatten = 3) +
  geom_text(aes(y = ci_high, label = sig_stars),
            vjust = -0.5, size = 5, color = "black", show.legend = FALSE) +
  facet_wrap(~ Stage, ncol = 2) +
  scale_color_manual(values = c("HR Stage" = "#C44E52", "Engineer Stage" = "#4C72B0")) +
  scale_x_continuous(breaks = 1:18, name = "Selection threshold $k$") +
  labs(
    subtitle = "Per-k change in the within-respondent LPM slope of selection on true coding ability under blinding (treat::blind x true_coding_z coefficient)",
    y       = "Slope shift in P(selected at top-k) per 1 SD true coding (blind - nonblind)",
    caption = "LPM with respondent FE + display-order (r_do) FE; two-way clustered SE on (respondent, resume). Resume-content FE intentionally not absorbed (would kill the true_coding_z slope). Positive: blinding tightens the link between true coding ability and being selected at top-k. Significance: * p<0.10, ** p<0.05, *** p<0.01."
  ) +
  theme_bw() +
  theme(
    legend.position    = "none",
    plot.subtitle      = element_text(size = 9, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 12),
    panel.grid.minor.x = element_blank(),
    axis.title.x       = element_text(margin = margin(t = 10)),
    axis.title.y       = element_text(margin = margin(r = 10)),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Underlying per-k coefficient table.
## ---------------------------------------------------------------------------
dt_plot[, cell := fmt_te_vec(estimate, se)]
tbl <- dcast(dt_plot, k ~ Stage, value.var = "cell")
setnames(tbl, "k", "$k$")

rm(results_list, dt_plot, tbl, p_obj, k,
   hr_col, eng_col, m_hr, m_eng, ct, key, est, se, p_val)
```


\clearpage
## Alternative B: Evaluator-Level Rank Correlation (``Accuracy Score'')

Both prior alternatives still operate on the resume-evaluator long panel. Alternative B collapses that panel to one number per evaluator and asks a different but complementary question: across the 18 resumes a single evaluator rated, \emph{how well does their overall ranking of those 18 resumes line up with the objective ranking by lab coding score?} For each respondent $r$ we compute
\vspace{-0.7em}
$$
\rho_r \;=\; \mathrm{cor}\!\Big(\,\mathrm{rank}\big(\widehat{\text{sc\_overall}}_{r,\cdot}\big),\;\mathrm{rank}(\text{overall\_score}_{\cdot})\,\Big)\;\in\;[-1,+1],
$$

\vspace{-0.6em}
the Spearman rank correlation between the evaluator's overall ratings (\texttt{sc\_overall\_z}) and the resumes' objective lab coding scores (\texttt{overall\_score}). $\rho_r{=}{+}1$ means the evaluator's ranking is identical to the objective ranking; $\rho_r{=}0$ means pure noise; $\rho_r{=}{-}1$ means perfectly inverted. Spearman is rank-based, so the choice between raw and standardized versions of either input is irrelevant. We then regress the Fisher-$z$ transform $\tilde\rho_r = \tanh^{-1}(\rho_r)$ (variance-stabilized, unbounded) on treatment and a moderator:

\vspace{-0.5em}
$$
\tilde\rho_r \;\sim\; \mathbbm{1}[\text{Blind}]_r \times \text{Moderator}_r + \text{controls},\qquad \text{HC1 robust SEs.}
$$

\vspace{-0.6em}
Each observation is one evaluator (one row), so no clustering is needed --- independence is by design. \texttt{Blind} positive $\Rightarrow$ blinding raises rank-alignment with truth on average; \texttt{Blind}~$\times$~M nonzero $\Rightarrow$ that improvement varies with the moderator.

```{r alt_b_evaluator_accuracy, echo=FALSE, results='asis', warning=FALSE, message=FALSE, fig.width=10, fig.height=4.2}

if (!"firm_targets_fh" %in% names(firm_long_dt)) {
  firm_long_dt[, firm_targets_fh := as.integer(
    firm_targets_female == 1L | firm_targets_hispanic == 1L)]
}

## ---------------------------------------------------------------------------
## Step 1: One Spearman accuracy score per (responseid, role).
## Drop respondents with too few non-missing rating-truth pairs to compute a
## stable correlation (need at least 5 paired observations).
## ---------------------------------------------------------------------------
acc_dt <- firm_long_dt[
  !is.na(sc_overall_z) & !is.na(overall_score),
  .(accuracy = suppressWarnings(cor(sc_overall_z, overall_score, method = "spearman")),
    n_resumes = .N),
  by = .(responseid, role)
]
acc_dt <- acc_dt[n_resumes >= 5 & !is.na(accuracy)]

## Fisher z-transform (clip to +/-0.999 so atanh stays finite). At 18 paired
## resumes per evaluator, ties are rare and rho almost never hits the bounds,
## but the clip is the safe default.
acc_dt[, accuracy_fz := atanh(pmax(pmin(accuracy, 0.999), -0.999))]

## ---------------------------------------------------------------------------
## Step 2: Merge respondent-level moderators / controls. Each responseid
## maps to exactly one role, so unique() collapses cleanly.
## ---------------------------------------------------------------------------
resp_attrs <- unique(firm_long_dt[, .(responseid, treat, dei_index_z, firm_targets_fh,
                                       misalign_z, resp_age, resp_gender, resp_race,
                                       s2_educ, s2_income, q_version,
                                       resp_python, resp_java)])
acc_dt <- acc_dt[resp_attrs, on = "responseid", nomatch = NULL]

acc_hr  <- acc_dt[role == "HR"]
acc_eng <- acc_dt[role == "Eng"]

## ---------------------------------------------------------------------------
## Step 3: Eight respondent-level OLS models (HR/Eng x Pooled+3 het). Light
## FE structure (q_version + resp_python/java for Eng) given the small per-
## role sample (~137 HR / ~154 Eng). HC1 robust SE, no clustering.
## ---------------------------------------------------------------------------
## Standard demographic Respondent Characteristics (resp_gender + resp_race
## + s2_educ + s2_income) absorbed in BOTH HR and Eng specs for parallelism
## with §1, §2, §3, §5 conventions. Eng additionally absorbs the coding-
## language FEs (resp_python, resp_java), which are Eng-only survey items
## and don't exist for HR respondents.
m_hr_pool <- feols(accuracy_fz ~ i(treat, ref = "nonblind") + resp_age
                   | q_version + resp_gender + resp_race + s2_educ + s2_income,
                   data = acc_hr, vcov = "hetero")
m_hr_dei  <- feols(accuracy_fz ~ i(treat, ref = "nonblind") * dei_index_z + resp_age
                   | q_version + resp_gender + resp_race + s2_educ + s2_income,
                   data = acc_hr[!is.na(dei_index_z)], vcov = "hetero")
m_hr_ft   <- feols(accuracy_fz ~ i(treat, ref = "nonblind") * firm_targets_fh + resp_age
                   | q_version + resp_gender + resp_race + s2_educ + s2_income,
                   data = acc_hr[!is.na(firm_targets_fh)], vcov = "hetero")
m_hr_ms   <- feols(accuracy_fz ~ i(treat, ref = "nonblind") * misalign_z + resp_age
                   | q_version + resp_gender + resp_race + s2_educ + s2_income,
                   data = acc_hr[!is.na(misalign_z)], vcov = "hetero")

m_eng_pool <- feols(accuracy_fz ~ i(treat, ref = "nonblind") + resp_age
                    | q_version + resp_gender + resp_race + s2_educ + s2_income + resp_python + resp_java,
                    data = acc_eng, vcov = "hetero")
m_eng_dei  <- feols(accuracy_fz ~ i(treat, ref = "nonblind") * dei_index_z + resp_age
                    | q_version + resp_gender + resp_race + s2_educ + s2_income + resp_python + resp_java,
                    data = acc_eng[!is.na(dei_index_z)], vcov = "hetero")
m_eng_ft   <- feols(accuracy_fz ~ i(treat, ref = "nonblind") * firm_targets_fh + resp_age
                    | q_version + resp_gender + resp_race + s2_educ + s2_income + resp_python + resp_java,
                    data = acc_eng[!is.na(firm_targets_fh)], vcov = "hetero")
m_eng_ms   <- feols(accuracy_fz ~ i(treat, ref = "nonblind") * misalign_z + resp_age
                    | q_version + resp_gender + resp_race + s2_educ + s2_income + resp_python + resp_java,
                    data = acc_eng[!is.na(misalign_z)], vcov = "hetero")

## ---------------------------------------------------------------------------
## Step 4a: Distribution plot of raw rho by treat x role
## ---------------------------------------------------------------------------
acc_plot <- copy(acc_dt)
acc_plot[, role_lab := factor(role, levels = c("HR", "Eng"),
                              labels = c("HR Stage", "Engineer Stage"))]
acc_means <- acc_plot[, .(mean_acc = mean(accuracy)), by = .(role_lab, treat)]

p_obj <- ggplot(acc_plot, aes(x = accuracy, fill = treat, color = treat)) +
  geom_density(alpha = 0.35, linewidth = 0.6) +
  geom_vline(data = acc_means,
             aes(xintercept = mean_acc, color = treat),
             linetype = "dashed", linewidth = 0.6) +
  facet_wrap(~ role_lab, ncol = 2) +
  scale_color_manual(values = c("nonblind" = "#C44E52", "blind" = "#4C72B0"),
                     name = "Treatment") +
  scale_fill_manual( values = c("nonblind" = "#C44E52", "blind" = "#4C72B0"),
                     name = "Treatment") +
  scale_x_continuous(limits = c(-1, 1), breaks = seq(-1, 1, 0.25)) +
  labs(
    subtitle = "Distribution of evaluator-level Accuracy Score (Spearman rho between sc_overall_z and overall_score across 18 resumes)",
    x = "Accuracy Score (Spearman rho)",
    y = "Density",
    caption = "Dashed lines: arm-specific means. rho > 0 = evaluator's overall ranking aligns with objective coding ability; rho < 0 = anti-aligned."
  ) +
  theme_bw() +
  theme(
    legend.position    = "bottom",
    plot.subtitle      = element_text(size = 9, color = "gray30"),
    strip.text         = element_text(face = "bold", size = 11),
    panel.grid.minor   = element_blank(),
    plot.caption       = element_text(size = 8, hjust = 0)
  )
print(p_obj)

## ---------------------------------------------------------------------------
## Step 4b: Combined modelsummary table (8 columns)
## ---------------------------------------------------------------------------
models_list <- list(
  "(1) Pool"     = m_hr_pool,
  "(2) DEI"      = m_hr_dei,
  "(3) FirmTgt"  = m_hr_ft,
  "(4) Misalign" = m_hr_ms,
  "(5) Pool"     = m_eng_pool,
  "(6) DEI"      = m_eng_dei,
  "(7) FirmTgt"  = m_eng_ft,
  "(8) Misalign" = m_eng_ms
)

## Multiple raw moderator names share display rows so DEI/FT/Misalign
## triples line up.
coef_map <- c(
  "treat::blind"                  = "Blind",
  "dei_index_z"                   = "M (moderator)",
  "firm_targets_fh"               = "M (moderator)",
  "misalign_z"                    = "M (moderator)",
  "dei_index_z:treat::blind"      = "Blind $\\times$ M",
  "firm_targets_fh:treat::blind"  = "Blind $\\times$ M",
  "misalign_z:treat::blind"       = "Blind $\\times$ M",
  "resp_age"                      = "Resp. age"
)

## ---------------------------------------------------------------------------
## FE / GoF scaffolding per project convention. Alt B is respondent-level
## (one obs per evaluator), so r_do (display-order) and resume_id (resume
## content) FEs are not applicable -- still listed with X for transparency.
## ---------------------------------------------------------------------------
chk <- "\\checkmark"
nox <- "$\\times$"
## Standard unified 5-row FE block. Eng coding-language FEs (resp_python,
## resp_java) are bundled INTO row 5 ("Respondent Age + Demographic FEs")
## per project convention, since they are respondent-level traits absorbed
## together with gender/race/education/income.
fe_rows <- data.frame(
  term = c("Display Position FE",
           "Resume ID FE",
           "Resume - Coding Test Version FE",
           "Respondent ID FE",
           "Respondent Age (Cont) and Demographic FEs"),
  V1 = c(nox, nox, chk, nox, chk),
  V2 = c(nox, nox, chk, nox, chk),
  V3 = c(nox, nox, chk, nox, chk),
  V4 = c(nox, nox, chk, nox, chk),
  V5 = c(nox, nox, chk, nox, chk),
  V6 = c(nox, nox, chk, nox, chk),
  V7 = c(nox, nox, chk, nox, chk),
  V8 = c(nox, nox, chk, nox, chk),
  stringsAsFactors = FALSE
)
names(fe_rows) <- c("term", names(models_list))
## Coef block: 4 unique display labels x (est+se separate lines) = 8 rows.
## Inject 5 FE rows immediately after at positions 9:13.
attr(fe_rows, "position") <- 9:13

gof_map <- list(
  list("raw" = "nobs",         "clean" = "Obs.",       "fmt" = function(x) format(x, big.mark = ",")),
  list("raw" = "r.squared",    "clean" = "$R^2$",      "fmt" = function(x) sprintf("%.3f", x)),
  list("raw" = "adj.r.squared","clean" = "Adj. $R^2$", "fmt" = function(x) sprintf("%.3f", x))
)

ms_tex <- modelsummary(
  models_list,
  output   = "kableExtra",
  coef_map = coef_map,
  gof_map  = gof_map,
  add_rows = fe_rows,
  stars    = c("*" = 0.10, "**" = 0.05, "***" = 0.01),
  escape   = FALSE,
  align    = paste0("l", strrep("c", length(models_list))),
  title    = "Alternative B --- Evaluator-Level Accuracy Score: Fisher-z transformed Spearman rank correlation between the evaluator's overall ratings and resumes' objective lab coding scores across the 18 resumes they rated. OLS with HC1 robust SEs in parentheses; one observation per evaluator (no clustering). Resume-content / Display Position / Respondent FEs not applicable (respondent-level regression). Standard demographic Respondent Characteristics (resp\\_gender, resp\\_race, s2\\_educ, s2\\_income) absorbed in both HR and Eng specs. Eng additionally absorbs coding-language FEs (resp\\_python, resp\\_java), which are Eng-only survey items."
) |> kableExtra::kable_styling(
       latex_options = c("HOLD_position", "scale_down"),
       font_size = 7
     ) |> kableExtra::add_header_above(
       c(" " = 1, "HR" = 4, "Engineer" = 4)
     ) |> kableExtra::row_spec(8,  extra_latex_after = "\\midrule") |>
        kableExtra::row_spec(13, extra_latex_after = "\\midrule")
print(ms_tex)

rm(acc_dt, acc_hr, acc_eng, acc_plot, acc_means, resp_attrs,
   m_hr_pool, m_hr_dei, m_hr_ft, m_hr_ms,
   m_eng_pool, m_eng_dei, m_eng_ft, m_eng_ms,
   models_list, coef_map, gof_map, fe_rows, chk, nox, ms_tex, p_obj)
```


\clearpage
# Within-Session Demographic Calibration (Robustness)

```{r anchoring_setup, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
## Build running same-demo and other-demo means of objective overall_score
## (using TRUE assigned race-gender, so the variable is well-defined under
## both arms). lag_*_z are z-scored within sample.
firm_long_dt[, true_rg_anchor := factor(as.character(true_race_gender),
  levels = c("White_Male","White_Female","Asian_Male","Asian_Female",
             "Hispanic_Male","Hispanic_Female"))]
setorder(firm_long_dt, responseid, r_do)

firm_long_dt[, lag_same_sum   := 0]
firm_long_dt[, lag_same_count := 0L]
firm_long_dt[, lag_diff_sum   := 0]
firm_long_dt[, lag_diff_count := 0L]
for (rid in unique(firm_long_dt$responseid)) {
  idx <- which(firm_long_dt$responseid == rid)
  if (length(idx) < 2) next
  rg <- as.character(firm_long_dt$true_rg_anchor[idx])
  sc <- firm_long_dt$overall_score[idx]
  for (j in 2:length(idx)) {
    prev <- seq_len(j - 1)
    same <- which(rg[prev] == rg[j])
    diff <- which(rg[prev] != rg[j])
    firm_long_dt$lag_same_sum  [idx[j]] <- sum(sc[prev[same]], na.rm = TRUE)
    firm_long_dt$lag_same_count[idx[j]] <- sum(!is.na(sc[prev[same]]))
    firm_long_dt$lag_diff_sum  [idx[j]] <- sum(sc[prev[diff]], na.rm = TRUE)
    firm_long_dt$lag_diff_count[idx[j]] <- sum(!is.na(sc[prev[diff]]))
  }
}
firm_long_dt[, lag_same_avg := fifelse(lag_same_count > 0, lag_same_sum / lag_same_count, NA_real_)]
firm_long_dt[, lag_diff_avg := fifelse(lag_diff_count > 0, lag_diff_sum / lag_diff_count, NA_real_)]
firm_long_dt[, lag_same_z   := as.numeric(scale(lag_same_avg))]
firm_long_dt[, lag_diff_z   := as.numeric(scale(lag_diff_avg))]
firm_long_dt[, blind        := as.integer(treat == "blind")]
```

\vspace{-0.5em}

## Spec 1: Does Demographic-Conditional Anchoring Exist?

\textbf{Question:} Does the running mean of objective coding ability among \emph{same-demographic} candidates seen earlier in the session predict the current candidate's evaluation score? `lag_diff_z' (other-demographic running mean) is the placebo.

```{r anchoring_spec1, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
fit_spec1 <- function(role_lab, sample_label) {
  d <- if (sample_label == "nonblind") {
         firm_long_dt[role == role_lab & treat == "nonblind" & !is.na(lag_same_z) & !is.na(lag_diff_z)]
       } else {
         firm_long_dt[role == role_lab & treat == "blind" & !is.na(lag_same_z) & !is.na(lag_diff_z)]
       }
  fe_extra <- if (role_lab == "Eng") " + resp_python + resp_java" else ""
  fml <- if (sample_label == "nonblind") {
    sprintf("sc_overall_z ~ lag_same_z + lag_diff_z + i(true_rg_anchor, ref='White_Male') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s", fe_extra)
  } else {
    sprintf("sc_overall_z ~ lag_same_z + lag_diff_z + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s", fe_extra)
  }
  feols(as.formula(fml), data = d, vcov = ~ responseid)
}

m1_hr_nb  <- fit_spec1("HR",  "nonblind")
m1_eng_nb <- fit_spec1("Eng", "nonblind")
m1_hr_b   <- fit_spec1("HR",  "blind")
m1_eng_b  <- fit_spec1("Eng", "blind")

models_s1 <- list("HR (nonblind)" = m1_hr_nb, "Eng (nonblind)" = m1_eng_nb,
                  "HR (blind, placebo)" = m1_hr_b, "Eng (blind, placebo)" = m1_eng_b)

coef_map_s1 <- c("lag_same_z" = "Same-Demo Prior Mean (Z)",
                 "lag_diff_z" = "Other-Demo Prior Mean (Z, placebo)")

gof_s1 <- tribble(~raw, ~clean, ~fmt,
  "nobs",          "Observations", 0,
  "r.squared",     "R$^2$",        3,
  "adj.r.squared", "Adj. R$^2$",   3)

modelsummary(models_s1,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_s1,
  gof_map  = gof_s1,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  footnote(general = "Standard errors clustered by respondent. Sample: rows with $r\\_do \\geq 2$ and at least one prior of the indicated demographic class.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(m1_hr_nb, m1_eng_nb, m1_hr_b, m1_eng_b, models_s1, coef_map_s1, gof_s1, fit_spec1)
```

\vspace{0.3em}

## Spec 3: Are the §1.1 ATEs Robust to Lag Controls?

\textbf{Question:} If we add the Spec-1 lag controls to the §1.1 race-gender regression (full sample), do the demographic ATEs shrink? Both columns per role run on the same restricted sample (rows with both lags non-NA) so the comparison is purely about specification.

```{r anchoring_spec3, echo=FALSE, results='asis', warning=FALSE, message=FALSE}
flip <- function(m) { m$coefficients <- -1 * m$coefficients; m }

fit_base <- function(role_lab) {
  fe_extra <- if (role_lab == "Eng") " + resp_python + resp_java" else ""
  feols(as.formula(sprintf(
    "sc_overall_z ~ i(race_gender, ref='Blind') + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s",
    fe_extra)),
    data = firm_long_dt[role == role_lab & !is.na(lag_same_z) & !is.na(lag_diff_z)],
    vcov = ~ responseid)
}
fit_lag <- function(role_lab) {
  fe_extra <- if (role_lab == "Eng") " + resp_python + resp_java" else ""
  feols(as.formula(sprintf(
    "sc_overall_z ~ i(race_gender, ref='Blind') + lag_same_z + lag_diff_z + resp_age | resume_index + r_do + resp_gender + resp_race + s2_educ + s2_income%s",
    fe_extra)),
    data = firm_long_dt[role == role_lab & !is.na(lag_same_z) & !is.na(lag_diff_z)],
    vcov = ~ responseid)
}

m3_hr_base  <- flip(fit_base("HR"));  m3_hr_lag  <- flip(fit_lag("HR"))
m3_eng_base <- flip(fit_base("Eng")); m3_eng_lag <- flip(fit_lag("Eng"))

models_s3 <- list("HR (base)" = m3_hr_base, "HR (with lag)" = m3_hr_lag,
                  "Eng (base)" = m3_eng_base, "Eng (with lag)" = m3_eng_lag)

coef_map_s3 <- c(
  "race_gender::White_Male"      = "White Male",
  "race_gender::White_Female"    = "White Female",
  "race_gender::Asian_Male"      = "Asian Male",
  "race_gender::Asian_Female"    = "Asian Female",
  "race_gender::Hispanic_Male"   = "Hispanic Male",
  "race_gender::Hispanic_Female" = "Hispanic Female",
  "lag_same_z"                   = "Same-Demo Prior Mean (Z)",
  "lag_diff_z"                   = "Other-Demo Prior Mean (Z)"
)

gof_s3 <- tribble(~raw, ~clean, ~fmt,
  "nobs",          "Observations", 0,
  "r.squared",     "R$^2$",        3,
  "adj.r.squared", "Adj. R$^2$",   3)

modelsummary(models_s3,
  stars    = c('*' = 0.1, '**' = 0.05, '***' = 0.01),
  coef_map = coef_map_s3,
  gof_map  = gof_s3,
  escape   = FALSE,
  output   = "kableExtra"
) %>%
  kable_styling(latex_options = "HOLD_position", font_size = 8) %>%
  add_header_above(c(" " = 1,
                     "Resume-Screening Phase" = 2,
                     "Technical-Evaluation Phase" = 2)) %>%
  footnote(general = "Coefficients sign-flipped post-fit so positive = effect of blinding raises the score for that demographic. Standard errors clustered by respondent. Same restricted sample for base and lag-controlled columns within each role.",
           general_title = "", threeparttable = TRUE,
           footnote_as_chunk = FALSE, escape = FALSE)

rm(m3_hr_base, m3_hr_lag, m3_eng_base, m3_eng_lag,
   models_s3, coef_map_s3, gof_s3, fit_base, fit_lag, flip)
```

